---
title: "BSLE_P_Code"
author: "Morgan Barnes"
date: "'2023-08-18'r Sys.Date()'"
output:
  pdf_document: default
  html_document: default
---
##This is the code for figures and statistics from Barnes et al. (2024): Burn severity and vegetation type control phosphorus concentration, molecular composition, and mobilization

##Contact: Morgan E. Barnes morgan.barnes@pnnl.gov



## Set Up
```{r setup, include=FALSE, dev="CairoPNG"}
rm(list=ls(all=T))
knitr::opts_chunk$set(echo = TRUE)
```

#### Load libraries
```{r library}

require(pacman)

pacman::p_load(tidyverse,
              dplyr,plyr,ggplot2,
              lubridate, tidyr, tidyverse,
              scales, cowplot, gridExtra, RColorBrewer,
              wesanderson,readxl,openxlsx, stringr, hablar,
              janitor, stringr, naniar, forstringr, reshape2, 
              emmeans, rstatix, ggpubr, Hmisc, corrplot, ggrepel, 
              stringr, lme4, lmerTest, car, performance, vegan, 
              psych, lavaan, semPlot, semptools, bestNormalize, ggpattern)


```

```{r working directory check, echo=FALSE}
getwd()
```

##Load and clean data
The datasets and metadata needed for this manuscript are:
1) Chemistry datasets for solid chars and their leachates w/ all metadata that can be used directly from data package:
This includes: 
  a) Total elemental composition of solid chars
  b) Total elemental composition of leachate particulate and 0.7 um filtered phases
  c) Molybdate reactive P of leachate 0.7 um filtered phase
  d) XANES of solid chars
  e) NMR of solid char extracts

2) Chemistry data that needs post-data package processing after download from BSLE Data Package v3; this was done and provided within the BSLE P Manuscript Data Package (Barnes et al, 2024):
  a) XANES of solid chars (spectra of samples and reference compounds; linear combination fits)
  b) NMR of solid char extracts (spectra of samples, spiking experiment spectra, and deconvolution findings)

Downloading the BSLE Data Package is done manually and stored on your local computer. I recommend storing inside your github folder and gitignoring the subfolder with the data in it by adding this to your .gitignore: 
`#data folder` 
`data/`

BSLE v3 data package URL: https://data.ess-dive.lbl.gov/view/doi:10.15485/1894135
BSLE P manuscript data package URL: https://data.ess-dive.lbl.gov/datasets/doi:10.15485/2547035

Bring in the data package data:
```{r import data packages}
#metadata
Meta <- read_csv("./data/BSLE_Data_Package_v3/v1_BSLE_Metadata_and_Protocols/BSLE_Burn_and_Laboratory_Metadata.csv") %>%
  dplyr::rename(Sample_ID = Sample_Name,
                Leachate_vol_mL = Leachate_Volume,
                Char_leached_g = Char_Leached) %>%
  naniar::replace_with_na_all(condition = ~.x ==-9999) %>%
  naniar::replace_with_na_all(condition = ~.x == "N/A") %>%
  mutate(Burn_Severity=replace(Burn_Severity, Burn_Severity=='unburned', 'Unburned'))

Meta<-Meta[ c(2,3,5,8,21,25,26,6,20,22,23)]
Meta$Burn_Severity=factor(Meta$Burn_Severity, levels= c("Unburned", "Low", "Moderate", "High"))

#chemical data from BSLE v3 data package
ICP_Solid <- read_csv("./data/BSLE_Data_Package_v3/v3_BSLE_Data/BSLE_ICP_Solid.csv")
ICP_Leachate <- read_csv("./data/BSLE_Data_Package_v3/v3_BSLE_Data/BSLE_ICP.csv")
MBD <- read_csv("./data/BSLE_Data_Package_v3/v3_BSLE_Data/BSLE_MBD.csv")
ICP_PNMR <- read_csv("./data/BSLE_Data_Package_v3/v3_BSLE_Data/BSLE_ICP_PNMR.csv")
npoctdn <- read_csv("./data/BSLE_Data_Package_v3/v3_BSLE_Data/v2_BSLE_NPOC_TN.csv")
SolidCN <- read_csv("./data/BSLE_Data_Package_v3/v3_BSLE_Data/BSLE_CN.csv")
pH <- read_csv("./data/BSLE_Data_Package_v3/v3_BSLE_Data/BSLE_pH.csv")
NMR_spectra <- read_csv("./data/BSLE_Data_Package_v3/v3_BSLE_Data/BSLE_31P-NMR.csv")

#chemical data from BSLE P manuscript data package
NMR <- read.csv("./data/Barnes_2024_BSLE_P_Gradient/P-NMR/NMR_Deconvolutions.csv") %>%
  filter(Degradation_Corrected == 'Yes')
NMR_Spikes <- read.csv("./data/Barnes_2024_BSLE_P_Gradient/P-NMR/NMR_Spike_ppm.csv") 
NMR_Species_Per <- read.csv("./data/Barnes_2024_BSLE_P_Gradient/P-NMR/NMR_Species_Percent.csv") 
XANES <- read.csv("./data/Barnes_2024_BSLE_P_Gradient/P-XANES/P-XANES_Samples/P-XANES_LCF.csv")  
XANES_spectra <- read_csv("./data/Barnes_2024_BSLE_P_Gradient/P-XANES/P-XANES_Samples/xanes_example_spectra.csv") #this file was generated using XANES_Spectra_Merging script 
XANES_rc_spectra <- read_csv("./data/Barnes_2024_BSLE_P_Gradient/P-XANES/P-XANES_Reference_Compounds/xanes_example_referencecompounds.csv") #this file was generated using XANES_Spectra_Merging script 
BSLE_0013_solid_LCF <- read.table("./data/Barnes_2024_BSLE_P_Gradient/P-XANES/P-XANES_Samples/LCF/BSLE_0013-solid_P-XANES.xmu.lcf", quote="\"", col.names = c("eV", "BSLE_0013_solid", "fit", "residual", "Po_Na_AMP_std.xmu", "Pi_Fe_GoethSorb_std.xmu"))
BSLE_0007_solid_LCF <- read.table("./data/Barnes_2024_BSLE_P_Gradient/P-XANES/P-XANES_Samples/LCF/BSLE_0007-solid_P-XANES.xmu.lcf", quote="\"", col.names = c("eV", "BSLE_0007_solid", "fit", "residual", "Pi_Na_Tri_std.xmu", "Pi_Apatite_CaDefHydroxy_std.xmu", "Pi_Al_GibbSorb_std.xmu"))
BSLE_0002_solid_LCF <- read.table("./data/Barnes_2024_BSLE_P_Gradient/P-XANES/P-XANES_Samples/LCF/BSLE_0002-solid_P-XANES.xmu.lcf", quote="\"", col.names = c("eV", "BSLE_0002_solid", "fit", "residual", "Pi_Na_Tri_std.xmu", "Pi_Mg_Tri_std.xmu", "Pi_Apatite_CaDefHydroxy_std.xmu"))
BSLE_0050_solid_LCF <- read.table("./data/Barnes_2024_BSLE_P_Gradient/P-XANES/P-XANES_Samples/LCF/BSLE_0050-solid_P-XANES.xmu.lcf", quote="\"", col.names = c("eV", "BSLE_0050_solid", "fit", "residual", "Pi_Mg_Tri_std.xmu", "Pi_Ca_Tri_std.xmu", "Pi_Apatite_CaDefHydroxy_std.xmu"))
BSLE_0014_solid_LCF <- read.table("./data/Barnes_2024_BSLE_P_Gradient/P-XANES/P-XANES_Samples/LCF/BSLE_0014-solid_P-XANES.xmu.lcf", quote="\"", col.names = c("eV", "BSLE_0014_solid", "fit", "residual", "Po_Na_AMP_std.xmu", "Pi_Fe_GoethSorb_std.xmu", "Pi_Apatite_CaDefHydroxy_std.xmu"))
BSLE_0011_solid_LCF <- read.table("./data/Barnes_2024_BSLE_P_Gradient/P-XANES/P-XANES_Samples/LCF/BSLE_0011-solid_P-XANES.xmu.lcf", quote="\"", col.names = c("eV", "BSLE_0011_solid", "fit", "residual", "Pi_Mg_Tri_std.xmu", "Pi_K_Pyro_std.xmu", "Pi_Apatite_CaDefHydroxy_std.xmu"))
BSLE_0072_solid_LCF <- read.table("./data/Barnes_2024_BSLE_P_Gradient/P-XANES/P-XANES_Samples/LCF/BSLE_0072-solid_P-XANES.xmu.lcf", quote="\"", col.names = c("eV", "BSLE_0072_solid", "fit", "residual", "Pi_NH4_Mg_std.xmu", "Pi_Apatite_Carbonate_std.xmu", "Pi_Apatite_CaDefHydroxy_std.xmu"))
```

```{r functions for cleaning data}
#function to clean ESS dive formatted dataframe to be more R friendly
essdive_template_cleaning <- function(dataframe){
  cleaned <- dataframe %>% 
  janitor::row_to_names(row_number = which(dataframe[,1] == "Field_Name")) %>%
    slice(which(Field_Name == "#Start_Data"):which(Field_Name == "#End_Data")) %>%
 select(!Field_Name)
  }
#function to clean other formatted dataframes to be more R friendly
noreporting_format_cleaning <- function(dataframe){
  cleaned <- dataframe %>% 
  janitor::row_to_names(row_number = which(dataframe[,1] == "Date"))
}

#function to modify dataframes: -9999 is NA, below the limit of detection (LOD) is NA, negative values are NA; values are extracted if above (but within 20%) or below (but still above LOD) standard curve; code checks for all these so not all situations listed may apply to original dataframe
process_column <- function(column) {
  column <- case_when(
    column == -9999 ~ NA_character_,
    str_detect(column, "LOD") ~ NA_character_,
    str_detect(column, "Below|Standard") ~ {
      ifelse(str_detect(column, "Below"), {
        sub(".*\\|([^|]+)_ppm_Final.*", "\\1", column)
      }, {
        sub(".*\\|([^|]+)_ppm_Final.*", "\\1", column)
      })
    },
    str_detect(column, "Above|Standard") ~ {
      num_before_standard <- as.numeric(sub(".*\\|([^|]+)_ppm_Standard.*", "\\1", column))
      num_before_final <- as.numeric(sub(".*\\|([^|]+)_ppm_Final_Corrected.*", "\\1", column))
      ifelse(num_before_final > 1.15 * num_before_standard, NA_character_,
             sub(".*\\|([^|]+)_ppm_Final_Corrected.*", "\\1", column))
    },
    TRUE ~ as.character(column)
  )
  return(column)
}
```

```{r data package cleaning}
#you may get NAs introduced by coercion, which should be okay but check your final dataframe to ensure correct

pH_clean <- essdive_template_cleaning(pH)  %>%
  dplyr::rename(Sample_ID = Sample_Name,
                pH = '00403_pH') %>%
   mutate_at(c(3), as.numeric) %>%
  separate(col=Sample_ID, into = c("Sample_ID", "FilterSize"), sep="-")  %>%
  filter(grepl('unfilt', FilterSize)) %>%
  select(Sample_ID, pH)


npoctdn_clean <- essdive_template_cleaning(npoctdn) %>%
  dplyr::rename(NPOC_mg_C_per_L = `00681_NPOC_mg_per_L_as_C`,
                TN_mg_N_per_L = `00602_TN_mg_per_L_as_N`,
                Sample_ID = Sample_Name) %>%
  select(Sample_ID, NPOC_mg_C_per_L, TN_mg_N_per_L) %>%
  filter(grepl('filt0.7', Sample_ID)) %>%
  separate(col=Sample_ID, into = c("Sample_ID", "FilterSize"), sep="-") %>%
  mutate(
    NPOC_mg_C_per_L = process_column(NPOC_mg_C_per_L),
    TN_mg_N_per_L = process_column(TN_mg_N_per_L)
  )


SolidCN_clean <- essdive_template_cleaning(SolidCN) %>%
  dplyr::rename(C_weight_per = `01463_C_percent`,
         N_weight_per = `01472_N_percent`,
         Parent_ID = Sample_Name) %>%
  select(Parent_ID, C_weight_per,  N_weight_per) %>%
  filter(grepl('solid', Parent_ID)) %>%
  separate(col=Parent_ID, into = c("Parent_ID", "FilterSize"), sep="-") %>%
  mutate(
    C_weight_per = process_column(C_weight_per),
    N_weight_per = process_column(N_weight_per)
  ) %>%
  select(-FilterSize) 


ICP_Solid_clean<- essdive_template_cleaning(ICP_Solid) %>%
  dplyr::rename(Solid_Ca_mg_kg = '52718_Total_Ca_mg_per_kg',
                Solid_Mg_mg_kg = '52719_Total_Mg_mg_per_kg',
                Solid_P_mg_kg = 'Total_P_mg_per_kg',
                Solid_K_mg_kg = '52720_Total_K_mg_per_kg',
                Solid_Na_mg_kg = '52721_Total_Na_mg_per_kg',
                Solid_S_mg_kg = '01466_Total_S_mg_per_kg',
                Solid_Al_mg_kg = '01462_Total_Al_mg_per_kg',
                Solid_Fe_mg_kg = '01464_Total_Fe_mg_per_kg',
                Parent_ID = 'Sample_Name') %>%
  mutate(
    Solid_Ca_mg_kg = process_column(Solid_Ca_mg_kg),
    Solid_Mg_mg_kg = process_column(Solid_Mg_mg_kg),
    Solid_P_mg_kg = process_column(Solid_P_mg_kg),
    Solid_K_mg_kg = process_column(Solid_K_mg_kg),
    Solid_Na_mg_kg = process_column(Solid_Na_mg_kg),
    Solid_S_mg_kg = process_column(Solid_S_mg_kg),
    Solid_Al_mg_kg = process_column(Solid_Al_mg_kg),
    Solid_Fe_mg_kg = process_column(Solid_Fe_mg_kg)
  ) %>%
  separate(col=Parent_ID, into = c("Parent_ID", "FilterSize"), sep="-")  %>%
  filter(grepl('solid', FilterSize)) %>%
  select(Parent_ID, Solid_Ca_mg_kg,  Solid_Mg_mg_kg, Solid_P_mg_kg, Solid_K_mg_kg, Solid_Na_mg_kg, Solid_S_mg_kg, Solid_Al_mg_kg, Solid_Fe_mg_kg)


ICP_Leachate_clean <- essdive_template_cleaning(ICP_Leachate) %>%
  dplyr::rename(Leachate_Ca_mg_L = 'Total_Ca_mg_per_L',
                Leachate_Mg_mg_L = 'Total_Mg_mg_per_L',
                Leachate_P_mg_L = 'Total_P_mg_per_L',
                Leachate_K_mg_L = 'Total_K_mg_per_L',
                Leachate_Na_mg_L = 'Total_Na_mg_per_L',
                Leachate_S_mg_L = 'Total_S_mg_per_L',
                Leachate_Al_mg_L = 'Total_Al_mg_per_L',
                Leachate_Fe_mg_L = 'Total_Fe_mg_per_L',
                Sample_ID = 'Sample_Name') %>%
  mutate(
    Leachate_Ca_mg_L = process_column(Leachate_Ca_mg_L),
    Leachate_Mg_mg_L = process_column(Leachate_Mg_mg_L),
    Leachate_P_mg_L = process_column(Leachate_P_mg_L),
    Leachate_K_mg_L = process_column(Leachate_K_mg_L),
    Leachate_Na_mg_L = process_column(Leachate_Na_mg_L),
    Leachate_S_mg_L = process_column(Leachate_S_mg_L),
    Leachate_Al_mg_L = process_column(Leachate_Al_mg_L),
    Leachate_Fe_mg_L = process_column(Leachate_Fe_mg_L)
  ) %>%
  select(Sample_ID, Leachate_Ca_mg_L,  Leachate_Mg_mg_L, Leachate_P_mg_L, Leachate_K_mg_L, Leachate_Na_mg_L, Leachate_S_mg_L, Leachate_Al_mg_L, Leachate_Fe_mg_L) %>%
  filter(grepl('filt', Sample_ID)) %>%
  separate(col=Sample_ID, into = c("Sample_ID", "FilterSize"), sep="-") 


ICP_Leachate_Filt_clean<- ICP_Leachate_clean %>%
                filter(str_detect(FilterSize, "filt0.")) %>%
  dplyr::rename(Leachate_Ca_mg_L_filt0.7 = 'Leachate_Ca_mg_L',
                Leachate_Mg_mg_L_filt0.7 = 'Leachate_Mg_mg_L',
                Leachate_P_mg_L_filt0.7 = 'Leachate_P_mg_L',
                Leachate_K_mg_L_filt0.7 = 'Leachate_K_mg_L',
                Leachate_Na_mg_L_filt0.7 = 'Leachate_Na_mg_L',
                Leachate_S_mg_L_filt0.7 = 'Leachate_S_mg_L',
                Leachate_Al_mg_L_filt0.7 = 'Leachate_Al_mg_L',
                Leachate_Fe_mg_L_filt0.7 = 'Leachate_Fe_mg_L') %>%
  select(Sample_ID, Leachate_Ca_mg_L_filt0.7,  Leachate_Mg_mg_L_filt0.7, Leachate_P_mg_L_filt0.7, Leachate_K_mg_L_filt0.7, Leachate_Na_mg_L_filt0.7, Leachate_S_mg_L_filt0.7, Leachate_Al_mg_L_filt0.7, Leachate_Fe_mg_L_filt0.7)


ICP_Leachate_Unfilt_clean<- ICP_Leachate_clean %>%
                filter(str_detect(FilterSize, "unfilt")) %>%
  dplyr::rename(Leachate_Ca_mg_L_unfilt = 'Leachate_Ca_mg_L',
                Leachate_Mg_mg_L_unfilt = 'Leachate_Mg_mg_L',
                Leachate_P_mg_L_unfilt = 'Leachate_P_mg_L',
                Leachate_K_mg_L_unfilt = 'Leachate_K_mg_L',
                Leachate_Na_mg_L_unfilt = 'Leachate_Na_mg_L',
                Leachate_S_mg_L_unfilt = 'Leachate_S_mg_L',
                Leachate_Al_mg_L_unfilt = 'Leachate_Al_mg_L',
                Leachate_Fe_mg_L_unfilt = 'Leachate_Fe_mg_L') %>%
  select(Sample_ID, Leachate_Ca_mg_L_unfilt,  Leachate_Mg_mg_L_unfilt, Leachate_P_mg_L_unfilt, Leachate_K_mg_L_unfilt, Leachate_Na_mg_L_unfilt, Leachate_S_mg_L_unfilt, Leachate_Al_mg_L_unfilt, Leachate_Fe_mg_L_unfilt)


MBD_Leachate_clean <- essdive_template_cleaning(MBD) %>%
  dplyr::rename(Sample_ID = 'Sample_Name',
                MBD_P_mg_per_L_filt0.7 = 'MBD_P_mg_per_L') %>%
  mutate(
    MBD_P_mg_per_L_filt0.7 = process_column(MBD_P_mg_per_L_filt0.7)
  ) %>%
  filter(grepl('filt', Sample_ID)) %>%
  separate(col=Sample_ID, into = c("Sample_ID", "FilterSize"), sep="-") %>%
  select(Sample_ID, MBD_P_mg_per_L_filt0.7) 


ICP_PNMR_clean <- essdive_template_cleaning(ICP_PNMR) %>%
  dplyr::rename(Parent_ID = 'Sample_Name') %>%
  mutate(
    Total_Extractable_Ca_mg_per_kg = process_column(Total_Extractable_Ca_mg_per_kg),
    Total_Extractable_Mg_mg_per_kg = process_column(Total_Extractable_Mg_mg_per_kg),
    Total_Extractable_P_mg_per_kg = process_column(Total_Extractable_P_mg_per_kg),
    Total_Extractable_K_mg_per_kg = process_column(Total_Extractable_K_mg_per_kg),
    Total_Extractable_S_mg_per_kg = process_column(Total_Extractable_S_mg_per_kg),
    Total_Extractable_Al_mg_per_kg = process_column(Total_Extractable_Al_mg_per_kg),
    Total_Extractable_Fe_mg_per_kg = process_column(Total_Extractable_Fe_mg_per_kg)
  ) %>% 
  filter(grepl('solid', Parent_ID)) %>%
  separate(col=Parent_ID, into = c("Parent_ID", "FilterSize"), sep="-") %>%
  select(Parent_ID, Total_Extractable_Ca_mg_per_kg, Total_Extractable_Mg_mg_per_kg, Total_Extractable_P_mg_per_kg, Total_Extractable_K_mg_per_kg,  Total_Extractable_S_mg_per_kg, Total_Extractable_Al_mg_per_kg, Total_Extractable_Fe_mg_per_kg)


XANES_clean <- XANES %>%
  select(-where(~all(is.na(.)))) %>%
  mutate(XANES_Po = rowSums(select(., contains("Po")), na.rm = TRUE)) %>%
  mutate(XANES_Pi = rowSums(select(., contains("Pi")), na.rm = TRUE)) %>%
  mutate(XANES_Fe = rowSums(select(., contains("Fe")), na.rm = TRUE)) %>%
  mutate(XANES_Na = rowSums(select(., contains("Pi_Na") | contains("Po_Na")), na.rm = TRUE)) %>%
  mutate(XANES_Ca = rowSums(select(., contains("Ca") | contains("Apatite")), na.rm = TRUE)) %>%
  mutate(XANES_Al = rowSums(select(., contains("Al")), na.rm = TRUE)) %>%
  mutate(XANES_Mg = rowSums(select(., contains("Mg") | contains("NH4_Mg")), na.rm = TRUE)) %>%
  mutate(XANES_K = rowSums(select(., contains("K")), na.rm = TRUE)) %>%
  mutate(XANES_Pi_Fe = rowSums(select(., contains("Pi_Fe")), na.rm = TRUE)) %>%
  mutate(XANES_Pi_Na = rowSums(select(., contains("Pi_Na")), na.rm = TRUE)) %>%
  mutate(XANES_Pi_Ca = rowSums(select(., contains("Pi_Ca") | contains("Apatite")), na.rm = TRUE)) %>%
  mutate(XANES_Pi_Al = rowSums(select(., contains("Pi_Al")), na.rm = TRUE)) %>%
  mutate(XANES_Pi_Mg = rowSums(select(., contains("Pi_Mg") | contains("NH4_Mg")), na.rm = TRUE)) %>%
  mutate(XANES_Pi_K = rowSums(select(., contains("Pi_K")), na.rm = TRUE)) %>%
  mutate(XANES_Po_Fe = rowSums(select(., contains("Po_Fe")), na.rm = TRUE)) %>%
  mutate(XANES_Po_Na = rowSums(select(., contains("Po_Na")), na.rm = TRUE)) %>%
  mutate(XANES_Po_Ca = rowSums(select(., contains("Po_Ca")), na.rm = TRUE)) %>%
  mutate(XANES_Po_Al = rowSums(select(., contains("Po_Al")), na.rm = TRUE)) %>%
  mutate(XANES_Po_Mg = rowSums(select(., contains("Po_Mg")), na.rm = TRUE)) %>%
  mutate(XANES_Po_K = rowSums(select(., contains("Po_K")), na.rm = TRUE)) %>%
  separate(col=Sample_Name, into = c("Parent_ID", "FilterSize"), sep="-") %>%
  filter(str_detect(FilterSize, "solid"))


NMR_clean <- NMR %>%
  separate(col=Sample_Name, into = c("Parent_ID", "FilterSize"), sep="-") 


NMR_Species_Per_clean <- NMR_Species_Per %>%
  select(Parent_ID, Percent, Species) %>%
  filter(Species!='Unknown Monoester')%>%
  drop_na() %>%
  mutate(Species = ifelse(Species == "Ortho", "OrthoP", Species)) %>%
  mutate(Species = ifelse(Species == "Pyro", "PyroP", Species)) %>%
  pivot_wider(names_from = Species, values_from = Percent) %>%
  mutate(across(2:11, ~ ifelse(is.na(.), 0, .))) %>%
  mutate(Lipids = AlphaGP + BetaGP) 


XANES_rc_spectra <- XANES_rc_spectra %>%
  mutate_all(~ifelse(. == -9999, NA, .))
```


```{r combine and format data}
data <- Meta %>%
  full_join(SolidCN_clean, by = 'Parent_ID') %>%
  full_join(ICP_Solid_clean, by = 'Parent_ID') %>%
  full_join(ICP_PNMR_clean, by = 'Parent_ID') %>%
  full_join(npoctdn_clean, by = 'Sample_ID') %>%
  full_join(ICP_Leachate_Filt_clean, by = 'Sample_ID') %>%
  full_join(ICP_Leachate_Unfilt_clean, by = 'Sample_ID') %>%
  full_join(MBD_Leachate_clean, by = 'Sample_ID') %>%
  full_join(pH_clean, by = 'Sample_ID') %>%
  mutate_at(c(10:48), as.numeric) %>%
  filter(!is.na(Solid_P_mg_kg))

data$Burn_Severity=factor(data$Burn_Severity, levels= c("Unburned", "Low", "Moderate", "High"))

data<-data %>%
  mutate(Land_Coverage_Category = if_else(Land_Coverage_Category == "Douglas-fir forest", "Douglas-fir Forest", Land_Coverage_Category)) %>%
  mutate(Land_Coverage_Category = if_else(Land_Coverage_Category == "Sagebrush shrubland", "Sagebrush Shrubland", Land_Coverage_Category))

#create a dataframe for only solids figures and stats to prevent having reps appear as extra samples
data_solids <- data %>%
  filter(str_detect(Sample_ID, "A")) %>%
  select(1:28) %>%
  left_join(NMR_clean) %>%
  left_join(XANES_clean) %>%
  left_join(NMR_Species_Per_clean)

data_solids$Burn_Severity=factor(data_solids$Burn_Severity, levels= c("Unburned", "Low", "Moderate", "High"))

#XANES
XANES_clean <- Meta %>%
  full_join(XANES_clean, by = 'Parent_ID') %>%
  filter(str_detect(Sample_ID, "A")) %>%
  mutate(Burn_Treatment = as.character(Burn_Treatment)) %>%
  filter(Burn_Treatment %in% c("burn table" , "raw")) %>%
  filter(Land_Coverage_Category %in% c("Douglas-fir forest" , "Sagebrush shrubland")) %>%
  filter(!is.na(FilterSize))
```

```{r additional calcs}
#NMR extraction efficiency
data_solids<-data_solids %>%
  mutate(NMR_EE_P_perc=Total_Extractable_P_mg_per_kg/Solid_P_mg_kg*100)


#calculate NMR monoester:diester ratio
data_solids<-data_solids %>%
  mutate(M_D_ratio=Mono/Di)


#percent change of NMR results with burning based on average percent monoester and diester in the unburned
data_solids <- data_solids %>%
  mutate(mono_per_change = case_when(
    Land_Coverage_Category == "Sagebrush Shrubland" ~ ((Mono - 26.1)/26.1)*100,
    Land_Coverage_Category == "Douglas-fir Forest" ~ ((Mono - 4.1)/4.1)*100))

data_solids <- data_solids %>%
  mutate(di_per_change = case_when(
    Land_Coverage_Category == "Sagebrush Shrubland" ~ ((Di - 27.6)/27.6)*100,
    Land_Coverage_Category == "Douglas-fir Forest" ~ ((Di - 36.5)/36.5)*100))


#NMR Pi and Po
data_solids<-data_solids %>%
  mutate(NMR_Pi = Ortho+Pyro) %>%
  mutate(NMR_Po = Mono + Di)


#convert C and N of solids: from percent to mg/kg in data_solids dataframe
data_solids<-data_solids %>%
  mutate(Solid_C_mg_kg = (C_weight_per*10000),
  Solid_N_mg_kg = (N_weight_per*10000))


#convert solid elemental concentrations from mg/kg to g/kg in data_solids dataframe
data_solids<-data_solids %>%
  mutate(Solid_P_g_kg = Solid_P_mg_kg/1000) %>%
  mutate(Solid_Ca_g_kg = Solid_Ca_mg_kg/1000) %>%
  mutate(Solid_Fe_g_kg = Solid_Fe_mg_kg/1000) %>%
  mutate(Solid_Al_g_kg = Solid_Al_mg_kg/1000) %>%
  mutate(Solid_K_g_kg = Solid_K_mg_kg/1000) %>%
  mutate(Solid_Mg_g_kg = Solid_Mg_mg_kg/1000) %>%
  mutate(Solid_Na_g_kg = Solid_Na_mg_kg/1000) %>%
  mutate(Solid_S_g_kg = Solid_S_mg_kg/1000) %>%
  mutate(Solid_C_g_kg = Solid_C_mg_kg/1000) %>%
  mutate(Solid_N_g_kg = Solid_N_mg_kg/1000)


#molar stoichiometry of P:element in solid phase
data_solids<-data_solids %>%
  mutate(Fe.P.MolarRatio=(Solid_Fe_mg_kg/55.845)/(Solid_P_mg_kg/30.97))%>%
  mutate(K.P.MolarRatio=(Solid_K_mg_kg/39.0983)/(Solid_P_mg_kg/30.97))%>%
  mutate(Na.P.MolarRatio=(Solid_Na_mg_kg/22.989)/(Solid_P_mg_kg/30.97))%>%
  mutate(Al.P.MolarRatio=(Solid_Al_mg_kg/26.982)/(Solid_P_mg_kg/30.97))%>%
  mutate(Mg.P.MolarRatio=(Solid_Mg_mg_kg/24.305)/(Solid_P_mg_kg/30.97))%>%
  mutate(Ca.P.MolarRatio=(Solid_Ca_mg_kg/40.078)/(Solid_P_mg_kg/30.97))%>%
  mutate(S.P.MolarRatio=(Solid_S_mg_kg/32.065)/(Solid_P_mg_kg/30.97))%>%
  mutate(C.P.MolarRatio=(Solid_C_mg_kg/12.011)/(Solid_P_mg_kg/30.97))%>%
  mutate(N.P.MolarRatio=(Solid_N_mg_kg/14.01)/(Solid_P_mg_kg/30.97))


#calculate leachate particulate concentrations as the difference between filtered and unfiltered
data<-data %>%
  mutate(Leachate_Ca_mg_L_part = Leachate_Ca_mg_L_unfilt - Leachate_Ca_mg_L_filt0.7) %>%
  mutate(Leachate_Ca_mg_L_part = if_else(Leachate_Ca_mg_L_part < 0, NA, Leachate_Ca_mg_L_part))%>%
  mutate(Leachate_Mg_mg_L_part = Leachate_Mg_mg_L_unfilt - Leachate_Mg_mg_L_filt0.7) %>%
  mutate(Leachate_Mg_mg_L_part = if_else(Leachate_Mg_mg_L_part < 0, NA, Leachate_Mg_mg_L_part))%>%
  mutate(Leachate_P_mg_L_part = Leachate_P_mg_L_unfilt - Leachate_P_mg_L_filt0.7) %>%
  mutate(Leachate_P_mg_L_part = if_else(Leachate_P_mg_L_part < 0, NA, Leachate_P_mg_L_part))%>%
  mutate(Leachate_K_mg_L_part = Leachate_K_mg_L_unfilt - Leachate_K_mg_L_filt0.7) %>%
  mutate(Leachate_K_mg_L_part = if_else(Leachate_K_mg_L_part < 0, NA, Leachate_K_mg_L_part))%>%
  mutate(Leachate_Na_mg_L_part = Leachate_Na_mg_L_unfilt - Leachate_Na_mg_L_filt0.7) %>%
  mutate(Leachate_Na_mg_L_part = if_else(Leachate_Na_mg_L_part < 0, NA, Leachate_Na_mg_L_part))%>%
  mutate(Leachate_S_mg_L_part = Leachate_S_mg_L_unfilt - Leachate_S_mg_L_filt0.7) %>%
  mutate(Leachate_S_mg_L_part = if_else(Leachate_S_mg_L_part < 0, NA, Leachate_S_mg_L_part))%>%
  mutate(Leachate_Al_mg_L_part = Leachate_Al_mg_L_unfilt - Leachate_Al_mg_L_filt0.7) %>%
  mutate(Leachate_Al_mg_L_part = if_else(Leachate_Al_mg_L_part < 0, NA, Leachate_Al_mg_L_part))%>%
  mutate(Leachate_Fe_mg_L_part = Leachate_Fe_mg_L_unfilt - Leachate_Fe_mg_L_filt0.7) %>%
  mutate(Leachate_Fe_mg_L_part = if_else(Leachate_Fe_mg_L_part < 0, NA, Leachate_Fe_mg_L_part))
  

#convert units of leachates: normalize by concentration in solid char (as mg leachate conc/solid g following Fischer et al. 2023)
data<-data %>%
  mutate(Solid_C_mg_kg = (C_weight_per*10000),
  Solid_N_mg_kg = (N_weight_per*10000))%>%
  mutate(Leachate_mg_Ca_per_g_Ca_in_solid_unfilt = Leachate_Ca_mg_L_unfilt*(1/1000)*Leachate_vol_mL*(1/Char_leached_g)*(1/Solid_Ca_mg_kg)*1000*1000)%>%
  mutate(Leachate_mg_Mg_per_g_Mg_in_solid_unfilt = Leachate_Mg_mg_L_unfilt*(1/1000)*Leachate_vol_mL*(1/Char_leached_g)*(1/Solid_Mg_mg_kg)*1000*1000)%>%
  mutate(Leachate_mg_P_per_g_P_in_solid_unfilt = Leachate_P_mg_L_unfilt*(1/1000)*Leachate_vol_mL*(1/Char_leached_g)*(1/Solid_P_mg_kg)*1000*1000)%>%
  mutate(Leachate_mg_K_per_g_Ca_in_solid_unfilt = Leachate_K_mg_L_unfilt*(1/1000)*Leachate_vol_mL*(1/Char_leached_g)*(1/Solid_K_mg_kg)*1000*1000)%>%
  mutate(Leachate_mg_Na_per_g_Ca_in_solid_unfilt = Leachate_Na_mg_L_unfilt*(1/1000)*Leachate_vol_mL*(1/Char_leached_g)*(1/Solid_Na_mg_kg)*1000*1000)%>% 
  mutate(Leachate_mg_S_per_g_S_in_solid_unfilt = Leachate_S_mg_L_unfilt*(1/1000)*Leachate_vol_mL*(1/Char_leached_g)*(1/Solid_S_mg_kg)*1000*1000)%>%
  mutate(Leachate_mg_Al_per_g_Al_in_solid_unfilt = Leachate_Al_mg_L_unfilt*(1/1000)*Leachate_vol_mL*(1/Char_leached_g)*(1/Solid_Al_mg_kg)*1000*1000)%>%
  mutate(Leachate_mg_Fe_per_g_Fe_in_solid_unfilt = Leachate_Fe_mg_L_unfilt*(1/1000)*Leachate_vol_mL*(1/Char_leached_g)*(1/Solid_Fe_mg_kg)*1000*1000)%>%
  mutate(Leachate_mg_Ca_per_g_Ca_in_solid_part = Leachate_Ca_mg_L_part*(1/1000)*Leachate_vol_mL*(1/Char_leached_g)*(1/Solid_Ca_mg_kg)*1000*1000)%>%
  mutate(Leachate_mg_Mg_per_g_Mg_in_solid_part = Leachate_Mg_mg_L_part*(1/1000)*Leachate_vol_mL*(1/Char_leached_g)*(1/Solid_Mg_mg_kg)*1000*1000)%>%
  mutate(Leachate_mg_P_per_g_P_in_solid_part = Leachate_P_mg_L_part*(1/1000)*Leachate_vol_mL*(1/Char_leached_g)*(1/Solid_P_mg_kg)*1000*1000)%>%
  mutate(Leachate_mg_K_per_g_K_in_solid_part = Leachate_K_mg_L_part*(1/1000)*Leachate_vol_mL*(1/Char_leached_g)*(1/Solid_K_mg_kg)*1000*1000)%>%
  mutate(Leachate_mg_Na_per_g_Na_in_solid_part = Leachate_Na_mg_L_part*(1/1000)*Leachate_vol_mL*(1/Char_leached_g)*(1/Solid_Na_mg_kg)*1000*1000)%>%
  mutate(Leachate_mg_S_per_g_S_in_solid_part = Leachate_S_mg_L_part*(1/1000)*Leachate_vol_mL*(1/Char_leached_g)*(1/Solid_S_mg_kg)*1000*1000)%>%
  mutate(Leachate_mg_Al_per_g_Al_in_solid_part = Leachate_Al_mg_L_part*(1/1000)*Leachate_vol_mL*(1/Char_leached_g)*(1/Solid_Al_mg_kg)*1000*1000)%>%
  mutate(Leachate_mg_Fe_per_g_Fe_in_solid_part = Leachate_Fe_mg_L_part*(1/1000)*Leachate_vol_mL*(1/Char_leached_g)*(1/Solid_Fe_mg_kg)*1000*1000)%>%
  mutate(Leachate_mg_Ca_per_g_Ca_in_solid_filt0.7 = Leachate_Ca_mg_L_filt0.7*(1/1000)*Leachate_vol_mL*(1/Char_leached_g)*(1/Solid_Ca_mg_kg)*1000*1000)%>%
  mutate(Leachate_mg_Mg_per_g_Mg_in_solid_filt0.7 = Leachate_Mg_mg_L_filt0.7*(1/1000)*Leachate_vol_mL*(1/Char_leached_g)*(1/Solid_Mg_mg_kg)*1000*1000)%>%
  mutate(Leachate_mg_P_per_g_P_in_solid_filt0.7 = Leachate_P_mg_L_filt0.7*(1/1000)*Leachate_vol_mL*(1/Char_leached_g)*(1/Solid_P_mg_kg)*1000*1000)%>%
  mutate(Leachate_mg_K_per_g_K_in_solid_filt0.7 = Leachate_K_mg_L_filt0.7*(1/1000)*Leachate_vol_mL*(1/Char_leached_g)*(1/Solid_K_mg_kg)*1000*1000)%>%
  mutate(Leachate_mg_Na_per_g_Na_in_solid_filt0.7 = Leachate_Na_mg_L_filt0.7*(1/1000)*Leachate_vol_mL*(1/Char_leached_g)*(1/Solid_Na_mg_kg)*1000*1000)%>%
  mutate(Leachate_mg_S_per_g_S_in_solid_filt0.7 = Leachate_S_mg_L_filt0.7*(1/1000)*Leachate_vol_mL*(1/Char_leached_g)*(1/Solid_S_mg_kg)*1000*1000)%>%
  mutate(Leachate_mg_Al_per_g_Al_in_solid_filt0.7 = Leachate_Al_mg_L_filt0.7*(1/1000)*Leachate_vol_mL*(1/Char_leached_g)*(1/Solid_Al_mg_kg)*1000*1000)%>%
  mutate(Leachate_mg_Fe_per_g_Fe_in_solid_filt0.7 = Leachate_Fe_mg_L_filt0.7*(1/1000)*Leachate_vol_mL*(1/Char_leached_g)*(1/Solid_Fe_mg_kg)*1000*1000)%>%
  mutate(Leachate_mg_C_per_g_C_in_solid_filt0.7 = NPOC_mg_C_per_L*(1/1000)*Leachate_vol_mL*(1/ Char_leached_g)*(1/Solid_C_mg_kg)*1000*1000)%>%
  mutate(Leachate_mg_N_per_g_N_in_solid_filt0.7 = TN_mg_N_per_L*(1/1000)*Leachate_vol_mL*(1/ Char_leached_g)*(1/Solid_N_mg_kg)*1000*1000)%>%
  mutate(Leachate_mg_MBD_per_g_P_in_solid_filt0.7 = MBD_P_mg_per_L_filt0.7*(1/1000)*Leachate_vol_mL*(1/Char_leached_g)*(1/Solid_P_mg_kg)*1000*1000)


#molar stoichiometry of P:element in particulate and aqueous phases
data <- data %>%
  mutate(Fe.P.MolarRatio_part=(Leachate_Fe_mg_L_part/55.845)/(Leachate_P_mg_L_part/30.97))%>%
  mutate(K.P.MolarRatio_part=(Leachate_K_mg_L_part/39.0983)/(Leachate_P_mg_L_part/30.97))%>%
  mutate(Na.P.MolarRatio_part=(Leachate_Na_mg_L_part/22.989)/(Leachate_P_mg_L_part/30.97))%>%
  mutate(Al.P.MolarRatio_part=(Leachate_Al_mg_L_part/26.982)/(Leachate_P_mg_L_part/30.97))%>%
  mutate(Mg.P.MolarRatio_part=(Leachate_Mg_mg_L_part/24.305)/(Leachate_P_mg_L_part/30.97))%>%
  mutate(Ca.P.MolarRatio_part=(Leachate_Ca_mg_L_part/40.078)/(Leachate_P_mg_L_part/30.97))%>%
  mutate(S.P.MolarRatio_part=(Leachate_S_mg_L_part/32.065)/(Leachate_P_mg_L_part/30.97))%>%
  mutate(Fe.P.MolarRatio_filt0.7=(Leachate_Fe_mg_L_filt0.7/55.845)/(Leachate_P_mg_L_filt0.7/30.97))%>%
  mutate(K.P.MolarRatio_filt0.7=(Leachate_K_mg_L_filt0.7/39.0983)/(Leachate_P_mg_L_filt0.7/30.97))%>%
  mutate(Na.P.MolarRatio_filt0.7=(Leachate_Na_mg_L_filt0.7/22.989)/(Leachate_P_mg_L_filt0.7/30.97))%>%
  mutate(Al.P.MolarRatio_filt0.7=(Leachate_Al_mg_L_filt0.7/26.982)/(Leachate_P_mg_L_filt0.7/30.97))%>%
  mutate(Mg.P.MolarRatio_filt0.7=(Leachate_Mg_mg_L_filt0.7/24.305)/(Leachate_P_mg_L_filt0.7/30.97))%>%
  mutate(Ca.P.MolarRatio_filt0.7=(Leachate_Ca_mg_L_filt0.7/40.078)/(Leachate_P_mg_L_filt0.7/30.97))%>%
  mutate(S.P.MolarRatio_filt0.7=(Leachate_S_mg_L_filt0.7/32.065)/(Leachate_P_mg_L_filt0.7/30.97))%>%
  mutate(C.P.MolarRatio_filt0.7=(NPOC_mg_C_per_L/12.011)/(Leachate_P_mg_L_filt0.7/30.97))%>%
  mutate(N.P.MolarRatio_filt0.7=(TN_mg_N_per_L/14.01)/(Leachate_P_mg_L_filt0.7/30.97))
  
  
#calculate non-reactive leachable P (in aqueous phase)
data<-data %>%
  mutate(Leachate_mg_nonMBD_per_g_P_in_solid_filt0.7 = Leachate_mg_P_per_g_P_in_solid_filt0.7 - Leachate_mg_MBD_per_g_P_in_solid_filt0.7) %>%
  mutate(Leachate_mg_nonMBD_per_g_P_in_solid_filt0.7 = ifelse(Leachate_mg_nonMBD_per_g_P_in_solid_filt0.7 < 0, 0, Leachate_mg_nonMBD_per_g_P_in_solid_filt0.7))

```

if you would like to save these data for ease of use later on, remove the comments from this chunk and run:
```{r save csv}
#save csv of final collated data with manipulations
#write.csv(data, "../data/data.csv", row.names = FALSE) #all data
#write.csv(data_solids, "../data/data_solids.csv", row.names = FALSE) #solids only
```

```{r functions for figures}
split_labels_with_parentheses <- function(x) {
  sapply(x, function(label) {
    parts <- strsplit(as.character(label), " ")[[1]]
    if (length(parts) > 1) {
      paste(parts[1], "\n", paste0("(", parts[2], " °C)"), sep = "")
    } else {
      label
    }
  })
}
```

##Quick data import
if you'd like to use the files saved above, run this chunk:
```{r quick import}
#import data quickly by removing #s and running; so you don't have to run above code

#data <- read_csv("../data/data.csv")
#data_solids <- read_csv("../data/data_solids.csv")

#data$Burn_Severity=factor(data$Burn_Severity, levels= c("Unburned", "Low", "Moderate", "High"))
#data_solids$Burn_Severity=factor(data_solids$Burn_Severity, levels= c("Unburned", "Low", "Moderate", "High"))
```

##summary stats
```{r BS variables}
summary_bs <- data_solids %>%
  dplyr::group_by(Burn_Severity, Land_Coverage_Category) %>%
  dplyr::summarize(
    Temp_Mean = mean(Char_Max_Temp, na.rm = TRUE),
    Temp_Standard_Deviation = sd(Char_Max_Temp, na.rm = TRUE),
    Temp_Min = min(Char_Max_Temp, na.rm = TRUE),
    Temp_Max = max(Char_Max_Temp, na.rm = TRUE),
    Duration_Mean = mean(Burn_Duration, na.rm = TRUE),
    Duration_Standard_Deviation = sd(Burn_Duration, na.rm = TRUE),
    Count = n()
  )

```


```{r solids and leachates}
#solid elemental concentrations, NMR, and XANES summary
summary_solids_conc <- data_solids %>%
  dplyr::group_by(Burn_Severity, Land_Coverage_Category) %>%
  mutate(NMR_Pi = Ortho + Pyro) %>%
  mutate( NMR_Po = Mono + Di) %>%
  dplyr::summarize(
    P_Mean = mean(Solid_P_g_kg, na.rm = TRUE),
    P_Standard_Deviation = sd(Solid_P_g_kg, na.rm = TRUE),
    Ca_Mean = mean(Solid_Ca_g_kg, na.rm = TRUE),
    Ca_Standard_Deviation = sd(Solid_Ca_g_kg, na.rm = TRUE),
    Fe_Mean = mean(Solid_Fe_g_kg, na.rm = TRUE),
    Fe_Standard_Deviation = sd(Solid_Fe_g_kg, na.rm = TRUE),
    Al_Mean = mean(Solid_Al_g_kg, na.rm = TRUE),
    Al_Standard_Deviation = sd(Solid_Al_g_kg, na.rm = TRUE),
    K_Mean = mean(Solid_K_g_kg, na.rm = TRUE),
    K_Standard_Deviation = sd(Solid_K_g_kg, na.rm = TRUE),
    Mg_Mean = mean(Solid_Mg_g_kg, na.rm = TRUE),
    Mg_Standard_Deviation = sd(Solid_Mg_g_kg, na.rm = TRUE),
    Na_Mean = mean(Solid_Na_g_kg, na.rm = TRUE),
    Na_Standard_Deviation = sd(Solid_Na_g_kg, na.rm = TRUE),
    S_Mean = mean(Solid_S_g_kg, na.rm = TRUE),
    S_Standard_Deviation = sd(Solid_S_g_kg, na.rm = TRUE),
    C_Mean = mean(Solid_C_g_kg, na.rm = TRUE),
    C_Standard_Deviation = sd(Solid_C_g_kg, na.rm = TRUE),
    N_Mean = mean(Solid_N_g_kg, na.rm = TRUE),
    N_Standard_Deviation = sd(Solid_N_g_kg, na.rm = TRUE),
    NMR_Pi_Mean = mean(NMR_Pi, na.rm = TRUE),
    NMR_Pi_Standard_Deviation = sd(NMR_Pi, na.rm = TRUE),
    NMR_Po_Mean = mean(NMR_Po, na.rm = TRUE),
    NMR_Po_Standard_Deviation = sd(NMR_Po, na.rm = TRUE),
    Ortho_Mean = mean(Ortho, na.rm = TRUE),
    Ortho_Standard_Deviation = sd(Ortho, na.rm = TRUE),
    Mono_Mean = mean(Mono, na.rm = TRUE),
    Mono_Standard_Deviation = sd(Mono, na.rm = TRUE),
    Di_Mean = mean(Di, na.rm = TRUE),
    Di_Standard_Deviation = sd(Di, na.rm = TRUE),
    Pyro_Mean = mean(Pyro, na.rm = TRUE),
    Pyro_Standard_Deviation = sd(Pyro, na.rm = TRUE),
    M_D_Mean = mean(M_D_ratio, na.rm = TRUE),
    M_D_Standard_Deviation = sd(M_D_ratio, na.rm = TRUE),
    PyroP_Mean = mean(PyroP, na.rm = TRUE),
    PyroP_Standard_Deviation = sd(PyroP, na.rm = TRUE),
    Phytate_Mean = mean(Phytate, na.rm = TRUE),
    Phytate_Standard_Deviation = sd(Phytate, na.rm = TRUE),
    Lipids_Mean = mean(Lipids, na.rm = TRUE),
    Lipids_Standard_Deviation = sd(Lipids, na.rm = TRUE),
    DNA_Mean = mean(DNA, na.rm = TRUE),
    DNA_Standard_Deviation = sd(DNA, na.rm = TRUE),
    RNA_Mean = mean(RNA, na.rm = TRUE),
    RNA_Standard_Deviation = sd(RNA, na.rm = TRUE),
    G6P_Mean = mean(G6P, na.rm = TRUE),
    G6P_Standard_Deviation = sd(G6P, na.rm = TRUE),
    XANES_Po_Mean = mean(XANES_Po, na.rm = TRUE),
    XANES_Po_Standard_Deviation = sd(XANES_Po, na.rm = TRUE),
    XANES_Pi_Mean = mean(XANES_Pi, na.rm = TRUE),
    XANES_Pi_Standard_Deviation = sd(XANES_Pi, na.rm = TRUE),
    XANES_Fe_Mean = mean(XANES_Fe, na.rm = TRUE),
    XANES_Fe_Standard_Deviation = sd(XANES_Fe, na.rm = TRUE),
    XANES_Na_Mean = mean(XANES_Na, na.rm = TRUE),
    XANES_Na_Standard_Deviation = sd(XANES_Na, na.rm = TRUE),
    XANES_Ca_Mean = mean(XANES_Ca, na.rm = TRUE),
    XANES_Ca_Standard_Deviation = sd(XANES_Ca, na.rm = TRUE),
    XANES_Al_Mean = mean(XANES_Al, na.rm = TRUE),
    XANES_Al_Standard_Deviation = sd(XANES_Al, na.rm = TRUE),
    XANES_Mg_Mean = mean(XANES_Mg, na.rm = TRUE),
    XANES_Mg_Standard_Deviation = sd(XANES_Mg, na.rm = TRUE),
    XANES_K_Mean = mean(XANES_K, na.rm = TRUE),
    XANES_K_Standard_Deviation = sd(XANES_K, na.rm = TRUE),
    XANES_Pi_Fe_Mean = mean(XANES_Pi_Fe, na.rm = TRUE),
    XANES_Pi_Fe_Standard_Deviation = sd(XANES_Pi_Fe, na.rm = TRUE),
    XANES_Pi_Na_Mean = mean(XANES_Pi_Na, na.rm = TRUE),
    XANES_Pi_Na_Standard_Deviation = sd(XANES_Pi_Na, na.rm = TRUE),
    XANES_Pi_Ca_Mean = mean(XANES_Pi_Ca, na.rm = TRUE),
    XANES_Pi_Ca_Standard_Deviation = sd(XANES_Pi_Ca, na.rm = TRUE),
    XANES_Pi_Al_Mean = mean(XANES_Pi_Al, na.rm = TRUE),
    XANES_Pi_Al_Standard_Deviation = sd(XANES_Pi_Al, na.rm = TRUE),
    XANES_Pi_Mg_Mean = mean(XANES_Pi_Mg, na.rm = TRUE),
    XANES_Pi_Mg_Standard_Deviation = sd(XANES_Pi_Mg, na.rm = TRUE),
    XANES_Pi_K_Mean = mean(XANES_Pi_K, na.rm = TRUE),
    XANES_Pi_K_Standard_Deviation = sd(XANES_Pi_K, na.rm = TRUE),
    XANES_Po_Fe_Mean = mean(XANES_Po_Fe, na.rm = TRUE),
    XANES_Po_Fe_Standard_Deviation = sd(XANES_Po_Fe, na.rm = TRUE),
    XANES_Po_Na_Mean = mean(XANES_Po_Na, na.rm = TRUE),
    XANES_Po_Na_Standard_Deviation = sd(XANES_Po_Na, na.rm = TRUE),
    XANES_Po_Ca_Mean = mean(XANES_Po_Ca, na.rm = TRUE),
    XANES_Po_Ca_Standard_Deviation = sd(XANES_Po_Ca, na.rm = TRUE),
    XANES_Po_Al_Mean = mean(XANES_Po_Al, na.rm = TRUE),
    XANES_Po_Al_Standard_Deviation = sd(XANES_Po_Al, na.rm = TRUE),
    XANES_Po_Mg_Mean = mean(XANES_Po_Mg, na.rm = TRUE),
    XANES_Po_Mg_Standard_Deviation = sd(XANES_Po_Mg, na.rm = TRUE),
    XANES_Po_K_Mean = mean(XANES_Po_K, na.rm = TRUE),
    XANES_Po_K_Standard_Deviation = sd(XANES_Po_K, na.rm = TRUE),
    Count = n()
  )

#write.csv(summary_solids_conc, "../data/summary_solids_conc.csv") 


#NMR extraction efficiency
summary_solids_nmrEE <- data_solids %>%
  dplyr::group_by(Burn_Severity, Land_Coverage_Category) %>%
  dplyr::summarize(
    Mean = mean(NMR_EE_P_perc, na.rm = TRUE),
    Standard_Deviation = sd(NMR_EE_P_perc, na.rm = TRUE),
    Count = n()
  )

#write.csv(summary_solids_nmrEE, "../data/summary_solids_nmrEE.csv") 


#Chemical shift of spiked compounds into NMR experiments
summary_NMR_spike <-melt(NMR_Spikes, id=c("Parent_ID", "Compound_Name"))

summary_NMR_spike <- summary_NMR_spike %>%
  dplyr::group_by(Compound_Name, variable) %>%
  dplyr::summarize(
    Mean = mean(value, na.rm = TRUE),
    Standard_Deviation = sd(value, na.rm = TRUE),
    Count = n()
  )

#write.csv(summary_NMR_spike, "../data/summary_NMR_spike.csv")


#leachate concentrations
P.Conc.leach<- data %>%
  dplyr::group_by(Burn_Severity, Land_Coverage_Category) %>%
  dplyr::summarize(
    Leachate_mg_P_per_g_P_in_solid_unfilt_Mean = mean(Leachate_mg_P_per_g_P_in_solid_unfilt, na.rm = TRUE),
    Leachate_mg_P_per_g_P_in_solid_unfilt_Standard_Deviation = sd(Leachate_mg_P_per_g_P_in_solid_unfilt, na.rm = TRUE),
    Leachate_mg_P_per_g_P_in_solid_filt0.7_Mean = mean(Leachate_mg_P_per_g_P_in_solid_filt0.7, na.rm = TRUE),
    Leachate_mg_P_per_g_P_in_solid_filt0.7_Standard_Deviation = sd(Leachate_mg_P_per_g_P_in_solid_filt0.7, na.rm = TRUE),
    Leachate_mg_P_per_g_P_in_solid_part_Mean = mean(Leachate_mg_P_per_g_P_in_solid_part, na.rm = TRUE),
    Leachate_mg_P_per_g_P_in_solid_part_Standard_Deviation = sd(Leachate_mg_P_per_g_P_in_solid_part, na.rm = TRUE),
    Leachate_mg_MBD_per_g_P_in_solid_filt0.7_Mean = mean(Leachate_mg_MBD_per_g_P_in_solid_filt0.7, na.rm = TRUE),
    Leachate_mg_MBD_per_g_P_in_solid_filt0.7_Standard_Deviation = sd(Leachate_mg_MBD_per_g_P_in_solid_filt0.7, na.rm = TRUE),
    Leachate_mg_nonMBD_per_g_P_in_solid_filt0.7_Mean = mean(Leachate_mg_nonMBD_per_g_P_in_solid_filt0.7, na.rm = TRUE),
    Leachate_mg_nonMBD_per_g_P_in_solid_filt0.7_Standard_Deviation = sd(Leachate_mg_nonMBD_per_g_P_in_solid_filt0.7, na.rm = TRUE),
    Count = n()
  )

#write.csv(P.Conc.leach, "../data/summary_leachate_conc.csv")


#elemental stoichiometry
stoich_solid<-data_solids %>%
  select(Parent_ID, Burn_Severity, Land_Coverage_Category, Ca.P.MolarRatio, Mg.P.MolarRatio, Fe.P.MolarRatio, Al.P.MolarRatio, Na.P.MolarRatio, K.P.MolarRatio, S.P.MolarRatio, N.P.MolarRatio, C.P.MolarRatio) %>%
  dplyr::rename(
    'Ca:P' = 'Ca.P.MolarRatio',
    'Mg:P' = 'Mg.P.MolarRatio',
    'Fe:P' = 'Fe.P.MolarRatio',
    'Al:P' = 'Al.P.MolarRatio',
    'Na:P' = 'Na.P.MolarRatio',
    'K:P' = 'K.P.MolarRatio',
    'S:P' = 'S.P.MolarRatio',
    'N:P' = 'N.P.MolarRatio',
    'C:P' = 'C.P.MolarRatio')%>%
  mutate(filter = 'Solid')

stoich_leachates<-data %>%
  select(Parent_ID, Ca.P.MolarRatio_part, Mg.P.MolarRatio_part, Fe.P.MolarRatio_part, Al.P.MolarRatio_part, Na.P.MolarRatio_part, K.P.MolarRatio_part, S.P.MolarRatio_part, Ca.P.MolarRatio_filt0.7, Mg.P.MolarRatio_filt0.7, Fe.P.MolarRatio_filt0.7, Al.P.MolarRatio_filt0.7, Na.P.MolarRatio_filt0.7, K.P.MolarRatio_filt0.7, S.P.MolarRatio_filt0.7, N.P.MolarRatio_filt0.7, C.P.MolarRatio_filt0.7) %>%
  dplyr::rename(
    'Ca_P_part' = 'Ca.P.MolarRatio_part',
    'Mg_P_part' = 'Mg.P.MolarRatio_part',
    'Fe_P_part' = 'Fe.P.MolarRatio_part',
    'Al_P_part' = 'Al.P.MolarRatio_part',
    'Na_P_part' = 'Na.P.MolarRatio_part',
    'K_P_part' = 'K.P.MolarRatio_part',
    'S_P_part' = 'S.P.MolarRatio_part',
    'Ca_P_filt0.7' = 'Ca.P.MolarRatio_filt0.7',
    'Mg_P_filt0.7' = 'Mg.P.MolarRatio_filt0.7',
    'Fe_P_filt0.7' = 'Fe.P.MolarRatio_filt0.7',
    'Al_P_filt0.7' = 'Al.P.MolarRatio_filt0.7',
    'Na_P_filt0.7' = 'Na.P.MolarRatio_filt0.7',
    'K_P_filt0.7' = 'K.P.MolarRatio_filt0.7',
    'S_P_filt0.7' = 'S.P.MolarRatio_filt0.7',
    'N_P_filt0.7' = 'N.P.MolarRatio_filt0.7',
    'C_P_filt0.7' = 'C.P.MolarRatio_filt0.7'
  )

stoich_part<-data %>%
  select(Parent_ID, Burn_Severity, Land_Coverage_Category, Ca.P.MolarRatio_part, Mg.P.MolarRatio_part, Fe.P.MolarRatio_part, Al.P.MolarRatio_part, Na.P.MolarRatio_part, K.P.MolarRatio_part, S.P.MolarRatio_part) %>%
  dplyr::rename(
    'Ca:P' = 'Ca.P.MolarRatio_part',
    'Mg:P' = 'Mg.P.MolarRatio_part',
    'Fe:P' = 'Fe.P.MolarRatio_part',
    'Al:P' = 'Al.P.MolarRatio_part',
    'Na:P' = 'Na.P.MolarRatio_part',
    'K:P' = 'K.P.MolarRatio_part',
    'S:P' = 'S.P.MolarRatio_part')%>%
  mutate(filter = 'Particulate')

stoich_filt<-data %>%
  select(Parent_ID, Burn_Severity, Land_Coverage_Category, Ca.P.MolarRatio_filt0.7, Mg.P.MolarRatio_filt0.7, Fe.P.MolarRatio_filt0.7, Al.P.MolarRatio_filt0.7, Na.P.MolarRatio_filt0.7, K.P.MolarRatio_filt0.7, S.P.MolarRatio_filt0.7, C.P.MolarRatio_filt0.7, N.P.MolarRatio_filt0.7) %>%
  dplyr::rename(
    'Ca:P' = 'Ca.P.MolarRatio_filt0.7',
    'Mg:P' = 'Mg.P.MolarRatio_filt0.7',
    'Fe:P' = 'Fe.P.MolarRatio_filt0.7',
    'Al:P' = 'Al.P.MolarRatio_filt0.7',
    'Na:P' = 'Na.P.MolarRatio_filt0.7',
    'K:P' = 'K.P.MolarRatio_filt0.7',
    'S:P' = 'S.P.MolarRatio_filt0.7',
    'C:P' = 'C.P.MolarRatio_filt0.7',
    'N:P' = 'N.P.MolarRatio_filt0.7') %>%
  mutate(filter = 'Aqueous')

stoich<- stoich_leachates %>%
  full_join(stoich_solid)

stoich<- stoich_part %>%
  full_join(stoich_filt)%>%
  full_join(stoich_solid)
  
stoich<-melt(stoich, id=c("Parent_ID", "Burn_Severity", "Land_Coverage_Category", "filter"))

stoich_mean <- stoich %>%
  dplyr::group_by(Burn_Severity, Land_Coverage_Category, filter, variable) %>%
  dplyr::summarize(
    value_mean = mean(value, na.rm = TRUE),
    value_sd = sd(value, na.rm = TRUE))

#write csv
#write.csv(stoich_mean, "../data/summary_stoich.csv")
```

##Solid Char 
###P Concentration
```{r figure}
#relationship of P in solid chars with burn severity and vegetation type
data_solids_Pconc <- data_solids %>%
  mutate(
    Annotation = case_when(
      Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "Unburned" ~ "a",
      Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "Low" ~ "a",
      Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "Moderate" ~ "a",
      Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "High" ~ "b",
      Land_Coverage_Category == "Sagebrush Shrubland" & Burn_Severity == "Unburned" ~ "a",
      Land_Coverage_Category == "Sagebrush Shrubland" & Burn_Severity == "Low" ~ "b",
      Land_Coverage_Category == "Sagebrush Shrubland" & Burn_Severity == "Moderate" ~ "c"),
    x = case_when(
      Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "Unburned" ~ "Unburned",
      Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "Low" ~ "Low",
      Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "Moderate" ~ "Moderate",
      Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "High" ~ "High",
      Land_Coverage_Category == "Sagebrush Shrubland" & Burn_Severity == "Unburned" ~ "Unburned",
      Land_Coverage_Category == "Sagebrush Shrubland" & Burn_Severity == "Low" ~ "Low",
      Land_Coverage_Category == "Sagebrush Shrubland" & Burn_Severity == "Moderate" ~ "Moderate"),
    y = case_when(
      Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "Unburned" ~ 2.8,
      Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "Low" ~ 3.8,
      Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "Moderate" ~ 3.6,
      Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "High" ~ 9.2,
      Land_Coverage_Category == "Sagebrush Shrubland" & Burn_Severity == "Unburned" ~2.35,
      Land_Coverage_Category == "Sagebrush Shrubland" & Burn_Severity == "Low" ~ 6.9,
      Land_Coverage_Category == "Sagebrush Shrubland" & Burn_Severity == "Moderate" ~ 17.5))

solid.P.BS.fig<-ggplot(data_solids_Pconc, aes(x=Burn_Severity, y=Solid_P_mg_kg/1000, fill=Land_Coverage_Category))+geom_boxplot(show.legend=FALSE)+theme_classic()+ylab(expression(paste(Solid~Total~P~(g~P~kg^-1), sep="")))+ xlab("Burn Severity")+ scale_fill_manual(values=c("lightgray","lightgray"))+facet_grid(.~Land_Coverage_Category, scales = "free") + theme(text = element_text(size = 18),panel.border = element_rect(color = "black", fill = NA, linewidth = 1)) + geom_text(aes(label = Annotation, x = x, y = y), size = 4.5, fontface = "plain")

solid.P.BS.fig
#cowplot::save_plot("../figures/solid.P.BS.fig.pdf", solid.P.BS.fig, base_width = 8,    base_height = 4, dpi = 300)
```

```{r stats}
#relationship of P in solid chars with burn severity and vegetation type
model<-aov(log10(Solid_P_mg_kg)~Burn_Severity*Land_Coverage_Category, data = data_solids)
summary(model)
#model assumptions
hist(log10(data_solids$Solid_P_mg_kg))
ggqqplot(residuals(model))
plot(fitted(model),residuals(model))
#interaction post hoc: 
emmeans::emmeans(model, pairwise~Burn_Severity*Land_Coverage_Category, at=list(Burn_Severity="Unburned"),adjust="tukey") 
emmeans::emmeans(model, pairwise~Burn_Severity*Land_Coverage_Category, at=list(Burn_Severity="Low"),adjust="tukey")
emmeans::emmeans(model, pairwise~Burn_Severity*Land_Coverage_Category, at=list(Burn_Severity="Moderate"),adjust="tukey") 
emmeans::emmeans(model, pairwise~Burn_Severity*Land_Coverage_Category, at=list(Land_Coverage_Category="Douglas-fir Forest"),adjust="tukey") 
emmeans::emmeans(model, pairwise~Burn_Severity*Land_Coverage_Category, at=list(Land_Coverage_Category="Sagebrush Shrubland"),adjust="tukey") 

```

###NMR
```{r Sample spectra fig}
NMR_spectra_df_subset <-NMR_spectra %>%
  select("Chemical_Shift_parts_per_million", "BSLE_0013-solid", "BSLE_0007-solid","BSLE_0002-solid", "BSLE_0050-solid") %>%
  dplyr::rename('solid_13' = 'BSLE_0013-solid',
                'solid_7' = 'BSLE_0007-solid',
                'solid_2' = 'BSLE_0002-solid',
                'solid_50' = 'BSLE_0050-solid') %>%
  mutate_all(~replace(., . == 0, NA)) %>%
  mutate(solid_13 = solid_13 + 1,
         solid_7 = solid_7 + 75,
         solid_2 = solid_2 + 150,
         solid_50 = solid_50 + 225) 
         
NMR_spectra_df_subset<-melt(NMR_spectra_df_subset, id=c("Chemical_Shift_parts_per_million"))

NMR_spectra_df_subset<-subset(NMR_spectra_df_subset, value!="")

NMR_stacked_spectra_df <- ggplot(NMR_spectra_df_subset, aes(x=Chemical_Shift_parts_per_million, y = value, color = as.factor(variable))) + geom_path()+theme_classic() + ylim(0,300) + scale_x_reverse() +xlim(10,-10) +scale_color_manual(values=c('Black','Black', 'Black', 'Black')) + theme(axis.ticks.y = element_blank(),  axis.text.y = element_blank(), legend.position = "none")  + ylab("") + xlab("Chemical Shift (ppm)")

#pdf(file = "../figures/NMR_stacked_spectra_df.pdf", width = 3.5, height = 7) 
print(NMR_stacked_spectra_df)
dev.off()

NMR_spectra_sb_subset <-NMR_spectra %>%
  select("Chemical_Shift_parts_per_million", "BSLE_0014-solid", "BSLE_0011-solid","BSLE_0072-solid") %>%
  dplyr::rename('solid_14' = 'BSLE_0014-solid',
                'solid_11' = 'BSLE_0011-solid',
                'solid_72' = 'BSLE_0072-solid') %>%
  mutate_all(~replace(., . == 0, NA)) %>%
  mutate(solid_14 = solid_14 + 1,
         solid_11 = solid_11 + 75,
         solid_72 = solid_72 + 150) 
         
NMR_spectra_sb_subset<-melt(NMR_spectra_sb_subset, id=c("Chemical_Shift_parts_per_million"))

NMR_spectra_sb_subset<-subset(NMR_spectra_sb_subset, value!="")

NMR_stacked_spectra_sb <- ggplot(NMR_spectra_sb_subset, aes(x=Chemical_Shift_parts_per_million, y = value, color = as.factor(variable))) + geom_path()+theme_classic() + ylim(0,300) + scale_x_reverse() +xlim(10,-10) +scale_color_manual(values=c('Black','Black', 'Black', 'Black')) + theme(axis.ticks.y = element_blank(),  axis.text.y = element_blank(), legend.position = "none")  + ylab("") + xlab("Chemical Shift (ppm)")

#pdf(file = "../figures/NMR_stacked_spectra_sb.pdf", width = 3.5, height = 7) 
print(NMR_stacked_spectra_sb)
dev.off()

#pie charts for relative percent of NMR species
NMR <- summary_solids_conc %>%
  select("Land_Coverage_Category", "Burn_Severity","Ortho_Mean", "Mono_Mean", "Di_Mean", "Pyro_Mean") %>%
  dplyr::rename(Ortho = Ortho_Mean,
                Mono = Mono_Mean,
                Di = Di_Mean,
                Pyro = Pyro_Mean)

NMR_melt<-melt(NMR, id=c("Land_Coverage_Category", "Burn_Severity"))

NMR_melt$variable=factor(NMR_melt$variable, levels= c("Ortho", "Pyro", "Mono", "Di"))

DF.raw<-subset(NMR_melt, Land_Coverage_Category=="Douglas-fir Forest" & Burn_Severity=="Unburned")
nmr.legend<-ggplot(DF.raw, aes(x = "", y = value, fill = variable, pattern = variable)) +
  geom_col_pattern(
    color = "black",
    pattern_fill = "black",
    pattern_density = 0.02,
    pattern_spacing = 0.06,
    pattern_angle = 45,
    pattern_key_scale_factor = 0.6  # helps display pattern in legend
  ) +
  coord_polar(theta = "y") +
  scale_fill_manual(values = c(
    "Ortho" = "#997B66",
    "Pyro"  = "#F1DCA7",
    "Mono"  = "#D08C60",
    "Di"    = "#e2b89d"
  )) +
  scale_pattern_manual(values = c(
    "Ortho" = "none",
    "Pyro"  = "none",
    "Mono"  = "stripe",
    "Di"    = "stripe"
  )) +
  guides(
    fill = guide_legend(override.aes = list(pattern = c("none", "none", "stripe", "stripe"))),
    pattern = "none"  # suppress separate pattern legend
  ) +
  theme_void() +
  theme(
    legend.key.size = unit(1, 'cm'),
    legend.key.height = unit(1, 'cm'),
    legend.key.width = unit(1, 'cm'),
    legend.title = element_text(size = 25),
    legend.text = element_text(size = 20)
  ) +
  labs(fill = "")
#pdf(file = "../figures/nmr.legend.pdf", width = 7, height = 3.5) 
print(nmr.legend)
dev.off()

DF.raw.nmr<-ggplot(DF.raw, aes(x = "", y = value, fill = variable, pattern = variable)) +
    geom_col_pattern(
        color = "black",
        pattern_fill = "black",
        pattern_density = 0.02,
        pattern_spacing = 0.06,
        pattern_angle = 45
    ) +
    coord_polar(theta = "y") +
    scale_fill_manual(values = c(
        "#997B66", "#F1DCA7", "#D08C60", "#e2b89d"
    )) +
    scale_pattern_manual(values = c(
        "Ortho" = "none",
        "Pyro" = "none",
        "Mono" = "stripe",
        "Di" = "stripe"
    )) +
    theme_void() +
    theme(legend.position = "none")
#pdf(file = "../figures/DF.raw.nmr.pdf", width = 1, height = 1) 
print(DF.raw.nmr)
dev.off()

DF.low<-subset(NMR_melt, Land_Coverage_Category=="Douglas-fir Forest" & Burn_Severity=="Low")
DF.low.nmr<-ggplot(DF.low, aes(x = "", y = value, fill = variable, pattern = variable)) +
    geom_col_pattern(
        color = "black",
        pattern_fill = "black",
        pattern_density = 0.02,
        pattern_spacing = 0.06,
        pattern_angle = 45
    ) +
    coord_polar(theta = "y") +
    scale_fill_manual(values = c(
        "#997B66", "#F1DCA7", "#D08C60", "#e2b89d"
    )) +
    scale_pattern_manual(values = c(
        "Ortho" = "none",
        "Pyro" = "none",
        "Mono" = "stripe",
        "Di" = "stripe"
    )) +
    theme_void() +
    theme(legend.position = "none")
#pdf(file = "../figures/DF.low.nmr.pdf", width = 1, height = 1) 
print(DF.low.nmr)
dev.off()

DF.mod<-subset(NMR_melt, Land_Coverage_Category=="Douglas-fir Forest" & Burn_Severity=="Moderate")
DF.mod.nmr<-ggplot(DF.mod, aes(x = "", y = value, fill = variable, pattern = variable)) +
    geom_col_pattern(
        color = "black",
        pattern_fill = "black",
        pattern_density = 0.02,
        pattern_spacing = 0.06,
        pattern_angle = 45
    ) +
    coord_polar(theta = "y") +
    scale_fill_manual(values = c(
        "#997B66", "#F1DCA7", "#D08C60", "#e2b89d"
    )) +
    scale_pattern_manual(values = c(
        "Ortho" = "none",
        "Pyro" = "none",
        "Mono" = "stripe",
        "Di" = "stripe"
    )) +
    theme_void() +
    theme(legend.position = "none")
#pdf(file = "../figures/DF.mod.nmr.pdf", width = 1, height = 1) 
print(DF.mod.nmr)
dev.off()

DF.high<-subset(NMR_melt, Land_Coverage_Category=="Douglas-fir Forest" & Burn_Severity=="High")
DF.high.nmr<-ggplot(DF.high, aes(x = "", y = value, fill = variable, pattern = variable)) +
    geom_col_pattern(
        color = "black",
        pattern_fill = "black",
        pattern_density = 0.02,
        pattern_spacing = 0.06,
        pattern_angle = 45
    ) +
    coord_polar(theta = "y") +
    scale_fill_manual(values = c(
        "#997B66", "#F1DCA7", "#D08C60", "#e2b89d"
    )) +
    scale_pattern_manual(values = c(
        "Ortho" = "none",
        "Pyro" = "none",
        "Mono" = "stripe",
        "Di" = "stripe"
    )) +
    theme_void() +
    theme(legend.position = "none")
#pdf(file = "../figures/DF.high.nmr.pdf", width = 1, height = 1) 
print(DF.high.nmr)
dev.off()

SB.raw<-subset(NMR_melt, Land_Coverage_Category=="Sagebrush Shrubland" & Burn_Severity=="Unburned")
SB.raw.nmr<-ggplot(SB.raw, aes(x = "", y = value, fill = variable, pattern = variable)) +
    geom_col_pattern(
        color = "black",
        pattern_fill = "black",
        pattern_density = 0.02,
        pattern_spacing = 0.06,
        pattern_angle = 45
    ) +
    coord_polar(theta = "y") +
    scale_fill_manual(values = c(
        "#997B66", "#F1DCA7", "#D08C60", "#e2b89d"
    )) +
    scale_pattern_manual(values = c(
        "Ortho" = "none",
        "Pyro" = "none",
        "Mono" = "stripe",
        "Di" = "stripe"
    )) +
    theme_void() +
    theme(legend.position = "none")
#pdf(file = "../figures/SB.raw.nmr.pdf", width = 1, height = 1) 
print(SB.raw.nmr)
dev.off()

SB.low<-subset(NMR_melt, Land_Coverage_Category=="Sagebrush Shrubland" & Burn_Severity=="Low")
SB.low.nmr<-ggplot(SB.low, aes(x = "", y = value, fill = variable, pattern = variable)) +
    geom_col_pattern(
        color = "black",
        pattern_fill = "black",
        pattern_density = 0.02,
        pattern_spacing = 0.06,
        pattern_angle = 45
    ) +
    coord_polar(theta = "y") +
    scale_fill_manual(values = c(
        "#997B66", "#F1DCA7", "#D08C60", "#e2b89d"
    )) +
    scale_pattern_manual(values = c(
        "Ortho" = "none",
        "Pyro" = "none",
        "Mono" = "stripe",
        "Di" = "stripe"
    )) +
    theme_void() +
    theme(legend.position = "none")
#pdf(file = "../figures/SB.low.nmr.pdf", width = 1, height = 1) 
print(SB.low.nmr)
dev.off()

SB.mod<-subset(NMR_melt, Land_Coverage_Category=="Sagebrush Shrubland" & Burn_Severity=="Moderate")
SB.mod.nmr<-ggplot(SB.mod, aes(x = "", y = value, fill = variable, pattern = variable)) +
    geom_col_pattern(
        color = "black",
        pattern_fill = "black",
        pattern_density = 0.02,
        pattern_spacing = 0.06,
        pattern_angle = 45
    ) +
    coord_polar(theta = "y") +
    scale_fill_manual(values = c(
        "#997B66", "#F1DCA7", "#D08C60", "#e2b89d"
    )) +
    scale_pattern_manual(values = c(
        "Ortho" = "none",
        "Pyro" = "none",
        "Mono" = "stripe",
        "Di" = "stripe"
    )) +
    theme_void() +
    theme(legend.position = "none")
#pdf(file = "../figures/SB.mod.nmr.pdf", width = 1, height = 1) 
print(SB.mod.nmr)
dev.off()

```

```{r Mono Die % Change Fig}
#figures for NMR monoester and diester percent change with burning
per_change<-data_solids %>%
  select(Land_Coverage_Category, Burn_Severity, mono_per_change, di_per_change) %>%
  filter(Burn_Severity != "Unburned") %>%
  dplyr::rename(Monoester = mono_per_change,
         Diester = di_per_change) %>%
  mutate(
    Burn_Severity = case_when(
      Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "Unburned" ~ "Unburned 25",
      Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "Low" ~ "Low 295-627",
      Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "Moderate" ~ "Moderate 589-757",
      Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "High" ~ "High 589-757",
      Land_Coverage_Category == "Sagebrush Shrubland" & Burn_Severity == "Unburned" ~ "Unburned 25",
      Land_Coverage_Category == "Sagebrush Shrubland" & Burn_Severity == "Low" ~ "Low 308-502",
      Land_Coverage_Category == "Sagebrush Shrubland" & Burn_Severity == "Moderate" ~ "Moderate 512-547",
      TRUE ~ as.character(Burn_Severity)),
    Burn_Severity = factor(Burn_Severity, levels = c("Low 295-627", "Low 308-502", "Moderate 589-757",
                                                     "Moderate 512-547", "High 589-757")))

per_change<-melt(per_change, id=c("Burn_Severity", "Land_Coverage_Category"))

mono_die_loss<- ggplot(per_change, aes(x = Burn_Severity, y = value, fill = variable)) +
  geom_boxplot() +
  theme_classic() +
  ylab("Percent Loss (%)") +
  xlab("Burn Severity") +
  scale_fill_manual(values = c("#D08C60", "#e2b89d")) +
  facet_grid(. ~ Land_Coverage_Category, scales = "free_x") +
  theme(
    text = element_text(size = 15),
    axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1),
    panel.border = element_rect(color = "black", fill = NA, linewidth = 1)
  ) +
  labs(fill = NULL) +
  scale_x_discrete(labels = split_labels_with_parentheses)

#pdf(file = "../figures/mono_die_loss.pdf", width = 6, height = 3) 
print(mono_die_loss)
dev.off()
```

```{r Mono Die % Change Fig stats}
per_change <- per_change %>%
  mutate(Burn_Severity = gsub("[0-9 \\-]", "", Burn_Severity))

model<-aov(log10(abs(value))~variable*Burn_Severity*Land_Coverage_Category, data = per_change)
summary(model)
hist((per_change$value))
ggqqplot(residuals(model))
plot(fitted(model),residuals(model))

```

```{r NMR and Ca-P stats}
model<-lm(XANES_Pi_Ca ~ NMR_EE_P_perc, data = data_solids)
summary(model)
#model assumptions
hist((data_solids$NMR_EE_P_perc))
ggqqplot(residuals(model))
plot(fitted(model),residuals(model))
```

###XANES
```{r Sample spectra fig}

XANES_spectra_df_subset <-XANES_spectra %>%
  select("eV", "BSLE_0013-solid_P-XANES.xmu.nor", "BSLE_0007-solid_P-XANES.xmu.nor","BSLE_0002-solid_P-XANES.xmu.nor", "BSLE_0050-solid_P-XANES.xmu.nor") %>%
  dplyr::rename('solid_13' = 'BSLE_0013-solid_P-XANES.xmu.nor',
                'solid_7' = 'BSLE_0007-solid_P-XANES.xmu.nor',
                'solid_2' = 'BSLE_0002-solid_P-XANES.xmu.nor',
                'solid_50' = 'BSLE_0050-solid_P-XANES.xmu.nor') %>%
  mutate_all(~replace(., . == 0, NA)) %>%
  mutate(solid_13 = solid_13 + 1,
         solid_7 = solid_7 + 8,
         solid_2 = solid_2 + 16,
         solid_50 = solid_50 + 24) 
         
XANES_spectra_df_subset<-melt(XANES_spectra_df_subset, id=c("eV"))

XANES_spectra_df_subset<-subset(XANES_spectra_df_subset, value!="")

XANES_stacked_spectra_df <- ggplot(XANES_spectra_df_subset, aes(x=eV, y = value, color = as.factor(variable))) + geom_path()+theme_classic() + scale_color_manual(values=c('Black','Black', 'Black', 'Black')) + theme(axis.ticks.y = element_blank(),  axis.text.y = element_blank(), legend.position = "none")  + ylab("") + xlab("Energy (eV)") + xlim(2140, 2200) + ylab ("Normalized Absorption (arb. units)")

#pdf(file = "../figures/XANES_stacked_spectra_df.pdf", width = 3, height = 7) 
print(XANES_stacked_spectra_df)
dev.off()

XANES_spectra_sb_subset <-XANES_spectra %>%
  select("eV", "BSLE_0014-solid_P-XANES.xmu.nor", "BSLE_0011-solid_P-XANES.xmu.nor","BSLE_0072-solid_P-XANES.xmu.nor") %>%
  dplyr::rename('solid_14' = 'BSLE_0014-solid_P-XANES.xmu.nor',
                'solid_11' = 'BSLE_0011-solid_P-XANES.xmu.nor',
                'solid_72' = 'BSLE_0072-solid_P-XANES.xmu.nor') %>%
  mutate_all(~replace(., . == 0, NA)) %>%
  mutate(blank = solid_72) %>%
  mutate(solid_14 = solid_14 + 1,
         solid_11 = solid_11 + 8,
         solid_72 = solid_72 + 16,
         blank = blank + 24) 
         
XANES_spectra_sb_subset<-melt(XANES_spectra_sb_subset, id=c("eV"))

XANES_spectra_sb_subset<-subset(XANES_spectra_sb_subset, value!="")

XANES_stacked_spectra_sb <- ggplot(XANES_spectra_sb_subset, aes(x=eV, y = value, color = as.factor(variable))) + geom_path()+theme_classic() + scale_color_manual(values=c('Black','Black', 'Black', 'White')) + theme(axis.ticks.y = element_blank(),  axis.text.y = element_blank(), legend.position = "none")  + ylab("") + xlab("Energy (eV)") + xlim(2140, 2200) + ylab ("Normalized Absorption (arb. units)")

#pdf(file = "../figures/XANES_stacked_spectra_sb.pdf", width = 3, height = 7) 
print(XANES_stacked_spectra_sb)
dev.off()

#pie charts with Po grouped and inorganic separate metals
XANES <- summary_solids_conc %>%
  select("Land_Coverage_Category", "Burn_Severity","XANES_Pi_K_Mean", "XANES_Pi_Mg_Mean", "XANES_Pi_Al_Mean", "XANES_Pi_Ca_Mean", "XANES_Pi_Na_Mean", "XANES_Pi_Fe_Mean", "XANES_Po_Mean") %>%
  dplyr::rename(K = XANES_Pi_K_Mean,
                Mg = XANES_Pi_Mg_Mean,
                Al = XANES_Pi_Al_Mean,
                Ca = XANES_Pi_Ca_Mean,
                Na = XANES_Pi_Na_Mean,
                Fe = XANES_Pi_Fe_Mean,
                Po = XANES_Po_Mean)

XANES_melt<-melt(XANES, id=c("Land_Coverage_Category", "Burn_Severity"))

DF.raw<-subset(XANES_melt, Land_Coverage_Category=="Douglas-fir Forest" & Burn_Severity=="Unburned")
xanes.legend<-ggplot(DF.raw, aes(x = "", y = value, fill = variable, pattern = variable)) +
    geom_col_pattern(
        color = "black",
        pattern_fill = "black",
        pattern_density = 0.02,
        pattern_spacing = 0.06,
        pattern_angle = 45,
        pattern_key_scale_factor = 0.6
    ) +
    coord_polar(theta = "y") +
    scale_fill_manual(values = c(
        "K" = "#493C32",
        "Mg" = "#87745D",
        "Al" = "#C5AC87",
        "Ca" = "#F1DCA7",
        "Na" = "#FFF4DC",
        "Fe" = "#FFFCF5",
        "Po"   = "#ae6433"
    )) +
    scale_pattern_manual(values = c(
        "K" = "none",
        "Mg" = "none",
        "Al" = "none",
        "Ca" = "none",
        "Na" = "none",
        "Fe" = "none",
        "Po"   = "stripe"
    )) +
    guides(
        fill = guide_legend(override.aes = list(pattern = c(
            "none", "none", "none", "none", "none", "none", "stripe"
        ))),
        pattern = "none"
    ) +
    theme_void() +
    theme(
        legend.key.size = unit(1, 'cm'),
        legend.key.height = unit(1, 'cm'),
        legend.key.width = unit(1, 'cm'),
        legend.title = element_text(size = 25),
        legend.text = element_text(size = 20)
    ) +
    labs(fill = "")
#pdf(file = "../figures/xanes.legend.pdf", width = 7, height = 3.5) 
print(xanes.legend)
dev.off()

DF.raw.xanes<-ggplot(DF.raw, aes(x = "", y = value, fill = variable, pattern = variable)) +
    geom_col_pattern(
        color = "black",
        pattern_fill = "black",
        pattern_density = 0.02,
        pattern_spacing = 0.06,
        pattern_angle = 45,
        pattern_key_scale_factor = 0.6
    ) +
    coord_polar(theta = "y") +
    scale_fill_manual(values = c(
        "K" = "#493C32",
        "Mg" = "#87745D",
        "Al" = "#C5AC87",
        "Ca" = "#F1DCA7",
        "Na" = "#FFF4DC",
        "Fe" = "#FFFCF5",
        "Po"   = "#ae6433"
    )) +
    scale_pattern_manual(values = c(
        "K" = "none",
        "Mg" = "none",
        "Al" = "none",
        "Ca" = "none",
        "Na" = "none",
        "Fe" = "none",
        "Po"   = "stripe"
    )) +
    guides(
        fill = guide_legend(override.aes = list(pattern = c(
            "none", "none", "none", "none", "none", "none", "stripe"
        ))),
        pattern = "none"
    ) +
    theme_void() +
    theme(legend.position = "none")
#pdf(file = "../figures/DF.raw.xanes.pdf", width = 1, height = 1) 
print(DF.raw.xanes)
dev.off()

DF.low<-subset(XANES_melt, Land_Coverage_Category=="Douglas-fir Forest" & Burn_Severity=="Low")
DF.low.xanes<-ggplot(DF.low, aes(x = "", y = value, fill = variable, pattern = variable)) +
    geom_col_pattern(
        color = "black",
        pattern_fill = "black",
        pattern_density = 0.02,
        pattern_spacing = 0.06,
        pattern_angle = 45,
        pattern_key_scale_factor = 0.6
    ) +
    coord_polar(theta = "y") +
    scale_fill_manual(values = c(
        "K" = "#493C32",
        "Mg" = "#87745D",
        "Al" = "#C5AC87",
        "Ca" = "#F1DCA7",
        "Na" = "#FFF4DC",
        "Fe" = "#FFFCF5",
        "Po"   = "#ae6433"
    )) +
    scale_pattern_manual(values = c(
        "K" = "none",
        "Mg" = "none",
        "Al" = "none",
        "Ca" = "none",
        "Na" = "none",
        "Fe" = "none",
        "Po"   = "stripe"
    )) +
    guides(
        fill = guide_legend(override.aes = list(pattern = c(
            "none", "none", "none", "none", "none", "none", "stripe"
        ))),
        pattern = "none"
    ) +
    theme_void() +
    theme(legend.position = "none")
#pdf(file = "../figures/DF.low.xanes.pdf", width = 1, height = 1) 
print(DF.low.xanes)
dev.off()

DF.mod<-subset(XANES_melt, Land_Coverage_Category=="Douglas-fir Forest" & Burn_Severity=="Moderate")
DF.mod.xanes<-ggplot(DF.mod, aes(x = "", y = value, fill = variable, pattern = variable)) +
    geom_col_pattern(
        color = "black",
        pattern_fill = "black",
        pattern_density = 0.02,
        pattern_spacing = 0.06,
        pattern_angle = 45,
        pattern_key_scale_factor = 0.6
    ) +
    coord_polar(theta = "y") +
    scale_fill_manual(values = c(
        "K" = "#493C32",
        "Mg" = "#87745D",
        "Al" = "#C5AC87",
        "Ca" = "#F1DCA7",
        "Na" = "#FFF4DC",
        "Fe" = "#FFFCF5",
        "Po"   = "#ae6433"
    )) +
    scale_pattern_manual(values = c(
        "K" = "none",
        "Mg" = "none",
        "Al" = "none",
        "Ca" = "none",
        "Na" = "none",
        "Fe" = "none",
        "Po"   = "stripe"
    )) +
    guides(
        fill = guide_legend(override.aes = list(pattern = c(
            "none", "none", "none", "none", "none", "none", "stripe"
        ))),
        pattern = "none"
    ) +
    theme_void() +
    theme(legend.position = "none")
#pdf(file = "../figures/DF.mod.xanes.pdf", width = 1, height = 1) 
print(DF.mod.xanes)
dev.off()

DF.high<-subset(XANES_melt, Land_Coverage_Category=="Douglas-fir Forest" & Burn_Severity=="High")
DF.high.xanes<-ggplot(DF.high, aes(x = "", y = value, fill = variable, pattern = variable)) +
    geom_col_pattern(
        color = "black",
        pattern_fill = "black",
        pattern_density = 0.02,
        pattern_spacing = 0.06,
        pattern_angle = 45,
        pattern_key_scale_factor = 0.6
    ) +
    coord_polar(theta = "y") +
    scale_fill_manual(values = c(
        "K" = "#493C32",
        "Mg" = "#87745D",
        "Al" = "#C5AC87",
        "Ca" = "#F1DCA7",
        "Na" = "#FFF4DC",
        "Fe" = "#FFFCF5",
        "Po"   = "#ae6433"
    )) +
    scale_pattern_manual(values = c(
        "K" = "none",
        "Mg" = "none",
        "Al" = "none",
        "Ca" = "none",
        "Na" = "none",
        "Fe" = "none",
        "Po"   = "stripe"
    )) +
    guides(
        fill = guide_legend(override.aes = list(pattern = c(
            "none", "none", "none", "none", "none", "none", "stripe"
        ))),
        pattern = "none"
    ) +
    theme_void() +
    theme(legend.position = "none")
#pdf(file = "../figures/DF.high.xanes.pdf", width = 1, height = 1) 
print(DF.high.xanes)
dev.off()

SB.raw<-subset(XANES_melt, Land_Coverage_Category=="Sagebrush Shrubland" & Burn_Severity=="Unburned")
SB.raw.xanes<-ggplot(SB.raw, aes(x = "", y = value, fill = variable, pattern = variable)) +
    geom_col_pattern(
        color = "black",
        pattern_fill = "black",
        pattern_density = 0.02,
        pattern_spacing = 0.06,
        pattern_angle = 45,
        pattern_key_scale_factor = 0.6
    ) +
    coord_polar(theta = "y") +
    scale_fill_manual(values = c(
        "K" = "#493C32",
        "Mg" = "#87745D",
        "Al" = "#C5AC87",
        "Ca" = "#F1DCA7",
        "Na" = "#FFF4DC",
        "Fe" = "#FFFCF5",
        "Po"   = "#ae6433"
    )) +
    scale_pattern_manual(values = c(
        "K" = "none",
        "Mg" = "none",
        "Al" = "none",
        "Ca" = "none",
        "Na" = "none",
        "Fe" = "none",
        "Po"   = "stripe"
    )) +
    guides(
        fill = guide_legend(override.aes = list(pattern = c(
            "none", "none", "none", "none", "none", "none", "stripe"
        ))),
        pattern = "none"
    ) +
    theme_void() +
    theme(legend.position = "none")
#pdf(file = "../figures/SB.raw.xanes.pdf", width = 1, height = 1) 
print(SB.raw.xanes)
dev.off()

SB.low<-subset(XANES_melt, Land_Coverage_Category=="Sagebrush Shrubland" & Burn_Severity=="Low")
SB.low.xanes<-ggplot(SB.low, aes(x = "", y = value, fill = variable, pattern = variable)) +
    geom_col_pattern(
        color = "black",
        pattern_fill = "black",
        pattern_density = 0.02,
        pattern_spacing = 0.06,
        pattern_angle = 45,
        pattern_key_scale_factor = 0.6
    ) +
    coord_polar(theta = "y") +
    scale_fill_manual(values = c(
        "K" = "#493C32",
        "Mg" = "#87745D",
        "Al" = "#C5AC87",
        "Ca" = "#F1DCA7",
        "Na" = "#FFF4DC",
        "Fe" = "#FFFCF5",
        "Po"   = "#ae6433"
    )) +
    scale_pattern_manual(values = c(
        "K" = "none",
        "Mg" = "none",
        "Al" = "none",
        "Ca" = "none",
        "Na" = "none",
        "Fe" = "none",
        "Po"   = "stripe"
    )) +
    guides(
        fill = guide_legend(override.aes = list(pattern = c(
            "none", "none", "none", "none", "none", "none", "stripe"
        ))),
        pattern = "none"
    ) +
    theme_void() +
    theme(legend.position = "none")
#pdf(file = "../figures/SB.low.xanes.pdf", width = 1, height = 1) 
print(SB.low.xanes)
dev.off()

SB.mod<-subset(XANES_melt, Land_Coverage_Category=="Sagebrush Shrubland" & Burn_Severity=="Moderate")
SB.mod.xanes<-ggplot(SB.mod, aes(x = "", y = value, fill = variable, pattern = variable)) +
    geom_col_pattern(
        color = "black",
        pattern_fill = "black",
        pattern_density = 0.02,
        pattern_spacing = 0.06,
        pattern_angle = 45,
        pattern_key_scale_factor = 0.6
    ) +
    coord_polar(theta = "y") +
    scale_fill_manual(values = c(
        "K" = "#493C32",
        "Mg" = "#87745D",
        "Al" = "#C5AC87",
        "Ca" = "#F1DCA7",
        "Na" = "#FFF4DC",
        "Fe" = "#FFFCF5",
        "Po"   = "#ae6433"
    )) +
    scale_pattern_manual(values = c(
        "K" = "none",
        "Mg" = "none",
        "Al" = "none",
        "Ca" = "none",
        "Na" = "none",
        "Fe" = "none",
        "Po"   = "stripe"
    )) +
    guides(
        fill = guide_legend(override.aes = list(pattern = c(
            "none", "none", "none", "none", "none", "none", "stripe"
        ))),
        pattern = "none"
    ) +
    theme_void() +
    theme(legend.position = "none")
#pdf(file = "../figures/SB.mod.xanes.pdf", width = 1, height = 1) 
print(SB.mod.xanes)
dev.off()
```


```{r Ref Cmpd spectra fig}
XANES_spectra_rc_subset <-XANES_rc_spectra %>%
  dplyr::rename('Al' = 'Pi_Al_GibbSorb_std.xmu.nor',
                'Ca' = 'Pi_Apatite_CaDefHydroxy_std.xmu.nor',
                'Fe' = 'Pi_Fe_GoethSorb_std.xmu.nor',
                'K' = 'Pi_K_Pyro_std.xmu.nor',
                'Mg' = 'Pi_NH4_Mg_std.xmu.nor',
                'Mg2' = 'Pi_Mg_Tri_std.xmu.nor',
                'Na' = 'Pi_Na_Tri_std.xmu.nor',
                'Po' = 'Po_Ca_Lecithin_std.xmu.nor') %>%
  mutate_all(~replace(., . == 0, NA)) %>%
  mutate(Po = Po + 1,
         Fe = Fe + 8,
         Na = Na + 16,
         Ca = Ca + 24,
         Al = Al + 32,
         Mg = Mg + 40,
         K = K + 48) 
         
XANES_spectra_rc_subset<-melt(XANES_spectra_rc_subset, id=c("eV"))

XANES_spectra_rc_subset<-subset(XANES_spectra_rc_subset, value!="")

XANES_spectra_rc_subset<-subset(XANES_spectra_rc_subset, variable!="Mg2")

XANES_spectra_rc_subset$variable=factor(XANES_spectra_rc_subset$variable, levels= c("K", "Mg", "Al","Ca", "Na", "Fe", "Po"))

XANES_stacked_spectra_rc <- ggplot(XANES_spectra_rc_subset, aes(x = eV, y = value, color = as.factor(variable))) +
  geom_path(size = 1.25) +
  geom_vline(xintercept = 2152.3, linetype = "dashed", color = "black", size = 1) +
  theme_classic() +
  scale_color_manual(values = c("black", "black", "black", "black", "black", "black", "black")) +
  theme(
    axis.ticks.y = element_blank(),
    axis.text.y = element_blank(),
    legend.title = element_blank(),
    legend.position = "none"
  ) +
  ylab("") +
  xlab("Energy (eV)") +
  xlim(2140, 2190) +
  ylab("Normalized Absorption (arb. units)") +
  geom_text(aes(x = 2180, y = 51, label = "K-Pi"), size = 5) +
  geom_text(aes(x = 2180, y = 43, label = "Mg-Pi"), size = 5) +
  geom_text(aes(x = 2180, y = 35, label = "Al-Pi"), size = 5) +
  geom_text(aes(x = 2180, y = 27, label = "Ca-Pi"), size = 5) +
  geom_text(aes(x = 2180, y = 19, label = "Na-Pi"), size = 5) +
  geom_text(aes(x = 2180, y = 11, label = "Fe-Pi"), size = 5) +
  geom_text(aes(x = 2180, y = 4, label = "Po"), size = 5)

#pdf(file = "../figures/XANES_stacked_spectra_rc.pdf", width = 2.25, height = 9) 
print(XANES_stacked_spectra_rc)
dev.off()

```

```{r LCF figs}
#BSLE_0013-solid
BSLE_0013_solid_LCF_combined <- BSLE_0013_solid_LCF %>%
  gather(key = "component", value = "value", BSLE_0013_solid, fit, Po_Na_AMP_std.xmu, Pi_Fe_GoethSorb_std.xmu)

BSLE_0013_solid_LCF_combined<-BSLE_0013_solid_LCF_combined %>%
  mutate(component = ifelse(grepl("BSLE", component), "Sample", component)) %>%
  mutate(component = ifelse(grepl("fit", component), "Fit", component)) %>%
  mutate(component = ifelse(grepl("Pi_K", component), "K-Pi", component)) %>%
  mutate(component = ifelse(grepl("Pi_Mg", component), "Mg-Pi", component)) %>%
  mutate(component = ifelse(grepl("Pi_Al", component), "Al-Pi", component)) %>%
  mutate(component = ifelse(grepl("Pi_Ca", component), "Ca-Pi", component)) %>%
  mutate(component = ifelse(grepl("Apatite", component), "Ca-Pi", component)) %>%
  mutate(component = ifelse(grepl("Pi_Na", component), "Na-Pi", component)) %>%
  mutate(component = ifelse(grepl("Pi_Fe", component), "Fe-Pi", component)) %>%
  mutate(component = ifelse(grepl("Po", component), "Po", component)) %>%
  mutate(component = factor(component, levels = c("Sample", "Fit", "K-Pi", "Mg-Pi", "Al-Pi", "Ca-Pi", "Na-Pi", "Fe-Pi", "Po")))

LCF13<-ggplot(BSLE_0013_solid_LCF_combined, aes(x = eV, y = value, color = component, linetype = component)) +
    geom_line(size=1.5) +
    scale_color_manual(
        values = c("Sample" = "black", "Fit" = "#565e60", "Po" = "#ae6433", "Fe-Pi" = "#493C32"),
        name = NULL 
    ) +
    scale_linetype_manual(
        values = c("Sample" = "solid", "Fit" = "dashed", "Po" = "solid", "Fe-Pi" = "solid"),
        name = NULL 
    ) +
    xlab("Energy (eV)") +
    xlim(2140, 2200) +
    ylab("Normalized Absorption (arb. units)") +
    theme_classic()+
    theme(axis.text.y = element_blank())  +
  theme(legend.position = c(0.85, 0.85), legend.justification = c(1, 1))

#pdf(file = "../figures/LCF13.pdf", width = 3, height = 3) 
print(LCF13)
dev.off()

#BSLE_0007-solid
BSLE_0007_solid_LCF_combined <- BSLE_0007_solid_LCF %>%
  gather(key = "component", value = "value", BSLE_0007_solid, fit, Pi_Na_Tri_std.xmu, Pi_Apatite_CaDefHydroxy_std.xmu, Pi_Al_GibbSorb_std.xmu)

BSLE_0007_solid_LCF_combined<-BSLE_0007_solid_LCF_combined %>%
  mutate(component = ifelse(grepl("BSLE", component), "Sample", component)) %>%
  mutate(component = ifelse(grepl("fit", component), "Fit", component)) %>%
  mutate(component = ifelse(grepl("Pi_K", component), "K-Pi", component)) %>%
  mutate(component = ifelse(grepl("Pi_Mg", component), "Mg-Pi", component)) %>%
  mutate(component = ifelse(grepl("Pi_Al", component), "Al-Pi", component)) %>%
  mutate(component = ifelse(grepl("Pi_Ca", component), "Ca-Pi", component)) %>%
  mutate(component = ifelse(grepl("Apatite", component), "Ca-Pi", component)) %>%
  mutate(component = ifelse(grepl("Pi_Na", component), "Na-Pi", component)) %>%
  mutate(component = ifelse(grepl("Pi_Fe", component), "Fe-Pi", component)) %>%
  mutate(component = ifelse(grepl("Po", component), "Po", component)) %>%
  mutate(component = factor(component, levels = c("Sample", "Fit", "K-Pi", "Mg-Pi", "Al-Pi", "Ca-Pi", "Na-Pi", "Fe-Pi", "Po")))

LCF7<-ggplot(BSLE_0007_solid_LCF_combined, aes(x = eV, y = value, color = component, linetype = component)) +
    geom_line(size=1.5) +
    scale_color_manual(
        values = c("Sample" = "black", "Fit" = "#565e60", "Na-Pi" = "#C5AC87", "Ca-Pi" = "#87745D", "Al-Pi" = "#493C32"), 
        name = NULL
    ) +
    scale_linetype_manual(
        values = c("Sample" = "solid", "Fit" = "dashed", "Na-Pi" = "solid", "Ca-Pi" = "solid", "Al-Pi" = "solid"),
        name = NULL
    ) +
    xlab("Energy (eV)") +
    xlim(2140, 2200) +
    ylab("Normalized Absorption (arb. units)") +
    theme_classic()+
    theme(axis.text.y = element_blank()) +
  theme(legend.position = c(0.85, 0.85), legend.justification = c(1, 1))

#pdf(file = "../figures/LCF7.pdf", width = 3, height = 3) 
print(LCF7)
dev.off()


#BSLE_0002-solid
BSLE_0002_solid_LCF_combined <- BSLE_0002_solid_LCF %>%
  gather(key = "component", value = "value", BSLE_0002_solid, fit, Pi_Na_Tri_std.xmu, Pi_Mg_Tri_std.xmu, Pi_Apatite_CaDefHydroxy_std.xmu)

BSLE_0002_solid_LCF_combined<-BSLE_0002_solid_LCF_combined %>%
  mutate(component = ifelse(grepl("BSLE", component), "Sample", component)) %>%
  mutate(component = ifelse(grepl("fit", component), "Fit", component)) %>%
  mutate(component = ifelse(grepl("Pi_K", component), "K-Pi", component)) %>%
  mutate(component = ifelse(grepl("Pi_Mg", component), "Mg-Pi", component)) %>%
  mutate(component = ifelse(grepl("Pi_Al", component), "Al-Pi", component)) %>%
  mutate(component = ifelse(grepl("Pi_Ca", component), "Ca-Pi", component)) %>%
  mutate(component = ifelse(grepl("Apatite", component), "Ca-Pi", component)) %>%
  mutate(component = ifelse(grepl("Pi_Na", component), "Na-Pi", component)) %>%
  mutate(component = ifelse(grepl("Pi_Fe", component), "Fe-Pi", component)) %>%
  mutate(component = ifelse(grepl("Po", component), "Po", component)) %>%
  mutate(component = factor(component, levels = c("Sample", "Fit", "K-Pi", "Mg-Pi", "Al-Pi", "Ca-Pi", "Na-Pi", "Fe-Pi", "Po")))

LCF2<-ggplot(BSLE_0002_solid_LCF_combined, aes(x = eV, y = value, color = component, linetype = component)) +
    geom_line(size=1.5) +
    scale_color_manual(
        values = c("Sample" = "black", "Fit" = "#565e60", "Na-Pi" = "#C5AC87", "Mg-Pi" = "#87745D", "Ca-Pi" = "#493C32"),
        name = NULL
    ) +
    scale_linetype_manual(
        values = c("Sample" = "solid", "Fit" = "dashed", "Na-Pi" = "solid", "Mg-Pi" = "solid", "Ca-Pi" = "solid"),
        name = NULL
    ) +
    xlab("Energy (eV)") +
    xlim(2140, 2200) +
    ylab("Normalized Absorption (arb. units)") +
    theme_classic()+
    theme(axis.text.y = element_blank()) +
  theme(legend.position = c(0.85, 0.85), legend.justification = c(1, 1))

#pdf(file = "../figures/LCF2.pdf", width = 3, height = 3) 
print(LCF2)
dev.off()


#BSLE_0050-solid
BSLE_0050_solid_LCF_combined <- BSLE_0050_solid_LCF %>%
  gather(key = "component", value = "value", BSLE_0050_solid, fit, Pi_Mg_Tri_std.xmu, Pi_Ca_Tri_std.xmu, Pi_Apatite_CaDefHydroxy_std.xmu)

BSLE_0050_solid_LCF_combined<-BSLE_0050_solid_LCF_combined %>%
  mutate(component = ifelse(grepl("BSLE", component), "Sample", component)) %>%
  mutate(component = ifelse(grepl("fit", component), "Fit", component)) %>%
  mutate(component = ifelse(grepl("Pi_K", component), "K-Pi", component)) %>%
  mutate(component = ifelse(grepl("Pi_Mg", component), "Mg-Pi", component)) %>%
  mutate(component = ifelse(grepl("Pi_Al", component), "Al-Pi", component)) %>%
  mutate(component = ifelse(grepl("Pi_Ca", component), "Ca-Pi (1)", component)) %>%
  mutate(component = ifelse(grepl("Apatite", component), "Ca-Pi (2)", component)) %>%
  mutate(component = ifelse(grepl("Pi_Na", component), "Na-Pi", component)) %>%
  mutate(component = ifelse(grepl("Pi_Fe", component), "Fe-Pi", component)) %>%
  mutate(component = ifelse(grepl("Po", component), "Po", component)) %>%
  mutate(component = factor(component, levels = c("Sample", "Fit", "K-Pi", "Mg-Pi", "Al-Pi", "Ca-Pi (1)", "Ca-Pi (2)", "Na-Pi", "Fe-Pi", "Po")))

LCF50<-ggplot(BSLE_0050_solid_LCF_combined, aes(x = eV, y = value, color = component, linetype = component)) +
    geom_line(size=1.5) +
    scale_color_manual(
        values = c("Sample" = "black", "Fit" = "#565e60", "Mg-Pi" = "#C5AC87", "Ca-Pi (1)" = "#493C32", "Ca-Pi (2)" = "#87745D"),
        name = NULL
    ) +
    scale_linetype_manual(
        values = c("Sample" = "solid", "Fit" = "dashed", "Mg-Pi" = "solid", "Ca-Pi (1)" = "solid", "Ca-Pi (2)" = "solid"),
        name = NULL
    ) +
    xlab("Energy (eV)") +
    xlim(2140, 2200) +
    ylab("Normalized Absorption (arb. units)") +
    theme_classic()+
    theme(axis.text.y = element_blank()) +
  theme(legend.position = c(0.85, 0.90), legend.justification = c(1, 1))

#pdf(file = "../figures/LCF50.pdf", width = 3, height = 3) 
print(LCF50)
dev.off()


#BSLE_0014-solid
BSLE_0014_solid_LCF_combined <- BSLE_0014_solid_LCF %>%
  gather(key = "component", value = "value", BSLE_0014_solid, fit, Po_Na_AMP_std.xmu, Pi_Fe_GoethSorb_std.xmu, Pi_Apatite_CaDefHydroxy_std.xmu)

BSLE_0014_solid_LCF_combined<-BSLE_0014_solid_LCF_combined %>%
  mutate(component = ifelse(grepl("BSLE", component), "Sample", component)) %>%
  mutate(component = ifelse(grepl("fit", component), "Fit", component)) %>%
  mutate(component = ifelse(grepl("Pi_K", component), "K-Pi", component)) %>%
  mutate(component = ifelse(grepl("Pi_Mg", component), "Mg-Pi", component)) %>%
  mutate(component = ifelse(grepl("Pi_Al", component), "Al-Pi", component)) %>%
  mutate(component = ifelse(grepl("Pi_Ca", component), "Ca-Pi", component)) %>%
  mutate(component = ifelse(grepl("Apatite", component), "Ca-Pi", component)) %>%
  mutate(component = ifelse(grepl("Pi_Na", component), "Na-Pi", component)) %>%
  mutate(component = ifelse(grepl("Pi_Fe", component), "Fe-Pi", component)) %>%
  mutate(component = ifelse(grepl("Po", component), "Po", component)) %>%
  mutate(component = factor(component, levels = c("Sample", "Fit", "K-Pi", "Mg-Pi", "Al-Pi", "Ca-Pi", "Na-Pi", "Fe-Pi", "Po")))

LCF14<-ggplot(BSLE_0014_solid_LCF_combined, aes(x = eV, y = value, color = component, linetype = component)) +
    geom_line(size=1.5) +
    scale_color_manual(
        values = c("Sample" = "black", "Fit" = "#565e60", "Po" = "#ae6433", "Fe-Pi" = "#87745D", "Ca-Pi" = "#493C32"),
        name = NULL 
    ) +
    scale_linetype_manual(
        values = c("Sample" = "solid", "Fit" = "dashed", "Po" = "solid", "Fe-Pi" = "solid", "Ca-Pi" = "solid"),
        name = NULL
    ) +
    xlab("Energy (eV)") +
    xlim(2140, 2200) +
    ylab("Normalized Absorption (arb. units)") +
    theme_classic()+
    theme(axis.text.y = element_blank()) +
  theme(legend.position = c(0.85, 0.85), legend.justification = c(1, 1))

#pdf(file = "../figures/LCF14.pdf", width = 3, height = 3) 
print(LCF14)
dev.off()


#BSLE_0011-solid
BSLE_0011_solid_LCF_combined <- BSLE_0011_solid_LCF %>%
  gather(key = "component", value = "value", BSLE_0011_solid, fit, Pi_Mg_Tri_std.xmu, Pi_K_Pyro_std.xmu, Pi_Apatite_CaDefHydroxy_std.xmu)

BSLE_0011_solid_LCF_combined<-BSLE_0011_solid_LCF_combined %>%
  mutate(component = ifelse(grepl("BSLE", component), "Sample", component)) %>%
  mutate(component = ifelse(grepl("fit", component), "Fit", component)) %>%
  mutate(component = ifelse(grepl("Pi_K", component), "K-Pi", component)) %>%
  mutate(component = ifelse(grepl("Pi_Mg", component), "Mg-Pi", component)) %>%
  mutate(component = ifelse(grepl("Pi_Al", component), "Al-Pi", component)) %>%
  mutate(component = ifelse(grepl("Pi_Ca", component), "Ca-Pi", component)) %>%
  mutate(component = ifelse(grepl("Apatite", component), "Ca-Pi", component)) %>%
  mutate(component = ifelse(grepl("Pi_Na", component), "Na-Pi", component)) %>%
  mutate(component = ifelse(grepl("Pi_Fe", component), "Fe-Pi", component)) %>%
  mutate(component = ifelse(grepl("Po", component), "Po", component)) %>%
  mutate(component = factor(component, levels = c("Sample", "Fit", "K-Pi", "Mg-Pi", "Al-Pi", "Ca-Pi", "Na-Pi", "Fe-Pi", "Po")))

LCF11<-ggplot(BSLE_0011_solid_LCF_combined, aes(x = eV, y = value, color = component, linetype = component)) +
    geom_line(size=1.5) +
    scale_color_manual(
        values = c("Sample" = "black", "Fit" = "#565e60", "Mg-Pi" = "#C5AC87", "K-Pi" = "#87745D", "Ca-Pi" = "#493C32"),
        name = NULL
    ) +
    scale_linetype_manual(
        values = c("Sample" = "solid", "Fit" = "dashed", "Mg-Pi" = "solid", "K-Pi" = "solid", "Ca-Pi" = "solid"),
        name = NULL
    ) +
    xlab("Energy (eV)") +
    xlim(2140, 2200) +
    ylab("Normalized Absorption (arb. units)") +
    theme_classic()+
    theme(axis.text.y = element_blank()) +
  theme(legend.position = c(0.85, 0.85), legend.justification = c(1, 1))

#pdf(file = "../figures/LCF11.pdf", width = 3, height = 3) 
print(LCF11)
dev.off()


#BSLE_0072-solid
BSLE_0072_solid_LCF_combined <- BSLE_0072_solid_LCF %>%
  gather(key = "component", value = "value", BSLE_0072_solid, fit, Pi_NH4_Mg_std.xmu, Pi_Apatite_Carbonate_std.xmu, Pi_Apatite_CaDefHydroxy_std.xmu)

BSLE_0072_solid_LCF_combined<-BSLE_0072_solid_LCF_combined %>%
  mutate(component = ifelse(grepl("BSLE", component), "Sample", component)) %>%
  mutate(component = ifelse(grepl("fit", component), "Fit", component)) %>%
  mutate(component = ifelse(grepl("Pi_K", component), "K-Pi", component)) %>%
  mutate(component = ifelse(grepl("Pi_Mg", component), "Mg-Pi", component)) %>%
  mutate(component = ifelse(grepl("Pi_Al", component), "Al-Pi", component)) %>%
  mutate(component = ifelse(grepl("Carbonate", component), "Ca-Pi (1)", component)) %>%
  mutate(component = ifelse(grepl("Hydroxy", component), "Ca-Pi (2)", component)) %>%
  mutate(component = ifelse(grepl("Pi_Na", component), "Na-Pi", component)) %>%
  mutate(component = ifelse(grepl("Pi_Fe", component), "Fe-Pi", component)) %>%
  mutate(component = ifelse(grepl("Po", component), "Po", component)) %>%
  mutate(component = factor(component, levels = c("Sample", "Fit", "K-Pi", "Mg-Pi", "Al-Pi", "Ca-Pi (1)", "Ca-Pi (2)", "Na-Pi", "Fe-Pi", "Po")))

LCF72<-ggplot(BSLE_0072_solid_LCF_combined, aes(x = eV, y = value, color = component, linetype = component)) +
    geom_line(size=1.5) +
    scale_color_manual(
        values = c("Sample" = "black", "Fit" = "#565e60", "NH4-Pi" = "#C5AC87", "Ca-Pi (1)" = "#493C32", "Ca-Pi (2)" = "#87745D"),
        name = NULL
    ) +
    scale_linetype_manual(
        values = c("Sample" = "solid", "Fit" = "dashed", "NH4-Pi" = "solid", "Ca-Pi (1)" = "solid", "Ca-Pi (2)" = "solid"),
        name = NULL
    ) +
    xlab("Energy (eV)") +
    xlim(2140, 2200) +
    ylab("Normalized Absorption (arb. units)") +
    theme_classic()+
    theme(axis.text.y = element_blank()) +
  theme(legend.position = c(0.85, 0.85), legend.justification = c(1, 1))

#pdf(file = "../figures/LCF72.pdf", width = 3, height = 3) 
print(LCF72)
dev.off()


```

##Leachates
###Leachable P
```{r total P and MBD figs}
#relationship of leachable total P or molybdate-reactive P in solid chars with burn severity and vegetation type

#Leachable P (normalized by concentration of solid char) of total particulate and total aqueous P
leach.fig<-data %>%
  select(Burn_Severity, Land_Coverage_Category, Leachate_mg_P_per_g_P_in_solid_part, Leachate_mg_P_per_g_P_in_solid_filt0.7, Leachate_mg_MBD_per_g_P_in_solid_filt0.7, Leachate_mg_nonMBD_per_g_P_in_solid_filt0.7) %>%
  mutate(Land_Coverage_Category = if_else(Land_Coverage_Category == "Douglas-fir forest", "Douglas-fir Forest", Land_Coverage_Category)) %>%
  mutate(Land_Coverage_Category = if_else(Land_Coverage_Category == "Sagebrush shrubland", "Sagebrush Shrubland", Land_Coverage_Category))

leach.fig<-melt(leach.fig, id =c("Burn_Severity", "Land_Coverage_Category"))

leach.fig <- leach.fig %>%
  mutate(
    variable = case_when(
      variable == "Leachate_mg_P_per_g_P_in_solid_part" ~ "Particulate Total",
      variable == "Leachate_mg_P_per_g_P_in_solid_filt0.7" ~ "Aqueous Total",
      variable == "Leachate_mg_MBD_per_g_P_in_solid_filt0.7" ~ "Aqueous Molybdate Reactive",
          variable == "Leachate_mg_nonMBD_per_g_P_in_solid_filt0.7" ~ "Aqueous Non-Molybdate Reactive"),
    Annotation = case_when(
      variable == "Particulate Total" & Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "Unburned" ~ "a",
      variable == "Particulate Total" & Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "Low" ~ "a",
      variable == "Particulate Total" & Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "Moderate" ~ "ab",
      variable == "Particulate Total" & Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "High" ~ "b",
      variable == "Particulate Total" & Land_Coverage_Category == "Sagebrush Shrubland" & Burn_Severity == "Unburned" ~ "a",
      variable == "Particulate Total" & Land_Coverage_Category == "Sagebrush Shrubland" & Burn_Severity == "Low" ~ "a",
      variable == "Particulate Total" & Land_Coverage_Category == "Sagebrush Shrubland" & Burn_Severity == "Moderate" ~ "b",
      variable == "Aqueous Total" & Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "Unburned" ~ "a",
      variable == "Aqueous Total" & Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "Low" ~ "a",
      variable == "Aqueous Total" & Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "Moderate" ~ "ab",
      variable == "Aqueous Total" & Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "High" ~ "b",
      variable == "Aqueous Total" & Land_Coverage_Category == "Sagebrush Shrubland" & Burn_Severity == "Unburned" ~ "a",
      variable == "Aqueous Total" & Land_Coverage_Category == "Sagebrush Shrubland" & Burn_Severity == "Low" ~ "a",
      variable == "Aqueous Total" & Land_Coverage_Category == "Sagebrush Shrubland" & Burn_Severity == "Moderate" ~ "b",
      variable == "Aqueous Molybdate Reactive" & Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "Unburned" ~ "a",
      variable == "Aqueous Molybdate Reactive" & Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "Low" ~ "a",
      variable == "Aqueous Molybdate Reactive" & Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "Moderate" ~ "a",
      variable == "Aqueous Molybdate Reactive" & Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "High" ~ "a",
      variable == "Aqueous Molybdate Reactive" & Land_Coverage_Category == "Sagebrush Shrubland" & Burn_Severity == "Unburned" ~ "a",
      variable == "Aqueous Molybdate Reactive" & Land_Coverage_Category == "Sagebrush Shrubland" & Burn_Severity == "Low" ~ "a",
      variable == "Aqueous Molybdate Reactive" & Land_Coverage_Category == "Sagebrush Shrubland" & Burn_Severity == "Moderate" ~ "b",
      variable == "Aqueous Non-Molybdate Reactive" & Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "Unburned" ~ "ab",
      variable == "Aqueous Non-Molybdate Reactive" & Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "Low" ~ "a",
      variable == "Aqueous Non-Molybdate Reactive" & Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "Moderate" ~ "ab",
      variable == "Aqueous Non-Molybdate Reactive" & Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "High" ~ "b",
      variable == "Aqueous Non-Molybdate Reactive" & Land_Coverage_Category == "Sagebrush Shrubland" & Burn_Severity == "Unburned" ~ "a",
      variable == "Aqueous Non-Molybdate Reactive" & Land_Coverage_Category == "Sagebrush Shrubland" & Burn_Severity == "Low" ~ "a",
      variable == "Aqueous Non-Molybdate Reactive" & Land_Coverage_Category == "Sagebrush Shrubland" & Burn_Severity == "Moderate" ~ "b"),
    x = case_when(
      variable == "Particulate Total" & Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "Unburned" ~ "Unburned",
      variable == "Particulate Total" & Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "Low" ~ "Low",
      variable == "Particulate Total" & Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "Moderate" ~ "Moderate",
      variable == "Particulate Total" & Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "High" ~ "High",
      variable == "Particulate Total" & Land_Coverage_Category == "Sagebrush Shrubland" & Burn_Severity == "Unburned" ~ "Unburned",
      variable == "Particulate Total" & Land_Coverage_Category == "Sagebrush Shrubland" & Burn_Severity == "Low" ~ "Low",
      variable == "Particulate Total" & Land_Coverage_Category == "Sagebrush Shrubland" & Burn_Severity == "Moderate" ~ "Moderate",
      variable == "Aqueous Total" & Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "Unburned" ~ "Unburned",
      variable == "Aqueous Total" & Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "Low" ~ "Low",
      variable == "Aqueous Total" & Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "Moderate" ~ "Moderate",
      variable == "Aqueous Total" & Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "High" ~ "High",
      variable == "Aqueous Total" & Land_Coverage_Category == "Sagebrush Shrubland" & Burn_Severity == "Unburned" ~ "Unburned",
      variable == "Aqueous Total" & Land_Coverage_Category == "Sagebrush Shrubland" & Burn_Severity == "Low" ~ "Low",
      variable == "Aqueous Total" & Land_Coverage_Category == "Sagebrush Shrubland" & Burn_Severity == "Moderate" ~ "Moderate",
      variable == "Aqueous Molybdate Reactive" & Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "Unburned" ~ "Unburned",
      variable == "Aqueous Molybdate Reactive" & Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "Low" ~ "Low",
      variable == "Aqueous Molybdate Reactive" & Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "Moderate" ~ "Moderate",
      variable == "Aqueous Molybdate Reactive" & Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "High" ~ "High",
      variable == "Aqueous Molybdate Reactive" & Land_Coverage_Category == "Sagebrush Shrubland" & Burn_Severity == "Unburned" ~ "Unburned",
      variable == "Aqueous Molybdate Reactive" & Land_Coverage_Category == "Sagebrush Shrubland" & Burn_Severity == "Low" ~ "Low",
      variable == "Aqueous Molybdate Reactive" & Land_Coverage_Category == "Sagebrush Shrubland" & Burn_Severity == "Moderate" ~ "Moderate",
      variable == "Aqueous Non-Molybdate Reactive" & Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "Unburned" ~ "Unburned",
      variable == "Aqueous Non-Molybdate Reactive" & Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "Low" ~ "Low",
      variable == "Aqueous Non-Molybdate Reactive" & Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "Moderate" ~ "Moderate",
      variable == "Aqueous Non-Molybdate Reactive" & Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "High" ~ "High",
      variable == "Aqueous Non-Molybdate Reactive" & Land_Coverage_Category == "Sagebrush Shrubland" & Burn_Severity == "Unburned" ~ "Unburned",
      variable == "Aqueous Non-Molybdate Reactive" & Land_Coverage_Category == "Sagebrush Shrubland" & Burn_Severity == "Low" ~ "Low",
      variable == "Aqueous Non-Molybdate Reactive" & Land_Coverage_Category == "Sagebrush Shrubland" & Burn_Severity == "Moderate" ~ "Moderate"),
    y = case_when(
      variable == "Particulate Total" & Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "Unburned" ~ 300,
      variable == "Particulate Total" & Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "Low" ~ 255,
      variable == "Particulate Total" & Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "Moderate" ~ 250,
      variable == "Particulate Total" & Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "High" ~ 925,
      variable == "Particulate Total" & Land_Coverage_Category == "Sagebrush Shrubland" & Burn_Severity == "Unburned" ~ 110,
      variable == "Particulate Total" & Land_Coverage_Category == "Sagebrush Shrubland" & Burn_Severity == "Low" ~ 180,
      variable == "Particulate Total" & Land_Coverage_Category == "Sagebrush Shrubland" & Burn_Severity == "Moderate" ~ 905,
      variable == "Aqueous Total" & Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "Unburned" ~ 110,
      variable == "Aqueous Total" & Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "Low" ~ 140,
      variable == "Aqueous Total" & Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "Moderate" ~ 110,
      variable == "Aqueous Total" & Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "High" ~ 85,
      variable == "Aqueous Total" & Land_Coverage_Category == "Sagebrush Shrubland" & Burn_Severity == "Unburned" ~ 270,
      variable == "Aqueous Total" & Land_Coverage_Category == "Sagebrush Shrubland" & Burn_Severity == "Low" ~ 125,
      variable == "Aqueous Total" & Land_Coverage_Category == "Sagebrush Shrubland" & Burn_Severity == "Moderate" ~ 30,
      variable == "Aqueous Molybdate Reactive" & Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "Unburned" ~ 100,
      variable == "Aqueous Molybdate Reactive" & Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "Low" ~ 130,
      variable == "Aqueous Molybdate Reactive" & Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "Moderate" ~ 90,
      variable == "Aqueous Molybdate Reactive" & Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "High" ~ 70,
      variable == "Aqueous Molybdate Reactive" & Land_Coverage_Category == "Sagebrush Shrubland" & Burn_Severity == "Unburned" ~ 175,
      variable == "Aqueous Molybdate Reactive" & Land_Coverage_Category == "Sagebrush Shrubland" & Burn_Severity == "Low" ~ 90,
      variable == "Aqueous Molybdate Reactive" & Land_Coverage_Category == "Sagebrush Shrubland" & Burn_Severity == "Moderate" ~ 35,
      variable == "Aqueous Non-Molybdate Reactive" & Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "Unburned" ~ 40,
      variable == "Aqueous Non-Molybdate Reactive" & Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "Low" ~ 45,
      variable == "Aqueous Non-Molybdate Reactive" & Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "Moderate" ~ 45,
      variable == "Aqueous Non-Molybdate Reactive" & Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "High" ~ 35,
      variable == "Aqueous Non-Molybdate Reactive" & Land_Coverage_Category == "Sagebrush Shrubland" & Burn_Severity == "Unburned" ~ 110,
      variable == "Aqueous Non-Molybdate Reactive" & Land_Coverage_Category == "Sagebrush Shrubland" & Burn_Severity == "Low" ~ 80,
      variable == "Aqueous Non-Molybdate Reactive" & Land_Coverage_Category == "Sagebrush Shrubland" & Burn_Severity == "Moderate" ~ 26),
    Burn_Severity = case_when(
      Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "Unburned" ~ "Unburned",
      Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "Low" ~ "Low",
      Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "Moderate" ~ "Moderate",
      Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "High" ~ "High",
      Land_Coverage_Category == "Sagebrush Shrubland" & Burn_Severity == "Unburned" ~ "Unburned",
      Land_Coverage_Category == "Sagebrush Shrubland" & Burn_Severity == "Low" ~ "Low",
      Land_Coverage_Category == "Sagebrush Shrubland" & Burn_Severity == "Moderate" ~ "Moderate",
      TRUE ~ as.character(Burn_Severity)),
    Burn_Severity = factor(Burn_Severity, levels = c("Unburned", "Low", "Moderate", "High")),
    variable = factor(variable, levels = c("Particulate Total", "Aqueous Total", "Aqueous Molybdate Reactive", "Aqueous Non-Molybdate Reactive"))
    )

leach.fig.stack<-leach.fig %>%
  filter(str_detect(variable, "Total"))

leach.Pnorm.conc<-ggplot(leach.fig.stack, aes(x = Burn_Severity, y = value, fill = Land_Coverage_Category)) +
  geom_boxplot(show.legend = FALSE) +
  theme_classic() +
  ylab(expression(paste(Leachable~P~(mg~g^-1), sep = ""))) +
  xlab("Burn Severity") +
  scale_fill_manual(values = c("lightgray","lightgray")) +
  facet_grid(variable ~ Land_Coverage_Category, scales = "free") +
  scale_x_discrete(labels = split_labels_with_parentheses) +
  theme(
    text = element_text(size = 15),
    panel.border = element_rect(color = "black", fill = NA, linewidth = 1)
  ) + geom_text(aes(label = Annotation, x = x, y = y), size = 4.5, fontface = "plain")

leach.Pnorm.conc
#cowplot::save_plot("../figures/leach.Pnorm.conc.pdf", leach.Pnorm.conc, ncol = 1, nrow = 1, base_height = 6, base_aspect_ratio= 1:1, dpi=100)



#leachable molybdate reactive and non-reactive P figure
leach.fig.mbd<-leach.fig %>%
  filter(str_detect(variable, "Molybdate")) %>%
  mutate(variable = case_when(
    variable == "Aqueous Molybdate Reactive" ~ "Molybdate Reactive",
    variable == "Aqueous Non-Molybdate Reactive" ~ "Non-Molybdate Reactive",
    TRUE ~ variable
  ))

leach.Pnorm.conc.mbd<-ggplot(leach.fig.mbd, aes(x = Burn_Severity, y = value, fill = Land_Coverage_Category)) +
    geom_boxplot(show.legend = FALSE) +
    theme_classic() +
    ylab(expression(paste("Leachable Aqueous P (mg g"^"-1"*")"))) +
    xlab("Burn Severity") +
    scale_fill_manual(values = c("#9B9B7A","#FFCB69")) +
    scale_x_discrete(labels = split_labels_with_parentheses) +
    theme(
        text = element_text(size = 15),
        axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1),
        panel.border = element_rect(color = "black", fill = NA, linewidth = 1)
    ) +
    geom_text(aes(label = Annotation, x = x, y = y), size = 4.5, fontface = "plain")+
  facet_grid(variable ~ Land_Coverage_Category, scales = "free_x")

leach.Pnorm.conc.mbd
#cowplot::save_plot("../figures/leach.Pnorm.conc.mbd.pdf", leach.Pnorm.conc.mbd, ncol = 1, nrow = 1, base_height = 6, base_width = 5.5, base_aspect_ratio= 1:1, dpi=100)
```

```{r total P and MBD stats}
#relationship of leachable total P or molybdate-reactive P in solid chars with burn severity and vegetation type

#Leachable total P in particulate phase (>0.7 nominal phase); normalized to total P in solid char
model<-lmer(log10(Leachate_mg_P_per_g_P_in_solid_part)~Burn_Severity*Land_Coverage_Category+(1|Parent_ID), data=data)
model.BS<-lmer(log10(Leachate_mg_P_per_g_P_in_solid_part)~Land_Coverage_Category+(1|Parent_ID), data=data)
model.LC<-lmer(log10(Leachate_mg_P_per_g_P_in_solid_part)~Burn_Severity+(1|Parent_ID), data=data)
model.int<-lmer(log10(Leachate_mg_P_per_g_P_in_solid_part)~Burn_Severity+Land_Coverage_Category+(1|Parent_ID), data=data)
anova(model,model.BS)
anova(model,model.LC)
anova(model,model.int)
#check VIF
vif(model)
#model assumptions
hist(log10(data$Leachate_mg_P_per_g_P_in_solid_part))
ggqqplot(residuals(model))
plot(lmer(log10(Leachate_mg_P_per_g_P_in_solid_part)~Burn_Severity*Land_Coverage_Category+(1|Parent_ID), data=data))
#interaction post hoc: 
emmeans::lsmeans(model, pairwise~Burn_Severity*Land_Coverage_Category, at=list(Burn_Severity="Unburned"),adjust="tukey") 
emmeans::lsmeans(model, pairwise~Burn_Severity*Land_Coverage_Category, at=list(Burn_Severity="Low"),adjust="tukey")
emmeans::lsmeans(model, pairwise~Burn_Severity*Land_Coverage_Category, at=list(Burn_Severity="Moderate"),adjust="tukey") 
emmeans::lsmeans(model, pairwise~Burn_Severity*Land_Coverage_Category, at=list(Land_Coverage_Category="Douglas-fir Forest"),adjust="tukey") 
emmeans::lsmeans(model, pairwise~Burn_Severity*Land_Coverage_Category, at=list(Land_Coverage_Category="Sagebrush Shrubland"),adjust="tukey") 


#Leachable total P in aqueous phase (<0.7 nominal phase); normalized to total P in solid char
model<-lmer(log10(Leachate_mg_P_per_g_P_in_solid_filt0.7)~Burn_Severity*Land_Coverage_Category+(1|Parent_ID), data=data)
model.BS<-lmer(log10(Leachate_mg_P_per_g_P_in_solid_filt0.7)~Land_Coverage_Category+(1|Parent_ID), data=data)
model.LC<-lmer(log10(Leachate_mg_P_per_g_P_in_solid_filt0.7)~Burn_Severity+(1|Parent_ID), data=data)
model.int<-lmer(log10(Leachate_mg_P_per_g_P_in_solid_filt0.7)~Burn_Severity+Land_Coverage_Category+(1|Parent_ID), data=data)
anova(model,model.BS)
anova(model,model.LC)
anova(model,model.int)
#check VIF
vif(model)
#model assumptions
hist(log10(data$Leachate_mg_P_per_g_P_in_solid_filt0.7))
ggqqplot(residuals(model))
plot(lmer(log10(Leachate_mg_P_per_g_P_in_solid_filt0.7)~Burn_Severity*Land_Coverage_Category+(1|Parent_ID), data=data))
#interaction post hoc: 
emmeans::lsmeans(model, pairwise~Burn_Severity*Land_Coverage_Category, at=list(Burn_Severity="Unburned"),adjust="tukey") 
emmeans::lsmeans(model, pairwise~Burn_Severity*Land_Coverage_Category, at=list(Burn_Severity="Low"),adjust="tukey") 
emmeans::lsmeans(model, pairwise~Burn_Severity*Land_Coverage_Category, at=list(Burn_Severity="Moderate"),adjust="tukey") 
emmeans::lsmeans(model, pairwise~Burn_Severity*Land_Coverage_Category, at=list(Land_Coverage_Category="Douglas-fir Forest"),adjust="tukey") 
emmeans::lsmeans(model, pairwise~Burn_Severity*Land_Coverage_Category, at=list(Land_Coverage_Category="Sagebrush Shrubland"),adjust="tukey")


#Leachable molybdate reactive P in aqueous phase (<0.7 nominal phase); normalized to total P in solid char 
model<-lmer(log10(Leachate_mg_MBD_per_g_P_in_solid_filt0.7)~Burn_Severity*Land_Coverage_Category+(1|Parent_ID), data=data)
model.BS<-lmer(log10(Leachate_mg_MBD_per_g_P_in_solid_filt0.7)~Land_Coverage_Category+(1|Parent_ID), data=data)
model.LC<-lmer(log10(Leachate_mg_MBD_per_g_P_in_solid_filt0.7)~Burn_Severity+(1|Parent_ID), data=data)
model.int<-lmer(log10(Leachate_mg_MBD_per_g_P_in_solid_filt0.7)~Burn_Severity+Land_Coverage_Category+(1|Parent_ID), data=data)
anova(model,model.BS)
anova(model,model.LC)
anova(model,model.int)
#check VIF
vif(model)
#model assumptions
hist(log10(data$Leachate_mg_MBD_per_g_P_in_solid_filt0.7))
ggqqplot(residuals(model))
plot(lmer(log10(Leachate_mg_MBD_per_g_P_in_solid_filt0.7)~Burn_Severity*Land_Coverage_Category+(1|Parent_ID), data=data))
#post hoc tests for interaction term
emmeans::lsmeans(model, pairwise~Burn_Severity*Land_Coverage_Category, at=list(Burn_Severity="Unburned"),adjust="tukey")
emmeans::lsmeans(model, pairwise~Burn_Severity*Land_Coverage_Category, at=list(Burn_Severity="Low"),adjust="tukey")
emmeans::lsmeans(model, pairwise~Burn_Severity*Land_Coverage_Category, at=list(Burn_Severity="Moderate"),adjust="tukey")
emmeans::lsmeans(model, pairwise~Burn_Severity*Land_Coverage_Category, at=list(Land_Coverage_Category="Douglas-fir Forest"),adjust="tukey")
emmeans::lsmeans(model, pairwise~Burn_Severity*Land_Coverage_Category, at=list(Land_Coverage_Category="Sagebrush Shrubland"),adjust="tukey")


#Leachable non-molybdate reactive P in aqueous phase (<0.7 nominal phase); normalized to total P in solid char
model<-lmer(log10(Leachate_mg_nonMBD_per_g_P_in_solid_filt0.7+1)~Burn_Severity*Land_Coverage_Category+(1|Parent_ID), data=data)
model.BS<-lmer(log10(Leachate_mg_nonMBD_per_g_P_in_solid_filt0.7+1)~Land_Coverage_Category+(1|Parent_ID), data=data)
model.LC<-lmer(log10(Leachate_mg_nonMBD_per_g_P_in_solid_filt0.7+1)~Burn_Severity+(1|Parent_ID), data=data)
model.int<-lmer(log10(Leachate_mg_nonMBD_per_g_P_in_solid_filt0.7+1)~Burn_Severity+Land_Coverage_Category+(1|Parent_ID), data=data)
anova(model,model.BS)
anova(model,model.LC)
anova(model,model.int)
#check VIF
vif(model)
#model assumptions
hist(log10(data$Leachate_mg_nonMBD_per_g_P_in_solid_filt0.7+1))
ggqqplot(residuals(model))
plot(lmer(log10(Leachate_mg_nonMBD_per_g_P_in_solid_filt0.7+1)~Burn_Severity*Land_Coverage_Category+(1|Parent_ID), data=data))
#interaction post hoc: 
emmeans::lsmeans(model, pairwise~Burn_Severity*Land_Coverage_Category, at=list(Burn_Severity="Unburned"),adjust="tukey") 
emmeans::lsmeans(model, pairwise~Burn_Severity*Land_Coverage_Category, at=list(Burn_Severity="Low"),adjust="tukey") 
emmeans::lsmeans(model, pairwise~Burn_Severity*Land_Coverage_Category, at=list(Burn_Severity="Moderate"),adjust="tukey") 
emmeans::lsmeans(model, pairwise~Burn_Severity*Land_Coverage_Category, at=list(Land_Coverage_Category="Douglas-fir Forest"),adjust="tukey") 
emmeans::lsmeans(model, pairwise~Burn_Severity*Land_Coverage_Category, at=list(Land_Coverage_Category="Sagebrush Shrubland"),adjust="tukey")
```


###pH
```{r aqueous P fig}

facet_text <- data.frame(
  Land_Coverage_Category = c("Douglas-fir Forest", "Sagebrush Shrubland", "Douglas-fir Forest", "Sagebrush Shrubland"),
  x = c(10.5, 10.5,10.5, 10.5), # Adjust x position as needed
  y = c(250, 250, 225, 225), # Adjust y position as needed
  label = c("p~'<'~0.001", "p~'<'~0.001", "R^2~'='~0.45", "R^2~'='~0.97"))

#relationship between P in aqueous fraction and pH
aq_pH <-ggplot(data, aes(x=pH, y=Leachate_mg_P_per_g_P_in_solid_filt0.7, color=Burn_Severity))+
  geom_point() + geom_smooth(method = "lm", se = FALSE, na.rm = TRUE, fullrange = TRUE, aes(group=1), color = "black")+
  theme_classic()+
  labs(title = "b)") +
  ylab(expression(paste(Aqueous~P~(mg~g^-1), sep="")))+ 
  xlab("pH")+facet_grid(.~Land_Coverage_Category, scales = "free")+
  theme(text = element_text(size = 18), 
        title = element_text(size = 18), 
        legend.position ="bottom",
        panel.border = element_rect(color = "black", fill = NA, linewidth = 1))+
  scale_color_manual(name = "Burn Severity", values=c("#0a9396", "#ffba08", "#e85d04", "#9d0208")) +
  geom_text(data = facet_text, aes(x = x, y = y, label = label), size = 4.5, hjust = 1, vjust = 1, color = "black", parse = TRUE)

aq_pH

#cowplot::save_plot("./figures/aq_pH_revisions.pdf", aq_pH, ncol = 1, nrow = 1,  base_height = 3.85, base_width = 8.9, base_aspect_ratio= 2:1, dpi=100)
```

```{r aqueous P stats}
#relationship between aqueous P concentration and pH for each vegetation type separately
#sagebrush shrubland
model<-lm(log10(Leachate_mg_P_per_g_P_in_solid_filt0.7)~pH, data = subset(data, Land_Coverage_Category == "Sagebrush Shrubland"))
summary(model)
#model assumptions
hist(log10(data_solids$Solid_P_mg_kg))
ggqqplot(residuals(model))
plot(fitted(model),residuals(model))

#Douglas-fir forest
model<-lm(log10(Leachate_mg_P_per_g_P_in_solid_filt0.7)~pH, data = subset(data, Land_Coverage_Category == "Douglas-fir Forest"))
summary(model)
#model assumptions
hist(log10(data_solids$Solid_P_mg_kg))
ggqqplot(residuals(model))
plot(fitted(model),residuals(model))
```

```{r pH and burn severity fig}
data_pH <- data %>%
  mutate(
    Annotation = case_when(
      Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "Unburned" ~ "a",
      Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "Low" ~ "a",
      Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "Moderate" ~ "b",
      Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "High" ~ "c",
      Land_Coverage_Category == "Sagebrush Shrubland" & Burn_Severity == "Unburned" ~ "a",
      Land_Coverage_Category == "Sagebrush Shrubland" & Burn_Severity == "Low" ~ "b",
      Land_Coverage_Category == "Sagebrush Shrubland" & Burn_Severity == "Moderate" ~ "c"),
    x = Burn_Severity,
    # x = case_when(
    #   Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "Unburned" ~ "Unburned 25",
    #   Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "Low" ~ "Low 295-627",
    #   Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "Moderate" ~ "Moderate 589-757",
    #   Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "High" ~ "High 589-757",
    #   Land_Coverage_Category == "Sagebrush Shrubland" & Burn_Severity == "Unburned" ~ "Unburned 25",
    #   Land_Coverage_Category == "Sagebrush Shrubland" & Burn_Severity == "Low" ~ "Low 308-502",
    #   Land_Coverage_Category == "Sagebrush Shrubland" & Burn_Severity == "Moderate" ~ "Moderate 512-547"),
    y = case_when(
      Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "Unburned" ~ 5.75,
      Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "Low" ~ 9.5,
      Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "Moderate" ~ 10.25,
      Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "High" ~ 11.775,
      Land_Coverage_Category == "Sagebrush Shrubland" & Burn_Severity == "Unburned" ~4.75,
      Land_Coverage_Category == "Sagebrush Shrubland" & Burn_Severity == "Low" ~ 7.8,
      Land_Coverage_Category == "Sagebrush Shrubland" & Burn_Severity == "Moderate" ~ 11.3),
    # Burn_Severity = case_when(
    #   Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "Unburned" ~ "Unburned 25",
    #   Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "Low" ~ "Low 295-627",
    #   Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "Moderate" ~ "Moderate 589-757",
    #   Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "High" ~ "High 589-757",
    #   Land_Coverage_Category == "Sagebrush Shrubland" & Burn_Severity == "Unburned" ~ "Unburned 25",
    #   Land_Coverage_Category == "Sagebrush Shrubland" & Burn_Severity == "Low" ~ "Low 308-502",
    #   Land_Coverage_Category == "Sagebrush Shrubland" & Burn_Severity == "Moderate" ~ "Moderate 512-547",
    #   TRUE ~ as.character(Burn_Severity)),
    # Burn_Severity = factor(Burn_Severity, levels = c("Unburned 25", "Low 295-627", "Low 308-502", "Moderate 589-757",
    #                                                  "Moderate 512-547", "High 589-757"))
    )

pH_BS<-ggplot(data_pH, aes(x=Burn_Severity, y=pH, fill = Land_Coverage_Category))+
  geom_boxplot()+
  theme_classic()+ 
  xlab("Burn Severity")+ 
  ylab("\n pH")+
  scale_fill_manual(values=c("lightgray","lightgray"))+
  labs(title = "a)") +
  facet_grid(.~Land_Coverage_Category, scales = "free") + 
  theme(text = element_text(size = 18),
        title = element_text(size = 18), 
        legend.position = "none",
        panel.border = element_rect(color = "black", fill = NA, linewidth = 1)) + 
  geom_text(aes(label = Annotation, x = x, y = y), size = 4.5, fontface = "plain") 

pH_BS

#cowplot::save_plot("./figures/pH_BS_revisions.pdf", pH_BS, ncol = 1, nrow = 1, base_height = 5, base_width = 10, dpi=100)
```

```{r pH and burn severity stats}
#relationship of pH with burn severity and vegetation type 
model<-lmer(log10(pH)~Burn_Severity*Land_Coverage_Category+(1|Parent_ID), data=data)
model.BS<-lmer(log10(pH)~Land_Coverage_Category+(1|Parent_ID), data=data)
model.LC<-lmer(log10(pH)~Burn_Severity+(1|Parent_ID), data=data)
model.int<-lmer(log10(pH)~Burn_Severity+Land_Coverage_Category+(1|Parent_ID), data=data)
anova(model,model.BS)
anova(model,model.LC)
anova(model,model.int)
#check VIF
vif(model)
#model assumptions
hist(log10(data$pH))
ggqqplot(residuals(model))
plot(fitted(model),residuals(model))
#post hoc tests 
emmeans::lsmeans(model, pairwise~Burn_Severity*Land_Coverage_Category, at=list(Burn_Severity="Unburned"),adjust="tukey") 
emmeans::lsmeans(model, pairwise~Burn_Severity*Land_Coverage_Category, at=list(Burn_Severity="Low"),adjust="tukey")
emmeans::lsmeans(model, pairwise~Burn_Severity*Land_Coverage_Category, at=list(Burn_Severity="Moderate"),adjust="tukey")
emmeans::lsmeans(model, pairwise~Burn_Severity*Land_Coverage_Category, at=list(Land_Coverage_Category="Douglas-fir Forest"),adjust="tukey")
emmeans::lsmeans(model, pairwise~Burn_Severity*Land_Coverage_Category, at=list(Land_Coverage_Category="Sagebrush Shrubland"),adjust="tukey")
```

```{r Figure 6 ph for manuscript}

figure6 <- ggarrange(pH_BS, aq_pH, ncol = 1, align = "v")

figure6

#note that this is saving the plots at slightly different sizes. manually saved in export function in Rstudio to maintain sizes set in ggarrange()

#cowplot::save_plot("./figures/pH_all_revisions.pdf", figure6, ncol = 1, base_height = 8, base_width = 7, dpi=600)

```


##Path Analysis
```{r stats}
#reference: https://stats.oarc.ucla.edu/r/seminars/rsem/ #followed Model 4A
#reference: https://kevintshoemaker.github.io/NRES-746/SEM.RMarkdown.html
#reference: https://bookdown.org/jdholster1/idsr/structural-equation-modeling.html

#make dataframe with solid samples (leachate avg)
leachate_mean <- data %>%
  dplyr::group_by(Parent_ID) %>%
  dplyr::summarize(
    Leachate_mg_P_per_g_P_in_solid_unfilt_Mean = mean(Leachate_mg_P_per_g_P_in_solid_unfilt, na.rm = TRUE),
    Leachate_mg_P_per_g_P_in_solid_part_Mean = mean(Leachate_mg_P_per_g_P_in_solid_part, na.rm = TRUE),
    Leachate_mg_P_per_g_P_in_solid_filt0.7_Mean = mean(Leachate_mg_P_per_g_P_in_solid_filt0.7, na.rm = TRUE),
    Leachate_mg_MBD_per_g_P_in_solid_filt0.7_Mean = mean(Leachate_mg_MBD_per_g_P_in_solid_filt0.7, na.rm = TRUE),
    pH_Mean = mean(pH)
  )

solid <- data_solids %>%
  select(Parent_ID, Land_Coverage_Category, Burn_Severity, Burn_Duration, Char_Max_Temp, Ortho, Mono, Di, Pyro, XANES_Po, XANES_Pi, XANES_Fe, XANES_Na, XANES_Ca, XANES_Al, XANES_Mg, XANES_K, XANES_Pi_Fe, XANES_Pi_Na, XANES_Pi_Ca, XANES_Pi_Al, XANES_Pi_Mg, XANES_Pi_K, XANES_Po_Fe, XANES_Po_Na, XANES_Po_Ca, XANES_Po_Al, XANES_Po_Mg, XANES_Po_K, Solid_P_g_kg, Solid_Ca_g_kg, Solid_Fe_g_kg, Solid_Al_g_kg, Solid_K_g_kg, Solid_Mg_g_kg, Solid_Na_g_kg, Solid_S_g_kg, Solid_C_g_kg, Solid_N_g_kg)
  
data_rda<- solid %>%
  full_join(leachate_mean)

#normalize data
data_rda_sub<-as.data.frame(scale(data_rda[4:44]))

data_rda_combine<-cbind(data_rda[,c(1:3)], data_rda_sub)

#convert categorical variable
data_rda_combine$Burn_Severity=as.numeric(factor(data_rda_combine$Burn_Severity, levels= c("Unburned", "Low", "Moderate", "High")))
data_rda_combine$Land_Coverage_Category=as.numeric(factor(data_rda_combine$Land_Coverage_Category, levels= c("Douglas-fir Forest", "Sagebrush Shrubland")))

#model interpretation:
#chi-square: The model Chi-squared assesses overall fit and the discrepancy between the sample and fitted covariance matrices. Its p-value should be > .05 (i.e., the hypothesis of a perfect fit cannot be rejected). However, it is quite sensitive to sample size.
#CFI (comparitive fit index): range between 0-1; greater than 0.90 indicate a good fit
#TLI (Tucker Lewis Index): range between 0-1; greater than 0.90 indicate a good fit; if above 1 then round down to 1
#RMSEA (root mean square error of approximation): The Root Mean Square Error of Approximation is a parsimony-adjusted index. Values closer to 0 represent a good fit. It should be < .08 or < .05. The p-value printed with it tests the hypothesis that RMSEA is less than or equal to .05 (a cutoff sometimes used for good fit), and thus should be not significant.

#Aqueous phase model: filtered <0.7 nominal pore size
model <- '
  # Structural Model
    Solid_P_g_kg ~ Burn_Severity
    XANES_Pi_Ca ~ Burn_Severity
    Solid_P_g_kg ~ Land_Coverage_Category
    XANES_Pi_Ca ~ Land_Coverage_Category
    Burn_Severity ~ Land_Coverage_Category
    Leachate_mg_P_per_g_P_in_solid_filt0.7_Mean ~ XANES_Pi_Ca + Solid_P_g_kg
    
  # Residual Variances
    Solid_P_g_kg~~Solid_P_g_kg  
    XANES_Pi_Ca ~~ XANES_Pi_Ca
    Leachate_mg_P_per_g_P_in_solid_filt0.7_Mean ~~ Leachate_mg_P_per_g_P_in_solid_filt0.7_Mean
'

# Fit the SEM model
fit <- sem(model, data = data_rda_combine)

# Summarize the results
summary(fit, fit.measures=TRUE, standardized=TRUE, rsquare=TRUE)
fitMeasures(fit, c("chisq", "cfi", "tli", "rmsea", "aic"))

#visualize it
p_pa<-semPlot::semPaths(fit,'std',  edge.label.cex = 1.5,
         label.prop=0.9, rotation = 1, nCharNodes=0,
         equalizeManifests = FALSE, optimizeLatRes = TRUE, 
         edge.width = 0.6, shapeMan = "rectangle", shapeLat = "ellipse", 
         shapeInt = "triangle", sizeInt = 2, sizeLat = 4, 
         curve=2, residuals = FALSE, layout="tree2",
         edge.label.position=0.7, fade = TRUE, colFactor=0.25, 
         node.width = 4)
p_pa2 <- mark_sig(p_pa, fit)
plot(p_pa2)

#Particulate phase model: (>0.7um nominal pore size)
model <- '
  # Structural Model
    Solid_P_g_kg ~ Burn_Severity
    XANES_Pi_Ca ~ Burn_Severity
    Solid_P_g_kg ~ Land_Coverage_Category
    XANES_Pi_Ca ~ Land_Coverage_Category
    Burn_Severity ~ Land_Coverage_Category
    Leachate_mg_P_per_g_P_in_solid_part_Mean ~ XANES_Pi_Ca + Solid_P_g_kg
    
  # Residual Variances
    Solid_P_g_kg~~Solid_P_g_kg  
    XANES_Pi_Ca ~~ XANES_Pi_Ca
    Leachate_mg_P_per_g_P_in_solid_part_Mean ~~ Leachate_mg_P_per_g_P_in_solid_part_Mean
'

# Fit the SEM model
fit <- sem(model, data = data_rda_combine)

# Summarize the results
summary(fit, fit.measures=TRUE, standardized=TRUE, rsquare=TRUE)
fitMeasures(fit, c("chisq", "cfi", "tli", "rmsea", "aic"))

#visualize it
p_pa<-semPlot::semPaths(fit,'std',  edge.label.cex = 1.5,
         label.prop=0.9, rotation = 1, nCharNodes=0,
         equalizeManifests = FALSE, optimizeLatRes = TRUE, 
         edge.width = 0.6, shapeMan = "rectangle", shapeLat = "ellipse", 
         shapeInt = "triangle", sizeInt = 2, sizeLat = 4, 
         curve=2, residuals = FALSE, layout="tree2",
         edge.label.position=0.7, fade = TRUE, colFactor=0.25, 
         node.width = 4)
p_pa2 <- mark_sig(p_pa, fit)
plot(p_pa2)
```

##Burn Severity
```{r burn severity}
#relate burn severity to temp and duration

ggplot(data_solids, aes(x = Char_Max_Temp, y = Burn_Duration)) +
  geom_jitter(aes(color = Burn_Severity), width = 20, height = 20, size = 2, alpha = 0.7) +  # Color points by Burn_Severity
  geom_smooth(method = "lm", se=FALSE, color = "black") +  # Single best-fit line for all points
  theme_classic() +
  ylab("Burn Duration (s)") +
  xlab("Temperature (C)") +
  facet_grid(. ~ Land_Coverage_Category)+scale_color_manual(values=c("#0a9396","#ffba08", "#e85d04","#9d0208"))+
  labs(color = "Burn Severity")

SB <-subset(data_solids, Land_Coverage_Category=="Sagebrush Shrubland")
DF <-subset(data_solids, Land_Coverage_Category=="Douglas-fir Forest")

model<-lm(Char_Max_Temp~Burn_Duration, data = SB)
summary(model)

model<-lm(Char_Max_Temp~Burn_Duration, data = DF)
summary(model)

model<-anova(Burn_Severity~Char_Max_Temp + Burn_Duration, data = DF)
summary(model)

#burn duration and temp with burn severity
#veg together
ggplot(data_solids, aes(x=Burn_Severity, y=Burn_Duration))+geom_boxplot(show.legend=FALSE)+theme_classic()+ ylab("Burn Duration") + xlab("Burn Severity")

ggplot(data_solids, aes(x=Burn_Severity, y=Char_Max_Temp))+geom_boxplot(show.legend=FALSE)+theme_classic()+ ylab("Burn Duration") + xlab("Burn Severity")

#veg split
ggplot(data_solids, aes(x=Burn_Severity, y=Burn_Duration, fill = Land_Coverage_Category))+geom_boxplot(show.legend=FALSE)+theme_classic()+ ylab("Burn Duration") + xlab("Burn Severity")+scale_fill_manual(values=c("#9B9B7A","#FFCB69"))+facet_grid(.~Land_Coverage_Category, scales = "free")

model<-aov(Burn_Duration~Burn_Severity, data = SB)
summary(model)
#model assumptions
hist(log10(data_solids$Solid_P_mg_kg))
ggqqplot(residuals(model))
plot(fitted(model),residuals(model))

model<-aov(Burn_Duration~Burn_Severity, data = DF)
summary(model)
#model assumptions
hist(log10(data_solids$Solid_P_mg_kg))
ggqqplot(residuals(model))
plot(fitted(model),residuals(model))

model<-aov(Burn_Duration~Burn_Severity, data = data_solids)
summary(model)
#model assumptions
hist(log10(data_solids$Solid_P_mg_kg))
ggqqplot(residuals(model))
plot(fitted(model),residuals(model))

model<-aov(Char_Max_Temp~Burn_Severity, data = SB)
summary(model)
#model assumptions
hist(log10(data_solids$Solid_P_mg_kg))
ggqqplot(residuals(model))
plot(fitted(model),residuals(model))

model<-aov(Char_Max_Temp~Burn_Severity, data = DF)
summary(model)
#model assumptions
hist(log10(data_solids$Solid_P_mg_kg))
ggqqplot(residuals(model))
plot(fitted(model),residuals(model))

model<-aov(Char_Max_Temp~Burn_Severity, data = data_solids)
summary(model)
#model assumptions
hist(log10(data_solids$Solid_P_mg_kg))
ggqqplot(residuals(model))
plot(fitted(model),residuals(model))
```

```{r Elemental Concentration}
#solids
ggplot(data_solids_Pconc, aes(x=Burn_Severity, y=Solid_Ca_mg_kg/1000, fill=Land_Coverage_Category))+geom_boxplot(show.legend=FALSE)+theme_classic()+ xlab("Burn Severity")+scale_fill_manual(values=c("#9B9B7A","#FFCB69"))+facet_grid(.~Land_Coverage_Category, scales = "free")+scale_x_discrete(labels = split_labels_with_parentheses) + theme(text = element_text(size = 15),
axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1), panel.border = element_rect(color = "black", fill = NA, linewidth = 1))

ggplot(data_solids_Pconc, aes(x=Burn_Severity, y=Solid_Fe_mg_kg/1000, fill=Land_Coverage_Category))+geom_boxplot(show.legend=FALSE)+theme_classic()+ xlab("Burn Severity")+scale_fill_manual(values=c("#9B9B7A","#FFCB69"))+facet_grid(.~Land_Coverage_Category, scales = "free")+scale_x_discrete(labels = split_labels_with_parentheses) + theme(text = element_text(size = 15),
axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1), panel.border = element_rect(color = "black", fill = NA, linewidth = 1))

ggplot(data_solids_Pconc, aes(x=Burn_Severity, y=Solid_Al_mg_kg/1000, fill=Land_Coverage_Category))+geom_boxplot(show.legend=FALSE)+theme_classic()+ xlab("Burn Severity")+scale_fill_manual(values=c("#9B9B7A","#FFCB69"))+facet_grid(.~Land_Coverage_Category, scales = "free")+scale_x_discrete(labels = split_labels_with_parentheses) + theme(text = element_text(size = 15),
axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1), panel.border = element_rect(color = "black", fill = NA, linewidth = 1))

ggplot(data_solids_Pconc, aes(x=Burn_Severity, y=Solid_K_mg_kg/1000, fill=Land_Coverage_Category))+geom_boxplot(show.legend=FALSE)+theme_classic()+ xlab("Burn Severity")+scale_fill_manual(values=c("#9B9B7A","#FFCB69"))+facet_grid(.~Land_Coverage_Category, scales = "free")+scale_x_discrete(labels = split_labels_with_parentheses) + theme(text = element_text(size = 15),
axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1), panel.border = element_rect(color = "black", fill = NA, linewidth = 1))

ggplot(data_solids_Pconc, aes(x=Burn_Severity, y=Solid_Mg_mg_kg/1000, fill=Land_Coverage_Category))+geom_boxplot(show.legend=FALSE)+theme_classic()+ xlab("Burn Severity")+scale_fill_manual(values=c("#9B9B7A","#FFCB69"))+facet_grid(.~Land_Coverage_Category, scales = "free")+scale_x_discrete(labels = split_labels_with_parentheses) + theme(text = element_text(size = 15),
axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1), panel.border = element_rect(color = "black", fill = NA, linewidth = 1))

ggplot(data_solids_Pconc, aes(x=Burn_Severity, y=Solid_Na_mg_kg/1000, fill=Land_Coverage_Category))+geom_boxplot(show.legend=FALSE)+theme_classic()+ xlab("Burn Severity")+scale_fill_manual(values=c("#9B9B7A","#FFCB69"))+facet_grid(.~Land_Coverage_Category, scales = "free")+scale_x_discrete(labels = split_labels_with_parentheses) + theme(text = element_text(size = 15),
axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1), panel.border = element_rect(color = "black", fill = NA, linewidth = 1))

ggplot(data_solids_Pconc, aes(x=Burn_Severity, y=Solid_S_mg_kg/1000, fill=Land_Coverage_Category))+geom_boxplot(show.legend=FALSE)+theme_classic()+ xlab("Burn Severity")+scale_fill_manual(values=c("#9B9B7A","#FFCB69"))+facet_grid(.~Land_Coverage_Category, scales = "free")+scale_x_discrete(labels = split_labels_with_parentheses) + theme(text = element_text(size = 15),
axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1), panel.border = element_rect(color = "black", fill = NA, linewidth = 1))

ggplot(data_solids, aes(x=Burn_Severity, y=Solid_C_mg_kg/1000, fill=Land_Coverage_Category))+geom_boxplot(show.legend=FALSE)+theme_classic()+ xlab("Burn Severity")+scale_fill_manual(values=c("#9B9B7A","#FFCB69"))+facet_grid(.~Land_Coverage_Category, scales = "free")+scale_x_discrete(labels = split_labels_with_parentheses) + theme(text = element_text(size = 15),
axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1), panel.border = element_rect(color = "black", fill = NA, linewidth = 1))

ggplot(data_solids, aes(x=Burn_Severity, y=Solid_N_mg_kg/1000, fill=Land_Coverage_Category))+geom_boxplot(show.legend=FALSE)+theme_classic()+ xlab("Burn Severity")+scale_fill_manual(values=c("#9B9B7A","#FFCB69"))+facet_grid(.~Land_Coverage_Category, scales = "free")+scale_x_discrete(labels = split_labels_with_parentheses) + theme(text = element_text(size = 15),
axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1), panel.border = element_rect(color = "black", fill = NA, linewidth = 1))




#leachates
ggplot(data, aes(x = Burn_Severity, y = Leachate_Ca_mg_L_filt0.7, fill = Land_Coverage_Category)) +
    geom_boxplot(show.legend = FALSE) +
    theme_classic() +
    xlab("Burn Severity") +
    scale_fill_manual(values = c("#9B9B7A","#FFCB69")) +
    scale_x_discrete(labels = split_labels_with_parentheses) +facet_grid(.~Land_Coverage_Category, scales = "free")

ggplot(data, aes(x = Burn_Severity, y = Leachate_Mg_mg_L_filt0.7, fill = Land_Coverage_Category)) +
    geom_boxplot(show.legend = FALSE) +
    theme_classic() +
    xlab("Burn Severity") +
    scale_fill_manual(values = c("#9B9B7A","#FFCB69")) +
    scale_x_discrete(labels = split_labels_with_parentheses) +facet_grid(.~Land_Coverage_Category, scales = "free")

ggplot(data, aes(x = Burn_Severity, y = Leachate_Fe_mg_L_filt0.7, fill = Land_Coverage_Category)) +
    geom_boxplot(show.legend = FALSE) +
    theme_classic() +
    xlab("Burn Severity") +
    scale_fill_manual(values = c("#9B9B7A","#FFCB69")) +
    scale_x_discrete(labels = split_labels_with_parentheses) +facet_grid(.~Land_Coverage_Category, scales = "free")

ggplot(data, aes(x = Burn_Severity, y = Leachate_Al_mg_L_filt0.7, fill = Land_Coverage_Category)) +
    geom_boxplot(show.legend = FALSE) +
    theme_classic() +
    xlab("Burn Severity") +
    scale_fill_manual(values = c("#9B9B7A","#FFCB69")) +
    scale_x_discrete(labels = split_labels_with_parentheses) +facet_grid(.~Land_Coverage_Category, scales = "free")

ggplot(data, aes(x = Burn_Severity, y = Leachate_Na_mg_L_filt0.7, fill = Land_Coverage_Category)) +
    geom_boxplot(show.legend = FALSE) +
    theme_classic() +
    xlab("Burn Severity") +
    scale_fill_manual(values = c("#9B9B7A","#FFCB69")) +
    scale_x_discrete(labels = split_labels_with_parentheses) +facet_grid(.~Land_Coverage_Category, scales = "free")

ggplot(data, aes(x = Burn_Severity, y = Leachate_K_mg_L_filt0.7, fill = Land_Coverage_Category)) +
    geom_boxplot(show.legend = FALSE) +
    theme_classic() +
    xlab("Burn Severity") +
    scale_fill_manual(values = c("#9B9B7A","#FFCB69")) +
    scale_x_discrete(labels = split_labels_with_parentheses) +facet_grid(.~Land_Coverage_Category, scales = "free")

ggplot(data, aes(x = Burn_Severity, y = Leachate_S_mg_L_filt0.7, fill = Land_Coverage_Category)) +
    geom_boxplot(show.legend = FALSE) +
    theme_classic() +
    xlab("Burn Severity") +
    scale_fill_manual(values = c("#9B9B7A","#FFCB69")) +
    scale_x_discrete(labels = split_labels_with_parentheses) +facet_grid(.~Land_Coverage_Category, scales = "free")

ggplot(data, aes(x = Burn_Severity, y = NPOC_mg_C_per_L, fill = Land_Coverage_Category)) +
    geom_boxplot(show.legend = FALSE) +
    theme_classic() +
    xlab("Burn Severity") +
    scale_fill_manual(values = c("#9B9B7A","#FFCB69")) +
    scale_x_discrete(labels = split_labels_with_parentheses) +facet_grid(.~Land_Coverage_Category, scales = "free")

ggplot(data, aes(x = Burn_Severity, y = TN_mg_N_per_L, fill = Land_Coverage_Category)) +
    geom_boxplot(show.legend = FALSE) +
    theme_classic() +
    xlab("Burn Severity") +
    scale_fill_manual(values = c("#9B9B7A","#FFCB69")) +
    scale_x_discrete(labels = split_labels_with_parentheses) +facet_grid(.~Land_Coverage_Category, scales = "free")
```





