---
title: "BSLE_P_Code"
author: "Morgan Barnes"
date: "'2023-08-18'r Sys.Date()'"
output: html_document
---
##This is the code for figures and statistics from Barnes et al. (2024): phosphorus composition along a burn severity gradient
##Contact: Morgan E Barnes morgan.barnes@pnnl.gov
##Make your environemnt

#### Set Up
```{r setup, include=FALSE, dev="CairoPNG"}
rm(list=ls(all=T))
knitr::opts_chunk$set(echo = TRUE)
```



## Load libraries
```{r library}

require(pacman)

pacman::p_load(tidyverse,
              dplyr,plyr,ggplot2,
              lubridate, tidyr, tidyverse,
              scales, cowplot, gridExtra, RColorBrewer,
              wesanderson,readxl,openxlsx, stringr, hablar,
              janitor, stringr, naniar, forstringr, reshape2, 
              emmeans, rstatix, ggpubr, Hmisc, corrplot, ggrepel, 
              stringr, lme4, lmerTest, car)


```

##### Confirm working directory:
```{r working directory check, echo=FALSE}
getwd()
```

##Load data
The datasets and metadata needed for P BSLE Gradient manuscript are:
1) Chemistry datasets solids and liquids w/ all metadata that can be used directly from data package:
This includes: 
a) Total elemental composition of solids
b) Total elemental composition of leachate particulate and filtered fractions
c) Molybdate reactive P of leachate filtered fraction
d) XANES of solids
e) NMR of solids

2) Chemistry data that needs post-data package processing after download from BSLE Data Package v3; this was done and provided within the BSLE P Manuscript Data Package:
a) XANES of solids (spectra of samples and reference compounds and linear combination fits)
b) NMR of solids (deconvolution)


#### Download the BSLE Data Package

Until we can get the API to work, do this manually and store on your local. I recommend storing inside your github folder and gitignoring the subfolder with the data in it by adding this to your .gitignore: 
`#data folder` 
`data/`

BSLE v3 data package URL: https://data.ess-dive.lbl.gov/view/doi:10.15485/1894135
BSLE P manuscript data package URL: INSERT HERE!!! fix

Bring in the data package data:
```{r bsle v3 data package}
#metadata
Meta <- read_csv("../data/BSLE_Data_Package_v3/v1_BSLE_Metadata_and_Protocols/BSLE_Burn_and_Laboratory_Metadata.csv") %>%
  dplyr::rename(Sample_ID = Sample_Name,
                Leachate_vol_mL = Leachate_Volume,
                Char_leached_g = Char_Leached) %>%
  naniar::replace_with_na_all(condition = ~.x ==-9999) %>%
  naniar::replace_with_na_all(condition = ~.x == "N/A") %>%
  mutate(Burn_Severity=replace(Burn_Severity, Burn_Severity=='unburned', 'Unburned'))

Meta<-Meta[ c(2,3,5,8,21,25,26)]
Meta$Burn_Severity=factor(Meta$Burn_Severity, levels= c("Unburned", "Low", "Moderate", "High"))

#chemical data from BSLE v3 data package
ICP_Solid <- read_csv("../data/BSLE_Data_Package_v3/v3_BSLE_Data/BSLE_ICP_Solid.csv")
ICP_Leachate <- read_csv("../data/BSLE_Data_Package_v3/v3_BSLE_Data/BSLE_ICP.csv")
MBD <- read_csv("../data/BSLE_Data_Package_v3/v3_BSLE_Data/BSLE_MBD.csv")
ICP_PNMR <- read_csv("../data/BSLE_Data_Package_v3/v3_BSLE_Data/BSLE_ICP_PNMR.csv")
npoctdn <- read_csv("../data/BSLE_Data_Package_v3/v3_BSLE_Data/v2_BSLE_NPOC_TN.csv")
SolidCN <- read_csv("../data/BSLE_Data_Package_v3/v3_BSLE_Data/BSLE_CN.csv")
pH <- read_csv("../data/BSLE_Data_Package_v3/v3_BSLE_Data/BSLE_pH.csv")
NMR_spectra <- read_csv("../data/BSLE_Data_Package_v3/v3_BSLE_Data/BSLE_31P-NMR.csv")


#chemical data from BSLE P manuscript data package
NMR <- read.csv("../data/Barnes_2023_BSLE_P_Gradient_Manuscript_Data_Package/NMR_Deconvolutions.csv") %>%
  filter(Degradation_Corrected == 'Yes')
XANES <- read.csv("../data/Barnes_2023_BSLE_P_Gradient_Manuscript_Data_Package/P_XANES_Samples/P-XANES_LCF.csv")  
XANES_spectra <- read_csv("../data/Barnes_2023_BSLE_P_Gradient_Manuscript_Data_Package/P_XANES_Samples/xanes_example_spectra.csv") #this file was generated using XANES_Spectra_Merging script 

```

Clean up data functions:
```{r functions for cleaning}
essdive_template_cleaning <- function(dataframe){
  cleaned <- dataframe %>% 
  janitor::row_to_names(row_number = which(dataframe[,1] == "Field_Name")) %>% #this assumes that this name is somewhere in column #1. That follows some (most?) ESS-DIVE templates.
 slice(which(Field_Name == "#Start_Data"):which(Field_Name == "#End_Data")) %>%
 select(!Field_Name)
  }

noreporting_format_cleaning <- function(dataframe){
  cleaned <- dataframe %>% 
  janitor::row_to_names(row_number = which(dataframe[,1] == "Date")) #this assumes that this name is somewhere in column #1. This works for the thermocouple datasets
  }
```

```{r bsle v3 data package cleaning}
#subset_npoctdn <- npoctdn_clean %>% filter(str_detect(NPOC_mg_C_per_L, "Above") | str_detect(TN_mg_N_per_L, "Above"))
#write.csv(subset_npoctdn, file = "/Users/barn772/OneDrive - PNNL/Desktop/subset_npoctdn.csv", row.names=FALSE)

pH_clean <- essdive_template_cleaning(pH)  %>%
  dplyr::rename(Sample_ID = Sample_Name,
                pH = '00403_pH') %>%
   mutate_at(c(3), as.numeric) %>%
  separate(col=Sample_ID, into = c("Sample_ID", "FilterSize"), sep="-")  %>%
  filter(grepl('unfilt', FilterSize)) %>%
  select(Sample_ID, pH)

#fix
#wrote code so -9999 is NA, below LOD is NA, and if above or below standard curve then I pull out those values
#these data are NOT correct because values are not dilution corrected
#change this to 0.7 later
npoctdn_clean <- essdive_template_cleaning(npoctdn) %>%
  dplyr::rename(NPOC_mg_C_per_L = `00681_NPOC_mg_per_L_as_C`,
         TN_mg_N_per_L = `00602_TN_mg_per_L_as_N`,
         Sample_ID = Sample_Name) %>%
  select(Sample_ID, NPOC_mg_C_per_L, TN_mg_N_per_L) %>%
  filter(grepl('filt0.2', Sample_ID)) %>%
  mutate(Sample_ID = stringr::str_remove(Sample_ID ,"-filt0.2"),
         NPOC_mg_C_per_L = case_when(NPOC_mg_C_per_L == -9999 ~ NA,
                              str_detect(NPOC_mg_C_per_L, "LOD") ~ NA,
                              str_detect(NPOC_mg_C_per_L, "Below_0.1_ppm") ~
                                      str_extract_part(NPOC_mg_C_per_L, "_ppm_Below_0.1_ppm", before = TRUE),
                               TRUE ~ NPOC_mg_C_per_L),
         TN_mg_N_per_L = case_when(TN_mg_N_per_L == -9999 ~ NA,
                              str_detect(TN_mg_N_per_L, "LOD") ~ NA,
                              str_detect(TN_mg_N_per_L, "Below_0.1_ppm") ~ 
                                        str_extract_part(TN_mg_N_per_L, "_ppm_Below_0.1_ppm", before = TRUE),
                               TRUE ~ TN_mg_N_per_L)) %>%
  mutate(NPOC_mg_C_per_L = case_when(str_detect(NPOC_mg_C_per_L, "NPOC_") ~ 
                                     str_extract(NPOC_mg_C_per_L, "(\\d+\\.\\d+)"),
                                     NPOC_mg_C_per_L < 0 ~ NA,
                                     TRUE ~ NPOC_mg_C_per_L),
         TN_mg_N_per_L = case_when(str_detect(TN_mg_N_per_L, "TN_") ~ 
                                     str_extract(TN_mg_N_per_L, "(\\d+\\.\\d+)"),
                                     TN_mg_N_per_L < 0 ~ NA, 
                                     TRUE ~ TN_mg_N_per_L)) %>%
  mutate(NPOC_mg_C_per_L = as.numeric(NPOC_mg_C_per_L),
         TN_mg_N_per_L = as.numeric(TN_mg_N_per_L))

#fix
SolidCN_clean <- essdive_template_cleaning(SolidCN) %>%
  dplyr::rename(C_weight_per = `01463_C_percent`,
         N_weight_per = `01472_N_percent`,
         Parent_ID = Sample_Name) %>%
  select(Parent_ID, C_weight_per,  N_weight_per) %>%
  filter(grepl('solid', Parent_ID)) %>%
  mutate(Parent_ID = stringr::str_remove(Parent_ID ,"-solid"),
         C_weight_per = case_when(C_weight_per == -9999 ~ NA,
                                  str_detect(C_weight_per, "LOD") ~ NA,
                                     TRUE ~ C_weight_per),
         N_weight_per = case_when(N_weight_per == -9999 ~ NA,
                                   str_detect(N_weight_per, "LOD") ~ NA,
                                   TRUE ~ N_weight_per)) %>%
   mutate(C_weight_per = as.numeric(C_weight_per),
         N_weight_per = as.numeric(N_weight_per))

#did not remove samples with deviations but did modify flags: negative values were replaced with NA, below LOD were replaced with NA, and above/below standard curve were replaced with the value
ICP_Solid_clean<- essdive_template_cleaning(ICP_Solid) %>%
  dplyr::rename(Solid_Ca_mg_kg = '52718_Total_Ca_mg_per_kg',
                Solid_Mg_mg_kg = '52719_Total_Mg_mg_per_kg',
                Solid_P_mg_kg = 'Total_P_mg_per_kg',
                Solid_K_mg_kg = '52720_Total_K_mg_per_kg',
                Solid_Na_mg_kg = '52721_Total_Na_mg_per_kg',
                Solid_S_mg_kg = '01466_Total_S_mg_per_kg',
                Solid_Al_mg_kg = '01462_Total_Al_mg_per_kg',
                Solid_Fe_mg_kg = '01464_Total_Fe_mg_per_kg',
                Parent_ID = 'Sample_Name') %>%
  mutate(Solid_Na_mg_kg = case_when(
                Solid_Na_mg_kg == -9999 ~ NA,
                str_detect(Solid_Na_mg_kg, "Negative_Value") ~ NA, 
                str_detect(Solid_Na_mg_kg, "Below_213.43_LOD") ~ NA, 
                str_detect(Solid_Na_mg_kg, "TotNa_Below") ~ 
                str_extract(Solid_Na_mg_kg, "\\d+\\.?\\d*(?=_ppm_Final_Corrected)"),
                str_detect(Solid_Na_mg_kg, "TotNa_Above") ~ 
                str_extract(Solid_Na_mg_kg, "\\d+\\.?\\d*(?=_ppm_Final_Corrected)"),
                TRUE ~ Solid_Na_mg_kg)) %>%
   mutate_at(c(4:11), as.numeric) %>%
  separate(col=Parent_ID, into = c("Parent_ID", "FilterSize"), sep="-")  %>%
  filter(grepl('solid', FilterSize)) %>%
  select(Parent_ID, Solid_Ca_mg_kg,  Solid_Mg_mg_kg, Solid_P_mg_kg, Solid_K_mg_kg, Solid_Na_mg_kg, Solid_S_mg_kg, Solid_Al_mg_kg, Solid_Fe_mg_kg)


#did not remove samples with deviations but did modify flags: negative values were replaced with NA, below LOD were replaced with NA, and above/below standard curve were replaced with the value
ICP_Leachate_clean <- essdive_template_cleaning(ICP_Leachate) %>%
  dplyr::rename(Leachate_Ca_mg_L = 'Total_Ca_mg_per_L',
                Leachate_Mg_mg_L = 'Total_Mg_mg_per_L',
                Leachate_P_mg_L = 'Total_P_mg_per_L',
                Leachate_K_mg_L = 'Total_K_mg_per_L',
                Leachate_Na_mg_L = 'Total_Na_mg_per_L',
                Leachate_S_mg_L = 'Total_S_mg_per_L',
                Leachate_Al_mg_L = 'Total_Al_mg_per_L',
                Leachate_Fe_mg_L = 'Total_Fe_mg_per_L',
                Sample_ID = 'Sample_Name') %>%
  mutate(Leachate_Na_mg_L = case_when(
                Leachate_Na_mg_L == -9999 ~ NA,
                str_detect(Leachate_Na_mg_L, "Negative") ~ NA, 
                str_detect(Leachate_Na_mg_L, "LOD") ~ NA, 
                str_detect(Leachate_Na_mg_L, "TotNa_Below") ~ 
                str_extract(Leachate_Na_mg_L, "\\d+\\.?\\d*(?=_ppm_Final_Corrected)"),
                str_detect(Leachate_Na_mg_L, "TotNa_Above") ~ 
                str_extract(Leachate_Na_mg_L, "\\d+\\.?\\d*(?=_ppm_Final_Corrected)"),
                TRUE ~ Leachate_Na_mg_L)) %>%
  mutate(Leachate_Al_mg_L = case_when(
                Leachate_Na_mg_L == -9999 ~ NA,
                str_detect(Leachate_Al_mg_L, "Negative") ~ NA, 
                str_detect(Leachate_Al_mg_L, "LOD") ~ NA, 
                str_detect(Leachate_Al_mg_L, "TotAl_Below") ~ 
                str_extract(Leachate_Al_mg_L, "\\d+\\.?\\d*(?=_ppm_Final_Corrected)"),
                str_detect(Leachate_Al_mg_L, "TotAl_Above") ~ 
                str_extract(Leachate_Al_mg_L, "\\d+\\.?\\d*(?=_ppm_Final_Corrected)"),
                TRUE ~ Leachate_Al_mg_L)) %>%
  mutate(Leachate_Fe_mg_L = case_when(
                Leachate_Fe_mg_L == -9999 ~ NA,
                str_detect(Leachate_Fe_mg_L, "Negative") ~ NA, 
                str_detect(Leachate_Fe_mg_L, "LOD") ~ NA, 
                str_detect(Leachate_Fe_mg_L, "TotAl_Below") ~ 
                str_extract(Leachate_Fe_mg_L, "\\d+\\.?\\d*(?=_ppm_Final_Corrected)"),
                str_detect(Leachate_Fe_mg_L, "TotAl_Above") ~ 
                str_extract(Leachate_Fe_mg_L, "\\d+\\.?\\d*(?=_ppm_Final_Corrected)"),
                TRUE ~ Leachate_Fe_mg_L))  %>%
  mutate_at(c(2:9), as.numeric) %>%
  select(Sample_ID, Leachate_Ca_mg_L,  Leachate_Mg_mg_L, Leachate_P_mg_L, Leachate_K_mg_L, Leachate_Na_mg_L, Leachate_S_mg_L, Leachate_Al_mg_L, Leachate_Fe_mg_L) %>%
  filter(grepl('filt', Sample_ID)) %>%
  separate(col=Sample_ID, into = c("Sample_ID", "FilterSize"), sep="-") 

ICP_Leachate_Filt_clean<- ICP_Leachate_clean %>%
                filter(str_detect(FilterSize, "filt0.")) %>%
  dplyr::rename(Leachate_Ca_mg_L_filt0.7 = 'Leachate_Ca_mg_L',
                Leachate_Mg_mg_L_filt0.7 = 'Leachate_Mg_mg_L',
                Leachate_P_mg_L_filt0.7 = 'Leachate_P_mg_L',
                Leachate_K_mg_L_filt0.7 = 'Leachate_K_mg_L',
                Leachate_Na_mg_L_filt0.7 = 'Leachate_Na_mg_L',
                Leachate_S_mg_L_filt0.7 = 'Leachate_S_mg_L',
                Leachate_Al_mg_L_filt0.7 = 'Leachate_Al_mg_L',
                Leachate_Fe_mg_L_filt0.7 = 'Leachate_Fe_mg_L') %>%
  select(Sample_ID, Leachate_Ca_mg_L_filt0.7,  Leachate_Mg_mg_L_filt0.7, Leachate_P_mg_L_filt0.7, Leachate_K_mg_L_filt0.7, Leachate_Na_mg_L_filt0.7, Leachate_S_mg_L_filt0.7, Leachate_Al_mg_L_filt0.7, Leachate_Fe_mg_L_filt0.7)


ICP_Leachate_Unfilt_clean<- ICP_Leachate_clean %>%
                filter(str_detect(FilterSize, "unfilt")) %>%
  dplyr::rename(Leachate_Ca_mg_L_unfilt = 'Leachate_Ca_mg_L',
                Leachate_Mg_mg_L_unfilt = 'Leachate_Mg_mg_L',
                Leachate_P_mg_L_unfilt = 'Leachate_P_mg_L',
                Leachate_K_mg_L_unfilt = 'Leachate_K_mg_L',
                Leachate_Na_mg_L_unfilt = 'Leachate_Na_mg_L',
                Leachate_S_mg_L_unfilt = 'Leachate_S_mg_L',
                Leachate_Al_mg_L_unfilt = 'Leachate_Al_mg_L',
                Leachate_Fe_mg_L_unfilt = 'Leachate_Fe_mg_L') %>%
  select(Sample_ID, Leachate_Ca_mg_L_unfilt,  Leachate_Mg_mg_L_unfilt, Leachate_P_mg_L_unfilt, Leachate_K_mg_L_unfilt, Leachate_Na_mg_L_unfilt, Leachate_S_mg_L_unfilt, Leachate_Al_mg_L_unfilt, Leachate_Fe_mg_L_unfilt)


#did not remove samples with deviations but did modify flags: negative values were replaced with zero, below LOD were replaced with NA, and above/below standard curve were replaced with the value (value is corrected for dilution and subtracted by unreactive P to correct for color interference)
#only used concentrations above the high standard if within 15% of it
MBD_Leachate_clean <- essdive_template_cleaning(MBD) %>%
  dplyr::rename(Sample_ID = 'Sample_Name',
                MBD_P_mg_per_L_filt0.7 = 'MBD_P_mg_per_L') %>%
  mutate(MBD_P_mg_per_L_filt0.7 = case_when(
                MBD_P_mg_per_L_filt0.7 == -9999 ~ NA,
                str_detect(MBD_P_mg_per_L_filt0.7, "negative") ~ NA, 
                str_detect(MBD_P_mg_per_L_filt0.7, "LOD") ~ NA, 
                str_detect(Sample_ID, "50A") ~ NA, #hihger than 15% of high standard
                str_detect(MBD_P_mg_per_L_filt0.7, "MBD_Below") ~ 
                str_extract(MBD_P_mg_per_L_filt0.7, "\\d+\\.?\\d*(?=_ppm_Final_Corrected)"),
                str_detect(MBD_P_mg_per_L_filt0.7, "MBD_Above") ~ 
                str_extract(MBD_P_mg_per_L_filt0.7, "\\d+\\.?\\d*(?=_ppm_Final_Corrected)"),
                TRUE ~ MBD_P_mg_per_L_filt0.7)) %>%
  mutate_at(c(2), as.numeric) %>%
  filter(grepl('filt', Sample_ID)) %>%
  separate(col=Sample_ID, into = c("Sample_ID", "FilterSize"), sep="-") %>%
  select(Sample_ID, MBD_P_mg_per_L_filt0.7) %>%
  filter(Sample_ID != "BSLE_0073C") #remove 73C because below limit of quantification

#didn't need to modify b/c no text strings
ICP_PNMR_clean <- essdive_template_cleaning(ICP_PNMR) %>%
  dplyr::rename(Parent_ID = 'Sample_Name') %>%
  mutate_at(c(2:8), as.numeric) %>%
  filter(grepl('solid', Parent_ID)) %>%
  separate(col=Parent_ID, into = c("Parent_ID", "FilterSize"), sep="-") %>%
  select(Parent_ID, Total_Extractable_Ca_mg_per_kg,  Total_Extractable_Mg_mg_per_kg, Total_Extractable_P_mg_per_kg, Total_Extractable_K_mg_per_kg,  Total_Extractable_S_mg_per_kg, Total_Extractable_Al_mg_per_kg, Total_Extractable_Fe_mg_per_kg) 

XANES_clean <- XANES %>%
  select(-where(~all(is.na(.)))) %>%
  mutate(XANES_Po = rowSums(select(., contains("Po")), na.rm = TRUE)) %>%
  mutate(XANES_Pi = rowSums(select(., contains("Pi")), na.rm = TRUE)) %>%
  mutate(XANES_Fe = rowSums(select(., contains("Fe")), na.rm = TRUE)) %>%
  mutate(XANES_Na = rowSums(select(., contains("Pi_Na") | contains("Po_Na")), na.rm = TRUE)) %>%
  mutate(XANES_Ca = rowSums(select(., contains("Ca") | contains("Apatite")), na.rm = TRUE)) %>%
  mutate(XANES_Al = rowSums(select(., contains("Al")), na.rm = TRUE)) %>%
  mutate(XANES_Mg = rowSums(select(., contains("Mg") | contains("NH4_Mg")), na.rm = TRUE)) %>%
  mutate(XANES_K = rowSums(select(., contains("K")), na.rm = TRUE)) %>%
  mutate(XANES_Pi_Fe = rowSums(select(., contains("Pi_Fe")), na.rm = TRUE)) %>%
  mutate(XANES_Pi_Na = rowSums(select(., contains("Pi_Na")), na.rm = TRUE)) %>%
  mutate(XANES_Pi_Ca = rowSums(select(., contains("Pi_Ca") | contains("Apatite")), na.rm = TRUE)) %>%
  mutate(XANES_Pi_Al = rowSums(select(., contains("Pi_Al")), na.rm = TRUE)) %>%
  mutate(XANES_Pi_Mg = rowSums(select(., contains("Pi_Mg") | contains("NH4_Mg")), na.rm = TRUE)) %>%
  mutate(XANES_Pi_K = rowSums(select(., contains("Pi_K")), na.rm = TRUE)) %>%
  mutate(XANES_Po_Fe = rowSums(select(., contains("Po_Fe")), na.rm = TRUE)) %>%
  mutate(XANES_Po_Na = rowSums(select(., contains("Po_Na")), na.rm = TRUE)) %>%
  mutate(XANES_Po_Ca = rowSums(select(., contains("Po_Ca")), na.rm = TRUE)) %>%
  mutate(XANES_Po_Al = rowSums(select(., contains("Po_Al")), na.rm = TRUE)) %>%
  mutate(XANES_Po_Mg = rowSums(select(., contains("Po_Mg")), na.rm = TRUE)) %>%
  mutate(XANES_Po_K = rowSums(select(., contains("Po_K")), na.rm = TRUE)) %>%
  separate(col=Sample_Name, into = c("Parent_ID", "FilterSize"), sep="-") %>%
  filter(str_detect(FilterSize, "solid"))

NMR_clean <- NMR %>%
  separate(col=Sample_Name, into = c("Parent_ID", "FilterSize"), sep="-") 
```


```{r combine and format data}
data <- Meta %>%
  full_join(SolidCN_clean, by = 'Parent_ID') %>%
  full_join(ICP_Solid_clean, by = 'Parent_ID') %>%
  full_join(ICP_PNMR_clean, by = 'Parent_ID') %>%
  full_join(npoctdn_clean, by = 'Sample_ID') %>%
  full_join(ICP_Leachate_Filt_clean, by = 'Sample_ID') %>%
  full_join(ICP_Leachate_Unfilt_clean, by = 'Sample_ID') %>%
  full_join(MBD_Leachate_clean, by = 'Sample_ID') %>%
  full_join(pH_clean, by = 'Sample_ID') %>%
  mutate_at(c(6:44), as.numeric) %>%
  filter(!is.na(Solid_P_mg_kg))

data$Burn_Severity=factor(data$Burn_Severity, levels= c("Unburned", "Low", "Moderate", "High"))

#create a dataframe for only solids figures and stats to prevent having reps count as extra samples; add NMR data
data_solids <- data %>%
  filter(str_detect(Sample_ID, "A")) %>%
  select(1:24) %>%
  left_join(NMR_clean) %>%
  left_join(XANES_clean)

data_solids$Burn_Severity=factor(data_solids$Burn_Severity, levels= c("Unburned", "Low", "Moderate", "High"))

#keep XANES separate too
XANES_clean<- Meta %>%
  full_join(XANES_clean, by = 'Parent_ID') %>%
  filter(str_detect(Sample_ID, "A")) %>%
  mutate(Burn_Treatment = as.character(Burn_Treatment)) %>%
  filter(Burn_Treatment %in% c("burn table" , "raw")) %>%
  filter(Land_Coverage_Category %in% c("Douglas-fir forest" , "Sagebrush shrubland")) %>%
  filter(!is.na(FilterSize))
```

####Additional Calcs
```{r Calcs}
#NMR extraction efficiency
data_solids<-data_solids %>%
  mutate(NMR_EE_P_perc=Total_Extractable_P_mg_per_kg/Solid_P_mg_kg*100)

#convert C and N of solids from percent to mg/kg
data_solids<-data_solids %>%
  mutate(Solid_C_mg_kg = (C_weight_per*10000),
  Solid_N_mg_kg = (N_weight_per*10000))


#convert to P relative to solid mass and water volume for Molybdate
data<-data %>%
  mutate(MBD_P_mg_kgchar = MBD_P_mg_per_L_filt0.7*Leachate_vol_mL/Char_leached_g*1000/1000) 

#normalize by P concentration in solid char for Molybdate
data<-data %>%
  mutate(MBD_P_percentofsolid = MBD_P_mg_kgchar/Solid_P_mg_kg*100)

#calculate particulate concentrations as the difference between filtered and unfiltered
data<-data %>%
  mutate(Leachate_Ca_mg_L_part = Leachate_Ca_mg_L_unfilt - Leachate_Ca_mg_L_filt0.7) %>%
  mutate(Leachate_Mg_mg_L_part = Leachate_Mg_mg_L_unfilt - Leachate_Mg_mg_L_filt0.7) %>%
  mutate(Leachate_P_mg_L_part = Leachate_P_mg_L_unfilt - Leachate_P_mg_L_filt0.7) %>%
  mutate(Leachate_K_mg_L_part = Leachate_K_mg_L_unfilt - Leachate_K_mg_L_filt0.7) %>%
  mutate(Leachate_Na_mg_L_part = Leachate_Na_mg_L_unfilt - Leachate_Na_mg_L_filt0.7) %>%
  mutate(Leachate_S_mg_L_part = Leachate_S_mg_L_unfilt - Leachate_S_mg_L_filt0.7) %>%
  mutate(Leachate_Al_mg_L_part = Leachate_Al_mg_L_unfilt - Leachate_Al_mg_L_filt0.7) %>%
  mutate(Leachate_Fe_mg_L_part = Leachate_Fe_mg_L_unfilt - Leachate_Fe_mg_L_filt0.7)

#convert to P relative to solid mass and water volume for the soluble and particulate fractions
data<-data %>%
  mutate(Leachate_Ca_mg_kgchar_part = Leachate_Ca_mg_L_part*Leachate_vol_mL/Char_leached_g*1000/1000) %>%
  mutate(Leachate_Mg_mg_kgchar_part  = Leachate_Mg_mg_L_part*Leachate_vol_mL/Char_leached_g*1000/1000) %>%
  mutate(Leachate_P_mg_kgchar_part  = Leachate_P_mg_L_part*Leachate_vol_mL/Char_leached_g*1000/1000) %>%
  mutate(Leachate_K_mg_kgchar_part  = Leachate_K_mg_L_part*Leachate_vol_mL/Char_leached_g*1000/1000) %>%
  mutate(Leachate_Na_mg_kgchar_part  = Leachate_Na_mg_L_part*Leachate_vol_mL/Char_leached_g*1000/1000) %>%
  mutate(Leachate_S_mg_kgchar_part  = Leachate_S_mg_L_part*Leachate_vol_mL/Char_leached_g*1000/1000) %>%
  mutate(Leachate_Al_mg_kgchar_part  = Leachate_Al_mg_L_part*Leachate_vol_mL/Char_leached_g*1000/1000) %>%
  mutate(Leachate_Fe_mg_kgchar_part  = Leachate_Fe_mg_L_part*Leachate_vol_mL/Char_leached_g*1000/1000) %>%
  mutate(Leachate_Ca_mg_kgchar_filt0.7 = Leachate_Ca_mg_L_filt0.7*Leachate_vol_mL/Char_leached_g*1000/1000) %>%
  mutate(Leachate_Mg_mg_kgchar_filt0.7 = Leachate_Mg_mg_L_filt0.7*Leachate_vol_mL/Char_leached_g*1000/1000) %>%
  mutate(Leachate_P_mg_kgchar_filt0.7 = Leachate_P_mg_L_filt0.7*Leachate_vol_mL/Char_leached_g*1000/1000) %>%
  mutate(Leachate_K_mg_kgchar_filt0.7 = Leachate_K_mg_L_filt0.7*Leachate_vol_mL/Char_leached_g*1000/1000) %>%
  mutate(Leachate_Na_mg_kgchar_filt0.7 = Leachate_Na_mg_L_filt0.7*Leachate_vol_mL/Char_leached_g*1000/1000) %>%
  mutate(Leachate_S_mg_kgchar_filt0.7 = Leachate_S_mg_L_filt0.7*Leachate_vol_mL/Char_leached_g*1000/1000) %>%
  mutate(Leachate_Al_mg_kgchar_filt0.7 = Leachate_Al_mg_L_filt0.7*Leachate_vol_mL/Char_leached_g*1000/1000) %>%
  mutate(Leachate_Fe_mg_kgchar_filt0.7 = Leachate_Fe_mg_L_filt0.7*Leachate_vol_mL/Char_leached_g*1000/1000) %>%
  mutate(Leachate_Ca_mg_kgchar_unfilt = Leachate_Ca_mg_L_unfilt*Leachate_vol_mL/Char_leached_g*1000/1000) %>%
  mutate(Leachate_Mg_mg_kgchar_unfilt  = Leachate_Mg_mg_L_unfilt*Leachate_vol_mL/Char_leached_g*1000/1000) %>%
  mutate(Leachate_P_mg_kgchar_unfilt = Leachate_P_mg_L_unfilt*Leachate_vol_mL/Char_leached_g*1000/1000) %>%
  mutate(Leachate_K_mg_kgchar_unfilt  = Leachate_K_mg_L_unfilt*Leachate_vol_mL/Char_leached_g*1000/1000) %>%
  mutate(Leachate_Na_mg_kgchar_unfilt  = Leachate_Na_mg_L_unfilt*Leachate_vol_mL/Char_leached_g*1000/1000) %>%
  mutate(Leachate_S_mg_kgchar_unfilt  = Leachate_S_mg_L_unfilt*Leachate_vol_mL/Char_leached_g*1000/1000) %>%
  mutate(Leachate_Al_mg_kgchar_unfilt  = Leachate_Al_mg_L_unfilt*Leachate_vol_mL/Char_leached_g*1000/1000) %>%
  mutate(Leachate_Fe_mg_kgchar_unfilt = Leachate_Fe_mg_L_unfilt*Leachate_vol_mL/Char_leached_g*1000/1000)

#convert solid elemental concentrations from to g/kg
data_solids<-data_solids %>%
  mutate(Solid_P_g_kg = Solid_P_mg_kg/1000) %>%
  mutate(Solid_Ca_g_kg = Solid_Ca_mg_kg/1000) %>%
  mutate(Solid_Fe_g_kg = Solid_Fe_mg_kg/1000) %>%
  mutate(Solid_Al_g_kg = Solid_Al_mg_kg/1000) %>%
  mutate(Solid_K_g_kg = Solid_K_mg_kg/1000) %>%
  mutate(Solid_Mg_g_kg = Solid_Mg_mg_kg/1000) %>%
  mutate(Solid_Na_g_kg = Solid_Na_mg_kg/1000) %>%
  mutate(Solid_S_g_kg = Solid_S_mg_kg/1000) %>%
  mutate(Solid_C_g_kg = C_weight_per/100*1000) %>%
  mutate(Solid_N_g_kg = N_weight_per/100*1000)

#normalize by P concentration in solid char fix
data<-data %>%
  mutate(Leachate_Ca_perc_solid_part = Leachate_Ca_mg_kgchar_part/Solid_P_mg_kg*100) %>%
  mutate(Leachate_Mg_perc_solid_part = Leachate_Mg_mg_kgchar_part/Solid_P_mg_kg*100) %>%
  mutate(Leachate_P_perc_solid_part = Leachate_P_mg_kgchar_part/Solid_P_mg_kg*100) %>%
  mutate(Leachate_K_perc_solid_part = Leachate_K_mg_kgchar_part/Solid_P_mg_kg*100) %>%
  mutate(Leachate_Na_perc_solid_part = Leachate_Na_mg_kgchar_part/Solid_P_mg_kg*100) %>%
  mutate(Leachate_S_perc_solid_part = Leachate_S_mg_kgchar_part/Solid_P_mg_kg*100) %>%
  mutate(Leachate_Al_perc_solid_part = Leachate_Al_mg_kgchar_part/Solid_P_mg_kg*100) %>%
  mutate(Leachate_Fe_perc_solid_part = Leachate_Fe_mg_kgchar_part/Solid_P_mg_kg*100) %>%
  mutate(Leachate_Ca_perc_solid_filt0.7 = Leachate_Ca_mg_kgchar_filt0.7/Solid_P_mg_kg*100) %>%
  mutate(Leachate_Mg_perc_solid_filt0.7 = Leachate_Mg_mg_kgchar_filt0.7/Solid_P_mg_kg*100) %>%
  mutate(Leachate_P_perc_solid_filt0.7 = Leachate_P_mg_kgchar_filt0.7/Solid_P_mg_kg*100) %>%
  mutate(Leachate_K_perc_solid_filt0.7 = Leachate_K_mg_kgchar_filt0.7/Solid_P_mg_kg*100) %>%
  mutate(Leachate_Na_perc_solid_filt0.7 = Leachate_Na_mg_kgchar_filt0.7/Solid_P_mg_kg*100) %>%
  mutate(Leachate_S_perc_solid_filt0.7 = Leachate_S_mg_kgchar_filt0.7/Solid_P_mg_kg*100) %>%
  mutate(Leachate_Al_perc_solid_filt0.7 = Leachate_Al_mg_kgchar_filt0.7/Solid_P_mg_kg*100) %>%
  mutate(Leachate_Fe_perc_solid_filt0.7 = Leachate_Fe_mg_kgchar_filt0.7/Solid_P_mg_kg*100)

#molar stoichiometry of P:element in solid phase fix
test<-data_solids %>%
  mutate(Fe.P.MolarRatio=(Solid_Fe_mg_kg/55.845/1000)/(Solid_P_mg_kg/30.97/1000))%>%
  mutate(K.P.MolarRatio=(Solid_K_mg_kg/39.0983/1000)/(Solid_P_mg_kg/30.97/1000))%>%
  mutate(Na.P.MolarRatio=(Solid_Na_mg_kg/22.989/1000)/(Solid_P_mg_kg/30.97/1000))%>%
  mutate(Al.P.MolarRatio=(Solid_Al_mg_kg/26.982/1000)/(Solid_P_mg_kg/30.97/1000))%>%
  mutate(Mg.P.MolarRatio=(Solid_Mg_mg_kg/24.305/1000)/(Solid_P_mg_kg/30.97/1000))%>%
  mutate(Ca.P.MolarRatio=(Solid_Ca_mg_kg/40.078/1000)/(Solid_P_mg_kg/30.97/1000))%>%
  mutate(S.P.MolarRatio=(Solid_S_mg_kg/32.065/1000)/(Solid_P_mg_kg/30.97/1000))



#molar stoichiometry of P:element in particulate phase

#molar stoichiometry of P:element in <0.7 phase



#save csv of final collated data with manipulations
write.csv(data, "../data/data.csv") #all data
write.csv(data_solids, "../data/data_solids.csv") #solids only
```


##Figures and Stats
```{r}
#import data so you don't have to run above code

data <- read_csv("../data/data.csv")
data_solids <- read_csv("../data/data_solids.csv")
```

####summary stats
```{r solids and leachate summary}

#solid elemental concentrations, NMR, and XANES summary
summary_solids_conc <- data_solids %>%
  dplyr::group_by(Burn_Severity, Land_Coverage_Category) %>%
  dplyr::summarize(
    P_Mean = mean(Solid_P_g_kg, na.rm = TRUE),
    P_Standard_Deviation = sd(Solid_P_g_kg, na.rm = TRUE),
    Ca_Mean = mean(Solid_Ca_g_kg, na.rm = TRUE),
    Ca_Standard_Deviation = sd(Solid_Ca_g_kg, na.rm = TRUE),
    Fe_Mean = mean(Solid_Fe_g_kg, na.rm = TRUE),
    Fe_Standard_Deviation = sd(Solid_Fe_g_kg, na.rm = TRUE),
    Al_Mean = mean(Solid_Al_g_kg, na.rm = TRUE),
    Al_Standard_Deviation = sd(Solid_Al_g_kg, na.rm = TRUE),
    K_Mean = mean(Solid_K_g_kg, na.rm = TRUE),
    K_Standard_Deviation = sd(Solid_K_g_kg, na.rm = TRUE),
    Mg_Mean = mean(Solid_Mg_g_kg, na.rm = TRUE),
    Mg_Standard_Deviation = sd(Solid_Mg_g_kg, na.rm = TRUE),
    Na_Mean = mean(Solid_Na_g_kg, na.rm = TRUE),
    Na_Standard_Deviation = sd(Solid_Na_g_kg, na.rm = TRUE),
    S_Mean = mean(Solid_S_g_kg, na.rm = TRUE),
    S_Standard_Deviation = sd(Solid_S_g_kg, na.rm = TRUE),
    C_Mean = mean(Solid_C_g_kg, na.rm = TRUE),
    C_Standard_Deviation = sd(Solid_C_g_kg, na.rm = TRUE),
    N_Mean = mean(Solid_N_g_kg, na.rm = TRUE),
    N_Standard_Deviation = sd(Solid_N_g_kg, na.rm = TRUE),
    Ortho_Mean = mean(Ortho, na.rm = TRUE),
    Ortho_Standard_Deviation = sd(Ortho, na.rm = TRUE),
    Mono_Mean = mean(Mono, na.rm = TRUE),
    Mono_Standard_Deviation = sd(Mono, na.rm = TRUE),
    Di_Mean = mean(Di, na.rm = TRUE),
    Di_Standard_Deviation = sd(Di, na.rm = TRUE),
    Pyro_Mean = mean(Pyro, na.rm = TRUE),
    Pyro_Standard_Deviation = sd(Pyro, na.rm = TRUE),
    XANES_Po_Mean = mean(XANES_Po, na.rm = TRUE),
    XANES_Po_Standard_Deviation = sd(XANES_Po, na.rm = TRUE),
    XANES_Pi_Mean = mean(XANES_Pi, na.rm = TRUE),
    XANES_Pi_Standard_Deviation = sd(XANES_Pi, na.rm = TRUE),
    XANES_Fe_Mean = mean(XANES_Fe, na.rm = TRUE),
    XANES_Fe_Standard_Deviation = sd(XANES_Fe, na.rm = TRUE),
    XANES_Na_Mean = mean(XANES_Na, na.rm = TRUE),
    XANES_Na_Standard_Deviation = sd(XANES_Na, na.rm = TRUE),
    XANES_Ca_Mean = mean(XANES_Ca, na.rm = TRUE),
    XANES_Ca_Standard_Deviation = sd(XANES_Ca, na.rm = TRUE),
    XANES_Al_Mean = mean(XANES_Al, na.rm = TRUE),
    XANES_Al_Standard_Deviation = sd(XANES_Al, na.rm = TRUE),
    XANES_Mg_Mean = mean(XANES_Mg, na.rm = TRUE),
    XANES_Mg_Standard_Deviation = sd(XANES_Mg, na.rm = TRUE),
    XANES_K_Mean = mean(XANES_K, na.rm = TRUE),
    XANES_K_Standard_Deviation = sd(XANES_K, na.rm = TRUE),
    XANES_Pi_Fe_Mean = mean(XANES_Pi_Fe, na.rm = TRUE),
    XANES_Pi_Fe_Standard_Deviation = sd(XANES_Pi_Fe, na.rm = TRUE),
    XANES_Pi_Na_Mean = mean(XANES_Pi_Na, na.rm = TRUE),
    XANES_Pi_Na_Standard_Deviation = sd(XANES_Pi_Na, na.rm = TRUE),
    XANES_Pi_Ca_Mean = mean(XANES_Pi_Ca, na.rm = TRUE),
    XANES_Pi_Ca_Standard_Deviation = sd(XANES_Pi_Ca, na.rm = TRUE),
    XANES_Pi_Al_Mean = mean(XANES_Pi_Al, na.rm = TRUE),
    XANES_Pi_Al_Standard_Deviation = sd(XANES_Pi_Al, na.rm = TRUE),
    XANES_Pi_Mg_Mean = mean(XANES_Pi_Mg, na.rm = TRUE),
    XANES_Pi_Mg_Standard_Deviation = sd(XANES_Pi_Mg, na.rm = TRUE),
    XANES_Pi_K_Mean = mean(XANES_Pi_K, na.rm = TRUE),
    XANES_Pi_K_Standard_Deviation = sd(XANES_Pi_K, na.rm = TRUE),
    XANES_Po_Fe_Mean = mean(XANES_Po_Fe, na.rm = TRUE),
    XANES_Po_Fe_Standard_Deviation = sd(XANES_Po_Fe, na.rm = TRUE),
    XANES_Po_Na_Mean = mean(XANES_Po_Na, na.rm = TRUE),
    XANES_Po_Na_Standard_Deviation = sd(XANES_Po_Na, na.rm = TRUE),
    XANES_Po_Ca_Mean = mean(XANES_Po_Ca, na.rm = TRUE),
    XANES_Po_Ca_Standard_Deviation = sd(XANES_Po_Ca, na.rm = TRUE),
    XANES_Po_Al_Mean = mean(XANES_Po_Al, na.rm = TRUE),
    XANES_Po_Al_Standard_Deviation = sd(XANES_Po_Al, na.rm = TRUE),
    XANES_Po_Mg_Mean = mean(XANES_Po_Mg, na.rm = TRUE),
    XANES_Po_Mg_Standard_Deviation = sd(XANES_Po_Mg, na.rm = TRUE),
    XANES_Po_K_Mean = mean(XANES_Po_K, na.rm = TRUE),
    XANES_Po_K_Standard_Deviation = sd(XANES_Po_K, na.rm = TRUE),
    Count = n()
  )

                   
write.csv(summary_solids_conc, "../data/summary_solids_conc.csv") #save this for a table


#NMR extraction efficiency
summary_solids <- data_solids %>%
  dplyr::group_by(Burn_Severity, Land_Coverage_Category) %>%
  dplyr::summarize(
    Mean = mean(NMR_EE_P_perc, na.rm = TRUE),
    Standard_Deviation = sd(NMR_EE_P_perc, na.rm = TRUE),
    Count = n()
  )

#leachate concentrations
P.Conc.leach<- data %>%
  dplyr::group_by(Burn_Severity, Land_Coverage_Category) %>%
  dplyr::summarize(
    Leachate_P_mg_kgchar_part_Mean = mean(Leachate_P_mg_kgchar_part, na.rm = TRUE),
    Leachate_P_mg_kgchar_part_Standard_Deviation = sd(Leachate_P_mg_kgchar_part, na.rm = TRUE),
    Count = n(),
    Leachate_P_mg_kgchar_filt0.7_Mean = mean(Leachate_P_mg_kgchar_filt0.7, na.rm = TRUE),
    Leachate_P_mg_kgchar_filt0.7_Standard_Deviation = sd(Leachate_P_mg_kgchar_filt0.7, na.rm = TRUE),
    Leachate_P_mg_kgchar_unfilt_Mean = mean(Leachate_P_mg_kgchar_unfilt, na.rm = TRUE),
    Leachate_P_mg_kgchar_unfilt_Standard_Deviation = sd(Leachate_P_mg_kgchar_unfilt, na.rm = TRUE)
  )


  
```

####Molybdate
```{r MBD fig and stats}
#MBD mg/L figure
ggplot(data, aes(x=Burn_Severity, y=MBD_P_mg_per_L_filt0.7, fill=Land_Coverage_Category))+geom_boxplot(show.legend=FALSE)+theme_classic()+ylab(expression(paste(Soluble~Reactive~P~(mg~P~L^-1), sep="")))+ xlab("Burn Severity")+scale_fill_manual(values=c("#346648", "#dbb40d"))+facet_grid(.~Land_Coverage_Category)+theme(text = element_text(size = 15))

#MBD mg/kg figure; likely use this one for publication
MBD.BS.fig<-ggplot(data, aes(x=Burn_Severity, y=MBD_P_mg_kgchar/1000, fill=Land_Coverage_Category))+geom_boxplot(show.legend=FALSE)+theme_classic()+ylab(expression(paste(Soluble~Reactive~P~(g~P~kg^-1), sep="")))+ xlab("Burn Severity")+scale_fill_manual(values=c("#346648", "#dbb40d"))+facet_grid(.~Land_Coverage_Category)+theme(text = element_text(size = 15))

cowplot::save_plot("../figures/MBD.BS.fig.pdf", MBD.BS.fig, ncol = 1, nrow = 1, base_aspect_ratio= 2:1, dpi=72)

#MBD as percent of solid P concentration figure
ggplot(data, aes(x=Burn_Severity, y=MBD_P_percentofsolid, fill=Land_Coverage_Category))+geom_boxplot(show.legend=FALSE)+theme_classic()+ylab("Soluble Reactive P (%)")+ xlab("Burn Severity")+scale_fill_manual(values=c("#346648", "#dbb40d"))+facet_grid(.~Land_Coverage_Category)+theme(text = element_text(size = 15))

#note: I think would be okay with this model b/c I would only need to interpret the interaction since it is significant
#MBD mg/kg stats; likely use this one for publication
#need to figure out how to transform the data to meet assumptions
model<-lmer(log(MBD_P_mg_kgchar)~Burn_Severity*Land_Coverage_Category+(1|Parent_ID), data=data) #if want to use maximum likelihood , REML=FALSE
model.BS<-lmer(log(MBD_P_mg_kgchar)~Land_Coverage_Category+(1|Parent_ID), data=data)
model.LC<-lmer(log(MBD_P_mg_kgchar)~Burn_Severity+(1|Parent_ID), data=data)
model.int<-lmer(log(MBD_P_mg_kgchar)~Burn_Severity+Land_Coverage_Category+(1|Parent_ID), data=data)
anova(model,model.BS) #not sig
anova(model,model.LC) #sig
anova(model,model.int) #sig
#summary(model)
vif(model)
#check normality of residuals 
ggqqplot(residuals(model))
shapiro_test(residuals(model)) #sig = bad 
#check homogeneity of variance assumption 
data %>% levene_test(log(MBD_P_mg_kgchar) ~ Burn_Severity*Land_Coverage_Category) #sig = bad
#leveneTest(residuals(model) ~ MBD$Burn_Severity*Land_Coverage_Category)
#plotNormalHistogram(residuals(model))
#qqnorm(residuals(model))
#qqline(residuals(model), col="blue")

#POST HOCs: land cover and interaction were significant in the main model
#burn severity post hoc: is burn severity significant across all land covers?
emmeans::lsmeans(model, list(pairwise~Burn_Severity), adjust="tukey") #only get results for raw-low, raw-mod, low-mod (no comparison to high)
#land cover post hoc: is sage sig different than doug across all severities?
emmeans::lsmeans(model, list(pairwise~Land_Coverage_Category), adjust="tukey") #don't get any results
#interaction post hoc: Is the relationship sage has with severity different than doug?
emmeans::lsmeans(model, pairwise~Burn_Severity*Land_Coverage_Category, at=list(Burn_Severity="Unburned"),adjust="tukey") #between doug and sage at unburned severity
emmeans::lsmeans(model, pairwise~Burn_Severity*Land_Coverage_Category, at=list(Burn_Severity="Low"),adjust="tukey") #between doug and sage at low severity
emmeans::lsmeans(model, pairwise~Burn_Severity*Land_Coverage_Category, at=list(Burn_Severity="Moderate"),adjust="tukey") #between doug and sage at mod severity
emmeans::lsmeans(model, pairwise~Burn_Severity*Land_Coverage_Category, at=list(Burn_Severity="High"),adjust="tukey") #can't run b/c no sage high
emmeans::lsmeans(model, pairwise~Burn_Severity*Land_Coverage_Category, at=list(Land_Coverage_Category="Douglas-fir forest"),adjust="tukey") #within doug how BS changes
emmeans::lsmeans(model, pairwise~Burn_Severity*Land_Coverage_Category, at=list(Land_Coverage_Category="Sagebrush shrubland"),adjust="tukey") #within sage how BS changes

```


####ICP Leachates
```{r leachate ICP fig and stats}
#convert to percent of total P in unfiltered sample
#ICP$P.filt.percentofunfilt<-(ICP$Total_P_mg_per_L_filt/ICP$Total_P_mg_per_L_unfilt)*100
#ICP$P.part.percentofunfilt<-(ICP$Total_P_mg_per_L_part/ICP$Total_P_mg_per_L_unfilt)*100

#total P in unfilted leachate
Leachate.total.P.BS.boxplot <- ggplot(data, aes(x=Burn_Severity, y=Leachate_P_mg_kgchar_unfilt, fill=Land_Coverage_Category))+geom_boxplot(show.legend=FALSE)+theme_classic()+ylab(expression(paste(Total~P~(mg~P~kg^-1), sep="")))+ xlab("Burn Severity")+scale_fill_manual(values=c("#346648", "#dbb40d"))+facet_grid(.~Land_Coverage_Category)+theme(text = element_text(size = 15))

cowplot::save_plot("../figures/Leachate.total.P.BS.boxplot.pdf", Leachate.total.P.BS.boxplot, ncol = 1, nrow = 1, base_aspect_ratio= 2:1, dpi=72)

model<-lmer(log(Leachate_P_mg_kgchar_unfilt)~Burn_Severity*Land_Coverage_Category+(1|Parent_ID), data=data)
model.BS<-lmer(log(Leachate_P_mg_kgchar_unfilt)~Land_Coverage_Category+(1|Parent_ID), data=data)
model.LC<-lmer(log(Leachate_P_mg_kgchar_unfilt)~Burn_Severity+(1|Parent_ID), data=data)
model.int<-lmer(log(Leachate_P_mg_kgchar_unfilt)~Burn_Severity+Land_Coverage_Category+(1|Parent_ID), data=data)
anova(model,model.BS) #sig
anova(model,model.LC) #sig
anova(model,model.int) #sig
summary(model)
vif(model)
#check normality of residuals 
ggqqplot(residuals(model))
shapiro_test(residuals(model)) #sig = bad 
#check homogeneity of variance assumption 
#MBD %>% levene_test(log(Leachate_P_mg_kgchar_unfilt) ~ Burn_Severity*Land_Coverage_Category)

#POST HOCs: burn severity. land cover, and interaction were significant in the main model
#burn severity post hoc: is burn severity significant across all land covers?
emmeans::lsmeans(model, list(pairwise~Burn_Severity), adjust="tukey") #only get results for raw-low, raw-mod, low-mod (no comparison to high)
#land cover post hoc: is sage sig different than doug across all severities?
emmeans::lsmeans(model, list(pairwise~Land_Coverage_Category), adjust="tukey") #don't get any results
#interaction post hoc: Is the relationship sage has with severity different than doug?
emmeans::lsmeans(model, pairwise~Burn_Severity*Land_Coverage_Category, at=list(Burn_Severity="Unburned"),adjust="tukey") #between doug and sage at unburned severity
emmeans::lsmeans(model, pairwise~Burn_Severity*Land_Coverage_Category, at=list(Burn_Severity="Low"),adjust="tukey") #between doug and sage at low severity
emmeans::lsmeans(model, pairwise~Burn_Severity*Land_Coverage_Category, at=list(Burn_Severity="Moderate"),adjust="tukey") #between doug and sage at mod severity
emmeans::lsmeans(model, pairwise~Burn_Severity*Land_Coverage_Category, at=list(Burn_Severity="High"),adjust="tukey") #can't run b/c no sage high
emmeans::lsmeans(model, pairwise~Burn_Severity*Land_Coverage_Category, at=list(Land_Coverage_Category="Douglas-fir forest"),adjust="tukey") #within doug how BS changes
emmeans::lsmeans(model, pairwise~Burn_Severity*Land_Coverage_Category, at=list(Land_Coverage_Category="Sagebrush shrubland"),adjust="tukey") #within sage how BS changes

Leachate.filt0.7.total.P.BS.boxplot <- ggplot(data, aes(x=Burn_Severity, y=Leachate_P_mg_kgchar_filt0.7, fill=Land_Coverage_Category))+geom_boxplot(show.legend=FALSE)+theme_classic()+ylab(expression(paste(Total~Soluble~P~(mg~P~kg^-1), sep="")))+ xlab("Burn Severity")+scale_fill_manual(values=c("#346648", "#dbb40d"))+facet_grid(.~Land_Coverage_Category)+theme(text = element_text(size = 15))

cowplot::save_plot("../figures/Leachate.filt0.7.total.P.BS.boxplot.pdf", Leachate.filt0.7.total.P.BS.boxplot, ncol = 1, nrow = 1, base_aspect_ratio= 2:1, dpi=72)

Leachate.unfilt.total.P.BS.boxplot <- ggplot(data, aes(x=Burn_Severity, y=Leachate_P_mg_kgchar_part, fill=Land_Coverage_Category))+geom_boxplot(show.legend=FALSE)+theme_classic()+ylab(expression(paste(Total~Particulate~P~(mg~P~kg^-1), sep="")))+ xlab("Burn Severity")+scale_fill_manual(values=c("#346648", "#dbb40d"))+facet_grid(.~Land_Coverage_Category)+theme(text = element_text(size = 15))

cowplot::save_plot("../figures/Leachate.unfilt.total.P.BS.boxplot.pdf", Leachate.unfilt.total.P.BS.boxplot, ncol = 1, nrow = 1, base_aspect_ratio= 2:1, dpi=72)


#stacked bar chart
P.Conc.leach.bar <- P.Conc.leach %>%
  mutate(sd.high=Leachate_P_mg_kgchar_unfilt_Mean+Leachate_P_mg_kgchar_unfilt_Standard_Deviation) %>%
  mutate(sd.low=Leachate_P_mg_kgchar_unfilt_Mean-Leachate_P_mg_kgchar_unfilt_Standard_Deviation)


P.Conc.leach_melt<-melt(P.Conc.leach.bar, id=c("Burn_Severity", "Land_Coverage_Category","sd.low", "sd.high")) %>%
  filter(variable %in% c("Leachate_P_mg_kgchar_part_Mean" , "Leachate_P_mg_kgchar_filt0.7_Mean"))

#here

Leachate_stacked_bar <- ggplot(subset(P.Conc.leach_melt, variable=="Leachate_P_mg_kgchar_part_Mean" | variable=="Leachate_P_mg_kgchar_filt0.7_Mean"), aes(x = Burn_Severity, y = value, fill=variable)) + geom_bar(stat = "identity")  + theme_classic()+ylab(expression(paste(Leachate~Mean~Total~P~(mg~P~kg^-1), sep="")))+ xlab("Burn Severity")+scale_fill_manual(values=c("#2274A5", "#E7DFC6"), labels = c("Particulate", "Soluble"), name = "")+facet_grid(.~Land_Coverage_Category)+theme(text = element_text(size = 15)) + geom_errorbar(aes(ymax=sd.high, ymin=sd.low), width = 0.2, size = 1, color = "black")

cowplot::save_plot("../figures/Leachate_stacked_bar.pdf", Leachate_stacked_bar, ncol = 1, nrow = 1, base_aspect_ratio= 2:1, dpi=72)


model<-lmer(log(Leachate_P_mg_kgchar_filt0.7)~Burn_Severity*Land_Coverage_Category+(1|Parent_ID), data=data)
model.BS<-lmer(log(Leachate_P_mg_kgchar_filt0.7)~Land_Coverage_Category+(1|Parent_ID), data=data)
model.LC<-lmer(log(Leachate_P_mg_kgchar_filt0.7)~Burn_Severity+(1|Parent_ID), data=data)
model.int<-lmer(log(Leachate_P_mg_kgchar_filt0.7)~Burn_Severity+Land_Coverage_Category+(1|Parent_ID), data=data)
anova(model,model.BS)
anova(model,model.LC) #sig
anova(model,model.int) #not sig but since BS also isn't sig I probably don't care that much about the LC main effect (so not being able to run the post hoc isn't an issue)
summary(model)
vif(model)
#check normality of residuals 
ggqqplot(residuals(model))
shapiro_test(residuals(model)) #sig = bad 
#check homogeneity of variance assumption 
MBD %>% levene_test(log(Leachate_P_mg_kgchar_filt0.7) ~ Burn_Severity*Land_Coverage_Category) 
#POST HOCs: land cover was the only significant main effect in the main model
#burn severity post hoc: is burn severity significant across all land covers?
emmeans::lsmeans(model, list(pairwise~Burn_Severity), adjust="tukey") #only get results for raw-low, raw-mod, low-mod (no comparison to high)
#land cover post hoc: is sage sig different than doug across all severities?
emmeans::lsmeans(model, list(pairwise~Land_Coverage_Category), adjust="tukey") #don't get any results
#interaction post hoc: Is the relationship sage has with severity different than doug?
emmeans::lsmeans(model, pairwise~Burn_Severity*Land_Coverage_Category, at=list(Burn_Severity="Unburned"),adjust="tukey") #between doug and sage at unburned severity
emmeans::lsmeans(model, pairwise~Burn_Severity*Land_Coverage_Category, at=list(Burn_Severity="Low"),adjust="tukey") #between doug and sage at low severity
emmeans::lsmeans(model, pairwise~Burn_Severity*Land_Coverage_Category, at=list(Burn_Severity="Moderate"),adjust="tukey") #between doug and sage at mod severity
emmeans::lsmeans(model, pairwise~Burn_Severity*Land_Coverage_Category, at=list(Burn_Severity="High"),adjust="tukey") #can't run b/c no sage high
emmeans::lsmeans(model, pairwise~Burn_Severity*Land_Coverage_Category, at=list(Land_Coverage_Category="Douglas-fir forest"),adjust="tukey") #within doug how BS changes
emmeans::lsmeans(model, pairwise~Burn_Severity*Land_Coverage_Category, at=list(Land_Coverage_Category="Sagebrush shrubland"),adjust="tukey") #within sage how BS changes


model<-lmer(log(Leachate_P_mg_kgchar_part)~Burn_Severity*Land_Coverage_Category+(1|Parent_ID), data=data)
model.BS<-lmer(log(Leachate_P_mg_kgchar_part)~Land_Coverage_Category+(1|Parent_ID), data=data)
model.LC<-lmer(log(Leachate_P_mg_kgchar_part)~Burn_Severity+(1|Parent_ID), data=data)
model.int<-lmer(log(Leachate_P_mg_kgchar_part)~Burn_Severity+Land_Coverage_Category+(1|Parent_ID), data=data)
anova(model,model.BS) #sig
anova(model,model.LC) #sig
anova(model,model.int) #sig
summary(model)
vif(model)
#check normality of residuals 
ggqqplot(residuals(model))
shapiro_test(residuals(model)) #sig = bad 
#check homogeneity of variance assumption 
#MBD %>% levene_test(log(Leachate_P_mg_kgchar_part) ~ Burn_Severity*Land_Coverage_Category) #not sig = good
#POST HOCs: land cover was the only significant main effect in the main model
#burn severity post hoc: is burn severity significant across all land covers?
emmeans::lsmeans(model, list(pairwise~Burn_Severity), adjust="tukey") #only get results for raw-low, raw-mod, low-mod (no comparison to high)
#land cover post hoc: is sage sig different than doug across all severities?
emmeans::lsmeans(model, list(pairwise~Land_Coverage_Category), adjust="tukey") #don't get any results
#interaction post hoc: Is the relationship sage has with severity different than doug?
emmeans::lsmeans(model, pairwise~Burn_Severity*Land_Coverage_Category, at=list(Burn_Severity="Unburned"),adjust="tukey") #between doug and sage at unburned severity
emmeans::lsmeans(model, pairwise~Burn_Severity*Land_Coverage_Category, at=list(Burn_Severity="Low"),adjust="tukey") #between doug and sage at low severity
emmeans::lsmeans(model, pairwise~Burn_Severity*Land_Coverage_Category, at=list(Burn_Severity="Moderate"),adjust="tukey") #between doug and sage at mod severity
emmeans::lsmeans(model, pairwise~Burn_Severity*Land_Coverage_Category, at=list(Burn_Severity="High"),adjust="tukey") #can't run b/c no sage high
emmeans::lsmeans(model, pairwise~Burn_Severity*Land_Coverage_Category, at=list(Land_Coverage_Category="Douglas-fir forest"),adjust="tukey") #within doug how BS changes
emmeans::lsmeans(model, pairwise~Burn_Severity*Land_Coverage_Category, at=list(Land_Coverage_Category="Sagebrush shrubland"),adjust="tukey") #within sage how BS changes
```

####Solid ICP
```{r solid fig and stats}
solid.P.BS.fig<-ggplot(data_solids, aes(x=Burn_Severity, y=Solid_P_mg_kg, fill=Land_Coverage_Category))+geom_boxplot(show.legend=FALSE)+theme_classic()+ylab(expression(paste(Solid~Total~P~(mg~P~kg^-1), sep="")))+ xlab("Burn Severity")+scale_fill_manual(values=c("#346648", "#dbb40d"))+facet_grid(.~Land_Coverage_Category)+theme(text = element_text(size = 15))

cowplot::save_plot("../figures/solid.P.BS.fig.pdf", solid.P.BS.fig, ncol = 1, nrow = 1, base_aspect_ratio= 2:1, dpi=72)

```


####Correlations
```{r elemental correlations}

#across both feedstocks
#subset only solid elemental concentrations (in mg/kg)
data_solids_corr <- data_solids %>%
  select(matches("Solid"))

# Rename columns by extracting everything between "Solid_" and "mg_Kg"
data_solids_corr <- data_solids_corr %>%
  rename_with(
    ~sub("Solid_(.*?)_mg_kg", "\\1", .),
    starts_with("Solid_")) %>%
  select(P, C, N, Ca, Mg, Na, Fe, Al, S, K)

#comput r=the correlation matrix, n=the matrix of the number of observations used in analyzing each pari fo variables, and P=the p-values corresponding to the significance levels of correlations
cor_5 <- rcorr(as.matrix(data_solids_corr), type=c("spearman"))
#define M as the correlation coefficient
M <- cor_5$r
#define p_mat as the p-value
p_mat <- cor_5$P 
#plot only significant pearson correlation coeffcients when p value >0.05
corrplot(M, type = "upper", p.mat = p_mat, sig.level = 0.05, insig = "blank", tl.col = "black", diag=FALSE, na.label="NA", tl.cex=1, cl.cex = 1, number.cex = 0.8, addCoef.col = "white", col = colorRampPalette(c("#346648", "#dbb40d"))(100))


#Douglas-fir forest
#subset only solid elemental concentrations (in mg/kg)
data_solids_corr <- data_solids  %>%
  filter(str_detect(Land_Coverage_Category, "Douglas")) %>%
  select(matches("Solid"))

# Rename columns by extracting everything between "Solid_" and "mg_Kg"
data_solids_corr <- data_solids_corr %>%
  rename_with(
    ~sub("Solid_(.*?)_mg_kg", "\\1", .),
    starts_with("Solid_")) %>%
  select(P, C, N, Ca, Mg, Na, Fe, Al, S, K)

#comput r=the correlation matrix, n=the matrix of the number of observations used in analyzing each pari fo variables, and P=the p-values corresponding to the significance levels of correlations
cor_5 <- rcorr(as.matrix(data_solids_corr), type=c("spearman"))
#define M as the correlation coefficient
M <- cor_5$r
#define p_mat as the p-value
p_mat <- cor_5$P 
#plot only significant pearson correlation coeffcients when p value >0.05
corrplot(M, type = "upper", p.mat = p_mat, sig.level = 0.05, insig = "blank", tl.col = "black", diag=FALSE, na.label="NA", tl.cex=1, cl.cex = 1, number.cex = 0.8, addCoef.col = "white", col = colorRampPalette(c("#346648", "#dbb40d"))(100))



#Big sagebrush
#subset only solid elemental concentrations (in mg/kg)
data_solids_corr <- data_solids  %>%
  filter(str_detect(Land_Coverage_Category, "Sagebrush")) %>%
  select(matches("Solid"))

# Rename columns by extracting everything between "Solid_" and "mg_Kg"
data_solids_corr <- data_solids_corr %>%
  rename_with(
    ~sub("Solid_(.*?)_mg_kg", "\\1", .),
    starts_with("Solid_")) %>%
  select(P, C, N, Ca, Mg, Na, Fe, Al, S, K)

#comput r=the correlation matrix, n=the matrix of the number of observations used in analyzing each pari fo variables, and P=the p-values corresponding to the significance levels of correlations
cor_5 <- rcorr(as.matrix(data_solids_corr), type=c("spearman"))
#define M as the correlation coefficient
M <- cor_5$r
#define p_mat as the p-value
p_mat <- cor_5$P 
#plot only significant pearson correlation coeffcients when p value >0.05
corrplot(M, type = "upper", p.mat = p_mat, sig.level = 0.05, insig = "blank", tl.col = "black", diag=FALSE, na.label="NA", tl.cex=1, cl.cex = 1, number.cex = 0.8, addCoef.col = "white", col = colorRampPalette(c("#346648", "#dbb40d"))(100))
```

```{r P w/ CN}
#P and C
ggplot(data_solids, aes(x=Solid_C_mg_kg, y=Solid_P_mg_kg, color = Land_Coverage_Category)) + geom_point() + geom_smooth(method="lm", se = FALSE) + theme_classic() + scale_color_manual(values = c("#346648", "#dbb40d"))

#all feedstocks
model<-lm(log(Solid_C_mg_kg)~log(Solid_P_mg_kg), data = data_solids)
summary(model)
#Douglas fir only
model<-lm(log(Solid_C_mg_kg)~log(Solid_P_mg_kg), data = subset(data_solids, Land_Coverage_Category=="Douglas-fir forest"))
summary(model)
#sagebrush
model<-lm(log(Solid_C_mg_kg)~log(Solid_P_mg_kg), data = subset(data_solids, Land_Coverage_Category=="Sagebrush shrubland"))
summary(model)



#P and N
ggplot(data_solids, aes(x=Solid_N_mg_kg, y=Solid_P_mg_kg, color = Land_Coverage_Category)) + geom_point() + geom_smooth(method="lm", se = FALSE) + theme_classic() + scale_color_manual(values = c("#346648", "#dbb40d"))

#all feedstocks
model<-lm(log(Solid_N_mg_kg)~log(Solid_P_mg_kg), data = data_solids)
summary(model)
#Douglas fir only
model<-lm(log(Solid_N_mg_kg)~log(Solid_P_mg_kg), data = subset(data_solids, Land_Coverage_Category=="Douglas-fir forest"))
summary(model)
#sagebrush
model<-lm(log(Solid_N_mg_kg)~log(Solid_P_mg_kg), data = subset(data_solids, Land_Coverage_Category=="Sagebrush shrubland"))
summary(model)



```


####PCA & RDAs
```{r PCA solid bulk chem}
#PCA of elemental concentration of the solid chars with burn severity and feedstock

#format dataframe using same code as correlation and then also remove NAs
data_solids_corr <- data_solids %>%
  rename_with(
    ~sub("Solid_(.*?)_mg_kg", "\\1", .),
    starts_with("Solid_")) %>%
  select(Burn_Severity, Land_Coverage_Category, P, C, N, Ca, Mg, Na, Fe, Al, S, K) %>%
  na.omit(data_solids)

pca <- prcomp(data_solids_corr[3:12], center=TRUE, scale=TRUE)

##Extract PCA information, including loadings, sample scores, and component percentages
eigval <- pca$sdev^2
eigvec <- data.frame(pca$rotation)
loadings1 <- eigvec$PC1*sqrt(eigval[1])
loadings2 <- eigvec$PC2*sqrt(eigval[2])
loadings <- cbind(loadings1, loadings2)

colnames(loadings)<-c('PC1','PC2')
rownames(loadings)<-colnames(data_solids_corr[3:12])
loadingstest<-as.data.frame(loadings)
pca_out <- as.data.frame(pca$x)
percentage <- round(pca$sdev^2/sum(pca$sdev^2)*100,1)
percentage <- paste(colnames(pca_out), "-", paste(as.character(percentage), "%", sep=""))


xscale <- 10
yscale <- 10
ggplot()+geom_point(data=pca_out,mapping=aes(x=PC1, y=PC2, colour=data_solids_corr$Land_Coverage_Category,shape=data_solids_corr$Burn_Severity),size=3)+xlim(-xscale,xscale)+ylim(-yscale,yscale)+geom_abline(intercept=0, slope=0, linetype="dashed", size=0.8, colour="gray")+geom_vline(aes(xintercept=0), linetype="dashed", size=0.8, colour="gray")+theme_light()+labs(colour="Land_Coverage_Category",shape="Burn_Severity")+theme(panel.grid.major=element_blank(),panel.grid.minor=element_blank(),panel.background=element_blank(),axis.title.x=element_text(size=16),axis.title.y=element_text(size=16),axis.text.y=element_text(size=16),axis.text.x=element_text(size=16),legend.title=element_text(size=12),legend.text=element_text(size=12),legend.position="bottom",legend.box="verticle",legend.margin=margin())+xlab(percentage[1])+ylab(percentage[2])+guides(color=guide_legend(nrow=2, byrow=TRUE))+scale_color_manual(values=c("#346648", "#dbb40d"))+scale_shape_manual(values=c(16,17,3,12))+geom_text_repel(data=loadingstest,mapping=aes(label=row.names(loadingstest), x=PC1*xscale, y=PC2*yscale),size=5, colour="black", alpha=0.5)


```

```{r PCA leachate bulk chem in both fractions}
#include pH, particulate concentrations from ICP, and filt0.7 concentrations from ICP, NPOC, TDN, MBD 

#fix THIS DOESN"T WORK RIGHT NOW
#format dataframe and then also remove NAs
data_solids_corr <- data_solids %>%
  rename_with(
    ~sub("Leachate_(.*?)_mg_kg", "\\1", .),
    starts_with("Leachate_")) %>%
  select(Burn_Severity, Land_Coverage_Category, P, C, N, Ca, Mg, Na, Fe, Al, S, K) %>%
  na.omit(data_solids)

```

```{r PCA XANES}
#PCAs of XANES LCF

#FIX THIS DOENS'T RUN RIGHT NOW

#all phases together; open air; Po individual species

#format dataframe using same code as correlation and then also remove NAs
XANES_corr <- XANES_clean %>%
  select(Parent_ID, Burn_Severity, Land_Coverage_Category, FilterSize, XANES_Pi_Al, XANES_Pi_Ca, XANES_Pi_Fe, XANES_Pi_K, XANES_Pi_Mg, XANES_Pi_Na, XANES_Po_Al, XANES_Po_Fe, XANES_Po_Ca, XANES_Po_Na) %>%
  na.omit(XANES_clean)

pca <- prcomp(XANES_corr[5:14], center=TRUE, scale=TRUE)

##Extract PCA information, including loadings, sample scores, and component percentages
eigval <- pca$sdev^2
eigvec <- data.frame(pca$rotation)
loadings1 <- eigvec$PC1*sqrt(eigval[1])
loadings2 <- eigvec$PC2*sqrt(eigval[2])
loadings <- cbind(loadings1, loadings2)

colnames(loadings)<-c('PC1','PC2')
rownames(loadings)<-colnames(XANES_corr[5:14])
loadingstest<-as.data.frame(loadings)
pca_out <- as.data.frame(pca$x)
percentage <- round(pca$sdev^2/sum(pca$sdev^2)*100,1)
percentage <- paste(colnames(pca_out), "-", paste(as.character(percentage), "%", sep=""))


xscale <- 4
yscale <- 4
ggplot()+geom_point(data=pca_out,mapping=aes(x=PC1, y=PC2, colour=XANES_corr$Land_Coverage_Category,shape=XANES_corr$Burn_Severity, size=XANES_corr$FilterSize))+xlim(-xscale,xscale)+ylim(-yscale,yscale)+geom_abline(intercept=0, slope=0, linetype="dashed", size=0.8, colour="gray")+geom_vline(aes(xintercept=0), linetype="dashed", size=0.8, colour="gray")+theme_light()+labs(colour="Land_Coverage_Category",shape="Burn_Severity")+theme(panel.grid.major=element_blank(),panel.grid.minor=element_blank(),panel.background=element_blank(),axis.title.x=element_text(size=16),axis.title.y=element_text(size=16),axis.text.y=element_text(size=16),axis.text.x=element_text(size=16),legend.title=element_text(size=12),legend.text=element_text(size=12),legend.position="bottom",legend.box="verticle",legend.margin=margin())+xlab(percentage[1])+ylab(percentage[2])+guides(color=guide_legend(nrow=2, byrow=TRUE))+scale_color_manual(values=c("#346648", "#dbb40d"))+scale_shape_manual(values=c(16,17,3,12))+scale_size_manual(values=c(3,6,9))+geom_text_repel(data=loadingstest,mapping=aes(label=row.names(loadingstest), x=PC1*xscale, y=PC2*yscale),size=5, colour="black", alpha=0.5)+ggtitle("Open Air XANES - all phases")


#all phases together; open air; Po total instead of individual

#format dataframe using same code as correlation and then also remove NAs
XANES_corr <- XANES_clean %>%
  select(Parent_ID, Burn_Severity, Land_Coverage_Category, FilterSize, XANES_Pi_Al, XANES_Pi_Ca, XANES_Pi_Fe, XANES_Pi_K, XANES_Pi_Mg, XANES_Pi_Na, XANES_Po) %>%
  na.omit(XANES_clean)

pca <- prcomp(XANES_corr[5:11], center=TRUE, scale=TRUE)

##Extract PCA information, including loadings, sample scores, and component percentages
eigval <- pca$sdev^2
eigvec <- data.frame(pca$rotation)
loadings1 <- eigvec$PC1*sqrt(eigval[1])
loadings2 <- eigvec$PC2*sqrt(eigval[2])
loadings <- cbind(loadings1, loadings2)

colnames(loadings)<-c('PC1','PC2')
rownames(loadings)<-colnames(XANES_corr[5:11])
loadingstest<-as.data.frame(loadings)
pca_out <- as.data.frame(pca$x)
percentage <- round(pca$sdev^2/sum(pca$sdev^2)*100,1)
percentage <- paste(colnames(pca_out), "-", paste(as.character(percentage), "%", sep=""))


xscale <- 4
yscale <- 4
ggplot()+geom_point(data=pca_out,mapping=aes(x=PC1, y=PC2, colour=XANES_corr$Land_Coverage_Category,shape=XANES_corr$Burn_Severity, size=XANES_corr$FilterSize))+xlim(-xscale,xscale)+ylim(-yscale,yscale)+geom_abline(intercept=0, slope=0, linetype="dashed", size=0.8, colour="gray")+geom_vline(aes(xintercept=0), linetype="dashed", size=0.8, colour="gray")+theme_light()+labs(colour="Land_Coverage_Category",shape="Burn_Severity")+theme(panel.grid.major=element_blank(),panel.grid.minor=element_blank(),panel.background=element_blank(),axis.title.x=element_text(size=16),axis.title.y=element_text(size=16),axis.text.y=element_text(size=16),axis.text.x=element_text(size=16),legend.title=element_text(size=12),legend.text=element_text(size=12),legend.position="bottom",legend.box="verticle",legend.margin=margin())+xlab(percentage[1])+ylab(percentage[2])+guides(color=guide_legend(nrow=2, byrow=TRUE))+scale_color_manual(values=c("#346648", "#dbb40d"))+scale_shape_manual(values=c(16,17,3,12))+scale_size_manual(values=c(3,6,9))+geom_text_repel(data=loadingstest,mapping=aes(label=row.names(loadingstest), x=PC1*xscale, y=PC2*yscale),size=5, colour="black", alpha=0.5)+ggtitle("Open Air XANES - all phases")



#solid only; open air; Po individual species

#format dataframe using same code as correlation and then also remove NAs; also removed columns that were all zeros for this phase
XANES_corr <- XANES_clean %>%
  select(Parent_ID, Burn_Severity, Land_Coverage_Category, FilterSize, XANES_Pi_Al, XANES_Pi_Ca, XANES_Pi_Fe, XANES_Pi_K, XANES_Pi_Mg, XANES_Pi_Na, XANES_Po_Ca, XANES_Po_Na) %>%
  na.omit(XANES_clean) %>%
  filter(FilterSize %in% c("solid"))

pca <- prcomp(XANES_corr[5:12], center=TRUE, scale=TRUE)

##Extract PCA information, including loadings, sample scores, and component percentages
eigval <- pca$sdev^2
eigvec <- data.frame(pca$rotation)
loadings1 <- eigvec$PC1*sqrt(eigval[1])
loadings2 <- eigvec$PC2*sqrt(eigval[2])
loadings <- cbind(loadings1, loadings2)

colnames(loadings)<-c('PC1','PC2')
rownames(loadings)<-colnames(XANES_corr[5:12])
loadingstest<-as.data.frame(loadings)
pca_out <- as.data.frame(pca$x)
percentage <- round(pca$sdev^2/sum(pca$sdev^2)*100,1)
percentage <- paste(colnames(pca_out), "-", paste(as.character(percentage), "%", sep=""))


xscale <- 4
yscale <- 4
ggplot()+geom_point(data=pca_out,mapping=aes(x=PC1, y=PC2, colour=XANES_corr$Land_Coverage_Category,shape=XANES_corr$Burn_Severity),size=5)+xlim(-xscale,xscale)+ylim(-yscale,yscale)+geom_abline(intercept=0, slope=0, linetype="dashed", size=0.8, colour="gray")+geom_vline(aes(xintercept=0), linetype="dashed", size=0.8, colour="gray")+theme_light()+labs(colour="Land_Coverage_Category",shape="Burn_Severity")+theme(panel.grid.major=element_blank(),panel.grid.minor=element_blank(),panel.background=element_blank(),axis.title.x=element_text(size=16),axis.title.y=element_text(size=16),axis.text.y=element_text(size=16),axis.text.x=element_text(size=16),legend.title=element_text(size=12),legend.text=element_text(size=12),legend.position="bottom",legend.box="verticle",legend.margin=margin())+xlab(percentage[1])+ylab(percentage[2])+guides(color=guide_legend(nrow=2, byrow=TRUE))+scale_color_manual(values=c("#346648", "#dbb40d"))+scale_shape_manual(values=c(16,17,3,12))+geom_text_repel(data=loadingstest,mapping=aes(label=row.names(loadingstest), x=PC1*xscale, y=PC2*yscale),size=5, colour="black", alpha=0.5)+ggtitle("Open Air XANES - Solid")



#solid only; open air; Po grouped

#format dataframe using same code as correlation and then also remove NAs; also removed columns that were all zeros for this phase
XANES_corr <- XANES_clean %>%
  select(Parent_ID, Burn_Severity, Land_Coverage_Category, FilterSize, XANES_Pi_Al, XANES_Pi_Ca, XANES_Pi_Fe, XANES_Pi_K, XANES_Pi_Mg, XANES_Pi_Na, XANES_Po) %>%
  na.omit(XANES_clean) %>%
  filter(FilterSize %in% c("solid"))

pca <- prcomp(XANES_corr[5:11], center=TRUE, scale=TRUE)

##Extract PCA information, including loadings, sample scores, and component percentages
eigval <- pca$sdev^2
eigvec <- data.frame(pca$rotation)
loadings1 <- eigvec$PC1*sqrt(eigval[1])
loadings2 <- eigvec$PC2*sqrt(eigval[2])
loadings <- cbind(loadings1, loadings2)

colnames(loadings)<-c('PC1','PC2')
rownames(loadings)<-colnames(XANES_corr[5:11])
loadingstest<-as.data.frame(loadings)
pca_out <- as.data.frame(pca$x)
percentage <- round(pca$sdev^2/sum(pca$sdev^2)*100,1)
percentage <- paste(colnames(pca_out), "-", paste(as.character(percentage), "%", sep=""))


xscale <- 4
yscale <- 4
ggplot()+geom_point(data=pca_out,mapping=aes(x=PC1, y=PC2, colour=XANES_corr$Land_Coverage_Category,shape=XANES_corr$Burn_Severity),size=5)+xlim(-xscale,xscale)+ylim(-yscale,yscale)+geom_abline(intercept=0, slope=0, linetype="dashed", size=0.8, colour="gray")+geom_vline(aes(xintercept=0), linetype="dashed", size=0.8, colour="gray")+theme_light()+labs(colour="Land_Coverage_Category",shape="Burn_Severity")+theme(panel.grid.major=element_blank(),panel.grid.minor=element_blank(),panel.background=element_blank(),axis.title.x=element_text(size=16),axis.title.y=element_text(size=16),axis.text.y=element_text(size=16),axis.text.x=element_text(size=16),legend.title=element_text(size=12),legend.text=element_text(size=12),legend.position="bottom",legend.box="verticle",legend.margin=margin())+xlab(percentage[1])+ylab(percentage[2])+guides(color=guide_legend(nrow=2, byrow=TRUE))+scale_color_manual(values=c("#346648", "#dbb40d"))+scale_shape_manual(values=c(16,17,3,12))+geom_text_repel(data=loadingstest,mapping=aes(label=row.names(loadingstest), x=PC1*xscale, y=PC2*yscale),size=5, colour="black", alpha=0.5)+ggtitle("Open Air XANES - Solid")
```

####stacked spectra and pie charts
```{r NMR}
#example stacked spectra
NMR_spectra_df_subset <-NMR_spectra %>%
  select("Chemical_Shift_parts_per_million", "BSLE_0013-solid", "BSLE_0007-solid","BSLE_0002-solid", "BSLE_0050-solid") %>%
  dplyr::rename('solid_13' = 'BSLE_0013-solid',
                'solid_7' = 'BSLE_0007-solid',
                'solid_2' = 'BSLE_0002-solid',
                'solid_50' = 'BSLE_0050-solid') %>%
  mutate_all(~replace(., . == 0, NA)) %>%
  mutate(solid_13 = solid_13 + 1,
         solid_7 = solid_7 + 75,
         solid_2 = solid_2 + 150,
         solid_50 = solid_50 + 225) 
         
NMR_spectra_df_subset<-melt(NMR_spectra_df_subset, id=c("Chemical_Shift_parts_per_million"))

NMR_spectra_df_subset<-subset(NMR_spectra_df_subset, value!="")

NMR_stacked_spectra_df <- ggplot(NMR_spectra_df_subset, aes(x=Chemical_Shift_parts_per_million, y = value, color = as.factor(variable))) + geom_path()+theme_classic() + ylim(0,300) + scale_x_reverse() +xlim(10,-10) +scale_color_manual(values=c('Black','Black', 'Black', 'Black')) + theme(axis.ticks.y = element_blank(),  axis.text.y = element_blank(), legend.position = "none")  + ylab("") + xlab("Chemical Shift (ppm)")

#cowplot::save_plot("../figures/NMR_stacked_spectra_df.pdf", NMR_stacked_spectra_df, ncol = 1, nrow = 1, base_aspect_ratio= 1:1.7, dpi=72)

pdf(file = "../figures/NMR_stacked_spectra_df.pdf", width = 3.5, height = 7) 
print(NMR_stacked_spectra_df)
dev.off()

NMR_spectra_sb_subset <-NMR_spectra %>%
  select("Chemical_Shift_parts_per_million", "BSLE_0014-solid", "BSLE_0011-solid","BSLE_0072-solid") %>%
  dplyr::rename('solid_14' = 'BSLE_0014-solid',
                'solid_11' = 'BSLE_0011-solid',
                'solid_72' = 'BSLE_0072-solid') %>%
  mutate_all(~replace(., . == 0, NA)) %>%
  mutate(solid_14 = solid_14 + 1,
         solid_11 = solid_11 + 75,
         solid_72 = solid_72 + 150) 
         
NMR_spectra_sb_subset<-melt(NMR_spectra_sb_subset, id=c("Chemical_Shift_parts_per_million"))

NMR_spectra_sb_subset<-subset(NMR_spectra_sb_subset, value!="")

NMR_stacked_spectra_sb <- ggplot(NMR_spectra_sb_subset, aes(x=Chemical_Shift_parts_per_million, y = value, color = as.factor(variable))) + geom_path()+theme_classic() + ylim(0,300) + scale_x_reverse() +xlim(10,-10) +scale_color_manual(values=c('Black','Black', 'Black', 'Black')) + theme(axis.ticks.y = element_blank(),  axis.text.y = element_blank(), legend.position = "none")  + ylab("") + xlab("Chemical Shift (ppm)")

#cowplot::save_plot("../figures/NMR_stacked_spectra_sb.pdf", NMR_stacked_spectra_sb, ncol = 1, nrow = 1, base_aspect_ratio= 1:1.7, dpi=72)

pdf(file = "../figures/NMR_stacked_spectra_sb.pdf", width = 3.5, height = 7) 
print(NMR_stacked_spectra_sb)
dev.off()

#pie charts
NMR <- summary_solids_conc %>%
  select("Land_Coverage_Category", "Burn_Severity","Ortho_Mean", "Mono_Mean", "Di_Mean", "Pyro_Mean") %>%
  dplyr::rename(Ortho = Ortho_Mean,
                Mono = Mono_Mean,
                Di = Di_Mean,
                Pyro = Pyro_Mean)


NMR_melt<-melt(NMR, id=c("Land_Coverage_Category", "Burn_Severity"))

NMR_melt$variable=factor(NMR_melt$variable, levels= c("Ortho", "Pyro", "Mono", "Di"))

DF.raw<-subset(NMR_melt, Land_Coverage_Category=="Douglas-fir forest" & Burn_Severity=="Unburned")
nmr.legend<-ggplot(DF.raw, aes(x = "", y = value, fill = variable)) +
    geom_col(color = "black") +
    coord_polar(theta = "y") + scale_fill_manual(values = c("#780000", "#c1121f", "#003049", "#669BBC"))+theme_void()+
    theme(legend.key.size = unit(1, 'cm'), #change legend key size
          legend.key.height = unit(1, 'cm'),  legend.title = element_text(size=25),
          legend.key.width = unit(1, 'cm'), #change legend key width
          legend.text = element_text(size=20))+labs(fill="")
pdf(file = "../figures/nmr.legend.pdf", width = 7, height = 3.5) 
print(nmr.legend)
dev.off()

DF.raw.nmr<-ggplot(DF.raw, aes(x = "", y = value, fill = variable)) +
    geom_col(color = "black") +
    coord_polar(theta = "y") + scale_fill_manual(values = c("#780000", "#c1121f", "#003049", "#669BBC"))+theme_void()+
    theme(legend.position = "none")
pdf(file = "../figures/DF.raw.nmr.pdf", width = 1, height = 1) 
print(DF.raw.nmr)
dev.off()

DF.low<-subset(NMR_melt, Land_Coverage_Category=="Douglas-fir forest" & Burn_Severity=="Low")
DF.low.nmr<-ggplot(DF.low, aes(x = "", y = value, fill = variable)) +
    geom_col(color = "black") +
    coord_polar(theta = "y") + scale_fill_manual(values = c("#780000", "#c1121f", "#003049", "#669BBC"))+theme_void()+
    theme(legend.position = "none")
pdf(file = "../figures/DF.low.nmr.pdf", width = 1, height = 1) 
print(DF.low.nmr)
dev.off()

DF.mod<-subset(NMR_melt, Land_Coverage_Category=="Douglas-fir forest" & Burn_Severity=="Moderate")
DF.mod.nmr<-ggplot(DF.mod, aes(x = "", y = value, fill = variable)) +
    geom_col(color = "black") +
    coord_polar(theta = "y") + scale_fill_manual(values = c("#780000", "#c1121f", "#003049", "#669BBC"))+theme_void()+
    theme(legend.position = "none")
pdf(file = "../figures/DF.mod.nmr.pdf", width = 1, height = 1) 
print(DF.mod.nmr)
dev.off()

DF.high<-subset(NMR_melt, Land_Coverage_Category=="Douglas-fir forest" & Burn_Severity=="High")
DF.high.nmr<-ggplot(DF.high, aes(x = "", y = value, fill = variable)) +
    geom_col(color = "black") +
    coord_polar(theta = "y") + scale_fill_manual(values = c("#780000", "#c1121f", "#003049", "#669BBC"))+theme_void()+
    theme(legend.position = "none")
pdf(file = "../figures/DF.high.nmr.pdf", width = 1, height = 1) 
print(DF.high.nmr)
dev.off()

SB.raw<-subset(NMR_melt, Land_Coverage_Category=="Sagebrush shrubland" & Burn_Severity=="Unburned")
SB.raw.nmr<-ggplot(SB.raw, aes(x = "", y = value, fill = variable)) +
    geom_col(color = "black") +
    coord_polar(theta = "y") + scale_fill_manual(values = c("#780000", "#c1121f", "#003049", "#669BBC"))+theme_void()+
    theme(legend.position = "none")
pdf(file = "../figures/SB.raw.nmr.pdf", width = 1, height = 1) 
print(SB.raw.nmr)
dev.off()

SB.low<-subset(NMR_melt, Land_Coverage_Category=="Sagebrush shrubland" & Burn_Severity=="Low")
SB.low.nmr<-ggplot(SB.low, aes(x = "", y = value, fill = variable)) +
    geom_col(color = "black") +
    coord_polar(theta = "y") + scale_fill_manual(values = c("#780000", "#c1121f", "#003049", "#669BBC"))+theme_void()+
    theme(legend.position = "none")
pdf(file = "../figures/SB.low.nmr.pdf", width = 1, height = 1) 
print(SB.low.nmr)
dev.off()

SB.mod<-subset(NMR_melt, Land_Coverage_Category=="Sagebrush shrubland" & Burn_Severity=="Moderate")
SB.mod.nmr<-ggplot(SB.mod, aes(x = "", y = value, fill = variable)) +
    geom_col(color = "black") +
    coord_polar(theta = "y") + scale_fill_manual(values = c("#780000", "#c1121f", "#003049", "#669BBC"))+theme_void()+
    theme(legend.position = "none")
pdf(file = "../figures/SB.mod.nmr.pdf", width = 1, height = 1) 
print(SB.mod.nmr)
dev.off()

```
```{r XANES}
#example stacked spectra
XANES_spectra_df_subset <-XANES_spectra %>%
  select("eV", "BSLE_0013-solid_P-XANES.xmu.nor", "BSLE_0007-solid_P-XANES.xmu.nor","BSLE_0002-solid_P-XANES.xmu.nor", "BSLE_0050-solid_P-XANES.xmu.nor") %>%
  dplyr::rename('solid_13' = 'BSLE_0013-solid_P-XANES.xmu.nor',
                'solid_7' = 'BSLE_0007-solid_P-XANES.xmu.nor',
                'solid_2' = 'BSLE_0002-solid_P-XANES.xmu.nor',
                'solid_50' = 'BSLE_0050-solid_P-XANES.xmu.nor') %>%
  mutate_all(~replace(., . == 0, NA)) %>%
  mutate(solid_13 = solid_13 + 1,
         solid_7 = solid_7 + 8,
         solid_2 = solid_2 + 16,
         solid_50 = solid_50 + 24) 
         
XANES_spectra_df_subset<-melt(XANES_spectra_df_subset, id=c("eV"))

XANES_spectra_df_subset<-subset(XANES_spectra_df_subset, value!="")

XANES_stacked_spectra_df <- ggplot(XANES_spectra_df_subset, aes(x=eV, y = value, color = as.factor(variable))) + geom_path()+theme_classic() + scale_color_manual(values=c('Black','Black', 'Black', 'Black')) + theme(axis.ticks.y = element_blank(),  axis.text.y = element_blank(), legend.position = "none")  + ylab("") + xlab("Energy (eV)") + xlim(2140, 2200) + ylab ("Normalized Absorption (arb. units)")

pdf(file = "../figures/XANES_stacked_spectra_df.pdf", width = 3, height = 7) 
print(XANES_stacked_spectra_df)
dev.off()

XANES_spectra_sb_subset <-XANES_spectra %>%
  select("eV", "BSLE_0014-solid_P-XANES.xmu.nor", "BSLE_0011-solid_P-XANES.xmu.nor","BSLE_0072-solid_P-XANES.xmu.nor") %>%
  dplyr::rename('solid_14' = 'BSLE_0014-solid_P-XANES.xmu.nor',
                'solid_11' = 'BSLE_0011-solid_P-XANES.xmu.nor',
                'solid_72' = 'BSLE_0072-solid_P-XANES.xmu.nor') %>%
  mutate_all(~replace(., . == 0, NA)) %>%
  mutate(blank = solid_72) %>%
  mutate(solid_14 = solid_14 + 1,
         solid_11 = solid_11 + 8,
         solid_72 = solid_72 + 16,
         blank = blank + 24) 
         
XANES_spectra_sb_subset<-melt(XANES_spectra_sb_subset, id=c("eV"))

XANES_spectra_sb_subset<-subset(XANES_spectra_sb_subset, value!="")

XANES_stacked_spectra_sb <- ggplot(XANES_spectra_sb_subset, aes(x=eV, y = value, color = as.factor(variable))) + geom_path()+theme_classic() + scale_color_manual(values=c('Black','Black', 'Black', 'White')) + theme(axis.ticks.y = element_blank(),  axis.text.y = element_blank(), legend.position = "none")  + ylab("") + xlab("Energy (eV)") + xlim(2140, 2200) + ylab ("Normalized Absorption (arb. units)")

#cowplot::save_plot("../figures/NMR_stacked_spectra_sb.pdf", NMR_stacked_spectra_sb, ncol = 1, nrow = 1, base_aspect_ratio= 1:1.7, dpi=72)

pdf(file = "../figures/XANES_stacked_spectra_sb.pdf", width = 3, height = 7) 
print(XANES_stacked_spectra_sb)
dev.off()
  
#xlab(expression(paste(~^31~P~Chemical~Shift~(ppm), sep="")))

#pie charts with Po grouped and inorganic separate metals
XANES <- summary_solids_conc %>%
  select("Land_Coverage_Category", "Burn_Severity","XANES_Pi_K_Mean", "XANES_Pi_Mg_Mean", "XANES_Pi_Al_Mean", "XANES_Pi_Ca_Mean", "XANES_Pi_Na_Mean", "XANES_Pi_Fe_Mean", "XANES_Po_Mean") %>%
  dplyr::rename(K = XANES_Pi_K_Mean,
                Mg = XANES_Pi_Mg_Mean,
                Al = XANES_Pi_Al_Mean,
                Ca = XANES_Pi_Ca_Mean,
                Na = XANES_Pi_Na_Mean,
                Fe = XANES_Pi_Fe_Mean,
                Po = XANES_Po_Mean)

XANES_melt<-melt(XANES, id=c("Land_Coverage_Category", "Burn_Severity"))

#XANES_melt$variable=factor(XANES_melt$variable, levels= c("Ortho", "Pyro", "Mono", "Di"))

DF.raw<-subset(XANES_melt, Land_Coverage_Category=="Douglas-fir forest" & Burn_Severity=="Unburned")
xanes.legend<-ggplot(DF.raw, aes(x = "", y = value, fill = variable)) +
    geom_col(color = "black") +
    coord_polar(theta = "y") + scale_fill_manual(values = c("#424a26", "#9B9B7A", "#D9AE94", "#F1DCA7", "#FFCB69", "#D08C60", "#997B66"))+theme_void()+
    theme(legend.key.size = unit(1, 'cm'), #change legend key size
          legend.key.height = unit(1, 'cm'),  legend.title = element_text(size=25),
          legend.key.width = unit(1, 'cm'), #change legend key width
          legend.text = element_text(size=20))+labs(fill="")
pdf(file = "../figures/xanes.legend.pdf", width = 7, height = 3.5) 
print(xanes.legend)
dev.off()

DF.raw.xanes<-ggplot(DF.raw, aes(x = "", y = value, fill = variable)) +
    geom_col(color = "black") +
    coord_polar(theta = "y") + scale_fill_manual(values = c("#424a26", "#9B9B7A", "#D9AE94", "#F1DCA7", "#FFCB69", "#D08C60", "#997B66"))+theme_void()+
    theme(legend.position = "none")
pdf(file = "../figures/DF.raw.xanes.pdf", width = 1, height = 1) 
print(DF.raw.xanes)
dev.off()

DF.low<-subset(XANES_melt, Land_Coverage_Category=="Douglas-fir forest" & Burn_Severity=="Low")
DF.low.xanes<-ggplot(DF.low, aes(x = "", y = value, fill = variable)) +
    geom_col(color = "black") +
    coord_polar(theta = "y") + scale_fill_manual(values = c("#424a26", "#9B9B7A", "#D9AE94", "#F1DCA7", "#FFCB69", "#D08C60", "#997B66"))+theme_void()+
    theme(legend.position = "none")
pdf(file = "../figures/DF.low.xanes.pdf", width = 1, height = 1) 
print(DF.low.xanes)
dev.off()

DF.mod<-subset(XANES_melt, Land_Coverage_Category=="Douglas-fir forest" & Burn_Severity=="Moderate")
DF.mod.xanes<-ggplot(DF.mod, aes(x = "", y = value, fill = variable)) +
    geom_col(color = "black") +
    coord_polar(theta = "y") + scale_fill_manual(values = c("#424a26", "#9B9B7A", "#D9AE94", "#F1DCA7", "#FFCB69", "#D08C60", "#997B66"))+theme_void()+
    theme(legend.position = "none")
pdf(file = "../figures/DF.mod.xanes.pdf", width = 1, height = 1) 
print(DF.mod.xanes)
dev.off()

DF.high<-subset(XANES_melt, Land_Coverage_Category=="Douglas-fir forest" & Burn_Severity=="High")
DF.high.xanes<-ggplot(DF.high, aes(x = "", y = value, fill = variable)) +
    geom_col(color = "black") +
    coord_polar(theta = "y") + scale_fill_manual(values = c("#424a26", "#9B9B7A", "#D9AE94", "#F1DCA7", "#FFCB69", "#D08C60", "#997B66"))+theme_void()+
    theme(legend.position = "none")
pdf(file = "../figures/DF.high.xanes.pdf", width = 1, height = 1) 
print(DF.high.xanes)
dev.off()

SB.raw<-subset(XANES_melt, Land_Coverage_Category=="Sagebrush shrubland" & Burn_Severity=="Unburned")
SB.raw.xanes<-ggplot(SB.raw, aes(x = "", y = value, fill = variable)) +
    geom_col(color = "black") +
    coord_polar(theta = "y") + scale_fill_manual(values = c("#424a26", "#9B9B7A", "#D9AE94", "#F1DCA7", "#FFCB69", "#D08C60", "#997B66"))+theme_void()+
    theme(legend.position = "none")
pdf(file = "../figures/SB.raw.xanes.pdf", width = 1, height = 1) 
print(SB.raw.xanes)
dev.off()

SB.low<-subset(XANES_melt, Land_Coverage_Category=="Sagebrush shrubland" & Burn_Severity=="Low")
SB.low.xanes<-ggplot(SB.low, aes(x = "", y = value, fill = variable)) +
    geom_col(color = "black") +
    coord_polar(theta = "y") + scale_fill_manual(values = c("#424a26", "#9B9B7A", "#D9AE94", "#F1DCA7", "#FFCB69", "#D08C60", "#997B66"))+theme_void()+
    theme(legend.position = "none")
pdf(file = "../figures/SB.low.xanes.pdf", width = 1, height = 1) 
print(SB.low.xanes)
dev.off()

SB.mod<-subset(XANES_melt, Land_Coverage_Category=="Sagebrush shrubland" & Burn_Severity=="Moderate")
SB.mod.xanes<-ggplot(SB.mod, aes(x = "", y = value, fill = variable)) +
    geom_col(color = "black") +
    coord_polar(theta = "y") + scale_fill_manual(values = c("#424a26", "#9B9B7A", "#D9AE94", "#F1DCA7", "#FFCB69", "#D08C60", "#997B66"))+theme_void()+
    theme(legend.position = "none")
pdf(file = "../figures/SB.mod.xanes.pdf", width = 1, height = 1) 
print(SB.mod.xanes)
dev.off()
```


#haven't updated below here yet (NMR and XANES code) fix

```{r}
#RDA for XANES
#RDA for speciation relative percent being predicted by EEMT, MAP, MAT, clay %, DI pH, Fe conc, Al conc, Ca conc, C conc, P conc; seperate for climosequences 

#this is example code of how to do an RDA
#reference: http://dmcglinn.github.io/quant_methods/lessons/multivariate_models.html
#other reference: https://popgen.nescent.org/2018-03-27_RDA_GEA.html
#citation in here: https://cran.r-project.org/web/packages/vegan/vignettes/FAQ-vegan.html
#good RDA info: https://mb3is.megx.net/gustame/constrained-analyses/rda

#Use (all samples in A, B, and C horizons relative percent)
#make spreadsheet
Master_CZO_WM_Soil_5.8.2020 <- read.csv("~/Documents/Research Notes/Dissertation General/Master_CZO_WM_Soil_5.8.2020.csv")
Master_CZO_WM_Soil_5.8.2020$Climo<-factor(Master_CZO_WM_Soil_5.8.2020$Climo, levels=c("WM", "CZO"))
xas.percent<-subset(Master_CZO_WM_Soil_5.8.2020, Sample.Type=="Soil")
xas.percent<-xas.percent[ , c("Horizon.Category.C",  "Climo", "Site", "EEMT", "AI", "MAT", "MAP","pH.CaCl2", "Clay.Percent", "Fe.g.kgsoil.PMnorm", "Ca.g.kgsoil.PMnorm", "Al.g.kgsoil.PMnorm", "C.g.kgsoil", "P.g.kgsoil.PMnorm", "N.g.kgsoil", "Ca.Pi.Percent", "Al.Pi.Percent", "Fe.Pi.Percent", "XANES.Total.Monoester.Percent", "XANES.Total.Diester.Percent")]
xas.percent<-subset(xas.percent, Ca.Pi.Percent!="NA")
colnames(xas.percent)[1:20]<-c("Horizon",  "Gradient", "Site","EEMT", "Humidity", "MAT", "MAP","pH", "Clay", "Fe", "Ca", "Al", "C", "P", "N", "Ca-Pi", "Al-Pi", "Fe-Pi", "Monoester", "Diester")

#remove NAs 
xas.percent<-subset(xas.percent, Clay!="NA")
xas.percent<-subset(xas.percent, pH!="NA")
xas.percent<-subset(xas.percent, Site!="NA")
#check no NA in XANES and that 0 is included for when samples didn't have a species 


#make RDA with site colored (climo together for this one)
#load libraries
library(vegan)
library(psych)

#create dataframe for sample variables
samples<-xas.percent[ -c(1:15)]
#create dataframe for environmental variables
enviro<-xas.percent[ -c(16:20)]

#make sure both dataframes have equal rows
all.equal(rownames(samples), rownames(enviro))

#RDA (this anaysis expects a linear response of each sample to the environmental variables)
rda_tree=rda(samples~ . , data=enviro[4:15])
rda_tree
RsquareAdj(rda_tree)
summary(eigenvals(rda_tree, model = "constrained"))

#reference about scaling: https://mb3is.megx.net/gustame/constrained-analyses/rda

#see the factor loadings (correlations of each variable with each pca axis)
scores(rda_tree, choices=1:2, display="species", scaling=2)

#plot it
plot(rda_tree, type='n', scaling=2)
orditorp(rda_tree, display='sp', cex=0.5, scaling=2, col='blue')
text(rda_tree, display='cn', col='red')

#check correlation
pairs.panels(enviro[,4:15], scale=T)

#can visualize RDA importance
screeplot(rda_tree)

#check significance of all PCAs
signif.full <- anova.cca(rda_tree, parallel=getOption("mc.cores")) # default is permutation=999
signif.full #model is significant

#check significance of individual PCAs
signif.axis <- anova.cca(rda_tree, by="axis", parallel=getOption("mc.cores"))
signif.axis #only RDA1 and RDA 2 are sig

#check VIF
vif.cca(rda_tree) #VIF is highest (4.23) for Aluminum

#compare the model to chance with permutation test
anova(rda_tree)

#plot again
plot(rda_tree, scaling=2) #Here, the elemental concentrations are in red (in the center of each plot), and the individuals are the black circles. The blue vectors are the environmental predictors. The relative arrangement of these items in the ordination space reflects their relationship with the ordination axes, which are linear combinations of the predictor variables.

#make a pretty plot
#use
#USE THIS ONE AS AN EXAMPLE!! (has horizons as difference shapes but need to figure out legend)
levels(enviro$Site) <- c("GR2","GR3","GR5","BAR","SJER","SPR", "PR", "SH")
eco <- enviro$Site
bgg <- c("#000080", "#8B0000","#0E5E0B","#606060","#5B94BA","#DF1111", "#069710",  "#C9D4D1") # 8 colors for our sites
shapes <- c(18, 16, 15,17) 
sh <- as.factor(enviro$Horizon)
plot(rda_tree, type="n", scaling=2)
points(rda_tree, display="species", pch=20, cex=0.7, col="gray32", scaling=2)           #the chemical species from NMR and XANES
points(rda_tree, display="sites", pch=shapes[sh], cex=1.3, scaling=2, col=bgg[eco]) # the soil samples
text(rda_tree, scaling=2, display="bp", col="#0868ac", cex=1)                           # the predictors
#legend("bottomright", legend=levels(eco), bty="n", pch=21, cex=1, col=bg)
legend("bottomright", legend=c("A", "B", "C", "GR2", "GR3", "GR5", "BAR", "SJER", "SPR", "PR", "SH"), col=c(rep("black",3), "#000080", "#8B0000","#0E5E0B","#606060","#5B94BA","#DF1111", "#069710",  "#C9D4D1"), pch=c(16, 15, 17, 16, 16, 16, 16, 16, 16, 16, 16))


#surface horizons only
Master_CZO_WM_Soil_5.8.2020 <- read.csv("~/Documents/Research Notes/Dissertation General/Master_CZO_WM_Soil_5.8.2020.csv")
Master_CZO_WM_Soil_5.8.2020$Climo<-factor(Master_CZO_WM_Soil_5.8.2020$Climo, levels=c("WM", "CZO"))
xas.percent<-subset(Master_CZO_WM_Soil_5.8.2020, Sample.Type=="Soil")
xas.percent<-xas.percent[ , c("Horizon.Category.C",  "Climo", "Site", "EEMT", "AI", "MAT", "MAP","pH.CaCl2", "Clay.Percent", "Fe.g.kgsoil.PMnorm", "Ca.g.kgsoil.PMnorm", "Al.g.kgsoil.PMnorm", "C.g.kgsoil", "P.g.kgsoil.PMnorm", "N.g.kgsoil", "Ca.Pi.Percent", "Al.Pi.Percent", "Fe.Pi.Percent", "XANES.Total.Monoester.Percent", "XANES.Total.Diester.Percent")]
xas.percent<-subset(xas.percent, Ca.Pi.Percent!="NA")
colnames(xas.percent)[1:20]<-c("Horizon",  "Gradient", "Site","EEMT", "Humidity", "MAT", "MAP","pH", "Clay", "Fe", "Ca", "Al", "C", "P", "N", "Ca-Pi", "Al-Pi", "Fe-Pi", "Monoester", "Diester")
xas.percent<-subset(xas.percent, Horizon=="A")

#remove NAs 
xas.percent<-subset(xas.percent, Clay!="NA")
xas.percent<-subset(xas.percent, pH!="NA")
xas.percent<-subset(xas.percent, Site!="NA")
#check no NA in XANES and that 0 is included for when samples didn't have a species 


#make RDA with site colored (climo together for this one)
#load libraries
library(vegan)
library(psych)

#create dataframe for sample variables
samples<-xas.percent[ -c(1:15)]
#create dataframe for environmental variables
enviro<-xas.percent[ -c(16:20)]

#make sure both dataframes have equal rows
all.equal(rownames(samples), rownames(enviro))

#RDA (this anaysis expects a linear response of each sample to the environmental variables)
rda_tree=rda(samples~ . , data=enviro[6:15])
rda_tree
RsquareAdj(rda_tree)
summary(eigenvals(rda_tree, model = "constrained"))

#reference about scaling: https://mb3is.megx.net/gustame/constrained-analyses/rda

#see the factor loadings (correlations of each variable with each pca axis)
scores(rda_tree, choices=1:2, display="species", scaling=2)

#plot it
plot(rda_tree, type='n', scaling=2)
orditorp(rda_tree, display='sp', cex=0.5, scaling=2, col='blue')
text(rda_tree, display='cn', col='red')

#check correlation
pairs.panels(enviro[,6:15], scale=T)

#can visualize RDA importance
screeplot(rda_tree)

#check significance of all PCAs
signif.full <- anova.cca(rda_tree, parallel=getOption("mc.cores")) # default is permutation=999
signif.full #model is significant

#check significance of individual PCAs
signif.axis <- anova.cca(rda_tree, by="axis", parallel=getOption("mc.cores"))
signif.axis #only RDA1 and RDA 2 are sig

#check VIF
vif.cca(rda_tree) #VIF is highest (4.23) for Aluminum

#compare the model to chance with permutation test
anova(rda_tree)

#plot again
plot(rda_tree, scaling=2) #Here, the elemental concentrations are in red (in the center of each plot), and the individuals are the black circles. The blue vectors are the environmental predictors. The relative arrangement of these items in the ordination space reflects their relationship with the ordination axes, which are linear combinations of the predictor variables.

#make a pretty plot
#use
levels(enviro$Site) <- c("GR2","GR3","GR5","BAR","SJER","SPR", "PR", "SH")
eco <- enviro$Site
bg <- c("#000080", "#8B0000","#0E5E0B","#606060","#5B94BA","#DF1111", "#069710",  "#C9D4D1") # 8 colors for our sites
#shapes = c(15, 16, 17) 
#shapes <- shapes[as.numeric(rda_tree$Horizon)]
plot(rda_tree, type="n", scaling=2)
points(rda_tree, display="species", pch=20, cex=0.7, col="gray32", scaling=2)           #the chemical species from NMR and XANES
points(rda_tree, display="sites", pch=21, cex=1.3, col="gray32", scaling=2, bg=bg[eco]) # the soil samples
text(rda_tree, scaling=2, display="bp", col="#0868ac", cex=1)                           # the predictors
legend("bottomright", legend=levels(eco), bty="n", col="gray32", pch=21, cex=1, pt.bg=bg)
```



```{r NMR}
NMR<-subset(NMR, Sample=="Leachate")
NMR<-subset(NMR, Deg.Corr=="Yes")
data<-NMR %>% left_join(metadata)
data<-subset(data, Burn_Treatment=="burn table" | Burn_Treatment=="raw")
data<-data[grep("A", data$Sample_Name, ignore.case=TRUE), ]


data<-melt(data, id=c("Parent_ID", "Sample", "Deg.Corr", "Sample_Name", "Land_Coverage_Category","Burn_Treatment", "Burn_Severity", "Char_Leached", "Leachate_Volume"))

summary.nmr.solid.deg.corr<-data %>%
  group_by(variable, Burn_Severity, Land_Coverage_Category) %>%
  dplyr::summarise(
    n = n(), mean = mean(value), sd=sd(value)
  )

write.csv(summary.nmr.solid.deg.corr, file = "~/PNNL/RC-3, River Corridor SFA - Burn Severity Experiments/Burn Severity Experiment/Data/P_all data streams/P NMR/Processed_Final/summary.nmr.solid.deg.corr.csv")

summary.nmr.solid.deg.corr$variable=factor(summary.nmr.solid.deg.corr$variable, levels= c("Ortho", "Pyro", "Mono", "Di"))

#no Pi or Po label: option 1
nmr.stacked.bar.noPiPo<-ggplot(summary.nmr.solid.deg.corr, aes(x=Burn_Severity, y=mean, fill=variable)) + geom_bar(stat="identity") + theme_classic() + facet_grid(.~Land_Coverage_Category)+scale_fill_manual(values=c("#346648", "#83aa8b", "#dbb40d", "lightgoldenrod", "lightsalmon3", "brown3", "tomato4"))+ theme(axis.text.x = element_text(angle = 45, hjust=1), legend.title = element_blank(),text = element_text(size = 15))+labs(x= "Burn Severity",y="Relative Percent (%)")

data<-summary.nmr.solid.deg.corr

#add PiPo Column
data$PiPo[data$variable=='Ortho' | data$variable=='Pyro']<-"Pi"
data$PiPo[data$variable=='Mono' | data$variable=='Di']<-"Po"

#Pi and Po labelled: option 2
nmr.stacked.bar.PiPo<-ggplot(data, aes(x=Burn_Severity, y=mean, fill=variable,  pattern=PiPo)) + geom_bar_pattern(stat="identity",color = "black", 
                   pattern_fill = "black",
                   pattern_angle = 45,
                   pattern_density = 0.1,
                   pattern_spacing = 0.05,
                   pattern_key_scale_factor = 0.6)+ theme_classic()+facet_grid(.~Land_Coverage_Category)+scale_fill_manual(values=c("#346648", "#83aa8b",  "#dbb40d", "lightgoldenrod","red4"))+scale_pattern_manual(values = c(Pi = "none", Po = "stripe"))+ theme(axis.text.x = element_text(angle = 45, hjust=1))+labs(x= "Burn Severity",y="Relative Percent (%)",pattern = "") + 
  guides(pattern = guide_legend(override.aes = list(fill = "white")),
         fill = guide_legend(override.aes = list(pattern = "none")))+ theme(legend.title = element_blank(),text = element_text(size = 15))

DF.raw<-subset(summary.nmr.solid.deg.corr, Land_Coverage_Category=="Douglas-fir forest" & Burn_Severity=="Unburned")
DF.raw.nmr<-ggplot(DF.raw, aes(x = "", y = mean, fill = variable)) +
    geom_col(color = "black") +
    coord_polar(theta = "y") + scale_fill_manual(values = c("#346648", "#83aa8b", "#dbb40d", "lightgoldenrod", "lightsalmon3"))+theme_void()+
    theme(legend.key.size = unit(1, 'cm'), #change legend key size
          legend.key.height = unit(1, 'cm'),  legend.title = element_text(size=25),
          legend.key.width = unit(1, 'cm'), #change legend key width
          legend.text = element_text(size=20))+labs(fill="")

DF.low<-subset(summary.nmr.solid.deg.corr, Land_Coverage_Category=="Douglas-fir forest" & Burn_Severity=="Low")
DF.raw.nmr<-ggplot(DF.low, aes(x = "", y = mean, fill = variable)) +
    geom_col(color = "black") +
    coord_polar(theta = "y") + scale_fill_manual(values = c("#346648", "#83aa8b", "#dbb40d", "lightgoldenrod", "lightsalmon3"))+theme_void()+
    theme(legend.key.size = unit(1, 'cm'), #change legend key size
          legend.key.height = unit(1, 'cm'),  legend.title = element_text(size=25),
          legend.key.width = unit(1, 'cm'), #change legend key width
          legend.text = element_text(size=20))+labs(fill="")

DF.mod<-subset(summary.nmr.solid.deg.corr, Land_Coverage_Category=="Douglas-fir forest" & Burn_Severity=="Moderate")
DF.raw.nmr<-ggplot(DF.mod, aes(x = "", y = mean, fill = variable)) +
    geom_col(color = "black") +
    coord_polar(theta = "y") + scale_fill_manual(values = c("#346648", "#83aa8b", "#dbb40d", "lightgoldenrod", "lightsalmon3"))+theme_void()+
    theme(legend.key.size = unit(1, 'cm'), #change legend key size
          legend.key.height = unit(1, 'cm'),  legend.title = element_text(size=25),
          legend.key.width = unit(1, 'cm'), #change legend key width
          legend.text = element_text(size=20))+labs(fill="")

DF.high<-subset(summary.nmr.solid.deg.corr, Land_Coverage_Category=="Douglas-fir forest" & Burn_Severity=="High")
DF.raw.nmr<-ggplot(DF.high, aes(x = "", y = mean, fill = variable)) +
    geom_col(color = "black") +
    coord_polar(theta = "y") + scale_fill_manual(values = c("#346648", "#83aa8b", "#dbb40d", "lightgoldenrod", "lightsalmon3"))+theme_void()+
    theme(legend.key.size = unit(1, 'cm'), #change legend key size
          legend.key.height = unit(1, 'cm'),  legend.title = element_text(size=25),
          legend.key.width = unit(1, 'cm'), #change legend key width
          legend.text = element_text(size=20))+labs(fill="")
```

```{r XANES calcs}
XANES <- read.csv("~/Library/CloudStorage/OneDrive-SharedLibraries-PNNL/RC-3, River Corridor SFA - Burn Severity Experiments/Burn Severity Experiment/Data/P_all data streams/P XAS/BLSE_R_Code_Testing/Sample_LCF_Details_8.2.23.csv")

XANES<-subset(XANES, Pi_Al_GibbSorb_std!="")

XANES$Pi_Ca<-XANES$Pi_Apatite_CaDefHydroxy_std+XANES$Pi_Apatite_Carbonate_std+XANES$Pi_Apatite_Fluor_std+XANES$Pi_Ca_Mono_std+XANES$Pi_Ca_Octa_std+XANES$Pi_Ca_Pyro_std+XANES$Pi_Ca_Tri_std

XANES$Po_Ca<-XANES$Po_Ca_Lecithin_std+XANES$Po_Ca_PA_std

XANES$Pi_Fe<-XANES$Pi_Fe_FerriSorb_2_std+XANES$Pi_Fe_FerriSorb_std+XANES$Pi_Fe_GoethSorb_2_std+XANES$Pi_Fe_GoethSorb_std+XANES$Pi_Fe_std

XANES$Po_Fe<-XANES$Po_Fe_DNA_GoethSorb_std+XANES$Po_Fe_PA_FerriSorb_std+XANES$Po_Fe_PA_GoethSorb_std

XANES$Pi_Na<-XANES$Pi_Na_Di_std+XANES$Pi_Na_Tri_std

XANES$Po_Na<-XANES$Po_Na_AMP_std+XANES$Po_Na_ATP_std+XANES$Po_Na_DNA_std+XANES$Po_Na_PA_std

XANES$Pi_Al<-XANES$Pi_Al_GibbSorb_std

XANES$Po_Al<-XANES$Po_Al_DNA_GibbSorb_2_std+XANES$Po_Al_PA_GibbSorb_std+XANES$Po_Al_PA_Precip_std

XANES$Pi_Mg<-XANES$Pi_Mg_Di_std+XANES$Pi_Mg_Tri_std+XANES$Pi_NH4_Mg_std

XANES$Pi_K<-XANES$Pi_K_Di_std+XANES$Pi_K_Pyro_std

XANES$Pi<-XANES$Pi_Al+XANES$Pi_Ca+XANES$Pi_K+XANES$Pi_Fe+XANES$Pi_Na+XANES$Pi_Mg

XANES$Po<-XANES$Po_Fe+XANES$Po_Na+XANES$Po_Al+XANES$Po_Ca

XANES$SUM<-XANES$Pi+XANES$Po


```

```{rr XANES figs}
XANES<-XANES[ -c(2:40)]

data<-XANES %>%
  separate(col=File_Name, into = c("Element", "StudyCode", "ID", "SampleType", "Sample"), sep="_") %>%
  mutate(Parent_ID= paste(StudyCode, ID, sep="_"))

data<-data[ -c(1:3,5)]

data<-data %>% left_join(metadata)

data<-data[grepl("A", data$Sample_Name), ]

data<-subset(data, Burn_Severity!="")

solid<-subset(data, SampleType=="solid")
part<-subset(data, SampleType=="part")
filt<-subset(data, SampleType=="filt07")


solid<-melt(solid, id=c("SampleType", "Parent_ID", "Sample_Name", "Land_Coverage_Category","Burn_Severity", "Burn_Treatment",  "Char_Leached", "Leachate_Volume"))
part<-melt(part, id=c("SampleType", "Parent_ID", "Sample_Name", "Land_Coverage_Category","Burn_Severity", "Burn_Treatment",  "Char_Leached", "Leachate_Volume"))
filt<-melt(filt, id=c("SampleType", "Parent_ID", "Sample_Name", "Land_Coverage_Category","Burn_Severity", "Burn_Treatment",  "Char_Leached", "Leachate_Volume"))

summary.xanes.solid<-solid %>%
  group_by(variable, Burn_Severity, Land_Coverage_Category) %>%
  summarise(
    n = n(), mean = mean(value), sd=sd(value)
  )
summary.xanes.part<-part %>%
  group_by(variable, Burn_Severity, Land_Coverage_Category) %>%
  summarise(
    n = n(), mean = mean(value), sd=sd(value)
  )
summary.xanes.filt<-filt %>%
  group_by(variable, Burn_Severity, Land_Coverage_Category) %>%
  summarise(
    n = n(), mean = mean(value), sd=sd(value)
  )

summary.solid<-subset(summary.xanes.solid, variable!="Pi" & variable!="Po" & variable!="SUM")
summary.part<-subset(summary.xanes.part, variable!="Pi" & variable!="Po" & variable!="SUM")
summary.filt<-subset(summary.xanes.filt, variable!="Pi" & variable!="Po" & variable!="SUM")

solid<-subset(solid, variable!="Pi" & variable!="Po" & variable!="SUM")
part<-subset(part, variable!="Pi" & variable!="Po" & variable!="SUM")
filt<-subset(filt, variable!="Pi" & variable!="Po" & variable!="SUM")

ggplot(solid, aes(x=Burn_Severity, y=value, fill=Land_Coverage_Category))+geom_boxplot()+facet_grid(variable~Land_Coverage_Category)+theme_classic()+ xlab("Burn Severity")+ ylab("Relative Percent")+scale_fill_manual(values=c("#346648", "#83aa8b", "#dbb40d"))+ggtitle("P XANES: BSLE Solids")

ggplot(part, aes(x=Burn_Severity, y=value, fill=Land_Coverage_Category))+geom_boxplot()+facet_grid(variable~Land_Coverage_Category)+theme_classic()+ xlab("Burn Severity")+ ylab("Relative Percent")+scale_fill_manual(values=c("#346648", "#83aa8b", "#dbb40d"))+ggtitle("P XANES: BSLE Particulate")

ggplot(filt, aes(x=Burn_Severity, y=value, fill=Land_Coverage_Category))+geom_boxplot()+facet_grid(variable~Land_Coverage_Category)+theme_classic()+ xlab("Burn Severity")+ ylab("Relative Percent")+scale_fill_manual(values=c("#346648", "#83aa8b", "#dbb40d"))+ggtitle("P XANES: BSLE Soluble")

ggplot(solid, aes(fill=variable, y=value, x=Burn_Severity)) + 
    geom_bar(position="fill", stat="identity")+theme_classic()+facet_grid(.~Land_Coverage_Category)+scale_fill_manual(values=c("#346648", "#83aa8b", "#dbb40d", "lightgoldenrod", "lightsalmon3", "brown3", "tomato4", "gray", "blue", "red"))+ggtitle("P XANES: BSLE Solids")


#trying pie chart instead
DF_unburn_part<-subset(summary.part, Land_Coverage_Category=="Douglas-fir forest" & Burn_Severity=="Unburned")

ggplot(DF_unburn_part, aes(x = "", y = mean, fill = variable)) +
    geom_col(color = "black") +
    coord_polar(theta = "y") + scale_fill_manual(values = c("#346648","#83aa8b","#dbb40d","lightgoldenrod","black", "gray" ,"#8c564b", "#c49c94", "lightsalmon3", "orange1", "cadetblue3"))+theme_void()+
    theme(legend.key.size = unit(1, 'cm'), #change legend key size
          legend.key.height = unit(1, 'cm'),  legend.title = element_text(size=25),
          legend.key.width = unit(1, 'cm'), #change legend key width
          legend.text = element_text(size=20))+theme(legend.title= element_blank())

, "darkorange3",  "indianred3" "deepskyblue4",

DF_low_part<-subset(summary.part, Land_Coverage_Category=="Douglas-fir forest" & Burn_Severity=="Low")

ggplot(DF_low_part, aes(x = "", y = mean, fill = variable)) +
    geom_col(color = "black") +
    coord_polar(theta = "y") + scale_fill_manual(values = c("black", "#346648", "#83aa8b", "lightsalmon3", "brown3", "tomato4","#dbb40d", "red", "blue", "grey"))+theme_void()+
    theme(legend.key.size = unit(1, 'cm'), #change legend key size
          legend.key.height = unit(1, 'cm'),  legend.title = element_text(size=25),
          legend.key.width = unit(1, 'cm'), #change legend key width
          legend.text = element_text(size=20))+theme(legend.title= element_blank())


DF_moderate_part<-subset(summary.part, Land_Coverage_Category=="Douglas-fir forest" & Burn_Severity=="Moderate")

ggplot(DF_moderate_part, aes(x = "", y = mean, fill = variable)) +
    geom_col(color = "black") +
    coord_polar(theta = "y") + scale_fill_manual(values = c("black", "#346648", "#83aa8b", "lightsalmon3", "brown3", "tomato4","#dbb40d", "red", "blue", "grey"))+theme_void()+
    theme(legend.key.size = unit(1, 'cm'), #change legend key size
          legend.key.height = unit(1, 'cm'),  legend.title = element_text(size=25),
          legend.key.width = unit(1, 'cm'), #change legend key width
          legend.text = element_text(size=20))+theme(legend.title= element_blank())

DF_High_part<-subset(summary.part, Land_Coverage_Category=="Douglas-fir forest" & Burn_Severity=="High")

ggplot(DF_High_part, aes(x = "", y = mean, fill = variable)) +
    geom_col(color = "black") +
    coord_polar(theta = "y") + scale_fill_manual(values = c("black", "#346648", "#83aa8b", "lightsalmon3", "brown3", "tomato4","#dbb40d", "red", "blue", "grey"))+theme_void()+
    theme(legend.key.size = unit(1, 'cm'), #change legend key size
          legend.key.height = unit(1, 'cm'),  legend.title = element_text(size=25),
          legend.key.width = unit(1, 'cm'), #change legend key width
          legend.text = element_text(size=20))+theme(legend.title= element_blank())



DF_unburn_filt<-subset(summary.filt, Land_Coverage_Category=="Douglas-fir forest" & Burn_Severity=="Unburned")

ggplot(DF_unburn_filt, aes(x = "", y = mean, fill = variable)) +
    geom_col(color = "black") +
    coord_polar(theta = "y") + scale_fill_manual(values = c("black", "#346648", "#83aa8b", "lightsalmon3", "brown3", "tomato4","#dbb40d", "red", "blue", "grey"))+theme_void()+
    theme(legend.key.size = unit(1, 'cm'), #change legend key size
          legend.key.height = unit(1, 'cm'),  legend.title = element_text(size=25),
          legend.key.width = unit(1, 'cm'), #change legend key width
          legend.text = element_text(size=20))+theme(legend.title= element_blank())

DF_low_filt<-subset(summary.filt, Land_Coverage_Category=="Douglas-fir forest" & Burn_Severity=="Low")

ggplot(DF_low_filt, aes(x = "", y = mean, fill = variable)) +
    geom_col(color = "black") +
    coord_polar(theta = "y") + scale_fill_manual(values = c("black", "#346648", "#83aa8b", "lightsalmon3", "brown3", "tomato4","#dbb40d", "red", "blue", "grey"))+theme_void()+
    theme(legend.key.size = unit(1, 'cm'), #change legend key size
          legend.key.height = unit(1, 'cm'),  legend.title = element_text(size=25),
          legend.key.width = unit(1, 'cm'), #change legend key width
          legend.text = element_text(size=20))+theme(legend.title= element_blank())


DF_moderate_filt<-subset(summary.filt, Land_Coverage_Category=="Douglas-fir forest" & Burn_Severity=="Moderate")

ggplot(DF_moderate_filt, aes(x = "", y = mean, fill = variable)) +
    geom_col(color = "black") +
    coord_polar(theta = "y") + scale_fill_manual(values = c("black", "#346648", "#83aa8b", "lightsalmon3", "brown3", "tomato4","#dbb40d", "red", "blue", "grey"))+theme_void()+
    theme(legend.key.size = unit(1, 'cm'), #change legend key size
          legend.key.height = unit(1, 'cm'),  legend.title = element_text(size=25),
          legend.key.width = unit(1, 'cm'), #change legend key width
          legend.text = element_text(size=20))+theme(legend.title= element_blank())

DF_High_filt<-subset(summary.part, Land_Coverage_Category=="Douglas-fir forest" & Burn_Severity=="High")

ggplot(DF_High_filt, aes(x = "", y = mean, fill = variable)) +
    geom_col(color = "black") +
    coord_polar(theta = "y") + scale_fill_manual(values = c("black", "#346648", "#83aa8b", "lightsalmon3", "brown3", "tomato4","#dbb40d", "red", "blue", "grey"))+theme_void()+
    theme(legend.key.size = unit(1, 'cm'), #change legend key size
          legend.key.height = unit(1, 'cm'),  legend.title = element_text(size=25),
          legend.key.width = unit(1, 'cm'), #change legend key width
          legend.text = element_text(size=20))+theme(legend.title= element_blank())





#changing grouping to be only the metals
data<-XANES %>%
  separate(col=File_Name, into = c("Element", "StudyCode", "ID", "SampleType", "Sample"), sep="_") %>%
  mutate(Parent_ID= paste(StudyCode, ID, sep="_"))

data<-data[ -c(1:3,5)]

data$Ca<-data$Pi_Ca+data$Po_Ca
data$Al<-data$Pi_Al+data$Po_Al
data$Mg<-data$Pi_Mg
data$K<-data$Pi_K
data$Na<-data$Pi_Na+data$Po_Na
data$Fe<-data$Pi_Fe+data$Po_Fe

data<-data[ -c(2:14)]

data<-data %>% left_join(metadata)

data<-data[grepl("A", data$Sample_Name), ]

data<-subset(data, Burn_Severity!="")

solid<-subset(data, SampleType=="solid")
part<-subset(data, SampleType=="part")
filt<-subset(data, SampleType=="filt07")


solid<-melt(solid, id=c("SampleType", "Parent_ID", "Sample_Name", "Land_Coverage_Category","Burn_Severity", "Burn_Treatment",  "Char_Leached", "Leachate_Volume"))
part<-melt(part, id=c("SampleType", "Parent_ID", "Sample_Name", "Land_Coverage_Category","Burn_Severity", "Burn_Treatment",  "Char_Leached", "Leachate_Volume"))
filt<-melt(filt, id=c("SampleType", "Parent_ID", "Sample_Name", "Land_Coverage_Category","Burn_Severity", "Burn_Treatment",  "Char_Leached", "Leachate_Volume"))

summary.xanes.solid<-solid %>%
  group_by(variable, Burn_Severity, Land_Coverage_Category) %>%
  summarise(
    n = n(), mean = mean(value), sd=sd(value)
  )
summary.xanes.part<-part %>%
  group_by(variable, Burn_Severity, Land_Coverage_Category) %>%
  summarise(
    n = n(), mean = mean(value), sd=sd(value)
  )
summary.xanes.filt<-filt %>%
  group_by(variable, Burn_Severity, Land_Coverage_Category) %>%
  summarise(
    n = n(), mean = mean(value), sd=sd(value)
  )

summary.solid<-summary.xanes.solid
summary.part<-summary.xanes.part
summary.filt<-summary.xanes.filt


#trying pie chart instead
DF_unburn_solid<-subset(summary.solid, Land_Coverage_Category=="Douglas-fir forest" & Burn_Severity=="Unburned")

ggplot(DF_unburn_solid, aes(x = "", y = mean, fill = variable)) +
    geom_col(color = "black") +
    coord_polar(theta = "y") + scale_fill_manual(values = c("#d55e00", "#cc79a7", "#0072b2", "#dbb40d", "#83aa8b","gray"))+theme_void()+
    theme(legend.key.size = unit(1, 'cm'), #change legend key size
          legend.key.height = unit(1, 'cm'),  legend.title = element_text(size=25),
          legend.key.width = unit(1, 'cm'), #change legend key width
          legend.text = element_text(size=20))+theme(legend.title= element_blank())

, "darkorange3",  "indianred3" "deepskyblue4","black", "gray" ,"#8c564b", "#c49c94", "orange1", "cadetblue3"

 "#F28E2B",  "#9C755F",  "#BAB0AC", "#79706E", "#B07AA1", "#4E79A7", "#DAA51B", "#EDC949","#59A14F"

DF_low_solid<-subset(summary.solid, Land_Coverage_Category=="Douglas-fir forest" & Burn_Severity=="Low")

ggplot(DF_low_solid, aes(x = "", y = mean, fill = variable)) +
    geom_col(color = "black") +
    coord_polar(theta = "y") + scale_fill_manual(values = c("#d55e00", "#cc79a7", "#0072b2", "#dbb40d", "#83aa8b","gray"))+theme_void()+
    theme(legend.key.size = unit(1, 'cm'), #change legend key size
          legend.key.height = unit(1, 'cm'),  legend.title = element_text(size=25),
          legend.key.width = unit(1, 'cm'), #change legend key width
          legend.text = element_text(size=20))+theme(legend.title= element_blank())


DF_moderate_solid<-subset(summary.solid, Land_Coverage_Category=="Douglas-fir forest" & Burn_Severity=="Moderate")

ggplot(DF_moderate_solid, aes(x = "", y = mean, fill = variable)) +
    geom_col(color = "black") +
    coord_polar(theta = "y") + scale_fill_manual(values = c("#d55e00", "#cc79a7", "#0072b2", "#dbb40d", "#83aa8b","gray"))+theme_void()+
    theme(legend.key.size = unit(1, 'cm'), #change legend key size
          legend.key.height = unit(1, 'cm'),  legend.title = element_text(size=25),
          legend.key.width = unit(1, 'cm'), #change legend key width
          legend.text = element_text(size=20))+theme(legend.title= element_blank())

DF_High_solid<-subset(summary.solid, Land_Coverage_Category=="Douglas-fir forest" & Burn_Severity=="High")

ggplot(DF_High_solid, aes(x = "", y = mean, fill = variable)) +
    geom_col(color = "black") +
    coord_polar(theta = "y") + scale_fill_manual(values = c("#d55e00", "#cc79a7", "#0072b2", "#dbb40d", "#83aa8b","gray"))+theme_void()+
    theme(legend.key.size = unit(1, 'cm'), #change legend key size
          legend.key.height = unit(1, 'cm'),  legend.title = element_text(size=25),
          legend.key.width = unit(1, 'cm'), #change legend key width
          legend.text = element_text(size=20))+theme(legend.title= element_blank())



SS_unburn_solid<-subset(summary.solid, Land_Coverage_Category=="Sagebrush shrubland" & Burn_Severity=="Unburned")

ggplot(SS_unburn_solid, aes(x = "", y = mean, fill = variable)) +
    geom_col(color = "black") +
    coord_polar(theta = "y") + scale_fill_manual(values = c("#d55e00", "#cc79a7", "#0072b2", "#dbb40d", "#83aa8b","gray"))+theme_void()+
    theme(legend.key.size = unit(1, 'cm'), #change legend key size
          legend.key.height = unit(1, 'cm'),  legend.title = element_text(size=25),
          legend.key.width = unit(1, 'cm'), #change legend key width
          legend.text = element_text(size=20))+theme(legend.title= element_blank())

, "darkorange3",  "indianred3" "deepskyblue4","black", "gray" ,"#8c564b", "#c49c94", "orange1", "cadetblue3"

 "#F28E2B",  "#9C755F",  "#BAB0AC", "#79706E", "#B07AA1", "#4E79A7", "#DAA51B", "#EDC949","#59A14F"

SS_low_solid<-subset(summary.solid, Land_Coverage_Category=="Sagebrush shrubland" & Burn_Severity=="Low")

ggplot(SS_low_solid, aes(x = "", y = mean, fill = variable)) +
    geom_col(color = "black") +
    coord_polar(theta = "y") + scale_fill_manual(values = c("#d55e00", "#cc79a7", "#0072b2", "#dbb40d", "#83aa8b","gray"))+theme_void()+
    theme(legend.key.size = unit(1, 'cm'), #change legend key size
          legend.key.height = unit(1, 'cm'),  legend.title = element_text(size=25),
          legend.key.width = unit(1, 'cm'), #change legend key width
          legend.text = element_text(size=20))+theme(legend.title= element_blank())


SS_moderate_solid<-subset(summary.solid, Land_Coverage_Category=="Sagebrush shrubland" & Burn_Severity=="Moderate")

ggplot(SS_moderate_solid, aes(x = "", y = mean, fill = variable)) +
    geom_col(color = "black") +
    coord_polar(theta = "y") + scale_fill_manual(values = c("#d55e00", "#cc79a7", "#0072b2", "#dbb40d", "#83aa8b","gray"))+theme_void()+
    theme(legend.key.size = unit(1, 'cm'), #change legend key size
          legend.key.height = unit(1, 'cm'),  legend.title = element_text(size=25),
          legend.key.width = unit(1, 'cm'), #change legend key width
          legend.text = element_text(size=20))+theme(legend.title= element_blank())



SS_unburn_part<-subset(summary.part, Land_Coverage_Category=="Sagebrush shrubland" & Burn_Severity=="Unburned")

ggplot(SS_unburn_part, aes(x = "", y = mean, fill = variable)) +
    geom_col(color = "black") +
    coord_polar(theta = "y") + scale_fill_manual(values = c("#d55e00", "#cc79a7", "#0072b2", "#dbb40d", "#83aa8b","gray"))+theme_void()+
    theme(legend.key.size = unit(1, 'cm'), #change legend key size
          legend.key.height = unit(1, 'cm'),  legend.title = element_text(size=25),
          legend.key.width = unit(1, 'cm'), #change legend key width
          legend.text = element_text(size=20))+theme(legend.title= element_blank())

, "darkorange3",  "indianred3" "deepskyblue4","black", "gray" ,"#8c564b", "#c49c94", "orange1", "cadetblue3"

 "#F28E2B",  "#9C755F",  "#BAB0AC", "#79706E", "#B07AA1", "#4E79A7", "#DAA51B", "#EDC949","#59A14F"

DF_low_part<-subset(summary.part, Land_Coverage_Category=="Douglas-fir forest" & Burn_Severity=="Low")

ggplot(DF_low_part, aes(x = "", y = mean, fill = variable)) +
    geom_col(color = "black") +
    coord_polar(theta = "y") + scale_fill_manual(values = c("#d55e00", "#cc79a7", "#0072b2", "#dbb40d", "#83aa8b","gray"))+theme_void()+
    theme(legend.key.size = unit(1, 'cm'), #change legend key size
          legend.key.height = unit(1, 'cm'),  legend.title = element_text(size=25),
          legend.key.width = unit(1, 'cm'), #change legend key width
          legend.text = element_text(size=20))+theme(legend.title= element_blank())


DF_moderate_part<-subset(summary.part, Land_Coverage_Category=="Douglas-fir forest" & Burn_Severity=="Moderate")

ggplot(DF_moderate_part, aes(x = "", y = mean, fill = variable)) +
    geom_col(color = "black") +
    coord_polar(theta = "y") + scale_fill_manual(values = c("#d55e00", "#cc79a7", "#0072b2", "#dbb40d", "#83aa8b","gray"))+theme_void()+
    theme(legend.key.size = unit(1, 'cm'), #change legend key size
          legend.key.height = unit(1, 'cm'),  legend.title = element_text(size=25),
          legend.key.width = unit(1, 'cm'), #change legend key width
          legend.text = element_text(size=20))+theme(legend.title= element_blank())

DF_High_part<-subset(summary.part, Land_Coverage_Category=="Douglas-fir forest" & Burn_Severity=="High")

ggplot(DF_High_part, aes(x = "", y = mean, fill = variable)) +
    geom_col(color = "black") +
    coord_polar(theta = "y") + scale_fill_manual(values = c("#d55e00", "#cc79a7", "#0072b2", "#dbb40d", "#83aa8b","gray"))+theme_void()+
    theme(legend.key.size = unit(1, 'cm'), #change legend key size
          legend.key.height = unit(1, 'cm'),  legend.title = element_text(size=25),
          legend.key.width = unit(1, 'cm'), #change legend key width
          legend.text = element_text(size=20))+theme(legend.title= element_blank())



DF_unburn_filt<-subset(summary.filt, Land_Coverage_Category=="Douglas-fir forest" & Burn_Severity=="Unburned")

ggplot(DF_unburn_filt, aes(x = "", y = mean, fill = variable)) +
    geom_col(color = "black") +
    coord_polar(theta = "y") + scale_fill_manual(values = c("#d55e00", "#cc79a7", "#0072b2", "#dbb40d", "#83aa8b","gray"))+theme_void()+
    theme(legend.key.size = unit(1, 'cm'), #change legend key size
          legend.key.height = unit(1, 'cm'),  legend.title = element_text(size=25),
          legend.key.width = unit(1, 'cm'), #change legend key width
          legend.text = element_text(size=20))+theme(legend.title= element_blank())

DF_low_filt<-subset(summary.filt, Land_Coverage_Category=="Douglas-fir forest" & Burn_Severity=="Low")

ggplot(DF_low_filt, aes(x = "", y = mean, fill = variable)) +
    geom_col(color = "black") +
    coord_polar(theta = "y") + scale_fill_manual(values = c("#d55e00", "#cc79a7", "#0072b2", "#dbb40d", "#83aa8b","gray"))+theme_void()+
    theme(legend.key.size = unit(1, 'cm'), #change legend key size
          legend.key.height = unit(1, 'cm'),  legend.title = element_text(size=25),
          legend.key.width = unit(1, 'cm'), #change legend key width
          legend.text = element_text(size=20))+theme(legend.title= element_blank())


DF_moderate_filt<-subset(summary.filt, Land_Coverage_Category=="Douglas-fir forest" & Burn_Severity=="Moderate")

ggplot(DF_moderate_filt, aes(x = "", y = mean, fill = variable)) +
    geom_col(color = "black") +
    coord_polar(theta = "y") + scale_fill_manual(values = c("#d55e00", "#cc79a7", "#0072b2", "#dbb40d", "#83aa8b","gray"))+theme_void()+
    theme(legend.key.size = unit(1, 'cm'), #change legend key size
          legend.key.height = unit(1, 'cm'),  legend.title = element_text(size=25),
          legend.key.width = unit(1, 'cm'), #change legend key width
          legend.text = element_text(size=20))+theme(legend.title= element_blank())

DF_High_filt<-subset(summary.part, Land_Coverage_Category=="Douglas-fir forest" & Burn_Severity=="High")

ggplot(DF_High_filt, aes(x = "", y = mean, fill = variable)) +
    geom_col(color = "black") +
    coord_polar(theta = "y") + scale_fill_manual(values = c("#d55e00", "#cc79a7", "#0072b2", "#dbb40d", "#83aa8b","gray"))+theme_void()+
    theme(legend.key.size = unit(1, 'cm'), #change legend key size
          legend.key.height = unit(1, 'cm'),  legend.title = element_text(size=25),
          legend.key.width = unit(1, 'cm'), #change legend key width
          legend.text = element_text(size=20))+theme(legend.title= element_blank())


#spectra stacked
spectra <- read.csv("~/Library/CloudStorage/OneDrive-SharedLibraries-PNNL/RC-3, River Corridor SFA - Presentations/ESA_2023/Morgan/spectra.csv")
#spectra<-melt(spectra, id=c("energy"))

#filt<-subset(spectra, variable=="P_BSLE_0013_filt07_sample" | variable=="P_BSLE_0002_filt07_sample" | variable=="P_BSLE_0050_filt07_sample" | variable=="P_BSLE_0007_filt07_sample")

#part<-subset(spectra, variable=="P_BSLE_0013_part_sample" | variable=="P_BSLE_0002_part_sample" | variable=="P_BSLE_0050_part_sample" | variable=="P_BSLE_0007_part_sample")

#DFL.sample.xas.spectra.gradient<-ggplot(DFL, aes(x=energy, y=value))+geom_line()+theme_classic()+ylab("Noramlized Absorption (arb. units)")+ xlab("Energy (eV)")+facet_grid(variable~.)+theme(text = element_text(size = 15))+xlim(2140,2200)

filt<-spectra[ -c(6:9)]
filt$P_BSLE_0007_filt07_sample<-filt$P_BSLE_0007_filt07_sample+7
filt$P_BSLE_0002_filt07_sample<-filt$P_BSLE_0002_filt07_sample+14
filt$P_BSLE_0050_filt07_sample<-filt$P_BSLE_0050_filt07_sample+21
filt<-melt(filt, id=c("energy"))

ggplot(filt, aes(x=energy, y=value))+geom_line(aes(color = variable), show.legend = FALSE)+theme_classic()+ylab("Noramlized Absorption (arb. units)")+ xlab("Energy (eV)")+theme(text = element_text(size = 15))+xlim(2140,2200)+scale_color_manual(values=c('Black','Black', 'Black', 'Black'))




part<-spectra[ -c(2:5)]
part$P_BSLE_0010_part_sample<-part$P_BSLE_0010_part_sample+7
part$P_BSLE_0002_part_sample<-part$P_BSLE_0002_part_sample+14
part$P_BSLE_0050_part_sample<-part$P_BSLE_0050_part_sample+21
part<-melt(part, id=c("energy"))

ggplot(part, aes(x=energy, y=value))+geom_line(aes(color = variable), show.legend = FALSE)+theme_classic()+ylab("Noramlized Absorption (arb. units)")+ xlab("Energy (eV)")+theme(text = element_text(size = 15))+xlim(2140,2200)+scale_color_manual(values=c('Black','Black', 'Black', 'Black'))





```



Solid XANES; open air
```{r}
Grouped_solid_LCF_R <- read.csv("~/PNNL/RC-3, River Corridor SFA - Burn Severity Experiments/Burn Severity Experiment/Data/P_all data streams/P XAS/Processed_final/BSLE_Solids_Final_Fits/Grouped_solid_LCF_R.csv")

data<-Grouped_solid_LCF_R %>% left_join(BSLE_solid_metadata_subset)

#removing some columns (where I added Po into the metal association but this gets weird b/c of lecithin)
data<-data[ -c(9:11, 13:19)]
#might want to add Pi column back in to compare Pi determined by NMR and XANES

data<-melt(data, id=c("Parent_ID", "Sample_ID", "Burn_Severity", "Burn_treatment", "Feedstock_Species", "Feedstock", "Land_Coverage_Category", "Feedstock_Status", "Moisture", "Char_Name", "Max_temp_C", "Burn_duration_sec"))

summary.xanes.solid<-data %>%
  group_by(variable, Burn_Severity, Feedstock) %>%
  summarise(
    n = n(), mean = mean(value), sd=sd(value)
  )

write.csv(summary.xanes.solid, file = "~/PNNL/RC-3, River Corridor SFA - Burn Severity Experiments/Burn Severity Experiment/Data/P_all data streams/P XAS/Processed_final/summary.xanes.solid.csv")


#summarySE(data, "value", c("variable", "Burn_Severity", "Phase"))


ggplot(data, aes(x=Burn_Severity, y=value, fill=Feedstock))+geom_boxplot()+facet_grid(variable~Feedstock)+theme_classic()+ xlab("Burn Severity")+ ylab("Relative Percent")+scale_fill_manual(values=c("#346648", "#83aa8b", "#dbb40d"))+ggtitle("P XANES: BSLE Solids")

ggplot(data, aes(fill=variable, y=value, x=Burn_Severity)) + 
    geom_bar(position="fill", stat="identity")+theme_classic()+facet_grid(.~Feedstock)+scale_fill_manual(values=c("#346648", "#83aa8b", "#dbb40d", "lightgoldenrod", "lightsalmon3", "brown3", "tomato4"))+ggtitle("P XANES: BSLE Solids")

ggplot(data, aes(fill=variable, y=value, x=Burn_Severity, color=variable)) + geom_point()+theme_classic()+facet_grid(variable~Feedstock)+scale_color_manual(values=c("#346648", "#83aa8b", "#dbb40d", "lightgoldenrod", "lightsalmon3", "brown3", "tomato4"))+ggtitle("P XANES: BSLE Solids")

dataset<-subset(data, variable=="Po" | variable=="Pi_Ca" | variable=="Pi_K" | variable=="Pi_Mg")

ggplot(dataset, aes(x=Burn_Severity, y=value, fill=Feedstock))+geom_boxplot()+facet_grid(variable~Feedstock)+theme_classic()+ xlab("Burn Severity")+ ylab("Relative Percent")+scale_fill_manual(values=c("#346648", "#83aa8b", "#dbb40d"))+ggtitle("P XANES: BSLE Solids")+theme(axis.text.x = element_text(angle = 45, hjust=1))


#trying pie chart instead
DFL.raw<-subset(summary.xanes.solid, Feedstock=="Douglas-fir Live" & Burn_Severity=="Raw")
#DFL.raw<-subset(DFL.raw, variable!="Mg_Total" & variable!= "Na_Total")
DFL.raw<-ggplot(DFL.raw, aes(x = "", y = mean, fill = variable)) +
    geom_col(color = "black") +
    coord_polar(theta = "y") + scale_fill_manual(values = c("black", "#346648", "#83aa8b", "lightsalmon3", "brown3", "tomato4","#dbb40d"))+theme_void()+
    theme(legend.key.size = unit(1, 'cm'), #change legend key size
          legend.key.height = unit(1, 'cm'),  legend.title = element_text(size=25),
          legend.key.width = unit(1, 'cm'), #change legend key width
          legend.text = element_text(size=20))+theme(legend.title= element_blank())

pdf(file = "~/PNNL/RC-3, River Corridor SFA - Burn Severity Experiments/Burn Severity Experiment/Data/P_all data streams/R_Code_AGU2022/DFL.raw.pdf", width = 10, height = 3.5) 
print(DFL.raw)
dev.off()

DFL.low<-subset(summary.xanes.solid, Feedstock=="Douglas-fir Live" & Burn_Severity=="Low")
DFL.low<-ggplot(DFL.low, aes(x = "", y = mean, fill = variable)) +
    geom_col(color = "black") +
    coord_polar(theta = "y") + scale_fill_manual(values = c("black", "#346648", "#83aa8b", "lightsalmon3", "brown3", "tomato4","#dbb40d"))+theme_void()+
    theme(legend.key.size = unit(1, 'cm'), #change legend key size
          legend.key.height = unit(1, 'cm'),  legend.title = element_text(size=25),
          legend.key.width = unit(1, 'cm'), #change legend key width
          legend.text = element_text(size=20))+theme(legend.title= element_blank())

pdf(file = "~/PNNL/RC-3, River Corridor SFA - Burn Severity Experiments/Burn Severity Experiment/Data/P_all data streams/R_Code_AGU2022/DFL.low.pdf", width = 10, height = 3.5) 
print(DFL.low)
dev.off()

DFL.mod<-subset(summary.xanes.solid, Feedstock=="Douglas-fir Live" & Burn_Severity=="Moderate")
DFL.mod<-ggplot(DFL.mod, aes(x = "", y = mean, fill = variable)) +
    geom_col(color = "black") +
    coord_polar(theta = "y") + scale_fill_manual(values = c("black", "#346648", "#83aa8b", "lightsalmon3", "brown3", "tomato4","#dbb40d"))+theme_void()+
    theme(legend.key.size = unit(1, 'cm'), #change legend key size
          legend.key.height = unit(1, 'cm'),  legend.title = element_text(size=25),
          legend.key.width = unit(1, 'cm'), #change legend key width
          legend.text = element_text(size=20))+theme(legend.title= element_blank())

pdf(file = "~/PNNL/RC-3, River Corridor SFA - Burn Severity Experiments/Burn Severity Experiment/Data/P_all data streams/R_Code_AGU2022/DFL.mod.pdf", width = 10, height = 3.5) 
print(DFL.mod)
dev.off()

DFL.high<-subset(summary.xanes.solid, Feedstock=="Douglas-fir Live" & Burn_Severity=="High")
DFL.high<-ggplot(DFL.high, aes(x = "", y = mean, fill = variable)) +
    geom_col(color = "black") +
    coord_polar(theta = "y") + scale_fill_manual(values = c("black", "#346648", "#83aa8b", "lightsalmon3", "brown3", "tomato4","#dbb40d"))+theme_void()+
    theme(legend.key.size = unit(1, 'cm'), #change legend key size
          legend.key.height = unit(1, 'cm'),  legend.title = element_text(size=25),
          legend.key.width = unit(1, 'cm'), #change legend key width
          legend.text = element_text(size=20))+theme(legend.title= element_blank())

pdf(file = "~/PNNL/RC-3, River Corridor SFA - Burn Severity Experiments/Burn Severity Experiment/Data/P_all data streams/R_Code_AGU2022/DFL.high.pdf", width = 10, height = 3.5) 
print(DFL.high)
dev.off()


DFD.raw<-subset(summary.xanes.solid, Feedstock=="Douglas-fir Litter" & Burn_Severity=="Raw")
#DFD.raw<-subset(DFD.raw, variable!="Mg_Total" & variable!= "Na_Total")
DFD.raw<-ggplot(DFD.raw, aes(x = "", y = mean, fill = variable)) +
    geom_col(color = "black") +
    coord_polar(theta = "y") + scale_fill_manual(values = c("black", "gray46","#346648", "#83aa8b", "purple4", "plum3", "#dbb40d"))+theme_void()+
    theme(legend.key.size = unit(1, 'cm'), #change legend key size
          legend.key.height = unit(1, 'cm'),  legend.title = element_text(size=25),
          legend.key.width = unit(1, 'cm'), #change legend key width
          legend.text = element_text(size=20))+theme(legend.title= element_blank())

pdf(file = "~/PNNL/RC-3, River Corridor SFA - Burn Severity Experiments/Burn Severity Experiment/Data/P_all data streams/R_Code_AGU2022/DFD.raw.pdf", width = 10, height = 3.5) 
print(DFD.raw)
dev.off()

DFD.low<-subset(summary.xanes.solid, Feedstock=="Douglas-fir Litter" & Burn_Severity=="Low")
DFD.low<-ggplot(DFD.low, aes(x = "", y = mean, fill = variable)) +
    geom_col(color = "black") +
    coord_polar(theta = "y") + scale_fill_manual(values = c("black", "gray46","#346648", "#83aa8b", "purple4", "plum3", "#dbb40d"))+theme_void()+
    theme(legend.key.size = unit(1, 'cm'), #change legend key size
          legend.key.height = unit(1, 'cm'),  legend.title = element_text(size=25),
          legend.key.width = unit(1, 'cm'), #change legend key width
          legend.text = element_text(size=20))+theme(legend.title= element_blank())

pdf(file = "~/PNNL/RC-3, River Corridor SFA - Burn Severity Experiments/Burn Severity Experiment/Data/P_all data streams/R_Code_AGU2022/DFD.low.pdf", width = 10, height = 3.5) 
print(DFD.low)
dev.off()

DFD.mod<-subset(summary.xanes.solid, Feedstock=="Douglas-fir Litter" & Burn_Severity=="Moderate")
DFD.mod<-ggplot(DFD.mod, aes(x = "", y = mean, fill = variable)) +
    geom_col(color = "black") +
    coord_polar(theta = "y") + scale_fill_manual(values = c("black", "gray46","#346648", "#83aa8b", "purple4", "plum3", "#dbb40d"))+theme_void()+
    theme(legend.key.size = unit(1, 'cm'), #change legend key size
          legend.key.height = unit(1, 'cm'),  legend.title = element_text(size=25),
          legend.key.width = unit(1, 'cm'), #change legend key width
          legend.text = element_text(size=20))+theme(legend.title= element_blank())

pdf(file = "~/PNNL/RC-3, River Corridor SFA - Burn Severity Experiments/Burn Severity Experiment/Data/P_all data streams/R_Code_AGU2022/DFD.mod.pdf", width = 10, height = 3.5) 
print(DFD.mod)
dev.off()

DFD.high<-subset(summary.xanes.solid, Feedstock=="Douglas-fir Litter" & Burn_Severity=="High")
DFD.high<-ggplot(DFD.high, aes(x = "", y = mean, fill = variable)) +
    geom_col(color = "black") +
    coord_polar(theta = "y") + scale_fill_manual(values = c("black", "gray46","#346648", "#83aa8b", "purple4", "plum3", "#dbb40d"))+theme_void()+
    theme(legend.key.size = unit(1, 'cm'), #change legend key size
          legend.key.height = unit(1, 'cm'),  legend.title = element_text(size=25),
          legend.key.width = unit(1, 'cm'), #change legend key width
          legend.text = element_text(size=20))+theme(legend.title= element_blank())

pdf(file = "~/PNNL/RC-3, River Corridor SFA - Burn Severity Experiments/Burn Severity Experiment/Data/P_all data streams/R_Code_AGU2022/DFD.high.pdf", width = 10, height = 3.5) 
print(DFD.high)
dev.off()



SB.raw<-subset(summary.xanes.solid, Feedstock=="Big Sagebrush" & Burn_Severity=="Raw")
SB.raw<-ggplot(SB.raw, aes(x = "", y = mean, fill = variable)) +
    geom_col(color = "black") +
    coord_polar(theta = "y") + scale_fill_manual(values = c("black", "#346648", "#83aa8b", "lightsalmon3", "brown3", "tomato4","#dbb40d"))+theme_void()+
    theme(legend.key.size = unit(1, 'cm'), #change legend key size
          legend.key.height = unit(1, 'cm'),  legend.title = element_text(size=25),
          legend.key.width = unit(1, 'cm'), #change legend key width
          legend.text = element_text(size=20))+theme(legend.title= element_blank())

pdf(file = "~/PNNL/RC-3, River Corridor SFA - Burn Severity Experiments/Burn Severity Experiment/Data/P_all data streams/R_Code_AGU2022/SB.raw.pdf", width = 10, height = 3.5)
print(SB.raw)
dev.off()

SB.low<-subset(summary.xanes.solid, Feedstock=="Big Sagebrush" & Burn_Severity=="Low")
SB.low<-ggplot(SB.low, aes(x = "", y = mean, fill = variable)) +
    geom_col(color = "black") +
    coord_polar(theta = "y") + scale_fill_manual(values = c("black", "#346648", "#83aa8b", "lightsalmon3", "brown3", "tomato4","#dbb40d"))+theme_void()+
    theme(legend.key.size = unit(1, 'cm'), #change legend key size
          legend.key.height = unit(1, 'cm'),  legend.title = element_text(size=25),
          legend.key.width = unit(1, 'cm'), #change legend key width
          legend.text = element_text(size=20))+theme(legend.title= element_blank())

pdf(file = "~/PNNL/RC-3, River Corridor SFA - Burn Severity Experiments/Burn Severity Experiment/Data/P_all data streams/R_Code_AGU2022/SB.low.pdf", width = 10, height = 3.5)
print(SB.low)
dev.off()

SB.mod<-subset(summary.xanes.solid, Feedstock=="Big Sagebrush" & Burn_Severity=="Moderate")
SB.mod<-ggplot(SB.mod, aes(x = "", y = mean, fill = variable)) +
    geom_col(color = "black") +
    coord_polar(theta = "y") + scale_fill_manual(values = c("black", "#346648", "#83aa8b", "lightsalmon3", "brown3", "tomato4","#dbb40d"))+theme_void()+
    theme(legend.key.size = unit(1, 'cm'), #change legend key size
          legend.key.height = unit(1, 'cm'),  legend.title = element_text(size=25),
          legend.key.width = unit(1, 'cm'), #change legend key width
          legend.text = element_text(size=20))+theme(legend.title= element_blank())

pdf(file = "~/PNNL/RC-3, River Corridor SFA - Burn Severity Experiments/Burn Severity Experiment/Data/P_all data streams/R_Code_AGU2022/SB.mod.pdf", width = 10, height = 3.5)
print(SB.mod)
dev.off()

#plot spectra of samples
BSLE_solid_sample_spectra_normalizedforfinalLCF_12.1.22 <- read.csv("~/PNNL/RC-3, River Corridor SFA - Burn Severity Experiments/Burn Severity Experiment/Data/P_all data streams/P XAS/Processed_final/BSLE_Solids_Final_Fits/BSLE_solid_sample_spectra_normalizedforfinalLCF_12.1.22.csv")


DFL<-BSLE_solid_sample_spectra_normalizedforfinalLCF_12.1.22[ c(25, 20, 19, 13, 1)]
DFL<-melt(DFL, id=c("energy"))

DFL.sample.xas.spectra.gradient<-ggplot(DFL, aes(x=energy, y=value))+geom_line()+theme_classic()+ylab("Noramlized Absorption (arb. units)")+ xlab("Energy (eV)")+facet_grid(variable~.)+theme(text = element_text(size = 15))+xlim(2140,2200)

pdf(file = "~/PNNL/RC-3, River Corridor SFA - Burn Severity Experiments/Burn Severity Experiment/Data/P_all data streams/R_Code_AGU2022/DFL.sample.xas.spectra.gradient.pdf", width = 3.5, height = 10) 
print(DFL.sample.xas.spectra.gradient)
dev.off()

#try to stack them differently
DFL<-BSLE_solid_sample_spectra_normalizedforfinalLCF_12.1.22[ c(25, 20, 19, 13, 1)]
DFL$P_BSLE_0073_solidchar_036_fl_4s_avg<-DFL$P_BSLE_0073_solidchar_036_fl_4s_avg+9
DFL$P_BSLE_0052_solidchar_035_fl_6sc_avg<-DFL$P_BSLE_0052_solidchar_035_fl_6sc_avg+6
DFL$P_BSLE_0051_solidchar_034_fl_6s_avg<-DFL$P_BSLE_0051_solidchar_034_fl_6s_avg+3
DFL<-melt(DFL, id=c("energy"))

DFL.sample.xas.spectra.gradient<-ggplot(DFL, aes(x=energy, y=value))+geom_line(aes(color = variable), show.legend = FALSE)+theme_classic()+ylab("Noramlized Absorption (arb. units)")+ xlab("Energy (eV)")+theme(text = element_text(size = 15))+xlim(2140,2200)+scale_color_manual(values=c('Black','Black', 'Black', 'Black'))

pdf(file = "~/PNNL/RC-3, River Corridor SFA - Burn Severity Experiments/Burn Severity Experiment/Data/P_all data streams/R_Code_AGU2022/DFL.sample.xas.spectra.gradient.pdf", width = 3.5, height = 7) 
print(DFL.sample.xas.spectra.gradient)
dev.off()

DFD<-BSLE_solid_sample_spectra_normalizedforfinalLCF_12.1.22[ c(18, 3, 8, 14, 1)]
DFD<-melt(DFD, id=c("energy"))

DFD.sample.xas.spectra.gradient<-ggplot(DFD, aes(x=energy, y=value))+geom_line()+theme_classic()+ylab("Noramlized Absorption (arb. units)")+ xlab("Energy (eV)")+facet_grid(variable~.)+theme(text = element_text(size = 15))+xlim(2140,2200)

pdf(file = "~/PNNL/RC-3, River Corridor SFA - Burn Severity Experiments/Burn Severity Experiment/Data/P_all data streams/R_Code_AGU2022/DFD.sample.xas.spectra.gradient.pdf", width = 3.5, height = 10) 
print(DFD.sample.xas.spectra.gradient)
dev.off()

#stack differently
DFD<-BSLE_solid_sample_spectra_normalizedforfinalLCF_12.1.22[ c(21, 26, 8, 14, 1)]
DFD$P_BSLE_0067_solidchar_017_fl_4s_avg<-DFD$P_BSLE_0067_solidchar_017_fl_4s_avg+9
DFD$P_BSLE_58_solid_8s_fl_avg.xdi<-DFD$P_BSLE_58_solid_8s_fl_avg.xdi+6
DFD$P_BSLE_0007_solidchar_042<-DFD$P_BSLE_0007_solidchar_042+3
DFD<-melt(DFD, id=c("energy"))

DFD.sample.xas.spectra.gradient<-ggplot(DFD, aes(x=energy, y=value))+geom_line(aes(color = variable), show.legend = FALSE)+theme_classic()+ylab("Noramlized Absorption (arb. units)")+ xlab("Energy (eV)")+theme(text = element_text(size = 15))+xlim(2140,2200)+scale_color_manual(values=c('Black','Black', 'Black', 'Black'))

pdf(file = "~/PNNL/RC-3, River Corridor SFA - Burn Severity Experiments/Burn Severity Experiment/Data/P_all data streams/R_Code_AGU2022/DFD.sample.xas.spectra.gradient.pdf", width = 3.5, height = 7) 
print(DFD.sample.xas.spectra.gradient)
dev.off()


SB<-BSLE_solid_sample_spectra_normalizedforfinalLCF_12.1.22[ c(22, 12, 15, 1)]
SB<-melt(SB, id=c("energy"))

SB.sample.xas.spectra.gradient<-ggplot(SB, aes(x=energy, y=value))+geom_line()+theme_classic()+ylab("Noramlized Absorption (arb. units)")+ xlab("Energy (eV)")+facet_grid(variable~.)+theme(text = element_text(size = 15))+xlim(2140,2200)

pdf(file = "~/PNNL/RC-3, River Corridor SFA - Burn Severity Experiments/Burn Severity Experiment/Data/P_all data streams/R_Code_AGU2022/SB.sample.xas.spectra.gradient.pdf", width = 3.5, height = 10) 
print(SB.sample.xas.spectra.gradient)
dev.off()

#stack differently
SB<-BSLE_solid_sample_spectra_normalizedforfinalLCF_12.1.22[ c(24, 12, 15, 1)]
SB$P_BSLE_0011_solidchar_023_fl_8s_avgblank<-SB$P_BSLE_0011_solidchar_023_fl_8s_avg+9
SB$P_BSLE_0072_solidchar_022_fl_4s_avg<-SB$P_BSLE_0072_solidchar_022_fl_4s_avg+6
SB$P_BSLE_0011_solidchar_023_fl_8s_avg<-SB$P_BSLE_0011_solidchar_023_fl_8s_avg+3
SB<-melt(SB, id=c("energy"))

SB.sample.xas.spectra.gradient<-ggplot(SB, aes(x=energy, y=value))+geom_line(aes(color = variable), show.legend = FALSE)+theme_classic()+ylab("Noramlized Absorption (arb. units)")+ xlab("Energy (eV)")+theme(text = element_text(size = 15))+xlim(2140,2200)+scale_color_manual(values=c('Black','Black', 'Black', 'White'))

pdf(file = "~/PNNL/RC-3, River Corridor SFA - Burn Severity Experiments/Burn Severity Experiment/Data/P_all data streams/R_Code_AGU2022/SB.sample.xas.spectra.gradient.pdf", width = 3.5, height = 7) 
print(SB.sample.xas.spectra.gradient)
dev.off()

```


BSLE Solid NMR
```{r}
BSLE_NMR_Solid_Deg_Corr_for_R <- read.csv("~/PNNL/RC-3, River Corridor SFA - Burn Severity Experiments/Burn Severity Experiment/Data/P_all data streams/P NMR/Processed_Final/BSLE_NMR_Solid_Deg_Corr_for_R.csv")

data<-BSLE_NMR_Solid_Deg_Corr_for_R %>% left_join(BSLE_solid_metadata_subset)

data<-melt(data, id=c("Parent_ID", "Burn_Severity", "Burn_treatment", "Feedstock_Species", "Feedstock", "Land_Coverage_Category", "Feedstock_Status", "Moisture", "Char_Name", "Max_temp_C", "Burn_duration_sec"))

summary.nmr.solid.deg.corr<-data %>%
  group_by(variable, Burn_Severity, Feedstock) %>%
  summarise(
    n = n(), mean = mean(value), sd=sd(value)
  )

write.csv(summary.nmr.solid.deg.corr, file = "~/PNNL/RC-3, River Corridor SFA - Burn Severity Experiments/Burn Severity Experiment/Data/P_all data streams/P NMR/Processed_Final/summary.nmr.solid.deg.corr.csv")

summary.nmr.solid.deg.corr$variable=factor(summary.nmr.solid.deg.corr$variable, levels= c("Ortho", "Pyro", "Mono", "Di"))

ggplot(data, aes(fill=variable, y=value, x=Burn_Severity)) + 
    geom_bar(position="fill", stat="identity")+theme_classic()+facet_grid(.~Feedstock)+scale_fill_manual(values=c("#346648", "#83aa8b", "#dbb40d", "lightgoldenrod", "lightsalmon3", "brown3", "tomato4"))+ggtitle("P NMR: BSLE Solids")

DFL.raw<-subset(summary.nmr.solid.deg.corr, Feedstock=="Douglas-fir Live" & Burn_Severity=="Raw")
DFL.raw.nmr<-ggplot(DFL.raw, aes(x = "", y = mean, fill = variable)) +
    geom_col(color = "black") +
    coord_polar(theta = "y") + scale_fill_manual(values = c("#346648", "#83aa8b", "#dbb40d", "lightgoldenrod", "lightsalmon3"))+theme_void()+
    theme(legend.key.size = unit(1, 'cm'), #change legend key size
          legend.key.height = unit(1, 'cm'),  legend.title = element_text(size=25),
          legend.key.width = unit(1, 'cm'), #change legend key width
          legend.text = element_text(size=20))+labs(fill="")

pdf(file = "~/PNNL/RC-3, River Corridor SFA - Burn Severity Experiments/Burn Severity Experiment/Data/P_all data streams/R_Code_AGU2022/DFL.raw.nmr.pdf", width = 10, height = 3.5) 
print(DFL.raw.nmr)
dev.off()

DFL.low<-subset(summary.nmr.solid.deg.corr, Feedstock=="Douglas-fir Live" & Burn_Severity=="Low")
DFL.low.nmr<-ggplot(DFL.low, aes(x = "", y = mean, fill = variable)) +
    geom_col(color = "black") +
    coord_polar(theta = "y") + scale_fill_manual(values = c("#346648", "#83aa8b", "#dbb40d", "lightgoldenrod", "lightsalmon3"))+theme_void()+
    theme(legend.key.size = unit(1, 'cm'), #change legend key size
          legend.key.height = unit(1, 'cm'),  legend.title = element_text(size=25),
          legend.key.width = unit(1, 'cm'), #change legend key width
          legend.text = element_text(size=20))+labs(fill="")

pdf(file = "~/PNNL/RC-3, River Corridor SFA - Burn Severity Experiments/Burn Severity Experiment/Data/P_all data streams/R_Code_AGU2022/DFL.low.nmr.pdf", width = 10, height = 3.5) 
print(DFL.low.nmr)
dev.off()

DFL.mod<-subset(summary.nmr.solid.deg.corr, Feedstock=="Douglas-fir Live" & Burn_Severity=="Moderate")
DFL.mod.nmr<-ggplot(DFL.mod, aes(x = "", y = mean, fill = variable)) +
    geom_col(color = "black") +
    coord_polar(theta = "y") + scale_fill_manual(values = c("#346648", "#83aa8b", "#dbb40d", "lightgoldenrod", "lightsalmon3"))+theme_void()+
    theme(legend.key.size = unit(1, 'cm'), #change legend key size
          legend.key.height = unit(1, 'cm'),  legend.title = element_text(size=25),
          legend.key.width = unit(1, 'cm'), #change legend key width
          legend.text = element_text(size=20))+labs(fill="")

pdf(file = "~/PNNL/RC-3, River Corridor SFA - Burn Severity Experiments/Burn Severity Experiment/Data/P_all data streams/R_Code_AGU2022/DFL.mod.nmr.pdf", width = 10, height = 3.5) 
print(DFL.mod.nmr)
dev.off()

DFL.high<-subset(summary.nmr.solid.deg.corr, Feedstock=="Douglas-fir Live" & Burn_Severity=="High")
DFL.high.nmr<-ggplot(DFL.high, aes(x = "", y = mean, fill = variable)) +
    geom_col(color = "black") +
    coord_polar(theta = "y") + scale_fill_manual(values = c("#346648", "#83aa8b", "#dbb40d", "lightgoldenrod", "lightsalmon3"))+theme_void()+
    theme(legend.key.size = unit(1, 'cm'), #change legend key size
          legend.key.height = unit(1, 'cm'),  legend.title = element_text(size=25),
          legend.key.width = unit(1, 'cm'), #change legend key width
          legend.text = element_text(size=20))+labs(fill="")

pdf(file = "~/PNNL/RC-3, River Corridor SFA - Burn Severity Experiments/Burn Severity Experiment/Data/P_all data streams/R_Code_AGU2022/DFL.high.nmr.pdf", width = 10, height = 3.5) 
print(DFL.high.nmr)
dev.off()


DFD.raw<-subset(summary.nmr.solid.deg.corr, Feedstock=="Douglas-fir Litter" & Burn_Severity=="Raw")
DFD.raw.nmr<-ggplot(DFD.raw, aes(x = "", y = mean, fill = variable)) +
    geom_col(color = "black") +
    coord_polar(theta = "y") + scale_fill_manual(values = c("#346648", "#83aa8b", "#dbb40d", "lightgoldenrod", "lightsalmon3"))+theme_void()+
    theme(legend.key.size = unit(1, 'cm'), #change legend key size
          legend.key.height = unit(1, 'cm'),  legend.title = element_text(size=25),
          legend.key.width = unit(1, 'cm'), #change legend key width
          legend.text = element_text(size=20))+labs(fill="")

pdf(file = "~/PNNL/RC-3, River Corridor SFA - Burn Severity Experiments/Burn Severity Experiment/Data/P_all data streams/R_Code_AGU2022/DFD.raw.nmr.pdf", width = 10, height = 3.5) 
print(DFD.raw.nmr)
dev.off()

DFD.low<-subset(summary.nmr.solid.deg.corr, Feedstock=="Douglas-fir Litter" & Burn_Severity=="Low")
DFD.low.nmr<-ggplot(DFD.low, aes(x = "", y = mean, fill = variable)) +
    geom_col(color = "black") +
    coord_polar(theta = "y") + scale_fill_manual(values = c("#346648", "#83aa8b", "#dbb40d", "lightgoldenrod", "lightsalmon3"))+theme_void()+
    theme(legend.key.size = unit(1, 'cm'), #change legend key size
          legend.key.height = unit(1, 'cm'),  legend.title = element_text(size=25),
          legend.key.width = unit(1, 'cm'), #change legend key width
          legend.text = element_text(size=20))+labs(fill="")

pdf(file = "~/PNNL/RC-3, River Corridor SFA - Burn Severity Experiments/Burn Severity Experiment/Data/P_all data streams/R_Code_AGU2022/DFD.low.nmr.pdf", width = 10, height = 3.5) 
print(DFD.low.nmr)
dev.off()

DFD.mod<-subset(summary.nmr.solid.deg.corr, Feedstock=="Douglas-fir Litter" & Burn_Severity=="Moderate")
DFD.mod.nmr<-ggplot(DFD.mod, aes(x = "", y = mean, fill = variable)) +
    geom_col(color = "black") +
    coord_polar(theta = "y") + scale_fill_manual(values = c("#346648", "#83aa8b", "#dbb40d", "lightgoldenrod", "lightsalmon3"))+theme_void()+
    theme(legend.key.size = unit(1, 'cm'), #change legend key size
          legend.key.height = unit(1, 'cm'),  legend.title = element_text(size=25),
          legend.key.width = unit(1, 'cm'), #change legend key width
          legend.text = element_text(size=20))+labs(fill="")

pdf(file = "~/PNNL/RC-3, River Corridor SFA - Burn Severity Experiments/Burn Severity Experiment/Data/P_all data streams/R_Code_AGU2022/DFD.mod.nmr.pdf", width = 10, height = 3.5) 
print(DFD.mod.nmr)
dev.off()

DFD.high<-subset(summary.nmr.solid.deg.corr, Feedstock=="Douglas-fir Litter" & Burn_Severity=="High")
DFD.high.nmr<-ggplot(DFD.high, aes(x = "", y = mean, fill = variable)) +
    geom_col(color = "black") +
    coord_polar(theta = "y") + scale_fill_manual(values = c("#346648", "#83aa8b", "#dbb40d", "lightgoldenrod", "lightsalmon3"))+theme_void()+
    theme(legend.key.size = unit(1, 'cm'), #change legend key size
          legend.key.height = unit(1, 'cm'),  legend.title = element_text(size=25),
          legend.key.width = unit(1, 'cm'), #change legend key width
          legend.text = element_text(size=20))+labs(fill="")

pdf(file = "~/PNNL/RC-3, River Corridor SFA - Burn Severity Experiments/Burn Severity Experiment/Data/P_all data streams/R_Code_AGU2022/DFD.high.nmr.pdf", width = 10, height = 3.5) 
print(DFD.high.nmr)
dev.off()


SB.raw<-subset(summary.nmr.solid.deg.corr, Feedstock=="Big Sagebrush" & Burn_Severity=="Raw")
SB.raw.nmr<-ggplot(SB.raw, aes(x = "", y = mean, fill = variable)) +
    geom_col(color = "black") +
    coord_polar(theta = "y") + scale_fill_manual(values = c("#346648", "#83aa8b", "#dbb40d", "lightgoldenrod", "lightsalmon3"))+theme_void()+
    theme(legend.key.size = unit(1, 'cm'), #change legend key size
          legend.key.height = unit(1, 'cm'),  legend.title = element_text(size=25),
          legend.key.width = unit(1, 'cm'), #change legend key width
          legend.text = element_text(size=20))+labs(fill="")

pdf(file = "~/PNNL/RC-3, River Corridor SFA - Burn Severity Experiments/Burn Severity Experiment/Data/P_all data streams/R_Code_AGU2022/SB.raw.nmr.pdf", width = 10, height = 3.5) 
print(SB.raw.nmr)
dev.off()

SB.low<-subset(summary.nmr.solid.deg.corr, Feedstock=="Big Sagebrush" & Burn_Severity=="Low")
SB.low.nmr<-ggplot(SB.low, aes(x = "", y = mean, fill = variable)) +
    geom_col(color = "black") +
    coord_polar(theta = "y") + scale_fill_manual(values = c("#346648", "#83aa8b", "#dbb40d", "lightgoldenrod", "lightsalmon3"))+theme_void()+
    theme(legend.key.size = unit(1, 'cm'), #change legend key size
          legend.key.height = unit(1, 'cm'),  legend.title = element_text(size=25),
          legend.key.width = unit(1, 'cm'), #change legend key width
          legend.text = element_text(size=20))+labs(fill="")

pdf(file = "~/PNNL/RC-3, River Corridor SFA - Burn Severity Experiments/Burn Severity Experiment/Data/P_all data streams/R_Code_AGU2022/SB.low.nmr.pdf", width = 10, height = 3.5) 
print(SB.low.nmr)
dev.off()

SB.mod<-subset(summary.nmr.solid.deg.corr, Feedstock=="Big Sagebrush" & Burn_Severity=="Moderate")
SB.mod.nmr<-ggplot(SB.mod, aes(x = "", y = mean, fill = variable)) +
    geom_col(color = "black") +
    coord_polar(theta = "y") + scale_fill_manual(values = c("#346648", "#83aa8b", "#dbb40d", "lightgoldenrod", "lightsalmon3"))+theme_void()+
    theme(legend.key.size = unit(1, 'cm'), #change legend key size
          legend.key.height = unit(1, 'cm'),  legend.title = element_text(size=25),
          legend.key.width = unit(1, 'cm'), #change legend key width
          legend.text = element_text(size=20))+labs(fill="")

pdf(file = "~/PNNL/RC-3, River Corridor SFA - Burn Severity Experiments/Burn Severity Experiment/Data/P_all data streams/R_Code_AGU2022/SB.mod.nmr.pdf", width = 10, height = 3.5) 
print(SB.mod.nmr)
dev.off()




```