---
title: "BSLE_P_Code"
author: "Morgan Barnes"
date: "'2023-08-18'r Sys.Date()'"
output:
  pdf_document: default
  html_document: default
---
##This is the code for figures and statistics from Barnes et al. (2024): Burn severity and land cover type control phosphorus concentration, molecular composition, and mobilization
##Contact: Morgan E Barnes morgan.barnes@pnnl.gov
##Make your environemnt

#### Set Up
```{r setup, include=FALSE, dev="CairoPNG"}
rm(list=ls(all=T))
knitr::opts_chunk$set(echo = TRUE)
```



## Load libraries
```{r library}

require(pacman)

pacman::p_load(tidyverse,
              dplyr,plyr,ggplot2,
              lubridate, tidyr, tidyverse,
              scales, cowplot, gridExtra, RColorBrewer,
              wesanderson,readxl,openxlsx, stringr, hablar,
              janitor, stringr, naniar, forstringr, reshape2, 
              emmeans, rstatix, ggpubr, Hmisc, corrplot, ggrepel, 
              stringr, lme4, lmerTest, car, performance, vegan, psych, lavaan, semPlot, semptools, bestNormalize)


```

##### Confirm working directory:
```{r working directory check, echo=FALSE}
getwd()
```

##Load data
The datasets and metadata needed for P BSLE Gradient manuscript are:
1) Chemistry datasets solids and liquids w/ all metadata that can be used directly from data package:
This includes: 
a) Total elemental composition of solids
b) Total elemental composition of leachate particulate and filtered fractions
c) Molybdate reactive P of leachate filtered fraction
d) XANES of solids
e) NMR of solids

2) Chemistry data that needs post-data package processing after download from BSLE Data Package v3; this was done and provided within the BSLE P Manuscript Data Package:
a) XANES of solids (spectra of samples and reference compounds and linear combination fits)
b) NMR of solids (deconvolution)


#### Download the BSLE Data Package

Until we can get the API to work, do this manually and store on your local. I recommend storing inside your github folder and gitignoring the subfolder with the data in it by adding this to your .gitignore: 
`#data folder` 
`data/`

BSLE v3 data package URL: https://data.ess-dive.lbl.gov/view/doi:10.15485/1894135
BSLE P manuscript data package URL: INSERT HERE!!! fix

Bring in the data package data:
```{r bsle v3 data package}
#metadata
Meta <- read_csv("../data/BSLE_Data_Package_v3/v1_BSLE_Metadata_and_Protocols/BSLE_Burn_and_Laboratory_Metadata.csv") %>%
  dplyr::rename(Sample_ID = Sample_Name,
                Leachate_vol_mL = Leachate_Volume,
                Char_leached_g = Char_Leached) %>%
  naniar::replace_with_na_all(condition = ~.x ==-9999) %>%
  naniar::replace_with_na_all(condition = ~.x == "N/A") %>%
  mutate(Burn_Severity=replace(Burn_Severity, Burn_Severity=='unburned', 'Unburned'))

Meta<-Meta[ c(2,3,5,8,21,25,26,6,20,22,23)]
Meta$Burn_Severity=factor(Meta$Burn_Severity, levels= c("Unburned", "Low", "Moderate", "High"))

#chemical data from BSLE v3 data package
ICP_Solid <- read_csv("../data/BSLE_Data_Package_v3/v3_BSLE_Data/BSLE_ICP_Solid.csv")
ICP_Leachate <- read_csv("../data/BSLE_Data_Package_v3/v3_BSLE_Data/BSLE_ICP.csv")
MBD <- read_csv("../data/BSLE_Data_Package_v3/v3_BSLE_Data/BSLE_MBD.csv")
ICP_PNMR <- read_csv("../data/BSLE_Data_Package_v3/v3_BSLE_Data/BSLE_ICP_PNMR.csv")
npoctdn <- read_csv("../data/BSLE_Data_Package_v3/v3_BSLE_Data/v2_BSLE_NPOC_TN.csv")
SolidCN <- read_csv("../data/BSLE_Data_Package_v3/v3_BSLE_Data/BSLE_CN.csv")
pH <- read_csv("../data/BSLE_Data_Package_v3/v3_BSLE_Data/BSLE_pH.csv")
NMR_spectra <- read_csv("../data/BSLE_Data_Package_v3/v3_BSLE_Data/BSLE_31P-NMR.csv")

#chemical data from BSLE P manuscript data package
NMR <- read.csv("../data/Barnes_2023_BSLE_P_Gradient_Manuscript_Data_Package/NMR_Deconvolutions.csv") %>%
  filter(Degradation_Corrected == 'Yes')
XANES <- read.csv("../data/Barnes_2023_BSLE_P_Gradient_Manuscript_Data_Package/P_XANES_Samples/P-XANES_LCF.csv")  
XANES_spectra <- read_csv("../data/Barnes_2023_BSLE_P_Gradient_Manuscript_Data_Package/P_XANES_Samples/xanes_example_spectra.csv") #this file was generated using XANES_Spectra_Merging script 
XANES_rc_spectra <- read_csv("../data/Barnes_2023_BSLE_P_Gradient_Manuscript_Data_Package/P_XANES_Reference_Compounds/xanes_example_referencecompounds.csv") #this file was generated using XANES_Spectra_Merging script 
BSLE_0013_solid_LCF <- read.table("../data/Barnes_2023_BSLE_P_Gradient_Manuscript_Data_Package/P_XANES_Samples/LCF/BSLE_0013-solid_P-XANES.xmu.lcf", quote="\"", col.names = c("eV", "BSLE_0013_solid", "fit", "residual", "Po_Na_AMP_std.xmu", "Pi_Fe_GoethSorb_std.xmu"))
BSLE_0007_solid_LCF <- read.table("../data/Barnes_2023_BSLE_P_Gradient_Manuscript_Data_Package/P_XANES_Samples/LCF/BSLE_0007-solid_P-XANES.xmu.lcf", quote="\"", col.names = c("eV", "BSLE_0007_solid", "fit", "residual", "Pi_Na_Tri_std.xmu", "Pi_Apatite_CaDefHydroxy_std.xmu", "Pi_Al_GibbSorb_std.xmu"))
BSLE_0002_solid_LCF <- read.table("../data/Barnes_2023_BSLE_P_Gradient_Manuscript_Data_Package/P_XANES_Samples/LCF/BSLE_0002-solid_P-XANES.xmu.lcf", quote="\"", col.names = c("eV", "BSLE_0002_solid", "fit", "residual", "Pi_Na_Tri_std.xmu", "Pi_Mg_Tri_std.xmu", "Pi_Apatite_CaDefHydroxy_std.xmu"))
BSLE_0050_solid_LCF <- read.table("../data/Barnes_2023_BSLE_P_Gradient_Manuscript_Data_Package/P_XANES_Samples/LCF/BSLE_0050-solid_P-XANES.xmu.lcf", quote="\"", col.names = c("eV", "BSLE_0050_solid", "fit", "residual", "Pi_Mg_Tri_std.xmu", "Pi_Ca_Tri_std.xmu", "Pi_Apatite_CaDefHydroxy_std.xmu"))
BSLE_0014_solid_LCF <- read.table("../data/Barnes_2023_BSLE_P_Gradient_Manuscript_Data_Package/P_XANES_Samples/LCF/BSLE_0014-solid_P-XANES.xmu.lcf", quote="\"", col.names = c("eV", "BSLE_0014_solid", "fit", "residual", "Po_Na_AMP_std.xmu", "Pi_Fe_GoethSorb_std.xmu", "Pi_Apatite_CaDefHydroxy_std.xmu"))
BSLE_0011_solid_LCF <- read.table("../data/Barnes_2023_BSLE_P_Gradient_Manuscript_Data_Package/P_XANES_Samples/LCF/BSLE_0011-solid_P-XANES.xmu.lcf", quote="\"", col.names = c("eV", "BSLE_0011_solid", "fit", "residual", "Pi_Mg_Tri_std.xmu", "Pi_K_Pyro_std.xmu", "Pi_Apatite_CaDefHydroxy_std.xmu"))
BSLE_0072_solid_LCF <- read.table("../data/Barnes_2023_BSLE_P_Gradient_Manuscript_Data_Package/P_XANES_Samples/LCF/BSLE_0072-solid_P-XANES.xmu.lcf", quote="\"", col.names = c("eV", "BSLE_0072_solid", "fit", "residual", "Pi_NH4_Mg_std.xmu", "Pi_Apatite_Carbonate_std.xmu", "Pi_Apatite_CaDefHydroxy_std.xmu"))
```

Clean up data functions:
```{r functions for cleaning}
essdive_template_cleaning <- function(dataframe){
  cleaned <- dataframe %>% 
  janitor::row_to_names(row_number = which(dataframe[,1] == "Field_Name")) %>% #this assumes that this name is somewhere in column #1. That follows some (most?) ESS-DIVE templates.
 slice(which(Field_Name == "#Start_Data"):which(Field_Name == "#End_Data")) %>%
 select(!Field_Name)
  }

noreporting_format_cleaning <- function(dataframe){
  cleaned <- dataframe %>% 
  janitor::row_to_names(row_number = which(dataframe[,1] == "Date")) #this assumes that this name is somewhere in column #1. This works for the thermocouple datasets
  }
```

```{r bsle v3 data package cleaning}
pH_clean <- essdive_template_cleaning(pH)  %>%
  dplyr::rename(Sample_ID = Sample_Name,
                pH = '00403_pH') %>%
   mutate_at(c(3), as.numeric) %>%
  separate(col=Sample_ID, into = c("Sample_ID", "FilterSize"), sep="-")  %>%
  filter(grepl('unfilt', FilterSize)) %>%
  select(Sample_ID, pH)

#wrote modifies so -9999 is NA, below LOD is NA, and if above or below standard curve then I pull out those values
npoctdn_clean <- essdive_template_cleaning(npoctdn) %>%
  dplyr::rename(NPOC_mg_C_per_L = `00681_NPOC_mg_per_L_as_C`,
         TN_mg_N_per_L = `00602_TN_mg_per_L_as_N`,
         Sample_ID = Sample_Name) %>%
  select(Sample_ID, NPOC_mg_C_per_L, TN_mg_N_per_L) %>%
  filter(grepl('filt0.7', Sample_ID)) %>%
  mutate(Sample_ID = stringr::str_remove(Sample_ID ,"-filt0.2"),
         NPOC_mg_C_per_L = case_when(NPOC_mg_C_per_L == -9999 ~ NA,
                              str_detect(NPOC_mg_C_per_L, "LOD") ~ NA,
                              str_detect(NPOC_mg_C_per_L, "Below_0.1_ppm") ~
                                      str_extract_part(NPOC_mg_C_per_L, "_ppm_Below_0.1_ppm", before = TRUE),
                               TRUE ~ NPOC_mg_C_per_L),
         TN_mg_N_per_L = case_when(TN_mg_N_per_L == -9999 ~ NA,
                              str_detect(TN_mg_N_per_L, "LOD") ~ NA,
                              str_detect(TN_mg_N_per_L, "Below_0.1_ppm") ~ 
                                        str_extract_part(TN_mg_N_per_L, "_ppm_Below_0.1_ppm", before = TRUE),
                               TRUE ~ TN_mg_N_per_L)) %>%
  mutate(NPOC_mg_C_per_L = case_when(str_detect(NPOC_mg_C_per_L, "NPOC_") ~ 
                                     str_extract(NPOC_mg_C_per_L, "(\\d+\\.\\d+)"),
                                     NPOC_mg_C_per_L < 0 ~ NA,
                                     TRUE ~ NPOC_mg_C_per_L),
         TN_mg_N_per_L = case_when(str_detect(TN_mg_N_per_L, "TN_") ~ 
                                     str_extract(TN_mg_N_per_L, "(\\d+\\.\\d+)"),
                                     TN_mg_N_per_L < 0 ~ NA, 
                                     TRUE ~ TN_mg_N_per_L)) %>%
  mutate(NPOC_mg_C_per_L = as.numeric(NPOC_mg_C_per_L),
         TN_mg_N_per_L = as.numeric(TN_mg_N_per_L)) %>%
  separate(col=Sample_ID, into = c("Sample_ID", "FilterSize"), sep="-") 

SolidCN_clean <- essdive_template_cleaning(SolidCN) %>%
  dplyr::rename(C_weight_per = `01463_C_percent`,
         N_weight_per = `01472_N_percent`,
         Parent_ID = Sample_Name) %>%
  select(Parent_ID, C_weight_per,  N_weight_per) %>%
  filter(grepl('solid', Parent_ID)) %>%
  mutate(Parent_ID = stringr::str_remove(Parent_ID ,"-solid"),
         C_weight_per = case_when(C_weight_per == -9999 ~ NA,
                                  str_detect(C_weight_per, "LOD") ~ NA,
                                     TRUE ~ C_weight_per),
         N_weight_per = case_when(N_weight_per == -9999 ~ NA,
                                   str_detect(N_weight_per, "LOD") ~ NA,
                                   TRUE ~ N_weight_per)) %>%
   mutate(C_weight_per = as.numeric(C_weight_per),
         N_weight_per = as.numeric(N_weight_per))

#negative values were replaced with NA, below LOD were replaced with NA, and above/below standard curve were replaced with the value
ICP_Solid_clean<- essdive_template_cleaning(ICP_Solid) %>%
  dplyr::rename(Solid_Ca_mg_kg = '52718_Total_Ca_mg_per_kg',
                Solid_Mg_mg_kg = '52719_Total_Mg_mg_per_kg',
                Solid_P_mg_kg = 'Total_P_mg_per_kg',
                Solid_K_mg_kg = '52720_Total_K_mg_per_kg',
                Solid_Na_mg_kg = '52721_Total_Na_mg_per_kg',
                Solid_S_mg_kg = '01466_Total_S_mg_per_kg',
                Solid_Al_mg_kg = '01462_Total_Al_mg_per_kg',
                Solid_Fe_mg_kg = '01464_Total_Fe_mg_per_kg',
                Parent_ID = 'Sample_Name') %>%
  mutate(Solid_Na_mg_kg = case_when(
                Solid_Na_mg_kg == -9999 ~ NA,
                str_detect(Solid_Na_mg_kg, "Negative_Value") ~ NA, 
                str_detect(Solid_Na_mg_kg, "Below_213.43_LOD") ~ NA, 
                str_detect(Solid_Na_mg_kg, "TotNa_Below") ~ 
                str_extract(Solid_Na_mg_kg, "\\d+\\.?\\d*(?=_ppm_Final_Corrected)"),
                str_detect(Solid_Na_mg_kg, "TotNa_Above") ~ 
                str_extract(Solid_Na_mg_kg, "\\d+\\.?\\d*(?=_ppm_Final_Corrected)"),
                TRUE ~ Solid_Na_mg_kg)) %>%
   mutate_at(c(4:11), as.numeric) %>%
  separate(col=Parent_ID, into = c("Parent_ID", "FilterSize"), sep="-")  %>%
  filter(grepl('solid', FilterSize)) %>%
  select(Parent_ID, Solid_Ca_mg_kg,  Solid_Mg_mg_kg, Solid_P_mg_kg, Solid_K_mg_kg, Solid_Na_mg_kg, Solid_S_mg_kg, Solid_Al_mg_kg, Solid_Fe_mg_kg)


#negative values were replaced with NA, below LOD were replaced with NA, and above/below standard curve were replaced with the value
ICP_Leachate_clean <- essdive_template_cleaning(ICP_Leachate) %>%
  dplyr::rename(Leachate_Ca_mg_L = 'Total_Ca_mg_per_L',
                Leachate_Mg_mg_L = 'Total_Mg_mg_per_L',
                Leachate_P_mg_L = 'Total_P_mg_per_L',
                Leachate_K_mg_L = 'Total_K_mg_per_L',
                Leachate_Na_mg_L = 'Total_Na_mg_per_L',
                Leachate_S_mg_L = 'Total_S_mg_per_L',
                Leachate_Al_mg_L = 'Total_Al_mg_per_L',
                Leachate_Fe_mg_L = 'Total_Fe_mg_per_L',
                Sample_ID = 'Sample_Name') %>%
  mutate(Leachate_Na_mg_L = case_when(
                Leachate_Na_mg_L == -9999 ~ NA,
                str_detect(Leachate_Na_mg_L, "Negative") ~ NA, 
                str_detect(Leachate_Na_mg_L, "LOD") ~ NA, 
                str_detect(Leachate_Na_mg_L, "TotNa_Below") ~ 
                str_extract(Leachate_Na_mg_L, "\\d+\\.?\\d*(?=_ppm_Final_Corrected)"),
                str_detect(Leachate_Na_mg_L, "TotNa_Above") ~ 
                str_extract(Leachate_Na_mg_L, "\\d+\\.?\\d*(?=_ppm_Final_Corrected)"),
                TRUE ~ Leachate_Na_mg_L)) %>%
  mutate(Leachate_Al_mg_L = case_when(
                Leachate_Na_mg_L == -9999 ~ NA,
                str_detect(Leachate_Al_mg_L, "Negative") ~ NA, 
                str_detect(Leachate_Al_mg_L, "LOD") ~ NA, 
                str_detect(Leachate_Al_mg_L, "TotAl_Below") ~ 
                str_extract(Leachate_Al_mg_L, "\\d+\\.?\\d*(?=_ppm_Final_Corrected)"),
                str_detect(Leachate_Al_mg_L, "TotAl_Above") ~ 
                str_extract(Leachate_Al_mg_L, "\\d+\\.?\\d*(?=_ppm_Final_Corrected)"),
                TRUE ~ Leachate_Al_mg_L)) %>%
  mutate(Leachate_Fe_mg_L = case_when(
                Leachate_Fe_mg_L == -9999 ~ NA,
                str_detect(Leachate_Fe_mg_L, "Negative") ~ NA, 
                str_detect(Leachate_Fe_mg_L, "LOD") ~ NA, 
                str_detect(Leachate_Fe_mg_L, "TotAl_Below") ~ 
                str_extract(Leachate_Fe_mg_L, "\\d+\\.?\\d*(?=_ppm_Final_Corrected)"),
                str_detect(Leachate_Fe_mg_L, "TotAl_Above") ~ 
                str_extract(Leachate_Fe_mg_L, "\\d+\\.?\\d*(?=_ppm_Final_Corrected)"),
                TRUE ~ Leachate_Fe_mg_L))  %>%
  mutate_at(c(3:10), as.numeric) %>%
  select(Sample_ID, Leachate_Ca_mg_L,  Leachate_Mg_mg_L, Leachate_P_mg_L, Leachate_K_mg_L, Leachate_Na_mg_L, Leachate_S_mg_L, Leachate_Al_mg_L, Leachate_Fe_mg_L) %>%
  filter(grepl('filt', Sample_ID)) %>%
  separate(col=Sample_ID, into = c("Sample_ID", "FilterSize"), sep="-") 

ICP_Leachate_Filt_clean<- ICP_Leachate_clean %>%
                filter(str_detect(FilterSize, "filt0.")) %>%
  dplyr::rename(Leachate_Ca_mg_L_filt0.7 = 'Leachate_Ca_mg_L',
                Leachate_Mg_mg_L_filt0.7 = 'Leachate_Mg_mg_L',
                Leachate_P_mg_L_filt0.7 = 'Leachate_P_mg_L',
                Leachate_K_mg_L_filt0.7 = 'Leachate_K_mg_L',
                Leachate_Na_mg_L_filt0.7 = 'Leachate_Na_mg_L',
                Leachate_S_mg_L_filt0.7 = 'Leachate_S_mg_L',
                Leachate_Al_mg_L_filt0.7 = 'Leachate_Al_mg_L',
                Leachate_Fe_mg_L_filt0.7 = 'Leachate_Fe_mg_L') %>%
  select(Sample_ID, Leachate_Ca_mg_L_filt0.7,  Leachate_Mg_mg_L_filt0.7, Leachate_P_mg_L_filt0.7, Leachate_K_mg_L_filt0.7, Leachate_Na_mg_L_filt0.7, Leachate_S_mg_L_filt0.7, Leachate_Al_mg_L_filt0.7, Leachate_Fe_mg_L_filt0.7)

ICP_Leachate_Unfilt_clean<- ICP_Leachate_clean %>%
                filter(str_detect(FilterSize, "unfilt")) %>%
  dplyr::rename(Leachate_Ca_mg_L_unfilt = 'Leachate_Ca_mg_L',
                Leachate_Mg_mg_L_unfilt = 'Leachate_Mg_mg_L',
                Leachate_P_mg_L_unfilt = 'Leachate_P_mg_L',
                Leachate_K_mg_L_unfilt = 'Leachate_K_mg_L',
                Leachate_Na_mg_L_unfilt = 'Leachate_Na_mg_L',
                Leachate_S_mg_L_unfilt = 'Leachate_S_mg_L',
                Leachate_Al_mg_L_unfilt = 'Leachate_Al_mg_L',
                Leachate_Fe_mg_L_unfilt = 'Leachate_Fe_mg_L') %>%
  select(Sample_ID, Leachate_Ca_mg_L_unfilt,  Leachate_Mg_mg_L_unfilt, Leachate_P_mg_L_unfilt, Leachate_K_mg_L_unfilt, Leachate_Na_mg_L_unfilt, Leachate_S_mg_L_unfilt, Leachate_Al_mg_L_unfilt, Leachate_Fe_mg_L_unfilt)


#negative values were replaced with zero, below LOD were replaced with NA, and above/below standard curve were replaced with the value (value is corrected for dilution and subtracted by unreactive P to correct for color interference)
#only used concentrations above the high standard if within 15% of it
MBD_Leachate_clean <- essdive_template_cleaning(MBD) %>%
  dplyr::rename(Sample_ID = 'Sample_Name',
                MBD_P_mg_per_L_filt0.7 = 'MBD_P_mg_per_L') %>%
  mutate(MBD_P_mg_per_L_filt0.7 = case_when(
                MBD_P_mg_per_L_filt0.7 == -9999 ~ NA,
                str_detect(MBD_P_mg_per_L_filt0.7, "negative") ~ NA, 
                str_detect(MBD_P_mg_per_L_filt0.7, "LOD") ~ NA, 
                str_detect(Sample_ID, "50A") ~ NA, #hihger than 15% of high standard
                str_detect(MBD_P_mg_per_L_filt0.7, "MBD_Below") ~ 
                str_extract(MBD_P_mg_per_L_filt0.7, "\\d+\\.?\\d*(?=_ppm_Final_Corrected)"),
                str_detect(MBD_P_mg_per_L_filt0.7, "MBD_Above") ~ 
                str_extract(MBD_P_mg_per_L_filt0.7, "\\d+\\.?\\d*(?=_ppm_Final_Corrected)"),
                TRUE ~ MBD_P_mg_per_L_filt0.7)) %>%
  mutate_at(c(2), as.numeric) %>%
  filter(grepl('filt', Sample_ID)) %>%
  separate(col=Sample_ID, into = c("Sample_ID", "FilterSize"), sep="-") %>%
  select(Sample_ID, MBD_P_mg_per_L_filt0.7) %>%
  mutate_at(c(2), as.numeric) %>%
  filter(Sample_ID != "BSLE_0073C") #remove 73C because below limit of quantification

ICP_PNMR_clean <- essdive_template_cleaning(ICP_PNMR) %>%
  dplyr::rename(Parent_ID = 'Sample_Name') %>%
  mutate_at(c(2:8), as.numeric) %>%
  filter(grepl('solid', Parent_ID)) %>%
  separate(col=Parent_ID, into = c("Parent_ID", "FilterSize"), sep="-") %>%
  select(Parent_ID, Total_Extractable_Ca_mg_per_kg,  Total_Extractable_Mg_mg_per_kg, Total_Extractable_P_mg_per_kg, Total_Extractable_K_mg_per_kg,  Total_Extractable_S_mg_per_kg, Total_Extractable_Al_mg_per_kg, Total_Extractable_Fe_mg_per_kg) %>%
  mutate_at(c(2:8), as.numeric) 

XANES_clean <- XANES %>%
  select(-where(~all(is.na(.)))) %>%
  mutate(XANES_Po = rowSums(select(., contains("Po")), na.rm = TRUE)) %>%
  mutate(XANES_Pi = rowSums(select(., contains("Pi")), na.rm = TRUE)) %>%
  mutate(XANES_Fe = rowSums(select(., contains("Fe")), na.rm = TRUE)) %>%
  mutate(XANES_Na = rowSums(select(., contains("Pi_Na") | contains("Po_Na")), na.rm = TRUE)) %>%
  mutate(XANES_Ca = rowSums(select(., contains("Ca") | contains("Apatite")), na.rm = TRUE)) %>%
  mutate(XANES_Al = rowSums(select(., contains("Al")), na.rm = TRUE)) %>%
  mutate(XANES_Mg = rowSums(select(., contains("Mg") | contains("NH4_Mg")), na.rm = TRUE)) %>%
  mutate(XANES_K = rowSums(select(., contains("K")), na.rm = TRUE)) %>%
  mutate(XANES_Pi_Fe = rowSums(select(., contains("Pi_Fe")), na.rm = TRUE)) %>%
  mutate(XANES_Pi_Na = rowSums(select(., contains("Pi_Na")), na.rm = TRUE)) %>%
  mutate(XANES_Pi_Ca = rowSums(select(., contains("Pi_Ca") | contains("Apatite")), na.rm = TRUE)) %>%
  mutate(XANES_Pi_Al = rowSums(select(., contains("Pi_Al")), na.rm = TRUE)) %>%
  mutate(XANES_Pi_Mg = rowSums(select(., contains("Pi_Mg") | contains("NH4_Mg")), na.rm = TRUE)) %>%
  mutate(XANES_Pi_K = rowSums(select(., contains("Pi_K")), na.rm = TRUE)) %>%
  mutate(XANES_Po_Fe = rowSums(select(., contains("Po_Fe")), na.rm = TRUE)) %>%
  mutate(XANES_Po_Na = rowSums(select(., contains("Po_Na")), na.rm = TRUE)) %>%
  mutate(XANES_Po_Ca = rowSums(select(., contains("Po_Ca")), na.rm = TRUE)) %>%
  mutate(XANES_Po_Al = rowSums(select(., contains("Po_Al")), na.rm = TRUE)) %>%
  mutate(XANES_Po_Mg = rowSums(select(., contains("Po_Mg")), na.rm = TRUE)) %>%
  mutate(XANES_Po_K = rowSums(select(., contains("Po_K")), na.rm = TRUE)) %>%
  separate(col=Sample_Name, into = c("Parent_ID", "FilterSize"), sep="-") %>%
  filter(str_detect(FilterSize, "solid"))

NMR_clean <- NMR %>%
  separate(col=Sample_Name, into = c("Parent_ID", "FilterSize"), sep="-") 

XANES_rc_spectra <- XANES_rc_spectra %>%
  mutate_all(~ifelse(. == -9999, NA, .))
  
```


```{r combine and format data}
data <- Meta %>%
  full_join(SolidCN_clean, by = 'Parent_ID') %>%
  full_join(ICP_Solid_clean, by = 'Parent_ID') %>%
  full_join(ICP_PNMR_clean, by = 'Parent_ID') %>%
  full_join(npoctdn_clean, by = 'Sample_ID') %>%
  full_join(ICP_Leachate_Filt_clean, by = 'Sample_ID') %>%
  full_join(ICP_Leachate_Unfilt_clean, by = 'Sample_ID') %>%
  full_join(MBD_Leachate_clean, by = 'Sample_ID') %>%
  full_join(pH_clean, by = 'Sample_ID') %>%
  mutate_at(c(10:48), as.numeric) %>%
  filter(!is.na(Solid_P_mg_kg))

data$Burn_Severity=factor(data$Burn_Severity, levels= c("Unburned", "Low", "Moderate", "High"))

#create a dataframe for only solids figures and stats to prevent having reps count as extra samples; add NMR and XANES data
data_solids <- data %>%
  filter(str_detect(Sample_ID, "A")) %>%
  select(1:28) %>%
  left_join(NMR_clean) %>%
  left_join(XANES_clean)

data_solids$Burn_Severity=factor(data_solids$Burn_Severity, levels= c("Unburned", "Low", "Moderate", "High"))

#keep XANES separate too
XANES_clean<- Meta %>%
  full_join(XANES_clean, by = 'Parent_ID') %>%
  filter(str_detect(Sample_ID, "A")) %>%
  mutate(Burn_Treatment = as.character(Burn_Treatment)) %>%
  filter(Burn_Treatment %in% c("burn table" , "raw")) %>%
  filter(Land_Coverage_Category %in% c("Douglas-fir forest" , "Sagebrush shrubland")) %>%
  filter(!is.na(FilterSize))

data<-data %>%
  mutate(Land_Coverage_Category = if_else(Land_Coverage_Category == "Douglas-fir forest", "Douglas-fir Forest", Land_Coverage_Category)) %>%
  mutate(Land_Coverage_Category = if_else(Land_Coverage_Category == "Sagebrush shrubland", "Sagebrush Shrubland", Land_Coverage_Category))

data_solids <-data_solids %>%
  mutate(Land_Coverage_Category = if_else(Land_Coverage_Category == "Douglas-fir forest", "Douglas-fir Forest", Land_Coverage_Category)) %>%
  mutate(Land_Coverage_Category = if_else(Land_Coverage_Category == "Sagebrush shrubland", "Sagebrush Shrubland", Land_Coverage_Category))
```

####Additional Calcs
```{r data_solids}
#NMR extraction efficiency
data_solids<-data_solids %>%
  mutate(NMR_EE_P_perc=Total_Extractable_P_mg_per_kg/Solid_P_mg_kg*100)

#calculate monoester:diester ratio
data_solids<-data_solids %>%
  mutate(M_D_ratio=Mono/Di)

#percent change based on average percent monoester and diester in the unburned
data_solids <- data_solids %>%
  mutate(mono_per_change = case_when(
    Land_Coverage_Category == "Sagebrush shrubland" ~ ((Mono - 27)/27)*100,
    Land_Coverage_Category == "Douglas-fir forest" ~ ((Mono - 3.2)/3.2)*100))

data_solids <- data_solids %>%
  mutate(di_per_change = case_when(
    Land_Coverage_Category == "Sagebrush shrubland" ~ ((Di - 26.9)/26.9)*100,
    Land_Coverage_Category == "Douglas-fir forest" ~ ((Di - 38.3)/38.3)*100))

#convert C and N of solids from percent to mg/kg in data_solids dataframe
data_solids<-data_solids %>%
  mutate(Solid_C_mg_kg = (C_weight_per*10000),
  Solid_N_mg_kg = (N_weight_per*10000))

#convert solid elemental concentrations from mg/kg to g/kg in data_solids dataframe
data_solids<-data_solids %>%
  mutate(Solid_P_g_kg = Solid_P_mg_kg/1000) %>%
  mutate(Solid_Ca_g_kg = Solid_Ca_mg_kg/1000) %>%
  mutate(Solid_Fe_g_kg = Solid_Fe_mg_kg/1000) %>%
  mutate(Solid_Al_g_kg = Solid_Al_mg_kg/1000) %>%
  mutate(Solid_K_g_kg = Solid_K_mg_kg/1000) %>%
  mutate(Solid_Mg_g_kg = Solid_Mg_mg_kg/1000) %>%
  mutate(Solid_Na_g_kg = Solid_Na_mg_kg/1000) %>%
  mutate(Solid_S_g_kg = Solid_S_mg_kg/1000) %>%
  mutate(Solid_C_g_kg = Solid_C_mg_kg/1000) %>%
  mutate(Solid_N_g_kg = Solid_N_mg_kg/1000)

#molar stoichiometry of P:element in solid phase
data_solids<-data_solids %>%
  mutate(Fe.P.MolarRatio=(Solid_Fe_mg_kg/55.845)/(Solid_P_mg_kg/30.97))%>%
  mutate(K.P.MolarRatio=(Solid_K_mg_kg/39.0983)/(Solid_P_mg_kg/30.97))%>%
  mutate(Na.P.MolarRatio=(Solid_Na_mg_kg/22.989)/(Solid_P_mg_kg/30.97))%>%
  mutate(Al.P.MolarRatio=(Solid_Al_mg_kg/26.982)/(Solid_P_mg_kg/30.97))%>%
  mutate(Mg.P.MolarRatio=(Solid_Mg_mg_kg/24.305)/(Solid_P_mg_kg/30.97))%>%
  mutate(Ca.P.MolarRatio=(Solid_Ca_mg_kg/40.078)/(Solid_P_mg_kg/30.97))%>%
  mutate(S.P.MolarRatio=(Solid_S_mg_kg/32.065)/(Solid_P_mg_kg/30.97))%>%
  mutate(C.P.MolarRatio=(Solid_C_mg_kg/12.011)/(Solid_P_mg_kg/30.97))%>%
  mutate(N.P.MolarRatio=(Solid_N_mg_kg/14.01)/(Solid_P_mg_kg/30.97))

#NMR Pi and Po
data_solids<-data_solids %>%
  mutate(NMR_Pi = Ortho+Pyro) %>%
  mutate(NMR_Po = Mono + Di)

```

```{r data}
#calculate leachate particulate concentrations as the difference between filtered and unfiltered
data<-data %>%
  mutate(Leachate_Ca_mg_L_part = Leachate_Ca_mg_L_unfilt - Leachate_Ca_mg_L_filt0.7) %>%
  mutate(Leachate_Ca_mg_L_part = if_else(Leachate_Ca_mg_L_part < 0, NA, Leachate_Ca_mg_L_part))%>%
  mutate(Leachate_Mg_mg_L_part = Leachate_Mg_mg_L_unfilt - Leachate_Mg_mg_L_filt0.7) %>%
  mutate(Leachate_Mg_mg_L_part = if_else(Leachate_Mg_mg_L_part < 0, NA, Leachate_Mg_mg_L_part))%>%
  mutate(Leachate_P_mg_L_part = Leachate_P_mg_L_unfilt - Leachate_P_mg_L_filt0.7) %>%
  mutate(Leachate_P_mg_L_part = if_else(Leachate_P_mg_L_part < 0, NA, Leachate_P_mg_L_part))%>%
  mutate(Leachate_K_mg_L_part = Leachate_K_mg_L_unfilt - Leachate_K_mg_L_filt0.7) %>%
  mutate(Leachate_K_mg_L_part = if_else(Leachate_K_mg_L_part < 0, NA, Leachate_K_mg_L_part))%>%
  mutate(Leachate_Na_mg_L_part = Leachate_Na_mg_L_unfilt - Leachate_Na_mg_L_filt0.7) %>%
  mutate(Leachate_Na_mg_L_part = if_else(Leachate_Na_mg_L_part < 0, NA, Leachate_Na_mg_L_part))%>%
  mutate(Leachate_S_mg_L_part = Leachate_S_mg_L_unfilt - Leachate_S_mg_L_filt0.7) %>%
  mutate(Leachate_S_mg_L_part = if_else(Leachate_S_mg_L_part < 0, NA, Leachate_S_mg_L_part))%>%
  mutate(Leachate_Al_mg_L_part = Leachate_Al_mg_L_unfilt - Leachate_Al_mg_L_filt0.7) %>%
  mutate(Leachate_Al_mg_L_part = if_else(Leachate_Al_mg_L_part < 0, NA, Leachate_Al_mg_L_part))%>%
  mutate(Leachate_Fe_mg_L_part = Leachate_Fe_mg_L_unfilt - Leachate_Fe_mg_L_filt0.7) %>%
  mutate(Leachate_Fe_mg_L_part = if_else(Leachate_Fe_mg_L_part < 0, NA, Leachate_Fe_mg_L_part))
  
#convert units of leachates: normalize to mass of char
data<-data %>%
  mutate(Leachate_Ca_mg_kgchar_unfilt = Leachate_Ca_mg_L_unfilt*Leachate_vol_mL/Char_leached_g*1000/1000) %>%
  mutate(Leachate_Mg_mg_kgchar_unfilt  = Leachate_Mg_mg_L_unfilt*Leachate_vol_mL/Char_leached_g*1000/1000) %>%
  mutate(Leachate_P_mg_kgchar_unfilt = Leachate_P_mg_L_unfilt*Leachate_vol_mL/Char_leached_g*1000/1000) %>%
  mutate(Leachate_K_mg_kgchar_unfilt  = Leachate_K_mg_L_unfilt*Leachate_vol_mL/Char_leached_g*1000/1000) %>%
  mutate(Leachate_Na_mg_kgchar_unfilt  = Leachate_Na_mg_L_unfilt*Leachate_vol_mL/Char_leached_g*1000/1000) %>%
  mutate(Leachate_S_mg_kgchar_unfilt  = Leachate_S_mg_L_unfilt*Leachate_vol_mL/Char_leached_g*1000/1000) %>%
  mutate(Leachate_Al_mg_kgchar_unfilt  = Leachate_Al_mg_L_unfilt*Leachate_vol_mL/Char_leached_g*1000/1000) %>%
  mutate(Leachate_Fe_mg_kgchar_unfilt = Leachate_Fe_mg_L_unfilt*Leachate_vol_mL/Char_leached_g*1000/1000) %>%
  mutate(Leachate_Ca_mg_kgchar_part = Leachate_Ca_mg_L_part*Leachate_vol_mL/Char_leached_g*1000/1000) %>%
  mutate(Leachate_Mg_mg_kgchar_part  = Leachate_Mg_mg_L_part*Leachate_vol_mL/Char_leached_g*1000/1000) %>%
  mutate(Leachate_P_mg_kgchar_part  = Leachate_P_mg_L_part*Leachate_vol_mL/Char_leached_g*1000/1000) %>%
  mutate(Leachate_K_mg_kgchar_part  = Leachate_K_mg_L_part*Leachate_vol_mL/Char_leached_g*1000/1000) %>%
  mutate(Leachate_Na_mg_kgchar_part  = Leachate_Na_mg_L_part*Leachate_vol_mL/Char_leached_g*1000/1000) %>%
  mutate(Leachate_S_mg_kgchar_part  = Leachate_S_mg_L_part*Leachate_vol_mL/Char_leached_g*1000/1000) %>%
  mutate(Leachate_Al_mg_kgchar_part  = Leachate_Al_mg_L_part*Leachate_vol_mL/Char_leached_g*1000/1000) %>%
  mutate(Leachate_Fe_mg_kgchar_part  = Leachate_Fe_mg_L_part*Leachate_vol_mL/Char_leached_g*1000/1000) %>%
  mutate(Leachate_Ca_mg_kgchar_filt0.7 = Leachate_Ca_mg_L_filt0.7*Leachate_vol_mL/Char_leached_g*1000/1000) %>%
  mutate(Leachate_Mg_mg_kgchar_filt0.7 = Leachate_Mg_mg_L_filt0.7*Leachate_vol_mL/Char_leached_g*1000/1000) %>%
  mutate(Leachate_P_mg_kgchar_filt0.7 = Leachate_P_mg_L_filt0.7*Leachate_vol_mL/Char_leached_g*1000/1000) %>%
  mutate(Leachate_K_mg_kgchar_filt0.7 = Leachate_K_mg_L_filt0.7*Leachate_vol_mL/Char_leached_g*1000/1000) %>%
  mutate(Leachate_Na_mg_kgchar_filt0.7 = Leachate_Na_mg_L_filt0.7*Leachate_vol_mL/Char_leached_g*1000/1000) %>%
  mutate(Leachate_S_mg_kgchar_filt0.7 = Leachate_S_mg_L_filt0.7*Leachate_vol_mL/Char_leached_g*1000/1000) %>%
  mutate(Leachate_Al_mg_kgchar_filt0.7 = Leachate_Al_mg_L_filt0.7*Leachate_vol_mL/Char_leached_g*1000/1000) %>%
  mutate(Leachate_Fe_mg_kgchar_filt0.7 = Leachate_Fe_mg_L_filt0.7*Leachate_vol_mL/Char_leached_g*1000/1000) %>%
  mutate(Leachate_C_mg_kgchar_filt0.7 = NPOC_mg_C_per_L*Leachate_vol_mL/Char_leached_g*1000/1000) %>%
  mutate(Leachate_N_mg_kgchar_filt0.7 = TN_mg_N_per_L*Leachate_vol_mL/Char_leached_g*1000/1000) %>%
  mutate(Leachate_MBD_mg_kgchar_filt0.7 = MBD_P_mg_per_L_filt0.7*Leachate_vol_mL/Char_leached_g*1000/1000) 

#convert units of leachates: normalize by concentration in solid char (as percent)  
data<-data %>%
  mutate(Solid_C_mg_kg = (C_weight_per*10000),
  Solid_N_mg_kg = (N_weight_per*10000)) %>%
  mutate(Leachate_Ca_perc_solid_unfilt = Leachate_Ca_mg_kgchar_unfilt/Solid_Ca_mg_kg*100) %>%
  mutate(Leachate_Mg_perc_solid_unfilt = Leachate_Mg_mg_kgchar_unfilt/Solid_Mg_mg_kg*100) %>%
  mutate(Leachate_P_perc_solid_unfilt = Leachate_P_mg_kgchar_unfilt/Solid_P_mg_kg*100) %>%
  mutate(Leachate_K_perc_solid_unfilt = Leachate_K_mg_kgchar_unfilt/Solid_K_mg_kg*100) %>%
  mutate(Leachate_Na_perc_solid_unfilt = Leachate_Na_mg_kgchar_unfilt/Solid_Na_mg_kg*100) %>%
  mutate(Leachate_S_perc_solid_unfilt = Leachate_S_mg_kgchar_unfilt/Solid_S_mg_kg*100) %>%
  mutate(Leachate_Al_perc_solid_unfilt = Leachate_Al_mg_kgchar_unfilt/Solid_Al_mg_kg*100) %>%
  mutate(Leachate_Fe_perc_solid_unfilt = Leachate_Fe_mg_kgchar_unfilt/Solid_Fe_mg_kg*100) %>%
  mutate(Leachate_Ca_perc_solid_part = Leachate_Ca_mg_kgchar_part/Solid_Ca_mg_kg*100) %>%
  mutate(Leachate_Mg_perc_solid_part = Leachate_Mg_mg_kgchar_part/Solid_Mg_mg_kg*100) %>%
  mutate(Leachate_P_perc_solid_part = Leachate_P_mg_kgchar_part/Solid_P_mg_kg*100) %>%
  mutate(Leachate_K_perc_solid_part = Leachate_K_mg_kgchar_part/Solid_K_mg_kg*100) %>%
  mutate(Leachate_Na_perc_solid_part = Leachate_Na_mg_kgchar_part/Solid_Na_mg_kg*100) %>%
  mutate(Leachate_S_perc_solid_part = Leachate_S_mg_kgchar_part/Solid_S_mg_kg*100) %>%
  mutate(Leachate_Al_perc_solid_part = Leachate_Al_mg_kgchar_part/Solid_Al_mg_kg*100) %>%
  mutate(Leachate_Fe_perc_solid_part = Leachate_Fe_mg_kgchar_part/Solid_Fe_mg_kg*100) %>%
  mutate(Leachate_Ca_perc_solid_filt0.7 = Leachate_Ca_mg_kgchar_filt0.7/Solid_Ca_mg_kg*100) %>%
  mutate(Leachate_Mg_perc_solid_filt0.7 = Leachate_Mg_mg_kgchar_filt0.7/Solid_Mg_mg_kg*100) %>%
  mutate(Leachate_P_perc_solid_filt0.7 = Leachate_P_mg_kgchar_filt0.7/Solid_P_mg_kg*100) %>%
  mutate(Leachate_K_perc_solid_filt0.7 = Leachate_K_mg_kgchar_filt0.7/Solid_K_mg_kg*100) %>%
  mutate(Leachate_Na_perc_solid_filt0.7 = Leachate_Na_mg_kgchar_filt0.7/Solid_Na_mg_kg*100) %>%
  mutate(Leachate_S_perc_solid_filt0.7 = Leachate_S_mg_kgchar_filt0.7/Solid_S_mg_kg*100) %>%
  mutate(Leachate_Al_perc_solid_filt0.7 = Leachate_Al_mg_kgchar_filt0.7/Solid_Al_mg_kg*100) %>%
  mutate(Leachate_Fe_perc_solid_filt0.7 = Leachate_Fe_mg_kgchar_filt0.7/Solid_Fe_mg_kg*100) %>%
  mutate(Leachate_C_perc_solid_filt0.7 = Leachate_C_mg_kgchar_filt0.7/Solid_C_mg_kg*100) %>%
  mutate(Leachate_N_perc_solid_filt0.7 = Leachate_N_mg_kgchar_filt0.7/Solid_Na_mg_kg*100) %>%
  mutate(Leachate_MBD_perc_solid_filt0.7 = Leachate_MBD_mg_kgchar_filt0.7/Solid_P_mg_kg*100) 

#convert units of leachates: normalize by concentration in solid char (as mg leachate conc/solid g following Fischer et al. 2023)
data<-data %>%
  mutate(Leachate_mg_Ca_per_g_Ca_in_solid_unfilt = Leachate_Ca_mg_L_unfilt*(1/1000)*Leachate_vol_mL*(1/Char_leached_g)*(1/Solid_Ca_mg_kg)*1000*1000)%>%
  mutate(Leachate_mg_Mg_per_g_Mg_in_solid_unfilt = Leachate_Mg_mg_L_unfilt*(1/1000)*Leachate_vol_mL*(1/Char_leached_g)*(1/Solid_Mg_mg_kg)*1000*1000)%>%
  mutate(Leachate_mg_P_per_g_P_in_solid_unfilt = Leachate_P_mg_L_unfilt*(1/1000)*Leachate_vol_mL*(1/Char_leached_g)*(1/Solid_P_mg_kg)*1000*1000)%>%
  mutate(Leachate_mg_K_per_g_Ca_in_solid_unfilt = Leachate_K_mg_L_unfilt*(1/1000)*Leachate_vol_mL*(1/Char_leached_g)*(1/Solid_K_mg_kg)*1000*1000)%>%
  mutate(Leachate_mg_Na_per_g_Ca_in_solid_unfilt = Leachate_Na_mg_L_unfilt*(1/1000)*Leachate_vol_mL*(1/Char_leached_g)*(1/Solid_Na_mg_kg)*1000*1000)%>% 
  mutate(Leachate_mg_S_per_g_S_in_solid_unfilt = Leachate_S_mg_L_unfilt*(1/1000)*Leachate_vol_mL*(1/Char_leached_g)*(1/Solid_S_mg_kg)*1000*1000)%>%
  mutate(Leachate_mg_Al_per_g_Al_in_solid_unfilt = Leachate_Al_mg_L_unfilt*(1/1000)*Leachate_vol_mL*(1/Char_leached_g)*(1/Solid_Al_mg_kg)*1000*1000)%>%
  mutate(Leachate_mg_Fe_per_g_Fe_in_solid_unfilt = Leachate_Fe_mg_L_unfilt*(1/1000)*Leachate_vol_mL*(1/Char_leached_g)*(1/Solid_Fe_mg_kg)*1000*1000)%>%
  mutate(Leachate_mg_Ca_per_g_Ca_in_solid_part = Leachate_Ca_mg_L_part*(1/1000)*Leachate_vol_mL*(1/Char_leached_g)*(1/Solid_Ca_mg_kg)*1000*1000)%>%
  mutate(Leachate_mg_Mg_per_g_Mg_in_solid_part = Leachate_Mg_mg_L_part*(1/1000)*Leachate_vol_mL*(1/Char_leached_g)*(1/Solid_Mg_mg_kg)*1000*1000)%>%
  mutate(Leachate_mg_P_per_g_P_in_solid_part = Leachate_P_mg_L_part*(1/1000)*Leachate_vol_mL*(1/Char_leached_g)*(1/Solid_P_mg_kg)*1000*1000)%>%
  mutate(Leachate_mg_K_per_g_K_in_solid_part = Leachate_K_mg_L_part*(1/1000)*Leachate_vol_mL*(1/Char_leached_g)*(1/Solid_K_mg_kg)*1000*1000)%>%
  mutate(Leachate_mg_Na_per_g_Na_in_solid_part = Leachate_Na_mg_L_part*(1/1000)*Leachate_vol_mL*(1/Char_leached_g)*(1/Solid_Na_mg_kg)*1000*1000)%>%
  mutate(Leachate_mg_S_per_g_S_in_solid_part = Leachate_S_mg_L_part*(1/1000)*Leachate_vol_mL*(1/Char_leached_g)*(1/Solid_S_mg_kg)*1000*1000)%>%
  mutate(Leachate_mg_Al_per_g_Al_in_solid_part = Leachate_Al_mg_L_part*(1/1000)*Leachate_vol_mL*(1/Char_leached_g)*(1/Solid_Al_mg_kg)*1000*1000)%>%
  mutate(Leachate_mg_Fe_per_g_Fe_in_solid_part = Leachate_Fe_mg_L_part*(1/1000)*Leachate_vol_mL*(1/Char_leached_g)*(1/Solid_Fe_mg_kg)*1000*1000)%>%
  mutate(Leachate_mg_Ca_per_g_Ca_in_solid_filt0.7 = Leachate_Ca_mg_L_filt0.7*(1/1000)*Leachate_vol_mL*(1/Char_leached_g)*(1/Solid_Ca_mg_kg)*1000*1000)%>%
  mutate(Leachate_mg_Mg_per_g_Mg_in_solid_filt0.7 = Leachate_Mg_mg_L_filt0.7*(1/1000)*Leachate_vol_mL*(1/Char_leached_g)*(1/Solid_Mg_mg_kg)*1000*1000)%>%
  mutate(Leachate_mg_P_per_g_P_in_solid_filt0.7 = Leachate_P_mg_L_filt0.7*(1/1000)*Leachate_vol_mL*(1/Char_leached_g)*(1/Solid_P_mg_kg)*1000*1000)%>%
  mutate(Leachate_mg_K_per_g_K_in_solid_filt0.7 = Leachate_K_mg_L_filt0.7*(1/1000)*Leachate_vol_mL*(1/Char_leached_g)*(1/Solid_K_mg_kg)*1000*1000)%>%
  mutate(Leachate_mg_Na_per_g_Na_in_solid_filt0.7 = Leachate_Na_mg_L_filt0.7*(1/1000)*Leachate_vol_mL*(1/Char_leached_g)*(1/Solid_Na_mg_kg)*1000*1000)%>%
  mutate(Leachate_mg_S_per_g_S_in_solid_filt0.7 = Leachate_S_mg_L_filt0.7*(1/1000)*Leachate_vol_mL*(1/Char_leached_g)*(1/Solid_S_mg_kg)*1000*1000)%>%
  mutate(Leachate_mg_Al_per_g_Al_in_solid_filt0.7 = Leachate_Al_mg_L_filt0.7*(1/1000)*Leachate_vol_mL*(1/Char_leached_g)*(1/Solid_Al_mg_kg)*1000*1000)%>%
  mutate(Leachate_mg_Fe_per_g_Fe_in_solid_filt0.7 = Leachate_Fe_mg_L_filt0.7*(1/1000)*Leachate_vol_mL*(1/Char_leached_g)*(1/Solid_Fe_mg_kg)*1000*1000)%>%
  mutate(Leachate_mg_C_per_g_C_in_solid_filt0.7 = NPOC_mg_C_per_L*(1/1000)*Leachate_vol_mL*(1/ Char_leached_g)*(1/Solid_C_mg_kg)*1000*1000)%>%
  mutate(Leachate_mg_N_per_g_N_in_solid_filt0.7 = TN_mg_N_per_L*(1/1000)*Leachate_vol_mL*(1/ Char_leached_g)*(1/Solid_N_mg_kg)*1000*1000)%>%
  mutate(Leachate_mg_MBD_per_g_P_in_solid_filt0.7 = MBD_P_mg_per_L_filt0.7*(1/1000)*Leachate_vol_mL*(1/Char_leached_g)*(1/Solid_N_mg_kg)*1000*1000)

#molar stoichiometry of P:element in particulate and aqueous phases
data <- data %>%
  mutate(Fe.P.MolarRatio_part=(Leachate_Fe_mg_L_part/55.845)/(Leachate_P_mg_L_part/30.97))%>%
  mutate(K.P.MolarRatio_part=(Leachate_K_mg_L_part/39.0983)/(Leachate_P_mg_L_part/30.97))%>%
  mutate(Na.P.MolarRatio_part=(Leachate_Na_mg_L_part/22.989)/(Leachate_P_mg_L_part/30.97))%>%
  mutate(Al.P.MolarRatio_part=(Leachate_Al_mg_L_part/26.982)/(Leachate_P_mg_L_part/30.97))%>%
  mutate(Mg.P.MolarRatio_part=(Leachate_Mg_mg_L_part/24.305)/(Leachate_P_mg_L_part/30.97))%>%
  mutate(Ca.P.MolarRatio_part=(Leachate_Ca_mg_L_part/40.078)/(Leachate_P_mg_L_part/30.97))%>%
  mutate(S.P.MolarRatio_part=(Leachate_S_mg_L_part/32.065)/(Leachate_P_mg_L_part/30.97))%>%
  mutate(Fe.P.MolarRatio_filt0.7=(Leachate_Fe_mg_L_filt0.7/55.845)/(Leachate_P_mg_L_filt0.7/30.97))%>%
  mutate(K.P.MolarRatio_filt0.7=(Leachate_K_mg_L_filt0.7/39.0983)/(Leachate_P_mg_L_filt0.7/30.97))%>%
  mutate(Na.P.MolarRatio_filt0.7=(Leachate_Na_mg_L_filt0.7/22.989)/(Leachate_P_mg_L_filt0.7/30.97))%>%
  mutate(Al.P.MolarRatio_filt0.7=(Leachate_Al_mg_L_filt0.7/26.982)/(Leachate_P_mg_L_filt0.7/30.97))%>%
  mutate(Mg.P.MolarRatio_filt0.7=(Leachate_Mg_mg_L_filt0.7/24.305)/(Leachate_P_mg_L_filt0.7/30.97))%>%
  mutate(Ca.P.MolarRatio_filt0.7=(Leachate_Ca_mg_L_filt0.7/40.078)/(Leachate_P_mg_L_filt0.7/30.97))%>%
  mutate(S.P.MolarRatio_filt0.7=(Leachate_S_mg_L_filt0.7/32.065)/(Leachate_P_mg_L_filt0.7/30.97))%>%
  mutate(C.P.MolarRatio_filt0.7=(NPOC_mg_C_per_L/12.011)/(Leachate_P_mg_L_filt0.7/30.97))%>%
  mutate(N.P.MolarRatio_filt0.7=(TN_mg_N_per_L/14.01)/(Leachate_P_mg_L_filt0.7/30.97))
  

```

```{r save csv}
#save csv of final collated data with manipulations
write.csv(data, "../data/data.csv", row.names = FALSE) #all data
write.csv(data_solids, "../data/data_solids.csv", row.names = FALSE) #solids only
```

##Functions
```{r axis label}
split_labels_with_parentheses <- function(x) {
  sapply(x, function(label) {
    parts <- strsplit(as.character(label), " ")[[1]]
    if (length(parts) > 1) {
      paste(parts[1], "\n", paste0("(", parts[2], " °C)"), sep = "")
    } else {
      label
    }
  })
}
```

##Quick data import
```{r quick import}
#import data so you don't have to run above code

data <- read_csv("../data/data.csv")
data_solids <- read_csv("../data/data_solids.csv")

data$Burn_Severity=factor(data$Burn_Severity, levels= c("Unburned", "Low", "Moderate", "High"))
```

####summary stats
```{r BS variables}
summary_bs <- data_solids %>%
  dplyr::group_by(Burn_Severity, Land_Coverage_Category) %>%
  dplyr::summarize(
    Temp_Mean = mean(Char_Max_Temp, na.rm = TRUE),
    Temp_Standard_Deviation = sd(Char_Max_Temp, na.rm = TRUE),
    Temp_Min = min(Char_Max_Temp, na.rm = TRUE),
    Temp_Max = max(Char_Max_Temp, na.rm = TRUE),
    Duration_Mean = mean(Burn_Duration, na.rm = TRUE),
    Duration_Standard_Deviation = sd(Burn_Duration, na.rm = TRUE),
    Count = n()
  )

```

```{r solids and leachate summary}

#solid elemental concentrations, NMR, and XANES summary
summary_solids_conc <- data_solids %>%
  dplyr::group_by(Burn_Severity, Land_Coverage_Category) %>%
  mutate(NMR_Pi = Ortho + Pyro) %>%
  mutate( NMR_Po = Mono + Di) %>%
  dplyr::summarize(
    P_Mean = mean(Solid_P_g_kg, na.rm = TRUE),
    P_Standard_Deviation = sd(Solid_P_g_kg, na.rm = TRUE),
    Ca_Mean = mean(Solid_Ca_g_kg, na.rm = TRUE),
    Ca_Standard_Deviation = sd(Solid_Ca_g_kg, na.rm = TRUE),
    Fe_Mean = mean(Solid_Fe_g_kg, na.rm = TRUE),
    Fe_Standard_Deviation = sd(Solid_Fe_g_kg, na.rm = TRUE),
    Al_Mean = mean(Solid_Al_g_kg, na.rm = TRUE),
    Al_Standard_Deviation = sd(Solid_Al_g_kg, na.rm = TRUE),
    K_Mean = mean(Solid_K_g_kg, na.rm = TRUE),
    K_Standard_Deviation = sd(Solid_K_g_kg, na.rm = TRUE),
    Mg_Mean = mean(Solid_Mg_g_kg, na.rm = TRUE),
    Mg_Standard_Deviation = sd(Solid_Mg_g_kg, na.rm = TRUE),
    Na_Mean = mean(Solid_Na_g_kg, na.rm = TRUE),
    Na_Standard_Deviation = sd(Solid_Na_g_kg, na.rm = TRUE),
    S_Mean = mean(Solid_S_g_kg, na.rm = TRUE),
    S_Standard_Deviation = sd(Solid_S_g_kg, na.rm = TRUE),
    C_Mean = mean(Solid_C_g_kg, na.rm = TRUE),
    C_Standard_Deviation = sd(Solid_C_g_kg, na.rm = TRUE),
    N_Mean = mean(Solid_N_g_kg, na.rm = TRUE),
    N_Standard_Deviation = sd(Solid_N_g_kg, na.rm = TRUE),
    NMR_Pi_Mean = mean(NMR_Pi, na.rm = TRUE),
    NMR_Pi_Standard_Deviation = sd(NMR_Pi, na.rm = TRUE),
    NMR_Po_Mean = mean(NMR_Po, na.rm = TRUE),
    NMR_Po_Standard_Deviation = sd(NMR_Po, na.rm = TRUE),
    Ortho_Mean = mean(Ortho, na.rm = TRUE),
    Ortho_Standard_Deviation = sd(Ortho, na.rm = TRUE),
    Mono_Mean = mean(Mono, na.rm = TRUE),
    Mono_Standard_Deviation = sd(Mono, na.rm = TRUE),
    Di_Mean = mean(Di, na.rm = TRUE),
    Di_Standard_Deviation = sd(Di, na.rm = TRUE),
    Pyro_Mean = mean(Pyro, na.rm = TRUE),
    Pyro_Standard_Deviation = sd(Pyro, na.rm = TRUE),
    M_D_Mean = mean(M_D_ratio, na.rm = TRUE),
    M_D_Standard_Deviation = sd(M_D_ratio, na.rm = TRUE),
    XANES_Po_Mean = mean(XANES_Po, na.rm = TRUE),
    XANES_Po_Standard_Deviation = sd(XANES_Po, na.rm = TRUE),
    XANES_Pi_Mean = mean(XANES_Pi, na.rm = TRUE),
    XANES_Pi_Standard_Deviation = sd(XANES_Pi, na.rm = TRUE),
    XANES_Fe_Mean = mean(XANES_Fe, na.rm = TRUE),
    XANES_Fe_Standard_Deviation = sd(XANES_Fe, na.rm = TRUE),
    XANES_Na_Mean = mean(XANES_Na, na.rm = TRUE),
    XANES_Na_Standard_Deviation = sd(XANES_Na, na.rm = TRUE),
    XANES_Ca_Mean = mean(XANES_Ca, na.rm = TRUE),
    XANES_Ca_Standard_Deviation = sd(XANES_Ca, na.rm = TRUE),
    XANES_Al_Mean = mean(XANES_Al, na.rm = TRUE),
    XANES_Al_Standard_Deviation = sd(XANES_Al, na.rm = TRUE),
    XANES_Mg_Mean = mean(XANES_Mg, na.rm = TRUE),
    XANES_Mg_Standard_Deviation = sd(XANES_Mg, na.rm = TRUE),
    XANES_K_Mean = mean(XANES_K, na.rm = TRUE),
    XANES_K_Standard_Deviation = sd(XANES_K, na.rm = TRUE),
    XANES_Pi_Fe_Mean = mean(XANES_Pi_Fe, na.rm = TRUE),
    XANES_Pi_Fe_Standard_Deviation = sd(XANES_Pi_Fe, na.rm = TRUE),
    XANES_Pi_Na_Mean = mean(XANES_Pi_Na, na.rm = TRUE),
    XANES_Pi_Na_Standard_Deviation = sd(XANES_Pi_Na, na.rm = TRUE),
    XANES_Pi_Ca_Mean = mean(XANES_Pi_Ca, na.rm = TRUE),
    XANES_Pi_Ca_Standard_Deviation = sd(XANES_Pi_Ca, na.rm = TRUE),
    XANES_Pi_Al_Mean = mean(XANES_Pi_Al, na.rm = TRUE),
    XANES_Pi_Al_Standard_Deviation = sd(XANES_Pi_Al, na.rm = TRUE),
    XANES_Pi_Mg_Mean = mean(XANES_Pi_Mg, na.rm = TRUE),
    XANES_Pi_Mg_Standard_Deviation = sd(XANES_Pi_Mg, na.rm = TRUE),
    XANES_Pi_K_Mean = mean(XANES_Pi_K, na.rm = TRUE),
    XANES_Pi_K_Standard_Deviation = sd(XANES_Pi_K, na.rm = TRUE),
    XANES_Po_Fe_Mean = mean(XANES_Po_Fe, na.rm = TRUE),
    XANES_Po_Fe_Standard_Deviation = sd(XANES_Po_Fe, na.rm = TRUE),
    XANES_Po_Na_Mean = mean(XANES_Po_Na, na.rm = TRUE),
    XANES_Po_Na_Standard_Deviation = sd(XANES_Po_Na, na.rm = TRUE),
    XANES_Po_Ca_Mean = mean(XANES_Po_Ca, na.rm = TRUE),
    XANES_Po_Ca_Standard_Deviation = sd(XANES_Po_Ca, na.rm = TRUE),
    XANES_Po_Al_Mean = mean(XANES_Po_Al, na.rm = TRUE),
    XANES_Po_Al_Standard_Deviation = sd(XANES_Po_Al, na.rm = TRUE),
    XANES_Po_Mg_Mean = mean(XANES_Po_Mg, na.rm = TRUE),
    XANES_Po_Mg_Standard_Deviation = sd(XANES_Po_Mg, na.rm = TRUE),
    XANES_Po_K_Mean = mean(XANES_Po_K, na.rm = TRUE),
    XANES_Po_K_Standard_Deviation = sd(XANES_Po_K, na.rm = TRUE),
    Count = n()
  )

                   
write.csv(summary_solids_conc, "../data/summary_solids_conc.csv") #save this for a table


#NMR extraction efficiency
summary_solids <- data_solids %>%
  dplyr::group_by(Burn_Severity, Land_Coverage_Category) %>%
  dplyr::summarize(
    Mean = mean(NMR_EE_P_perc, na.rm = TRUE),
    Standard_Deviation = sd(NMR_EE_P_perc, na.rm = TRUE),
    Count = n()
  )

write.csv(summary_solids, "../data/summary_solids_nmr.csv") #save this for a table
write.csv(data_solids, "../data/data_solids.csv") #save this for individual info collated

#leachate concentrations
P.Conc.leach<- data %>%
  dplyr::group_by(Burn_Severity, Land_Coverage_Category) %>%
  dplyr::summarize(
    Leachate_mg_P_per_g_P_in_solid_unfilt_Mean = mean(Leachate_mg_P_per_g_P_in_solid_unfilt, na.rm = TRUE),
    Leachate_mg_P_per_g_P_in_solid_unfilt_Standard_Deviation = sd(Leachate_mg_P_per_g_P_in_solid_unfilt, na.rm = TRUE),
    Leachate_mg_P_per_g_P_in_solid_filt0.7_Mean = mean(Leachate_mg_P_per_g_P_in_solid_filt0.7, na.rm = TRUE),
    Leachate_mg_P_per_g_P_in_solid_filt0.7_Standard_Deviation = sd(Leachate_mg_P_per_g_P_in_solid_filt0.7, na.rm = TRUE),
    Leachate_mg_P_per_g_P_in_solid_part_Mean = mean(Leachate_mg_P_per_g_P_in_solid_part, na.rm = TRUE),
    Leachate_mg_P_per_g_P_in_solid_part_Standard_Deviation = sd(Leachate_mg_P_per_g_P_in_solid_part, na.rm = TRUE),
    Leachate_mg_MBD_per_g_P_in_solid_filt0.7_Mean = mean(Leachate_mg_MBD_per_g_P_in_solid_filt0.7, na.rm = TRUE),
    Leachate_mg_MBD_per_g_P_in_solid_filt0.7_Standard_Deviation = sd(Leachate_mg_MBD_per_g_P_in_solid_filt0.7, na.rm = TRUE),
    Count = n()
  )

write.csv(P.Conc.leach, "../data/summary_leachate_conc.csv") #save this for a table
  
```

```{r stoichiometry solid and leachates}
#format data
stoich_solid<-data_solids %>%
  select(Parent_ID, Burn_Severity, Land_Coverage_Category, Ca.P.MolarRatio, Mg.P.MolarRatio, Fe.P.MolarRatio, Al.P.MolarRatio, Na.P.MolarRatio, K.P.MolarRatio, S.P.MolarRatio, N.P.MolarRatio, C.P.MolarRatio) %>%
  dplyr::rename(
    'Ca:P' = 'Ca.P.MolarRatio',
    'Mg:P' = 'Mg.P.MolarRatio',
    'Fe:P' = 'Fe.P.MolarRatio',
    'Al:P' = 'Al.P.MolarRatio',
    'Na:P' = 'Na.P.MolarRatio',
    'K:P' = 'K.P.MolarRatio',
    'S:P' = 'S.P.MolarRatio',
    'N:P' = 'N.P.MolarRatio',
    'C:P' = 'C.P.MolarRatio')%>%
  mutate(filter = 'Solid')

stoich_leachates<-data %>%
  select(Parent_ID, Ca.P.MolarRatio_part, Mg.P.MolarRatio_part, Fe.P.MolarRatio_part, Al.P.MolarRatio_part, Na.P.MolarRatio_part, K.P.MolarRatio_part, S.P.MolarRatio_part, Ca.P.MolarRatio_filt0.7, Mg.P.MolarRatio_filt0.7, Fe.P.MolarRatio_filt0.7, Al.P.MolarRatio_filt0.7, Na.P.MolarRatio_filt0.7, K.P.MolarRatio_filt0.7, S.P.MolarRatio_filt0.7, N.P.MolarRatio_filt0.7, C.P.MolarRatio_filt0.7) %>%
  dplyr::rename(
    'Ca_P_part' = 'Ca.P.MolarRatio_part',
    'Mg_P_part' = 'Mg.P.MolarRatio_part',
    'Fe_P_part' = 'Fe.P.MolarRatio_part',
    'Al_P_part' = 'Al.P.MolarRatio_part',
    'Na_P_part' = 'Na.P.MolarRatio_part',
    'K_P_part' = 'K.P.MolarRatio_part',
    'S_P_part' = 'S.P.MolarRatio_part',
    'Ca_P_filt0.7' = 'Ca.P.MolarRatio_filt0.7',
    'Mg_P_filt0.7' = 'Mg.P.MolarRatio_filt0.7',
    'Fe_P_filt0.7' = 'Fe.P.MolarRatio_filt0.7',
    'Al_P_filt0.7' = 'Al.P.MolarRatio_filt0.7',
    'Na_P_filt0.7' = 'Na.P.MolarRatio_filt0.7',
    'K_P_filt0.7' = 'K.P.MolarRatio_filt0.7',
    'S_P_filt0.7' = 'S.P.MolarRatio_filt0.7',
    'N_P_filt0.7' = 'N.P.MolarRatio_filt0.7',
    'C_P_filt0.7' = 'C.P.MolarRatio_filt0.7'
  )

stoich_part<-data %>%
  select(Parent_ID, Burn_Severity, Land_Coverage_Category, Ca.P.MolarRatio_part, Mg.P.MolarRatio_part, Fe.P.MolarRatio_part, Al.P.MolarRatio_part, Na.P.MolarRatio_part, K.P.MolarRatio_part, S.P.MolarRatio_part) %>%
  dplyr::rename(
    'Ca:P' = 'Ca.P.MolarRatio_part',
    'Mg:P' = 'Mg.P.MolarRatio_part',
    'Fe:P' = 'Fe.P.MolarRatio_part',
    'Al:P' = 'Al.P.MolarRatio_part',
    'Na:P' = 'Na.P.MolarRatio_part',
    'K:P' = 'K.P.MolarRatio_part',
    'S:P' = 'S.P.MolarRatio_part')%>%
  mutate(filter = 'Particulate')

stoich_filt<-data %>%
  select(Parent_ID, Burn_Severity, Land_Coverage_Category, Ca.P.MolarRatio_filt0.7, Mg.P.MolarRatio_filt0.7, Fe.P.MolarRatio_filt0.7, Al.P.MolarRatio_filt0.7, Na.P.MolarRatio_filt0.7, K.P.MolarRatio_filt0.7, S.P.MolarRatio_filt0.7, C.P.MolarRatio_filt0.7, N.P.MolarRatio_filt0.7) %>%
  dplyr::rename(
    'Ca:P' = 'Ca.P.MolarRatio_filt0.7',
    'Mg:P' = 'Mg.P.MolarRatio_filt0.7',
    'Fe:P' = 'Fe.P.MolarRatio_filt0.7',
    'Al:P' = 'Al.P.MolarRatio_filt0.7',
    'Na:P' = 'Na.P.MolarRatio_filt0.7',
    'K:P' = 'K.P.MolarRatio_filt0.7',
    'S:P' = 'S.P.MolarRatio_filt0.7',
    'C:P' = 'C.P.MolarRatio_filt0.7',
    'N:P' = 'N.P.MolarRatio_filt0.7')%>%
  mutate(filter = 'Aqueous')


stoich<- stoich_leachates %>%
  full_join(stoich_solid)

stoich<- stoich_part %>%
  full_join(stoich_filt)%>%
  full_join(stoich_solid)
  
#bar chart with phase as facet; different colored bars for the stoichiometry
stoich<-melt(stoich, id=c("Parent_ID", "Burn_Severity", "Land_Coverage_Category", "filter"))

stoich_mean <- stoich %>%
  dplyr::group_by(Burn_Severity, Land_Coverage_Category, filter, variable)%>%
  dplyr::summarize(
    value_mean = mean(value, na.rm = TRUE),
    value_sd = sd(value, na.rm = TRUE))
```

####Leachable P
```{r leachate stats}
#Leachable P statistics

#ICP particulates (leachable particulate phase; >0.7 nominal phase) normalized to total P in solid char
model<-lmer(log10(Leachate_mg_P_per_g_P_in_solid_part)~Burn_Severity*Land_Coverage_Category+(1|Parent_ID), data=data)
model.BS<-lmer(log10(Leachate_mg_P_per_g_P_in_solid_part)~Land_Coverage_Category+(1|Parent_ID), data=data)
model.LC<-lmer(log10(Leachate_mg_P_per_g_P_in_solid_part)~Burn_Severity+(1|Parent_ID), data=data)
model.int<-lmer(log10(Leachate_mg_P_per_g_P_in_solid_part)~Burn_Severity+Land_Coverage_Category+(1|Parent_ID), data=data)
anova(model,model.BS)
anova(model,model.LC)
anova(model,model.int)
#check VIF
vif(model)
#model assumptions
hist(log10(data$Leachate_mg_P_per_g_P_in_solid_part))
ggqqplot(residuals(model))
plot(lmer(log10(Leachate_mg_P_per_g_P_in_solid_part)~Burn_Severity*Land_Coverage_Category+(1|Parent_ID), data=data))
#interaction post hoc: 
emmeans::lsmeans(model, pairwise~Burn_Severity*Land_Coverage_Category, at=list(Burn_Severity="Unburned"),adjust="tukey") 
emmeans::lsmeans(model, pairwise~Burn_Severity*Land_Coverage_Category, at=list(Burn_Severity="Low"),adjust="tukey")
emmeans::lsmeans(model, pairwise~Burn_Severity*Land_Coverage_Category, at=list(Burn_Severity="Moderate"),adjust="tukey") 
emmeans::lsmeans(model, pairwise~Burn_Severity*Land_Coverage_Category, at=list(Land_Coverage_Category="Douglas-fir forest"),adjust="tukey") 
emmeans::lsmeans(model, pairwise~Burn_Severity*Land_Coverage_Category, at=list(Land_Coverage_Category="Sagebrush shrubland"),adjust="tukey") 

#ICP filtered (leachable aqueous phase; <0.7 nominal phase) normalized to total P in solid char
model<-lmer(log10(Leachate_mg_P_per_g_P_in_solid_filt0.7)~Burn_Severity*Land_Coverage_Category+(1|Parent_ID), data=data)
model.BS<-lmer(log10(Leachate_mg_P_per_g_P_in_solid_filt0.7)~Land_Coverage_Category+(1|Parent_ID), data=data)
model.LC<-lmer(log10(Leachate_mg_P_per_g_P_in_solid_filt0.7)~Burn_Severity+(1|Parent_ID), data=data)
model.int<-lmer(log10(Leachate_mg_P_per_g_P_in_solid_filt0.7)~Burn_Severity+Land_Coverage_Category+(1|Parent_ID), data=data)
anova(model,model.BS)
anova(model,model.LC)
anova(model,model.int)
#check VIF
vif(model)
#model assumptions
hist(log10(data$Leachate_mg_P_per_g_P_in_solid_filt0.7))
ggqqplot(residuals(model))
plot(lmer(log10(Leachate_mg_P_per_g_P_in_solid_filt0.7)~Burn_Severity*Land_Coverage_Category+(1|Parent_ID), data=data))
#interaction post hoc: 
emmeans::lsmeans(model, pairwise~Burn_Severity*Land_Coverage_Category, at=list(Burn_Severity="Unburned"),adjust="tukey") 
emmeans::lsmeans(model, pairwise~Burn_Severity*Land_Coverage_Category, at=list(Burn_Severity="Low"),adjust="tukey") 
emmeans::lsmeans(model, pairwise~Burn_Severity*Land_Coverage_Category, at=list(Burn_Severity="Moderate"),adjust="tukey") 
emmeans::lsmeans(model, pairwise~Burn_Severity*Land_Coverage_Category, at=list(Land_Coverage_Category="Douglas-fir forest"),adjust="tukey") 
emmeans::lsmeans(model, pairwise~Burn_Severity*Land_Coverage_Category, at=list(Land_Coverage_Category="Sagebrush shrubland"),adjust="tukey")


#Molybdate reactive P filtered (leachable aqueous phase; <0.7 nominal phase) normalized to total P in solid char
model<-lmer(log10(Leachate_mg_MBD_per_g_P_in_solid_filt0.7)~Burn_Severity*Land_Coverage_Category+(1|Parent_ID), data=data)
model.BS<-lmer(log10(Leachate_mg_MBD_per_g_P_in_solid_filt0.7)~Land_Coverage_Category+(1|Parent_ID), data=data)
model.LC<-lmer(log10(Leachate_mg_MBD_per_g_P_in_solid_filt0.7)~Burn_Severity+(1|Parent_ID), data=data)
model.int<-lmer(log10(Leachate_mg_MBD_per_g_P_in_solid_filt0.7)~Burn_Severity+Land_Coverage_Category+(1|Parent_ID), data=data)
anova(model,model.BS)
anova(model,model.LC)
anova(model,model.int)
#check VIF
vif(model)
#model assumptions
hist(log10(data$Leachate_mg_MBD_per_g_P_in_solid_filt0.7))
ggqqplot(residuals(model))
plot(lmer(log10(Leachate_mg_MBD_per_g_P_in_solid_filt0.7)~Burn_Severity*Land_Coverage_Category+(1|Parent_ID), data=data))
#interaction post hoc: 
emmeans::lsmeans(model, pairwise~Burn_Severity*Land_Coverage_Category, at=list(Burn_Severity="Unburned"),adjust="tukey") 
emmeans::lsmeans(model, pairwise~Burn_Severity*Land_Coverage_Category, at=list(Burn_Severity="Low"),adjust="tukey") 
emmeans::lsmeans(model, pairwise~Burn_Severity*Land_Coverage_Category, at=list(Burn_Severity="Moderate"),adjust="tukey") 
emmeans::lsmeans(model, pairwise~Burn_Severity*Land_Coverage_Category, at=list(Land_Coverage_Category="Douglas-fir forest"),adjust="tukey") 
emmeans::lsmeans(model, pairwise~Burn_Severity*Land_Coverage_Category, at=list(Land_Coverage_Category="Sagebrush shrubland"),adjust="tukey")
```

```{r leachate figs}
#Leachable P (normalized by concentration of solid char) stacked barchart of total particulate and total aqueous P
leach.fig<-data %>%
  select(Burn_Severity, Land_Coverage_Category, Leachate_mg_P_per_g_P_in_solid_part, Leachate_mg_P_per_g_P_in_solid_filt0.7, Leachate_mg_MBD_per_g_P_in_solid_filt0.7)%>%
  mutate(Land_Coverage_Category = if_else(Land_Coverage_Category == "Douglas-fir forest", "Douglas-fir Forest", Land_Coverage_Category)) %>%
  mutate(Land_Coverage_Category = if_else(Land_Coverage_Category == "Sagebrush shrubland", "Sagebrush Shrubland", Land_Coverage_Category))

leach.fig<-melt(leach.fig, id =c("Burn_Severity", "Land_Coverage_Category"))

leach.fig <- leach.fig %>%
  mutate(
    variable = case_when(
      variable == "Leachate_mg_P_per_g_P_in_solid_part" ~ "Particulate Total",
      variable == "Leachate_mg_P_per_g_P_in_solid_filt0.7" ~ "Aqueous Total",
      variable == "Leachate_mg_MBD_per_g_P_in_solid_filt0.7" ~ "Aqueous Molybdate Reactive"),
    Annotation = case_when(
      variable == "Particulate Total" & Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "Unburned" ~ "a",
      variable == "Particulate Total" & Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "Low" ~ "a",
      variable == "Particulate Total" & Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "Moderate" ~ "ab",
      variable == "Particulate Total" & Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "High" ~ "b",
      variable == "Particulate Total" & Land_Coverage_Category == "Sagebrush Shrubland" & Burn_Severity == "Unburned" ~ "a",
      variable == "Particulate Total" & Land_Coverage_Category == "Sagebrush Shrubland" & Burn_Severity == "Low" ~ "a",
      variable == "Particulate Total" & Land_Coverage_Category == "Sagebrush Shrubland" & Burn_Severity == "Moderate" ~ "b",
      variable == "Aqueous Total" & Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "Unburned" ~ "a",
      variable == "Aqueous Total" & Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "Low" ~ "a",
      variable == "Aqueous Total" & Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "Moderate" ~ "ab",
      variable == "Aqueous Total" & Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "High" ~ "b",
      variable == "Aqueous Total" & Land_Coverage_Category == "Sagebrush Shrubland" & Burn_Severity == "Unburned" ~ "a",
      variable == "Aqueous Total" & Land_Coverage_Category == "Sagebrush Shrubland" & Burn_Severity == "Low" ~ "a",
      variable == "Aqueous Total" & Land_Coverage_Category == "Sagebrush Shrubland" & Burn_Severity == "Moderate" ~ "b",
      variable == "Aqueous Molybdate Reactive" & Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "Unburned" ~ "a",
      variable == "Aqueous Molybdate Reactive" & Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "Low" ~ "a",
      variable == "Aqueous Molybdate Reactive" & Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "Moderate" ~ "a",
      variable == "Aqueous Molybdate Reactive" & Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "High" ~ "a",
      variable == "Aqueous Molybdate Reactive" & Land_Coverage_Category == "Sagebrush Shrubland" & Burn_Severity == "Unburned" ~ "a",
      variable == "Aqueous Molybdate Reactive" & Land_Coverage_Category == "Sagebrush Shrubland" & Burn_Severity == "Low" ~ "a",
      variable == "Aqueous Molybdate Reactive" & Land_Coverage_Category == "Sagebrush Shrubland" & Burn_Severity == "Moderate" ~ "a"),
    x = case_when(
      variable == "Particulate Total" & Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "Unburned" ~ "Unburned 25",
      variable == "Particulate Total" & Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "Low" ~ "Low 295-627",
      variable == "Particulate Total" & Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "Moderate" ~ "Moderate 589-757",
      variable == "Particulate Total" & Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "High" ~ "High 589-757",
      variable == "Particulate Total" & Land_Coverage_Category == "Sagebrush Shrubland" & Burn_Severity == "Unburned" ~ "Unburned 25",
      variable == "Particulate Total" & Land_Coverage_Category == "Sagebrush Shrubland" & Burn_Severity == "Low" ~ "Low 308-502",
      variable == "Particulate Total" & Land_Coverage_Category == "Sagebrush Shrubland" & Burn_Severity == "Moderate" ~ "Moderate 512-547",
      variable == "Aqueous Total" & Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "Unburned" ~ "Unburned 25",
      variable == "Aqueous Total" & Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "Low" ~ "Low 295-627",
      variable == "Aqueous Total" & Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "Moderate" ~ "Moderate 589-757",
      variable == "Aqueous Total" & Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "High" ~ "High 589-757",
      variable == "Aqueous Total" & Land_Coverage_Category == "Sagebrush Shrubland" & Burn_Severity == "Unburned" ~ "Unburned 25",
      variable == "Aqueous Total" & Land_Coverage_Category == "Sagebrush Shrubland" & Burn_Severity == "Low" ~ "Low 308-502",
      variable == "Aqueous Total" & Land_Coverage_Category == "Sagebrush Shrubland" & Burn_Severity == "Moderate" ~ "Moderate 512-547",
      variable == "Aqueous Molybdate Reactive" & Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "Unburned" ~ "Unburned 25",
      variable == "Aqueous Molybdate Reactive" & Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "Low" ~ "Low 295-627",
      variable == "Aqueous Molybdate Reactive" & Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "Moderate" ~ "Moderate 589-757",
      variable == "Aqueous Molybdate Reactive" & Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "High" ~ "High 589-757",
      variable == "Aqueous Molybdate Reactive" & Land_Coverage_Category == "Sagebrush Shrubland" & Burn_Severity == "Unburned" ~ "Unburned 25",
      variable == "Aqueous Molybdate Reactive" & Land_Coverage_Category == "Sagebrush Shrubland" & Burn_Severity == "Low" ~ "Low 308-502",
      variable == "Aqueous Molybdate Reactive" & Land_Coverage_Category == "Sagebrush Shrubland" & Burn_Severity == "Moderate" ~ "Moderate 512-547"),
    y = case_when(
      variable == "Particulate Total" & Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "Unburned" ~ 300,
      variable == "Particulate Total" & Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "Low" ~ 255,
      variable == "Particulate Total" & Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "Moderate" ~ 250,
      variable == "Particulate Total" & Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "High" ~ 925,
      variable == "Particulate Total" & Land_Coverage_Category == "Sagebrush Shrubland" & Burn_Severity == "Unburned" ~ 110,
      variable == "Particulate Total" & Land_Coverage_Category == "Sagebrush Shrubland" & Burn_Severity == "Low" ~ 180,
      variable == "Particulate Total" & Land_Coverage_Category == "Sagebrush Shrubland" & Burn_Severity == "Moderate" ~ 905,
      variable == "Aqueous Total" & Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "Unburned" ~ 110,
      variable == "Aqueous Total" & Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "Low" ~ 140,
      variable == "Aqueous Total" & Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "Moderate" ~ 110,
      variable == "Aqueous Total" & Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "High" ~ 85,
      variable == "Aqueous Total" & Land_Coverage_Category == "Sagebrush Shrubland" & Burn_Severity == "Unburned" ~ 270,
      variable == "Aqueous Total" & Land_Coverage_Category == "Sagebrush Shrubland" & Burn_Severity == "Low" ~ 125,
      variable == "Aqueous Total" & Land_Coverage_Category == "Sagebrush Shrubland" & Burn_Severity == "Moderate" ~ 30,
      variable == "Aqueous Molybdate Reactive" & Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "Unburned" ~ 14,
      variable == "Aqueous Molybdate Reactive" & Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "Low" ~ 37,
      variable == "Aqueous Molybdate Reactive" & Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "Moderate" ~ 35,
      variable == "Aqueous Molybdate Reactive" & Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "High" ~ 46,
      variable == "Aqueous Molybdate Reactive" & Land_Coverage_Category == "Sagebrush Shrubland" & Burn_Severity == "Unburned" ~ 28,
      variable == "Aqueous Molybdate Reactive" & Land_Coverage_Category == "Sagebrush Shrubland" & Burn_Severity == "Low" ~ 47,
      variable == "Aqueous Molybdate Reactive" & Land_Coverage_Category == "Sagebrush Shrubland" & Burn_Severity == "Moderate" ~ 44),
    Burn_Severity = case_when(
      Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "Unburned" ~ "Unburned 25",
      Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "Low" ~ "Low 295-627",
      Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "Moderate" ~ "Moderate 589-757",
      Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "High" ~ "High 589-757",
      Land_Coverage_Category == "Sagebrush Shrubland" & Burn_Severity == "Unburned" ~ "Unburned 25",
      Land_Coverage_Category == "Sagebrush Shrubland" & Burn_Severity == "Low" ~ "Low 308-502",
      Land_Coverage_Category == "Sagebrush Shrubland" & Burn_Severity == "Moderate" ~ "Moderate 512-547",
      TRUE ~ as.character(Burn_Severity)),
    Burn_Severity = factor(Burn_Severity, levels = c("Unburned 25", "Low 295-627", "Low 308-502", "Moderate 589-757", "Moderate 512-547", "High 589-757")),
    variable = factor(variable, levels = c("Particulate Total", "Aqueous Total", "Aqueous Molybdate Reactive"))
    )


leach.fig.stack<-leach.fig %>%
  filter(str_detect(variable, "Total"))

leach.Pnorm.conc<-ggplot(leach.fig.stack, aes(x = Burn_Severity, y = value, fill = Land_Coverage_Category)) +
  geom_boxplot(show.legend = FALSE) +
  theme_classic() +
  ylab(expression(paste(Leachable~P~(mg~g^-1), sep = ""))) +
  xlab("Burn Severity") +
  scale_fill_manual(values = c("#9B9B7A","#FFCB69")) +
  facet_grid(variable ~ Land_Coverage_Category, scales = "free") +
  scale_x_discrete(labels = split_labels_with_parentheses) +
  theme(
    text = element_text(size = 15),
    axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1),  # Tilted 45 degrees
    panel.border = element_rect(color = "black", fill = NA, linewidth = 1)  # Add border around facets
  )+
  geom_text(aes(label = Annotation, x = x, y = y), size = 4.5, fontface = "plain")

cowplot::save_plot("../figures/leach.Pnorm.conc.pdf", leach.Pnorm.conc, ncol = 1, nrow = 1, base_height = 6, base_aspect_ratio= 1:1, dpi=100)


 

#molybdate reactive P figure for SI
leach.fig.mbd<-leach.fig %>%
  filter(str_detect(variable, "Molybdate"))

leach.Pnorm.conc.mbd<-ggplot(leach.fig.mbd, aes(x = Burn_Severity, y = value, fill = Land_Coverage_Category)) +
    geom_boxplot(show.legend = FALSE) +
    theme_classic() +
    ylab(expression(paste(atop("Leachable Aqueous Molybdate", "Reactive P (mg g"^"-1"*")")))) +
    xlab("Burn Severity") +
    scale_fill_manual(values = c("#9B9B7A","#FFCB69")) +
    facet_grid(. ~ Land_Coverage_Category, scales = "free") +
    scale_x_discrete(labels = split_labels_with_parentheses) +
    theme(
        text = element_text(size = 15),
        axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1),  # Tilted 45 degrees
        panel.border = element_rect(color = "black", fill = NA, linewidth = 1)  # Add border around facets
    ) +
    geom_text(aes(label = Annotation, x = x, y = y), size = 4.5, fontface = "plain")

cowplot::save_plot("../figures/leach.Pnorm.conc.mbd.pdf", leach.Pnorm.conc.mbd, ncol = 1, nrow = 1, base_height = 4, base_width = 5.5, base_aspect_ratio= 1:1, dpi=100)


```

####pH
```{r aqueous P}
#figure to see relationship between P in aqueous fraction and pH
aq_pH<-ggplot(data, aes(x=pH, y=Leachate_mg_P_per_g_P_in_solid_filt0.7, color=Burn_Severity))+geom_point() + geom_smooth(method = "lm", se = FALSE, na.rm = TRUE, fullrange = TRUE, aes(group=1), color = "black") +theme_classic()+ylab(expression(paste(Aqueous~P~(mg~g^-1), sep="")))+ xlab("pH")+facet_grid(.~Land_Coverage_Category, scales = "free")+theme(text = element_text(size = 15), panel.border = element_rect(color = "black", fill = NA, linewidth = 1))+scale_color_manual(name = "Burn Severity", values=c("#0a9396", "#ffba08", "#e85d04", "#9d0208"))

cowplot::save_plot("../figures/aq_pH.pdf", aq_pH, ncol = 1, nrow = 1,  base_height = 3.85, base_width = 8.9, base_aspect_ratio= 2:1, dpi=100)

#Anova to see relationship between aqueous P concentration and pH for each ecosystem type separately
#sagebrush shrubland
model<-lm(log10(Leachate_mg_P_per_g_P_in_solid_filt0.7)~pH, data = subset(data, Land_Coverage_Category == "Sagebrush shrubland"))
summary(model)
#model assumptions
hist(log10(data_solids$Solid_P_mg_kg))
ggqqplot(residuals(model))
#check normality of residuals 
shapiro.test(log10(data_solids$Solid_P_mg_kg)) #p > 0.05 so can assume normality 
#check homogeneity of variance assumption (homoscedastcity)
plot(fitted(model),residuals(model))
performance::check_heteroscedasticity(model) #p > 0.05 so can assume homoscedastic

#Douglas-fir forest
model<-lm(log10(Leachate_mg_P_per_g_P_in_solid_filt0.7)~pH, data = subset(data, Land_Coverage_Category == "Douglas-fir forest"))
summary(model)
#model assumptions
hist(log10(data_solids$Solid_P_mg_kg))
ggqqplot(residuals(model))
#check normality of residuals 
shapiro.test(log10(data_solids$Solid_P_mg_kg)) #p > 0.05 so can assume normality 
#check homogeneity of variance assumption (homoscedastcity)
plot(fitted(model),residuals(model))
performance::check_heteroscedasticity(model) #p > 0.05 so can assume homoscedastic

```

```{r pH and BS}
#figure of pH and burn severity

data_pH <- data %>%
  mutate(
    Annotation = case_when(
      Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "Unburned" ~ "a",
      Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "Low" ~ "a",
      Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "Moderate" ~ "b",
      Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "High" ~ "c",
      Land_Coverage_Category == "Sagebrush Shrubland" & Burn_Severity == "Unburned" ~ "a",
      Land_Coverage_Category == "Sagebrush Shrubland" & Burn_Severity == "Low" ~ "b",
      Land_Coverage_Category == "Sagebrush Shrubland" & Burn_Severity == "Moderate" ~ "c"),
    x = case_when(
      Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "Unburned" ~ "Unburned 25",
      Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "Low" ~ "Low 295-627",
      Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "Moderate" ~ "Moderate 589-757",
      Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "High" ~ "High 589-757",
      Land_Coverage_Category == "Sagebrush Shrubland" & Burn_Severity == "Unburned" ~ "Unburned 25",
      Land_Coverage_Category == "Sagebrush Shrubland" & Burn_Severity == "Low" ~ "Low 308-502",
      Land_Coverage_Category == "Sagebrush Shrubland" & Burn_Severity == "Moderate" ~ "Moderate 512-547"),
    y = case_when(
      Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "Unburned" ~ 5.75,
      Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "Low" ~ 9.5,
      Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "Moderate" ~ 10.25,
      Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "High" ~ 11.775,
      Land_Coverage_Category == "Sagebrush Shrubland" & Burn_Severity == "Unburned" ~4.75,
      Land_Coverage_Category == "Sagebrush Shrubland" & Burn_Severity == "Low" ~ 7.8,
      Land_Coverage_Category == "Sagebrush Shrubland" & Burn_Severity == "Moderate" ~ 11.3),
    Burn_Severity = case_when(
      Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "Unburned" ~ "Unburned 25",
      Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "Low" ~ "Low 295-627",
      Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "Moderate" ~ "Moderate 589-757",
      Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "High" ~ "High 589-757",
      Land_Coverage_Category == "Sagebrush Shrubland" & Burn_Severity == "Unburned" ~ "Unburned 25",
      Land_Coverage_Category == "Sagebrush Shrubland" & Burn_Severity == "Low" ~ "Low 308-502",
      Land_Coverage_Category == "Sagebrush Shrubland" & Burn_Severity == "Moderate" ~ "Moderate 512-547",
      TRUE ~ as.character(Burn_Severity)),
    Burn_Severity = factor(Burn_Severity, levels = c("Unburned 25", "Low 295-627", "Low 308-502", "Moderate 589-757",
                                                     "Moderate 512-547", "High 589-757")))

pH_BS<-ggplot(data_pH, aes(x=Burn_Severity, y=pH, fill=Burn_Severity))+geom_boxplot()+theme_classic()+ xlab("Burn Severity")+scale_fill_manual(values=c("#0a9396", "#ffba08", "#ffba08", "#e85d04", "#e85d04","#9d0208"))+facet_grid(.~Land_Coverage_Category, scales = "free") +
    scale_x_discrete(labels = split_labels_with_parentheses) +
    theme(
        text = element_text(size = 15),
        axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1),  # Tilted 45 degrees
        panel.border = element_rect(color = "black", fill = NA, linewidth = 1)) +
    geom_text(aes(label = Annotation, x = x, y = y), size = 4.5, fontface = "plain")

cowplot::save_plot("../figures/pH_BS.pdf", pH_BS, ncol = 1, nrow = 1, base_height = 5, base_width = 10, dpi=100)


#stats to see relationship of pH with burn severity and ecosystem type 


model<-lmer(log10(pH)~Burn_Severity*Land_Coverage_Category+(1|Parent_ID), data=data)
model.BS<-lmer(log10(pH)~Land_Coverage_Category+(1|Parent_ID), data=data)
model.LC<-lmer(log10(pH)~Burn_Severity+(1|Parent_ID), data=data)
model.int<-lmer(log10(pH)~Burn_Severity+Land_Coverage_Category+(1|Parent_ID), data=data)
anova(model,model.BS)
anova(model,model.LC)
anova(model,model.int)
#check VIF
vif(model)
#model assumptions
hist(log10(data$pH))
#linearity
ggqqplot(residuals(model))
#check homogeneity of variance assumption (homoscedastcity)
plot(fitted(model),residuals(model))
#post hoc tests 
emmeans::lsmeans(model, pairwise~Burn_Severity*Land_Coverage_Category, at=list(Burn_Severity="Unburned"),adjust="tukey") 
emmeans::lsmeans(model, pairwise~Burn_Severity*Land_Coverage_Category, at=list(Burn_Severity="Low"),adjust="tukey")
emmeans::lsmeans(model, pairwise~Burn_Severity*Land_Coverage_Category, at=list(Burn_Severity="Moderate"),adjust="tukey")
emmeans::lsmeans(model, pairwise~Burn_Severity*Land_Coverage_Category, at=list(Land_Coverage_Category="Douglas-fir forest"),adjust="tukey")
emmeans::lsmeans(model, pairwise~Burn_Severity*Land_Coverage_Category, at=list(Land_Coverage_Category="Sagebrush shrubland"),adjust="tukey")
```



####Solid ICP
```{r solid fig and stats}
data_solids_Pconc <- data_solids %>%
  mutate(
    Annotation = case_when(
      Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "Unburned" ~ "a",
      Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "Low" ~ "a",
      Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "Moderate" ~ "a",
      Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "High" ~ "b",
      Land_Coverage_Category == "Sagebrush Shrubland" & Burn_Severity == "Unburned" ~ "a",
      Land_Coverage_Category == "Sagebrush Shrubland" & Burn_Severity == "Low" ~ "b",
      Land_Coverage_Category == "Sagebrush Shrubland" & Burn_Severity == "Moderate" ~ "c"),
    x = case_when(
      Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "Unburned" ~ "Unburned 25",
      Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "Low" ~ "Low 295-627",
      Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "Moderate" ~ "Moderate 589-757",
      Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "High" ~ "High 589-757",
      Land_Coverage_Category == "Sagebrush Shrubland" & Burn_Severity == "Unburned" ~ "Unburned 25",
      Land_Coverage_Category == "Sagebrush Shrubland" & Burn_Severity == "Low" ~ "Low 308-502",
      Land_Coverage_Category == "Sagebrush Shrubland" & Burn_Severity == "Moderate" ~ "Moderate 512-547"),
    y = case_when(
      Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "Unburned" ~ 2.8,
      Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "Low" ~ 3.8,
      Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "Moderate" ~ 3.6,
      Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "High" ~ 9.2,
      Land_Coverage_Category == "Sagebrush Shrubland" & Burn_Severity == "Unburned" ~2.35,
      Land_Coverage_Category == "Sagebrush Shrubland" & Burn_Severity == "Low" ~ 6.9,
      Land_Coverage_Category == "Sagebrush Shrubland" & Burn_Severity == "Moderate" ~ 17.5),
    Burn_Severity = case_when(
      Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "Unburned" ~ "Unburned 25",
      Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "Low" ~ "Low 295-627",
      Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "Moderate" ~ "Moderate 589-757",
      Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "High" ~ "High 589-757",
      Land_Coverage_Category == "Sagebrush Shrubland" & Burn_Severity == "Unburned" ~ "Unburned 25",
      Land_Coverage_Category == "Sagebrush Shrubland" & Burn_Severity == "Low" ~ "Low 308-502",
      Land_Coverage_Category == "Sagebrush Shrubland" & Burn_Severity == "Moderate" ~ "Moderate 512-547",
      TRUE ~ as.character(Burn_Severity)),
    Burn_Severity = factor(Burn_Severity, levels = c("Unburned 25", "Low 295-627", "Low 308-502", "Moderate 589-757",
                                                     "Moderate 512-547", "High 589-757")))

solid.P.BS.fig<-ggplot(data_solids_Pconc, aes(x=Burn_Severity, y=Solid_P_mg_kg/1000, fill=Land_Coverage_Category))+geom_boxplot(show.legend=FALSE)+theme_classic()+ylab(expression(paste(Solid~Total~P~(g~P~kg^-1), sep="")))+ xlab("Burn Severity")+scale_fill_manual(values=c("#9B9B7A","#FFCB69"))+facet_grid(.~Land_Coverage_Category, scales = "free")+
    scale_x_discrete(labels = split_labels_with_parentheses) +
    theme(
        text = element_text(size = 15),
        axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1),  # Tilted 45 degrees
        panel.border = element_rect(color = "black", fill = NA, linewidth = 1)) +
    geom_text(aes(label = Annotation, x = x, y = y), size = 4.5, fontface = "plain")

cowplot::save_plot("../figures/solid.P.BS.fig.pdf", solid.P.BS.fig, ncol = 1, nrow = 1, dpi=100)

#ICP solid total P stats; likely use this one for publication
model<-aov(log10(Solid_P_mg_kg)~Burn_Severity*Land_Coverage_Category, data = data_solids)
summary(model)
#model assumptions
hist(log10(data_solids$Solid_P_mg_kg))
ggqqplot(residuals(model))
#check normality of residuals 
shapiro.test(log10(data_solids$Solid_P_mg_kg)) #p > 0.05 so can assume normality 
#check homogeneity of variance assumption (homoscedastcity)
plot(fitted(model),residuals(model))
performance::check_heteroscedasticity(model) #p > 0.05 so can assume homoscedastic
#interaction post hoc: 
emmeans::emmeans(model, pairwise~Burn_Severity*Land_Coverage_Category, at=list(Burn_Severity="Unburned"),adjust="tukey") 
emmeans::emmeans(model, pairwise~Burn_Severity*Land_Coverage_Category, at=list(Burn_Severity="Low"),adjust="tukey")
emmeans::emmeans(model, pairwise~Burn_Severity*Land_Coverage_Category, at=list(Burn_Severity="Moderate"),adjust="tukey") 
emmeans::emmeans(model, pairwise~Burn_Severity*Land_Coverage_Category, at=list(Land_Coverage_Category="Douglas-fir forest"),adjust="tukey") 
emmeans::emmeans(model, pairwise~Burn_Severity*Land_Coverage_Category, at=list(Land_Coverage_Category="Sagebrush shrubland"),adjust="tukey") 

```

####stacked spectra and pie charts
```{r NMR fig}
#example stacked sample spectra
NMR_spectra_df_subset <-NMR_spectra %>%
  select("Chemical_Shift_parts_per_million", "BSLE_0013-solid", "BSLE_0007-solid","BSLE_0002-solid", "BSLE_0050-solid") %>%
  dplyr::rename('solid_13' = 'BSLE_0013-solid',
                'solid_7' = 'BSLE_0007-solid',
                'solid_2' = 'BSLE_0002-solid',
                'solid_50' = 'BSLE_0050-solid') %>%
  mutate_all(~replace(., . == 0, NA)) %>%
  mutate(solid_13 = solid_13 + 1,
         solid_7 = solid_7 + 75,
         solid_2 = solid_2 + 150,
         solid_50 = solid_50 + 225) 
         
NMR_spectra_df_subset<-melt(NMR_spectra_df_subset, id=c("Chemical_Shift_parts_per_million"))

NMR_spectra_df_subset<-subset(NMR_spectra_df_subset, value!="")

NMR_stacked_spectra_df <- ggplot(NMR_spectra_df_subset, aes(x=Chemical_Shift_parts_per_million, y = value, color = as.factor(variable))) + geom_path()+theme_classic() + ylim(0,300) + scale_x_reverse() +xlim(10,-10) +scale_color_manual(values=c('Black','Black', 'Black', 'Black')) + theme(axis.ticks.y = element_blank(),  axis.text.y = element_blank(), legend.position = "none")  + ylab("") + xlab("Chemical Shift (ppm)")

#cowplot::save_plot("../figures/NMR_stacked_spectra_df.pdf", NMR_stacked_spectra_df, ncol = 1, nrow = 1, base_aspect_ratio= 1:1.7, dpi=72)

pdf(file = "../figures/NMR_stacked_spectra_df.pdf", width = 3.5, height = 7) 
print(NMR_stacked_spectra_df)
dev.off()

NMR_spectra_sb_subset <-NMR_spectra %>%
  select("Chemical_Shift_parts_per_million", "BSLE_0014-solid", "BSLE_0011-solid","BSLE_0072-solid") %>%
  dplyr::rename('solid_14' = 'BSLE_0014-solid',
                'solid_11' = 'BSLE_0011-solid',
                'solid_72' = 'BSLE_0072-solid') %>%
  mutate_all(~replace(., . == 0, NA)) %>%
  mutate(solid_14 = solid_14 + 1,
         solid_11 = solid_11 + 75,
         solid_72 = solid_72 + 150) 
         
NMR_spectra_sb_subset<-melt(NMR_spectra_sb_subset, id=c("Chemical_Shift_parts_per_million"))

NMR_spectra_sb_subset<-subset(NMR_spectra_sb_subset, value!="")

NMR_stacked_spectra_sb <- ggplot(NMR_spectra_sb_subset, aes(x=Chemical_Shift_parts_per_million, y = value, color = as.factor(variable))) + geom_path()+theme_classic() + ylim(0,300) + scale_x_reverse() +xlim(10,-10) +scale_color_manual(values=c('Black','Black', 'Black', 'Black')) + theme(axis.ticks.y = element_blank(),  axis.text.y = element_blank(), legend.position = "none")  + ylab("") + xlab("Chemical Shift (ppm)")

#cowplot::save_plot("../figures/NMR_stacked_spectra_sb.pdf", NMR_stacked_spectra_sb, ncol = 1, nrow = 1, base_aspect_ratio= 1:1.7, dpi=72)

pdf(file = "../figures/NMR_stacked_spectra_sb.pdf", width = 3.5, height = 7) 
print(NMR_stacked_spectra_sb)
dev.off()

#pie charts
NMR <- summary_solids_conc %>%
  select("Land_Coverage_Category", "Burn_Severity","Ortho_Mean", "Mono_Mean", "Di_Mean", "Pyro_Mean") %>%
  dplyr::rename(Ortho = Ortho_Mean,
                Mono = Mono_Mean,
                Di = Di_Mean,
                Pyro = Pyro_Mean)


NMR_melt<-melt(NMR, id=c("Land_Coverage_Category", "Burn_Severity"))

NMR_melt$variable=factor(NMR_melt$variable, levels= c("Ortho", "Pyro", "Mono", "Di"))


"#9B9B7A","#424a26", "#997B66", "#E5C59E"

"#9B9B7A","#424a26",  "#F1DCA7"

"#D9AE94", "#D08C60",  "#997B66"

"#424a26", "#9B9B7A", "#D9AE94", "#F1DCA7", "#FFCB69", "#D08C60", "#997B66", "#E5C59E", "#6E411C", "#925E3A", "#ae6433", "#d07960"

"#493C32", "#675549",  "#C5AC87", "#F1DCA7", "#FFF4DC", "#FFFCF5", "#ae6433"

DF.raw<-subset(NMR_melt, Land_Coverage_Category=="Douglas-fir forest" & Burn_Severity=="Unburned")
nmr.legend<-ggplot(DF.raw, aes(x = "", y = value, fill = variable)) +
    geom_col(color = "black") +
    coord_polar(theta = "y") + scale_fill_manual(values = c("#997B66","#F1DCA7", "#D08C60", "#e2b89d"))+theme_void()+
    theme(legend.key.size = unit(1, 'cm'), #change legend key size
          legend.key.height = unit(1, 'cm'),  legend.title = element_text(size=25),
          legend.key.width = unit(1, 'cm'), #change legend key width
          legend.text = element_text(size=20))+labs(fill="")
pdf(file = "../figures/nmr.legend.pdf", width = 7, height = 3.5) 
print(nmr.legend)
dev.off()

DF.raw.nmr<-ggplot(DF.raw, aes(x = "", y = value, fill = variable)) +
    geom_col(color = "black") +
    coord_polar(theta = "y") + scale_fill_manual(values = c("#997B66","#F1DCA7", "#D08C60", "#e2b89d"))+theme_void()+
    theme(legend.position = "none")
pdf(file = "../figures/DF.raw.nmr.pdf", width = 1, height = 1) 
print(DF.raw.nmr)
dev.off()

DF.low<-subset(NMR_melt, Land_Coverage_Category=="Douglas-fir forest" & Burn_Severity=="Low")
DF.low.nmr<-ggplot(DF.low, aes(x = "", y = value, fill = variable)) +
    geom_col(color = "black") +
    coord_polar(theta = "y") + scale_fill_manual(values = c("#997B66","#F1DCA7", "#D08C60", "#e2b89d"))+theme_void()+
    theme(legend.position = "none")
pdf(file = "../figures/DF.low.nmr.pdf", width = 1, height = 1) 
print(DF.low.nmr)
dev.off()

DF.mod<-subset(NMR_melt, Land_Coverage_Category=="Douglas-fir forest" & Burn_Severity=="Moderate")
DF.mod.nmr<-ggplot(DF.mod, aes(x = "", y = value, fill = variable)) +
    geom_col(color = "black") +
    coord_polar(theta = "y") + scale_fill_manual(values = c("#997B66","#F1DCA7", "#D08C60", "#e2b89d"))+theme_void()+
    theme(legend.position = "none")
pdf(file = "../figures/DF.mod.nmr.pdf", width = 1, height = 1) 
print(DF.mod.nmr)
dev.off()

DF.high<-subset(NMR_melt, Land_Coverage_Category=="Douglas-fir forest" & Burn_Severity=="High")
DF.high.nmr<-ggplot(DF.high, aes(x = "", y = value, fill = variable)) +
    geom_col(color = "black") +
    coord_polar(theta = "y") + scale_fill_manual(values = c("#997B66","#F1DCA7", "#D08C60", "#e2b89d"))+theme_void()+
    theme(legend.position = "none")
pdf(file = "../figures/DF.high.nmr.pdf", width = 1, height = 1) 
print(DF.high.nmr)
dev.off()

SB.raw<-subset(NMR_melt, Land_Coverage_Category=="Sagebrush shrubland" & Burn_Severity=="Unburned")
SB.raw.nmr<-ggplot(SB.raw, aes(x = "", y = value, fill = variable)) +
    geom_col(color = "black") +
    coord_polar(theta = "y") + scale_fill_manual(values = c("#997B66","#F1DCA7", "#D08C60", "#e2b89d"))+theme_void()+
    theme(legend.position = "none")
pdf(file = "../figures/SB.raw.nmr.pdf", width = 1, height = 1) 
print(SB.raw.nmr)
dev.off()

SB.low<-subset(NMR_melt, Land_Coverage_Category=="Sagebrush shrubland" & Burn_Severity=="Low")
SB.low.nmr<-ggplot(SB.low, aes(x = "", y = value, fill = variable)) +
    geom_col(color = "black") +
    coord_polar(theta = "y") + scale_fill_manual(values = c("#997B66","#F1DCA7", "#D08C60", "#e2b89d"))+theme_void()+
    theme(legend.position = "none")
pdf(file = "../figures/SB.low.nmr.pdf", width = 1, height = 1) 
print(SB.low.nmr)
dev.off()

SB.mod<-subset(NMR_melt, Land_Coverage_Category=="Sagebrush shrubland" & Burn_Severity=="Moderate")
SB.mod.nmr<-ggplot(SB.mod, aes(x = "", y = value, fill = variable)) +
    geom_col(color = "black") +
    coord_polar(theta = "y") + scale_fill_manual(values = c("#997B66","#F1DCA7", "#D08C60", "#e2b89d"))+theme_void()+
    theme(legend.position = "none")
pdf(file = "../figures/SB.mod.nmr.pdf", width = 1, height = 1) 
print(SB.mod.nmr)
dev.off()

```

```{r XANES fig}
#example stacked sample spectra
XANES_spectra_df_subset <-XANES_spectra %>%
  select("eV", "BSLE_0013-solid_P-XANES.xmu.nor", "BSLE_0007-solid_P-XANES.xmu.nor","BSLE_0002-solid_P-XANES.xmu.nor", "BSLE_0050-solid_P-XANES.xmu.nor") %>%
  dplyr::rename('solid_13' = 'BSLE_0013-solid_P-XANES.xmu.nor',
                'solid_7' = 'BSLE_0007-solid_P-XANES.xmu.nor',
                'solid_2' = 'BSLE_0002-solid_P-XANES.xmu.nor',
                'solid_50' = 'BSLE_0050-solid_P-XANES.xmu.nor') %>%
  mutate_all(~replace(., . == 0, NA)) %>%
  mutate(solid_13 = solid_13 + 1,
         solid_7 = solid_7 + 8,
         solid_2 = solid_2 + 16,
         solid_50 = solid_50 + 24) 
         
XANES_spectra_df_subset<-melt(XANES_spectra_df_subset, id=c("eV"))

XANES_spectra_df_subset<-subset(XANES_spectra_df_subset, value!="")

XANES_stacked_spectra_df <- ggplot(XANES_spectra_df_subset, aes(x=eV, y = value, color = as.factor(variable))) + geom_path()+theme_classic() + scale_color_manual(values=c('Black','Black', 'Black', 'Black')) + theme(axis.ticks.y = element_blank(),  axis.text.y = element_blank(), legend.position = "none")  + ylab("") + xlab("Energy (eV)") + xlim(2140, 2200) + ylab ("Normalized Absorption (arb. units)")

pdf(file = "../figures/XANES_stacked_spectra_df.pdf", width = 3, height = 7) 
print(XANES_stacked_spectra_df)
dev.off()

XANES_spectra_sb_subset <-XANES_spectra %>%
  select("eV", "BSLE_0014-solid_P-XANES.xmu.nor", "BSLE_0011-solid_P-XANES.xmu.nor","BSLE_0072-solid_P-XANES.xmu.nor") %>%
  dplyr::rename('solid_14' = 'BSLE_0014-solid_P-XANES.xmu.nor',
                'solid_11' = 'BSLE_0011-solid_P-XANES.xmu.nor',
                'solid_72' = 'BSLE_0072-solid_P-XANES.xmu.nor') %>%
  mutate_all(~replace(., . == 0, NA)) %>%
  mutate(blank = solid_72) %>%
  mutate(solid_14 = solid_14 + 1,
         solid_11 = solid_11 + 8,
         solid_72 = solid_72 + 16,
         blank = blank + 24) 
         
XANES_spectra_sb_subset<-melt(XANES_spectra_sb_subset, id=c("eV"))

XANES_spectra_sb_subset<-subset(XANES_spectra_sb_subset, value!="")

XANES_stacked_spectra_sb <- ggplot(XANES_spectra_sb_subset, aes(x=eV, y = value, color = as.factor(variable))) + geom_path()+theme_classic() + scale_color_manual(values=c('Black','Black', 'Black', 'White')) + theme(axis.ticks.y = element_blank(),  axis.text.y = element_blank(), legend.position = "none")  + ylab("") + xlab("Energy (eV)") + xlim(2140, 2200) + ylab ("Normalized Absorption (arb. units)")

#cowplot::save_plot("../figures/NMR_stacked_spectra_sb.pdf", NMR_stacked_spectra_sb, ncol = 1, nrow = 1, base_aspect_ratio= 1:1.7, dpi=72)

pdf(file = "../figures/XANES_stacked_spectra_sb.pdf", width = 3, height = 7) 
print(XANES_stacked_spectra_sb)
dev.off()

#pie charts with Po grouped and inorganic separate metals
XANES <- summary_solids_conc %>%
  select("Land_Coverage_Category", "Burn_Severity","XANES_Pi_K_Mean", "XANES_Pi_Mg_Mean", "XANES_Pi_Al_Mean", "XANES_Pi_Ca_Mean", "XANES_Pi_Na_Mean", "XANES_Pi_Fe_Mean", "XANES_Po_Mean") %>%
  dplyr::rename(K = XANES_Pi_K_Mean,
                Mg = XANES_Pi_Mg_Mean,
                Al = XANES_Pi_Al_Mean,
                Ca = XANES_Pi_Ca_Mean,
                Na = XANES_Pi_Na_Mean,
                Fe = XANES_Pi_Fe_Mean,
                Po = XANES_Po_Mean)

XANES_melt<-melt(XANES, id=c("Land_Coverage_Category", "Burn_Severity"))

#XANES_melt$variable=factor(XANES_melt$variable, levels= c("Ortho", "Pyro", "Mono", "Di"))

DF.raw<-subset(XANES_melt, Land_Coverage_Category=="Douglas-fir forest" & Burn_Severity=="Unburned")
xanes.legend<-ggplot(DF.raw, aes(x = "", y = value, fill = variable)) +
    geom_col(color = "black") +
    coord_polar(theta = "y") + scale_fill_manual(values = c("#493C32", "#87745D",  "#C5AC87", "#F1DCA7", "#FFF4DC", "#FFFCF5", "#ae6433"))+theme_void()+
    theme(legend.key.size = unit(1, 'cm'), #change legend key size
          legend.key.height = unit(1, 'cm'),  legend.title = element_text(size=25),
          legend.key.width = unit(1, 'cm'), #change legend key width
          legend.text = element_text(size=20))+labs(fill="")
pdf(file = "../figures/xanes.legend.pdf", width = 7, height = 3.5) 
print(xanes.legend)
dev.off()



DF.raw.xanes<-ggplot(DF.raw, aes(x = "", y = value, fill = variable)) +
    geom_col(color = "black") +
    coord_polar(theta = "y") + scale_fill_manual(values = c("#493C32", "#87745D",  "#C5AC87", "#F1DCA7", "#FFF4DC", "#FFFCF5", "#ae6433"))+theme_void()+
    theme(legend.position = "none")
pdf(file = "../figures/DF.raw.xanes.pdf", width = 1, height = 1) 
print(DF.raw.xanes)
dev.off()

DF.low<-subset(XANES_melt, Land_Coverage_Category=="Douglas-fir forest" & Burn_Severity=="Low")
DF.low.xanes<-ggplot(DF.low, aes(x = "", y = value, fill = variable)) +
    geom_col(color = "black") +
    coord_polar(theta = "y") + scale_fill_manual(values = c("#493C32", "#87745D",  "#C5AC87", "#F1DCA7", "#FFF4DC", "#FFFCF5", "#ae6433"))+theme_void()+
    theme(legend.position = "none")
pdf(file = "../figures/DF.low.xanes.pdf", width = 1, height = 1) 
print(DF.low.xanes)
dev.off()

DF.mod<-subset(XANES_melt, Land_Coverage_Category=="Douglas-fir forest" & Burn_Severity=="Moderate")
DF.mod.xanes<-ggplot(DF.mod, aes(x = "", y = value, fill = variable)) +
    geom_col(color = "black") +
    coord_polar(theta = "y") + scale_fill_manual(values = c("#493C32", "#87745D",  "#C5AC87", "#F1DCA7", "#FFF4DC", "#FFFCF5", "#ae6433"))+theme_void()+
    theme(legend.position = "none")
pdf(file = "../figures/DF.mod.xanes.pdf", width = 1, height = 1) 
print(DF.mod.xanes)
dev.off()

DF.high<-subset(XANES_melt, Land_Coverage_Category=="Douglas-fir forest" & Burn_Severity=="High")
DF.high.xanes<-ggplot(DF.high, aes(x = "", y = value, fill = variable)) +
    geom_col(color = "black") +
    coord_polar(theta = "y") + scale_fill_manual(values = c("#493C32", "#87745D",  "#C5AC87", "#F1DCA7", "#FFF4DC", "#FFFCF5", "#ae6433"))+theme_void()+
    theme(legend.position = "none")
pdf(file = "../figures/DF.high.xanes.pdf", width = 1, height = 1) 
print(DF.high.xanes)
dev.off()

SB.raw<-subset(XANES_melt, Land_Coverage_Category=="Sagebrush shrubland" & Burn_Severity=="Unburned")
SB.raw.xanes<-ggplot(SB.raw, aes(x = "", y = value, fill = variable)) +
    geom_col(color = "black") +
    coord_polar(theta = "y") + scale_fill_manual(values = c("#493C32", "#87745D",  "#C5AC87", "#F1DCA7", "#FFF4DC", "#FFFCF5", "#ae6433"))+theme_void()+
    theme(legend.position = "none")
pdf(file = "../figures/SB.raw.xanes.pdf", width = 1, height = 1) 
print(SB.raw.xanes)
dev.off()

SB.low<-subset(XANES_melt, Land_Coverage_Category=="Sagebrush shrubland" & Burn_Severity=="Low")
SB.low.xanes<-ggplot(SB.low, aes(x = "", y = value, fill = variable)) +
    geom_col(color = "black") +
    coord_polar(theta = "y") + scale_fill_manual(values = c("#493C32", "#87745D",  "#C5AC87", "#F1DCA7", "#FFF4DC", "#FFFCF5", "#ae6433"))+theme_void()+
    theme(legend.position = "none")
pdf(file = "../figures/SB.low.xanes.pdf", width = 1, height = 1) 
print(SB.low.xanes)
dev.off()

SB.mod<-subset(XANES_melt, Land_Coverage_Category=="Sagebrush shrubland" & Burn_Severity=="Moderate")
SB.mod.xanes<-ggplot(SB.mod, aes(x = "", y = value, fill = variable)) +
    geom_col(color = "black") +
    coord_polar(theta = "y") + scale_fill_manual(values = c("#493C32", "#87745D",  "#C5AC87", "#F1DCA7", "#FFF4DC", "#FFFCF5", "#ae6433"))+theme_void()+
    theme(legend.position = "none")
pdf(file = "../figures/SB.mod.xanes.pdf", width = 1, height = 1) 
print(SB.mod.xanes)
dev.off()
```

###NMR and XANES stats
```{r NMR stats}
#anova to see how NMR species in the solid char is altered by burn severity and land cover; NMR species separate

#model assumptions assessed for: normality of the residuals with qqplot (x = theoretical quantiles, y = sample quantiles; https://sscc.wisc.edu/sscc/pubs/RegDiag-R/normality.html); homoscedasticity with scale location plot (x=fitted values, y=standardized residuals; https://sscc.wisc.edu/sscc/pubs/RegDiag-R/homoscedasticity.html)

#Ortho
model<-aov(rank(Ortho)~Burn_Severity*Land_Coverage_Category, data = data_solids)
summary(model)
#model assumptions
hist(rank(data_solids$Ortho))
ggqqplot(residuals(model))
plot(aov(rank(Ortho)~Burn_Severity*Land_Coverage_Category, data = data_solids))
#burn severity post hoc: 
emmeans::emmeans(model, pairwise~Burn_Severity,adjust="tukey") 

#Mono
model<-aov(log10(Mono+1)~Burn_Severity*Land_Coverage_Category, data = data_solids)
summary(model)
#model assumptions
hist(log10(data_solids$Mono+1))
ggqqplot(residuals(model))
plot(aov(log10(Mono+1)~Burn_Severity*Land_Coverage_Category, data = data_solids))
#post hoc: 
emmeans::emmeans(model, pairwise~Burn_Severity,adjust="tukey") 

#Di
model<-aov(log10(Di+1)~Burn_Severity*Land_Coverage_Category, data = data_solids)
summary(model)
#model assumptions
hist(log10(data_solids$Di+1))
ggqqplot(residuals(model))
plot(aov(log10(Di+1)~Burn_Severity*Land_Coverage_Category, data = data_solids))
#burn severity post hoc: 
emmeans::emmeans(model, pairwise~Burn_Severity,adjust="tukey") 
#land cover post hoc: 
emmeans::emmeans(model, pairwise~Land_Coverage_Category,adjust="tukey") 

#Pyro
model<-aov(log10(Pyro+1)~Burn_Severity*Land_Coverage_Category, data = data_solids)
summary(model)
#model assumptions
hist(log10(data_solids$Pyro+1))
ggqqplot(residuals(model))
plot(aov(log10(Pyro+1)~Burn_Severity*Land_Coverage_Category, data = data_solids))
#burn severity post hoc: 
emmeans::emmeans(model, pairwise~Burn_Severity,adjust="tukey") 
#land cover post hoc: 
emmeans::emmeans(model, pairwise~Land_Coverage_Category,adjust="tukey") 

#Pi
model<-aov(rank(NMR_Pi)~Burn_Severity*Land_Coverage_Category, data = data_solids)
summary(model)
#model assumptions
hist(rank(data_solids$NMR_Pi))
ggqqplot(residuals(model))
plot(aov(rank(NMR_Pi)~Burn_Severity*Land_Coverage_Category, data = data_solids))
#burn severity post hoc: 
emmeans::emmeans(model, pairwise~Burn_Severity,adjust="tukey") 

#Po
model<-aov(log10(NMR_Po+1)~Burn_Severity*Land_Coverage_Category, data = data_solids)
summary(model)
#model assumptions
hist(log10(data_solids$NMR_Po+1))
ggqqplot(residuals(model))
plot(aov(log10(NMR_Po+1)~Burn_Severity*Land_Coverage_Category, data = data_solids))
#burn severity post hoc: 
emmeans::emmeans(model, pairwise~Burn_Severity,adjust="tukey") 



```

```{r XANES stats}
#anova to see how NMR species in the solid char is altered by burn severity and land cover; NMR species separate

#model assumptions assessed for: normality of the residuals with qqplot (x = theoretical quantiles, y = sample quantiles; https://sscc.wisc.edu/sscc/pubs/RegDiag-R/normality.html); homoscedasticity with scale location plot (x=fitted values, y=standardized residuals; https://sscc.wisc.edu/sscc/pubs/RegDiag-R/homoscedasticity.html)

#Ca_Pi
model<-aov(rank(XANES_Pi_Ca)~Burn_Severity*Land_Coverage_Category, data = data_solids)
summary(model)
#model assumptions
hist(rank(data_solids$Ortho))
ggqqplot(residuals(model))
plot(aov(rank(XANES_Pi_Ca)~Burn_Severity*Land_Coverage_Category, data = data_solids))
#burn severity post hoc: 
emmeans::emmeans(model, pairwise~Burn_Severity,adjust="tukey") 

#Mg_Pi
model<-aov(log10(XANES_Pi_Mg+1)~Burn_Severity*Land_Coverage_Category, data = data_solids)
summary(model)
#model assumptions
hist(rank(data_solids$Ortho))
ggqqplot(residuals(model))
plot(aov(log10(XANES_Pi_Mg+1)~Burn_Severity*Land_Coverage_Category, data = data_solids))
#burn severity post hoc: 
emmeans::emmeans(model, pairwise~Burn_Severity,adjust="tukey") 

#Pi
model<-aov(rank(XANES_Pi)~Burn_Severity*Land_Coverage_Category, data = data_solids)
summary(model)
#model assumptions
hist(rank(data_solids$XANES_Pi))
ggqqplot(residuals(model))
plot(aov(rank(XANES_Pi)~Burn_Severity*Land_Coverage_Category, data = data_solids))
#burn severity post hoc: 
emmeans::emmeans(model, pairwise~Burn_Severity,adjust="tukey") 

#Po
model<-aov(log10(XANES_Po+1)~Burn_Severity*Land_Coverage_Category, data = data_solids)
summary(model)
#model assumptions
hist(log10(data_solids$XANES_Po+1))
ggqqplot(residuals(model))
plot(aov(log10(XANES_Po+1)~Burn_Severity*Land_Coverage_Category, data = data_solids))
#burn severity post hoc: 
emmeans::emmeans(model, pairwise~Burn_Severity,adjust="tukey") 
```

###NMR and Ca-P
```{r figure and stats}
#see if there is a correlation between NMR extraction efficiency and Ca-Pi

#figure
XANES_stacked_spectra_rc <- ggplot(data_solids, aes(x = XANES_Pi_Ca, y = NMR_EE_P_perc)) + geom_point() + geom_smooth(method = "lm", se = FALSE) + theme_classic() 

pdf(file = "../figures/XANES_stacked_spectra_rc.pdf", width = 2.25, height = 9) 
print(XANES_stacked_spectra_rc)
dev.off()

#stats
model<-lm(XANES_Pi_Ca ~ NMR_EE_P_perc, data = data_solids)
summary(model)
#model assumptions
hist((data_solids$NMR_EE_P_perc))
ggqqplot(residuals(model))
#check normality of residuals 
shapiro.test(data_solids$NMR_EE_P_perc)#p > 0.05 so can assume normality 
#check homogeneity of variance assumption (homoscedastcity)
plot(fitted(model),residuals(model))
```

###XANES example figs
```{r example RC spectra fig}

#example stacked RC spectra
XANES_spectra_rc_subset <-XANES_rc_spectra %>%
  dplyr::rename('Al' = 'Pi_Al_GibbSorb_std.xmu.nor',
                'Ca' = 'Pi_Apatite_CaDefHydroxy_std.xmu.nor',
                'Fe' = 'Pi_Fe_GoethSorb_std.xmu.nor',
                'K' = 'Pi_K_Pyro_std.xmu.nor',
                'Mg' = 'Pi_NH4_Mg_std.xmu.nor',
                'Mg2' = 'Pi_Mg_Tri_std.xmu.nor',
                'Na' = 'Pi_Na_Tri_std.xmu.nor',
                'Po' = 'Po_Ca_Lecithin_std.xmu.nor') %>%
  mutate_all(~replace(., . == 0, NA)) %>%
  mutate(Po = Po + 1,
         Fe = Fe + 8,
         Na = Na + 16,
         Ca = Ca + 24,
         Al = Al + 32,
         Mg = Mg + 40,
         K = K + 48) 
         
XANES_spectra_rc_subset<-melt(XANES_spectra_rc_subset, id=c("eV"))

XANES_spectra_rc_subset<-subset(XANES_spectra_rc_subset, value!="")

XANES_spectra_rc_subset<-subset(XANES_spectra_rc_subset, variable!="Mg2")

XANES_spectra_rc_subset$variable=factor(XANES_spectra_rc_subset$variable, levels= c("K", "Mg", "Al","Ca", "Na", "Fe", "Po"))

XANES_stacked_spectra_rc <- ggplot(XANES_spectra_rc_subset, aes(x = eV, y = value, color = as.factor(variable))) +
  geom_path(size = 1.25) +
  geom_vline(xintercept = 2152.3, linetype = "dashed", color = "black", size = 1) +  # Add dashed vertical line
  theme_classic() +
  scale_color_manual(values = c("black", "black", "black", "black", "black", "black", "black")) +
  theme(
    axis.ticks.y = element_blank(),
    axis.text.y = element_blank(),
    legend.title = element_blank(),
    legend.position = "none"  # Remove the legend
  ) +
  ylab("") +
  xlab("Energy (eV)") +
  xlim(2140, 2190) +
  ylab("Normalized Absorption (arb. units)") +
  geom_text(aes(x = 2180, y = 51, label = "K-Pi"), size = 5) +
  geom_text(aes(x = 2180, y = 43, label = "Mg-Pi"), size = 5) +
  geom_text(aes(x = 2180, y = 35, label = "Al-Pi"), size = 5) +
  geom_text(aes(x = 2180, y = 27, label = "Ca-Pi"), size = 5) +
  geom_text(aes(x = 2180, y = 19, label = "Na-Pi"), size = 5) +
  geom_text(aes(x = 2180, y = 11, label = "Fe-Pi"), size = 5) +
  geom_text(aes(x = 2180, y = 4, label = "Po"), size = 5)

pdf(file = "../figures/XANES_stacked_spectra_rc.pdf", width = 2.25, height = 9) 
print(XANES_stacked_spectra_rc)
dev.off()

```

```{r Example LCFs}
#COLORS Pi: "#87745D",  "#C5AC87", "#F1DCA7"

#BSLE_0013-solid
BSLE_0013_solid_LCF_combined <- BSLE_0013_solid_LCF %>%
  gather(key = "component", value = "value", BSLE_0013_solid, fit, Po_Na_AMP_std.xmu, Pi_Fe_GoethSorb_std.xmu)

BSLE_0013_solid_LCF_combined<-BSLE_0013_solid_LCF_combined %>%
  mutate(component = ifelse(grepl("BSLE", component), "Sample", component)) %>%
  mutate(component = ifelse(grepl("fit", component), "Fit", component)) %>%
  mutate(component = ifelse(grepl("Pi_K", component), "K-Pi", component)) %>%
  mutate(component = ifelse(grepl("Pi_Mg", component), "Mg-Pi", component)) %>%
  mutate(component = ifelse(grepl("Pi_Al", component), "Al-Pi", component)) %>%
  mutate(component = ifelse(grepl("Pi_Ca", component), "Ca-Pi", component)) %>%
  mutate(component = ifelse(grepl("Apatite", component), "Ca-Pi", component)) %>%
  mutate(component = ifelse(grepl("Pi_Na", component), "Na-Pi", component)) %>%
  mutate(component = ifelse(grepl("Pi_Fe", component), "Fe-Pi", component)) %>%
  mutate(component = ifelse(grepl("Po", component), "Po", component)) %>%
  mutate(component = factor(component, levels = c("Sample", "Fit", "K-Pi", "Mg-Pi", "Al-Pi", "Ca-Pi", "Na-Pi", "Fe-Pi", "Po")))

LCF13<-ggplot(BSLE_0013_solid_LCF_combined, aes(x = eV, y = value, color = component, linetype = component)) +
    geom_line(size=1.5) +
    scale_color_manual(
        values = c("Sample" = "black", "Fit" = "#565e60", "Po" = "#ae6433", "Fe-Pi" = "#493C32"),
        name = NULL  # Remove the legend title
    ) +
    scale_linetype_manual(
        values = c("Sample" = "solid", "Fit" = "dashed", "Po" = "solid", "Fe-Pi" = "solid"),
        name = NULL  # Remove the legend title
    ) +
    xlab("Energy (eV)") +
    xlim(2140, 2200) +
    ylab("Normalized Absorption (arb. units)") +
    theme_classic()+
    theme(axis.text.y = element_blank())  +
  theme(legend.position = c(0.85, 0.85), legend.justification = c(1, 1))

pdf(file = "../figures/LCF13.pdf", width = 3, height = 3) 
print(LCF13)
dev.off()

#BSLE_0007-solid
BSLE_0007_solid_LCF_combined <- BSLE_0007_solid_LCF %>%
  gather(key = "component", value = "value", BSLE_0007_solid, fit, Pi_Na_Tri_std.xmu, Pi_Apatite_CaDefHydroxy_std.xmu, Pi_Al_GibbSorb_std.xmu)

BSLE_0007_solid_LCF_combined<-BSLE_0007_solid_LCF_combined %>%
  mutate(component = ifelse(grepl("BSLE", component), "Sample", component)) %>%
  mutate(component = ifelse(grepl("fit", component), "Fit", component)) %>%
  mutate(component = ifelse(grepl("Pi_K", component), "K-Pi", component)) %>%
  mutate(component = ifelse(grepl("Pi_Mg", component), "Mg-Pi", component)) %>%
  mutate(component = ifelse(grepl("Pi_Al", component), "Al-Pi", component)) %>%
  mutate(component = ifelse(grepl("Pi_Ca", component), "Ca-Pi", component)) %>%
  mutate(component = ifelse(grepl("Apatite", component), "Ca-Pi", component)) %>%
  mutate(component = ifelse(grepl("Pi_Na", component), "Na-Pi", component)) %>%
  mutate(component = ifelse(grepl("Pi_Fe", component), "Fe-Pi", component)) %>%
  mutate(component = ifelse(grepl("Po", component), "Po", component)) %>%
  mutate(component = factor(component, levels = c("Sample", "Fit", "K-Pi", "Mg-Pi", "Al-Pi", "Ca-Pi", "Na-Pi", "Fe-Pi", "Po")))

LCF7<-ggplot(BSLE_0007_solid_LCF_combined, aes(x = eV, y = value, color = component, linetype = component)) +
    geom_line(size=1.5) +
    scale_color_manual(
        values = c("Sample" = "black", "Fit" = "#565e60", "Na-Pi" = "#C5AC87", "Ca-Pi" = "#87745D", "Al-Pi" = "#493C32"), 
        name = NULL  # Remove the legend title
    ) +
    scale_linetype_manual(
        values = c("Sample" = "solid", "Fit" = "dashed", "Na-Pi" = "solid", "Ca-Pi" = "solid", "Al-Pi" = "solid"),
        name = NULL  # Remove the legend title
    ) +
    xlab("Energy (eV)") +
    xlim(2140, 2200) +
    ylab("Normalized Absorption (arb. units)") +
    theme_classic()+
    theme(axis.text.y = element_blank()) +
  theme(legend.position = c(0.85, 0.85), legend.justification = c(1, 1))

pdf(file = "../figures/LCF7.pdf", width = 3, height = 3) 
print(LCF7)
dev.off()


#BSLE_0002-solid
BSLE_0002_solid_LCF_combined <- BSLE_0002_solid_LCF %>%
  gather(key = "component", value = "value", BSLE_0002_solid, fit, Pi_Na_Tri_std.xmu, Pi_Mg_Tri_std.xmu, Pi_Apatite_CaDefHydroxy_std.xmu)

BSLE_0002_solid_LCF_combined<-BSLE_0002_solid_LCF_combined %>%
  mutate(component = ifelse(grepl("BSLE", component), "Sample", component)) %>%
  mutate(component = ifelse(grepl("fit", component), "Fit", component)) %>%
  mutate(component = ifelse(grepl("Pi_K", component), "K-Pi", component)) %>%
  mutate(component = ifelse(grepl("Pi_Mg", component), "Mg-Pi", component)) %>%
  mutate(component = ifelse(grepl("Pi_Al", component), "Al-Pi", component)) %>%
  mutate(component = ifelse(grepl("Pi_Ca", component), "Ca-Pi", component)) %>%
  mutate(component = ifelse(grepl("Apatite", component), "Ca-Pi", component)) %>%
  mutate(component = ifelse(grepl("Pi_Na", component), "Na-Pi", component)) %>%
  mutate(component = ifelse(grepl("Pi_Fe", component), "Fe-Pi", component)) %>%
  mutate(component = ifelse(grepl("Po", component), "Po", component)) %>%
  mutate(component = factor(component, levels = c("Sample", "Fit", "K-Pi", "Mg-Pi", "Al-Pi", "Ca-Pi", "Na-Pi", "Fe-Pi", "Po")))

LCF2<-ggplot(BSLE_0002_solid_LCF_combined, aes(x = eV, y = value, color = component, linetype = component)) +
    geom_line(size=1.5) +
    scale_color_manual(
        values = c("Sample" = "black", "Fit" = "#565e60", "Na-Pi" = "#C5AC87", "Mg-Pi" = "#87745D", "Ca-Pi" = "#493C32"),
        name = NULL  # Remove the legend title
    ) +
    scale_linetype_manual(
        values = c("Sample" = "solid", "Fit" = "dashed", "Na-Pi" = "solid", "Mg-Pi" = "solid", "Ca-Pi" = "solid"),
        name = NULL  # Remove the legend title
    ) +
    xlab("Energy (eV)") +
    xlim(2140, 2200) +
    ylab("Normalized Absorption (arb. units)") +
    theme_classic()+
    theme(axis.text.y = element_blank()) +
  theme(legend.position = c(0.85, 0.85), legend.justification = c(1, 1))

pdf(file = "../figures/LCF2.pdf", width = 3, height = 3) 
print(LCF2)
dev.off()


#BSLE_0050-solid
BSLE_0050_solid_LCF_combined <- BSLE_0050_solid_LCF %>%
  gather(key = "component", value = "value", BSLE_0050_solid, fit, Pi_Mg_Tri_std.xmu, Pi_Ca_Tri_std.xmu, Pi_Apatite_CaDefHydroxy_std.xmu)

BSLE_0050_solid_LCF_combined<-BSLE_0050_solid_LCF_combined %>%
  mutate(component = ifelse(grepl("BSLE", component), "Sample", component)) %>%
  mutate(component = ifelse(grepl("fit", component), "Fit", component)) %>%
  mutate(component = ifelse(grepl("Pi_K", component), "K-Pi", component)) %>%
  mutate(component = ifelse(grepl("Pi_Mg", component), "Mg-Pi", component)) %>%
  mutate(component = ifelse(grepl("Pi_Al", component), "Al-Pi", component)) %>%
  mutate(component = ifelse(grepl("Pi_Ca", component), "Ca-Pi (1)", component)) %>%
  mutate(component = ifelse(grepl("Apatite", component), "Ca-Pi (2)", component)) %>%
  mutate(component = ifelse(grepl("Pi_Na", component), "Na-Pi", component)) %>%
  mutate(component = ifelse(grepl("Pi_Fe", component), "Fe-Pi", component)) %>%
  mutate(component = ifelse(grepl("Po", component), "Po", component)) %>%
  mutate(component = factor(component, levels = c("Sample", "Fit", "K-Pi", "Mg-Pi", "Al-Pi", "Ca-Pi (1)", "Ca-Pi (2)", "Na-Pi", "Fe-Pi", "Po")))

LCF50<-ggplot(BSLE_0050_solid_LCF_combined, aes(x = eV, y = value, color = component, linetype = component)) +
    geom_line(size=1.5) +
    scale_color_manual(
        values = c("Sample" = "black", "Fit" = "#565e60", "Mg-Pi" = "#C5AC87", "Ca-Pi (1)" = "#493C32", "Ca-Pi (2)" = "#87745D"),
        name = NULL  # Remove the legend title
    ) +
    scale_linetype_manual(
        values = c("Sample" = "solid", "Fit" = "dashed", "Mg-Pi" = "solid", "Ca-Pi (1)" = "solid", "Ca-Pi (2)" = "solid"),
        name = NULL  # Remove the legend title
    ) +
    xlab("Energy (eV)") +
    xlim(2140, 2200) +
    ylab("Normalized Absorption (arb. units)") +
    theme_classic()+
    theme(axis.text.y = element_blank()) +
  theme(legend.position = c(0.85, 0.90), legend.justification = c(1, 1))

pdf(file = "../figures/LCF50.pdf", width = 3, height = 3) 
print(LCF50)
dev.off()


#BSLE_0014-solid
BSLE_0014_solid_LCF_combined <- BSLE_0014_solid_LCF %>%
  gather(key = "component", value = "value", BSLE_0014_solid, fit, Po_Na_AMP_std.xmu, Pi_Fe_GoethSorb_std.xmu, Pi_Apatite_CaDefHydroxy_std.xmu)

BSLE_0014_solid_LCF_combined<-BSLE_0014_solid_LCF_combined %>%
  mutate(component = ifelse(grepl("BSLE", component), "Sample", component)) %>%
  mutate(component = ifelse(grepl("fit", component), "Fit", component)) %>%
  mutate(component = ifelse(grepl("Pi_K", component), "K-Pi", component)) %>%
  mutate(component = ifelse(grepl("Pi_Mg", component), "Mg-Pi", component)) %>%
  mutate(component = ifelse(grepl("Pi_Al", component), "Al-Pi", component)) %>%
  mutate(component = ifelse(grepl("Pi_Ca", component), "Ca-Pi", component)) %>%
  mutate(component = ifelse(grepl("Apatite", component), "Ca-Pi", component)) %>%
  mutate(component = ifelse(grepl("Pi_Na", component), "Na-Pi", component)) %>%
  mutate(component = ifelse(grepl("Pi_Fe", component), "Fe-Pi", component)) %>%
  mutate(component = ifelse(grepl("Po", component), "Po", component)) %>%
  mutate(component = factor(component, levels = c("Sample", "Fit", "K-Pi", "Mg-Pi", "Al-Pi", "Ca-Pi", "Na-Pi", "Fe-Pi", "Po")))

LCF14<-ggplot(BSLE_0014_solid_LCF_combined, aes(x = eV, y = value, color = component, linetype = component)) +
    geom_line(size=1.5) +
    scale_color_manual(
        values = c("Sample" = "black", "Fit" = "#565e60", "Po" = "#ae6433", "Fe-Pi" = "#87745D", "Ca-Pi" = "#493C32"),
        name = NULL  # Remove the legend title
    ) +
    scale_linetype_manual(
        values = c("Sample" = "solid", "Fit" = "dashed", "Po" = "solid", "Fe-Pi" = "solid", "Ca-Pi" = "solid"),
        name = NULL  # Remove the legend title
    ) +
    xlab("Energy (eV)") +
    xlim(2140, 2200) +
    ylab("Normalized Absorption (arb. units)") +
    theme_classic()+
    theme(axis.text.y = element_blank()) +
  theme(legend.position = c(0.85, 0.85), legend.justification = c(1, 1))

pdf(file = "../figures/LCF14.pdf", width = 3, height = 3) 
print(LCF14)
dev.off()


#BSLE_0011-solid
BSLE_0011_solid_LCF_combined <- BSLE_0011_solid_LCF %>%
  gather(key = "component", value = "value", BSLE_0011_solid, fit, Pi_Mg_Tri_std.xmu, Pi_K_Pyro_std.xmu, Pi_Apatite_CaDefHydroxy_std.xmu)

BSLE_0011_solid_LCF_combined<-BSLE_0011_solid_LCF_combined %>%
  mutate(component = ifelse(grepl("BSLE", component), "Sample", component)) %>%
  mutate(component = ifelse(grepl("fit", component), "Fit", component)) %>%
  mutate(component = ifelse(grepl("Pi_K", component), "K-Pi", component)) %>%
  mutate(component = ifelse(grepl("Pi_Mg", component), "Mg-Pi", component)) %>%
  mutate(component = ifelse(grepl("Pi_Al", component), "Al-Pi", component)) %>%
  mutate(component = ifelse(grepl("Pi_Ca", component), "Ca-Pi", component)) %>%
  mutate(component = ifelse(grepl("Apatite", component), "Ca-Pi", component)) %>%
  mutate(component = ifelse(grepl("Pi_Na", component), "Na-Pi", component)) %>%
  mutate(component = ifelse(grepl("Pi_Fe", component), "Fe-Pi", component)) %>%
  mutate(component = ifelse(grepl("Po", component), "Po", component)) %>%
  mutate(component = factor(component, levels = c("Sample", "Fit", "K-Pi", "Mg-Pi", "Al-Pi", "Ca-Pi", "Na-Pi", "Fe-Pi", "Po")))

LCF11<-ggplot(BSLE_0011_solid_LCF_combined, aes(x = eV, y = value, color = component, linetype = component)) +
    geom_line(size=1.5) +
    scale_color_manual(
        values = c("Sample" = "black", "Fit" = "#565e60", "Mg-Pi" = "#C5AC87", "K-Pi" = "#87745D", "Ca-Pi" = "#493C32"),
        name = NULL  # Remove the legend title
    ) +
    scale_linetype_manual(
        values = c("Sample" = "solid", "Fit" = "dashed", "Mg-Pi" = "solid", "K-Pi" = "solid", "Ca-Pi" = "solid"),
        name = NULL  # Remove the legend title
    ) +
    xlab("Energy (eV)") +
    xlim(2140, 2200) +
    ylab("Normalized Absorption (arb. units)") +
    theme_classic()+
    theme(axis.text.y = element_blank()) +
  theme(legend.position = c(0.85, 0.85), legend.justification = c(1, 1))

pdf(file = "../figures/LCF11.pdf", width = 3, height = 3) 
print(LCF11)
dev.off()


#BSLE_0072-solid
BSLE_0072_solid_LCF_combined <- BSLE_0072_solid_LCF %>%
  gather(key = "component", value = "value", BSLE_0072_solid, fit, Pi_NH4_Mg_std.xmu, Pi_Apatite_Carbonate_std.xmu, Pi_Apatite_CaDefHydroxy_std.xmu)

BSLE_0072_solid_LCF_combined<-BSLE_0072_solid_LCF_combined %>%
  mutate(component = ifelse(grepl("BSLE", component), "Sample", component)) %>%
  mutate(component = ifelse(grepl("fit", component), "Fit", component)) %>%
  mutate(component = ifelse(grepl("Pi_K", component), "K-Pi", component)) %>%
  mutate(component = ifelse(grepl("Pi_Mg", component), "Mg-Pi", component)) %>%
  mutate(component = ifelse(grepl("Pi_Al", component), "Al-Pi", component)) %>%
  mutate(component = ifelse(grepl("Carbonate", component), "Ca-Pi (1)", component)) %>%
  mutate(component = ifelse(grepl("Hydroxy", component), "Ca-Pi (2)", component)) %>%
  mutate(component = ifelse(grepl("Pi_Na", component), "Na-Pi", component)) %>%
  mutate(component = ifelse(grepl("Pi_Fe", component), "Fe-Pi", component)) %>%
  mutate(component = ifelse(grepl("Po", component), "Po", component)) %>%
  mutate(component = factor(component, levels = c("Sample", "Fit", "K-Pi", "Mg-Pi", "Al-Pi", "Ca-Pi (1)", "Ca-Pi (2)", "Na-Pi", "Fe-Pi", "Po")))

LCF72<-ggplot(BSLE_0072_solid_LCF_combined, aes(x = eV, y = value, color = component, linetype = component)) +
    geom_line(size=1.5) +
    scale_color_manual(
        values = c("Sample" = "black", "Fit" = "#565e60", "NH4-Pi" = "#C5AC87", "Ca-Pi (1)" = "#493C32", "Ca-Pi (2)" = "#87745D"),
        name = NULL  # Remove the legend title
    ) +
    scale_linetype_manual(
        values = c("Sample" = "solid", "Fit" = "dashed", "NH4-Pi" = "solid", "Ca-Pi (1)" = "solid", "Ca-Pi (2)" = "solid"),
        name = NULL  # Remove the legend title
    ) +
    xlab("Energy (eV)") +
    xlim(2140, 2200) +
    ylab("Normalized Absorption (arb. units)") +
    theme_classic()+
    theme(axis.text.y = element_blank()) +
  theme(legend.position = c(0.85, 0.85), legend.justification = c(1, 1))

pdf(file = "../figures/LCF72.pdf", width = 3, height = 3) 
print(LCF72)
dev.off()


```

#NMR percent change
```{r figure}
#figures for percent change with burning
per_change<-data_solids %>%
  select(Land_Coverage_Category, Burn_Severity, mono_per_change, di_per_change) %>%
  filter(Burn_Severity != "Unburned") %>%
  dplyr::rename(Monoester = mono_per_change,
         Diester = di_per_change) %>%
  mutate(
    Burn_Severity = case_when(
      Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "Unburned" ~ "Unburned 25",
      Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "Low" ~ "Low 295-627",
      Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "Moderate" ~ "Moderate 589-757",
      Land_Coverage_Category == "Douglas-fir Forest" & Burn_Severity == "High" ~ "High 589-757",
      Land_Coverage_Category == "Sagebrush Shrubland" & Burn_Severity == "Unburned" ~ "Unburned 25",
      Land_Coverage_Category == "Sagebrush Shrubland" & Burn_Severity == "Low" ~ "Low 308-502",
      Land_Coverage_Category == "Sagebrush Shrubland" & Burn_Severity == "Moderate" ~ "Moderate 512-547",
      TRUE ~ as.character(Burn_Severity)),
    Burn_Severity = factor(Burn_Severity, levels = c("Low 295-627", "Low 308-502", "Moderate 589-757",
                                                     "Moderate 512-547", "High 589-757")))

per_change<-melt(per_change, id=c("Burn_Severity", "Land_Coverage_Category"))

mono_die_loss<- ggplot(per_change, aes(x = Burn_Severity, y = value, fill = variable)) +
  geom_boxplot() +
  theme_classic() +
  ylab("Percent Loss (%)") +
  xlab("Burn Severity") +
  scale_fill_manual(values = c("#D08C60", "#e2b89d")) +
  facet_grid(. ~ Land_Coverage_Category, scales = "free_x") +
  theme(
    text = element_text(size = 15),
    axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1),  # Tilted 45 degrees
    panel.border = element_rect(color = "black", fill = NA, linewidth = 1)
  ) +
  labs(fill = NULL) +
  scale_x_discrete(labels = split_labels_with_parentheses)

pdf(file = "../figures/mono_die_loss.pdf", width = 6, height = 3) 
print(mono_die_loss)
dev.off()
```

```{r stats}
#stats to see if there is a significant difference between monoester and diester loss within a burn severity classification for each ecosystem type separately; two-way ANOVA with interaction
mono_DF<-per_change%>%
  filter(Land_Coverage_Category=="Douglas-fir forest" & variable=="Monoester")


model<- aov(value~Land_Coverage_Category*Burn_Severity, data = per_change)
summary(model)
```


#SEM
```{r path analysis setup}
#reference: https://stats.oarc.ucla.edu/r/seminars/rsem/ #followed Model 4A
#reference: https://kevintshoemaker.github.io/NRES-746/SEM.RMarkdown.html
#reference: https://bookdown.org/jdholster1/idsr/structural-equation-modeling.html

#make dataframe with solid samples (leachate avg) to prevent using same number so many times
leachate_mean <- data %>%
  dplyr::group_by(Parent_ID) %>%
  dplyr::summarize(
    Leachate_mg_P_per_g_P_in_solid_unfilt_Mean = mean(Leachate_mg_P_per_g_P_in_solid_unfilt, na.rm = TRUE),
    Leachate_mg_P_per_g_P_in_solid_part_Mean = mean(Leachate_mg_P_per_g_P_in_solid_part, na.rm = TRUE),
    Leachate_mg_P_per_g_P_in_solid_filt0.7_Mean = mean(Leachate_mg_P_per_g_P_in_solid_filt0.7, na.rm = TRUE),
    Leachate_mg_MBD_per_g_P_in_solid_filt0.7_Mean = mean(Leachate_mg_MBD_per_g_P_in_solid_filt0.7, na.rm = TRUE),
    pH_Mean = mean(pH)
  )

solid <- data_solids %>%
  select(Parent_ID, Land_Coverage_Category, Burn_Severity, Burn_Duration, Char_Max_Temp, Ortho, Mono, Di, Pyro, XANES_Po, XANES_Pi, XANES_Fe, XANES_Na, XANES_Ca, XANES_Al, XANES_Mg, XANES_K, XANES_Pi_Fe, XANES_Pi_Na, XANES_Pi_Ca, XANES_Pi_Al, XANES_Pi_Mg, XANES_Pi_K, XANES_Po_Fe, XANES_Po_Na, XANES_Po_Ca, XANES_Po_Al, XANES_Po_Mg, XANES_Po_K, Solid_P_g_kg, Solid_Ca_g_kg, Solid_Fe_g_kg, Solid_Al_g_kg, Solid_K_g_kg, Solid_Mg_g_kg, Solid_Na_g_kg, Solid_S_g_kg, Solid_C_g_kg, Solid_N_g_kg)
  

data_rda<- solid %>%
  full_join(leachate_mean)

#normalize data
data_rda_sub<-as.data.frame(scale(data_rda[4:44]))

data_rda_combine<-cbind(data_rda[,c(1:3)], data_rda_sub)

#convert categorical variable
data_rda_combine$Burn_Severity=as.numeric(factor(data_rda_combine$Burn_Severity, levels= c("Unburned", "Low", "Moderate", "High")))
data_rda_combine$Land_Coverage_Category=as.numeric(factor(data_rda_combine$Land_Coverage_Category, levels= c("Douglas-fir forest", "Sagebrush shrubland")))

#model interpretation:
#chi-square: The model Chi-squared assesses overall fit and the discrepancy between the sample and fitted covariance matrices. Its p-value should be > .05 (i.e., the hypothesis of a perfect fit cannot be rejected). However, it is quite sensitive to sample size.
#CFI (comparitive fit index): range between 0-1; greater than 0.90 indicate a good fit
#TLI (Tucker Lewis Index): range between 0-1; greater than 0.90 indicate a good fit; if above 1 then round down to 1
#RMSEA (root mean square error of approximation): The Root Mean Square Error of Approximation is a parsimony-adjusted index. Values closer to 0 represent a good fit. It should be < .08 or < .05. The p-value printed with it tests the hypothesis that RMSEA is less than or equal to .05 (a cutoff sometimes used for good fit), and thus should be not significant.

```

```{r BS models}
#SEMs for ecosystems in separate models
DFF_data_rda_combine<-subset(data_rda_combine, Land_Coverage_Category=="1")
SBS_data_rda_combine<-subset(data_rda_combine, Land_Coverage_Category=="2")

#both ecosystems together
#running only the Ca-Pi model
#unfiltered
model <- '
  # Structural Model
    Solid_P_g_kg ~ Burn_Severity
    XANES_Pi_Ca ~ Burn_Severity
    Leachate_mg_P_per_g_P_in_solid_unfilt_Mean ~ XANES_Pi_Ca + Solid_P_g_kg
    
  # Residual Variances
    Solid_P_g_kg~~Solid_P_g_kg  
    XANES_Pi_Ca ~~ XANES_Pi_Ca
    Leachate_mg_P_per_g_P_in_solid_unfilt_Mean ~~ Leachate_mg_P_per_g_P_in_solid_unfilt_Mean
'

# Fit the SEM model
fit <- sem(model, data = data_rda_combine)
#fit<-cfa(model, data = data_rda_combine)

# Summarize the results
summary(fit, fit.measures=TRUE, standardized=TRUE, rsquare=TRUE)
fitMeasures(fit, c("chisq", "cfi", "tli", "rmsea", "aic"))

#visualize it
#labels<-c("Char P","Char Pi-Ca","Aqueous MBD","Burn Severity","Ecosystem Type")
#nodeLabels = labels,
p_pa<-semPlot::semPaths(fit,'std',  edge.label.cex = 1.5,
         label.prop=0.9, rotation = 1, nCharNodes=0,
         equalizeManifests = FALSE, optimizeLatRes = TRUE, 
         edge.width = 0.6, shapeMan = "rectangle", shapeLat = "ellipse", 
         shapeInt = "triangle", sizeInt = 2, sizeLat = 4, 
         curve=2, residuals = FALSE, layout="tree2",
         edge.label.position=0.7, fade = TRUE, colFactor=0.25, 
         node.width = 4)
p_pa2 <- mark_sig(p_pa, fit)
plot(p_pa2)
cowplot::save_plot("../figures/SEM3.pdf", p_pa2, ncol = 1, nrow = 1, base_aspect_ratio= 2:1, dpi=72)

#filtered <0.7 um
model <- '
  # Structural Model
    Solid_P_g_kg ~ Burn_Severity
    XANES_Pi_Ca ~ Burn_Severity
    Leachate_mg_P_per_g_P_in_solid_filt0.7_Mean ~ XANES_Pi_Ca + Solid_P_g_kg
    
  # Residual Variances
    Solid_P_g_kg~~Solid_P_g_kg  
    XANES_Pi_Ca ~~ XANES_Pi_Ca
    Leachate_mg_P_per_g_P_in_solid_filt0.7_Mean ~~ Leachate_mg_P_per_g_P_in_solid_filt0.7_Mean
'

# Fit the SEM model
fit <- sem(model, data = data_rda_combine)
#fit<-cfa(model, data = data_rda_combine)

# Summarize the results
summary(fit, fit.measures=TRUE, standardized=TRUE, rsquare=TRUE)
fitMeasures(fit, c("chisq", "cfi", "tli", "rmsea", "aic"))

#visualize it
#labels<-c("Char P","Char Pi-Ca","Aqueous MBD","Burn Severity","Ecosystem Type")
#nodeLabels = labels,
p_pa<-semPlot::semPaths(fit,'std',  edge.label.cex = 1.5,
         label.prop=0.9, rotation = 1, nCharNodes=0,
         equalizeManifests = FALSE, optimizeLatRes = TRUE, 
         edge.width = 0.6, shapeMan = "rectangle", shapeLat = "ellipse", 
         shapeInt = "triangle", sizeInt = 2, sizeLat = 4, 
         curve=2, residuals = FALSE, layout="tree2",
         edge.label.position=0.7, fade = TRUE, colFactor=0.25, 
         node.width = 4)
p_pa2 <- mark_sig(p_pa, fit)
plot(p_pa2)
cowplot::save_plot("../figures/SEM3.pdf", p_pa2, ncol = 1, nrow = 1, base_aspect_ratio= 2:1, dpi=72)

#particulates
model <- '
  # Structural Model
    Solid_P_g_kg ~ Burn_Severity
    XANES_Pi_Ca ~ Burn_Severity
    Leachate_mg_P_per_g_P_in_solid_part_Mean ~ XANES_Pi_Ca + Solid_P_g_kg
    
  # Residual Variances
    Solid_P_g_kg~~Solid_P_g_kg  
    XANES_Pi_Ca ~~ XANES_Pi_Ca
    Leachate_mg_P_per_g_P_in_solid_part_Mean ~~ Leachate_mg_P_per_g_P_in_solid_part_Mean
'

# Fit the SEM model
fit <- sem(model, data = data_rda_combine)
#fit<-cfa(model, data = data_rda_combine)

# Summarize the results
summary(fit, fit.measures=TRUE, standardized=TRUE, rsquare=TRUE)
fitMeasures(fit, c("chisq", "cfi", "tli", "rmsea", "aic"))

#visualize it
#labels<-c("Char P","Char Pi-Ca","Aqueous MBD","Burn Severity","Ecosystem Type")
#nodeLabels = labels,
p_pa<-semPlot::semPaths(fit,'std',  edge.label.cex = 1.5,
         label.prop=0.9, rotation = 1, nCharNodes=0,
         equalizeManifests = FALSE, optimizeLatRes = TRUE, 
         edge.width = 0.6, shapeMan = "rectangle", shapeLat = "ellipse", 
         shapeInt = "triangle", sizeInt = 2, sizeLat = 4, 
         curve=2, residuals = FALSE, layout="tree2",
         edge.label.position=0.7, fade = TRUE, colFactor=0.25, 
         node.width = 4)
p_pa2 <- mark_sig(p_pa, fit)
plot(p_pa2)
cowplot::save_plot("../figures/SEM3.pdf", p_pa2, ncol = 1, nrow = 1, base_aspect_ratio= 2:1, dpi=72)

#molybdate
model <- '
  # Structural Model
    Solid_P_g_kg ~ Burn_Severity
    XANES_Pi_Ca ~ Burn_Severity
    Leachate_mg_MBD_per_g_P_in_solid_filt0.7_Mean ~ XANES_Pi_Ca + Solid_P_g_kg
    
  # Residual Variances
    Solid_P_g_kg~~Solid_P_g_kg  
    XANES_Pi_Ca ~~ XANES_Pi_Ca
    Leachate_mg_MBD_per_g_P_in_solid_filt0.7_Mean ~~ Leachate_mg_MBD_per_g_P_in_solid_filt0.7_Mean
'

# Fit the SEM model
fit <- sem(model, data = data_rda_combine)
#fit<-cfa(model, data = data_rda_combine)

# Summarize the results
summary(fit, fit.measures=TRUE, standardized=TRUE, rsquare=TRUE)
fitMeasures(fit, c("chisq", "cfi", "tli", "rmsea", "aic"))

#visualize it
#labels<-c("Char P","Char Pi-Ca","Aqueous MBD","Burn Severity","Ecosystem Type")
#nodeLabels = labels,
p_pa<-semPlot::semPaths(fit,'std',  edge.label.cex = 1.5,
         label.prop=0.9, rotation = 1, nCharNodes=0,
         equalizeManifests = FALSE, optimizeLatRes = TRUE, 
         edge.width = 0.6, shapeMan = "rectangle", shapeLat = "ellipse", 
         shapeInt = "triangle", sizeInt = 2, sizeLat = 4, 
         curve=2, residuals = FALSE, layout="tree2",
         edge.label.position=0.7, fade = TRUE, colFactor=0.25, 
         node.width = 4)
p_pa2 <- mark_sig(p_pa, fit)
plot(p_pa2)
cowplot::save_plot("../figures/SEM3.pdf", p_pa2, ncol = 1, nrow = 1, base_aspect_ratio= 2:1, dpi=72)



#split up by ecosystem and rerun the same models as above
#DFF
#unfiltered
model <- '
  # Structural Model
    Solid_P_g_kg ~ Burn_Severity
    XANES_Pi_Ca ~ Burn_Severity
    Leachate_mg_P_per_g_P_in_solid_unfilt_Mean ~ XANES_Pi_Ca + Solid_P_g_kg
    
  # Residual Variances
    Solid_P_g_kg~~Solid_P_g_kg  
    XANES_Pi_Ca ~~ XANES_Pi_Ca
    Leachate_mg_P_per_g_P_in_solid_unfilt_Mean ~~ Leachate_mg_P_per_g_P_in_solid_unfilt_Mean
'

# Fit the SEM model
fit <- sem(model, data = DFF_data_rda_combine)
#fit<-cfa(model, data = data_rda_combine)

# Summarize the results
summary(fit, fit.measures=TRUE, standardized=TRUE, rsquare=TRUE)
fitMeasures(fit, c("chisq", "cfi", "tli", "rmsea", "aic"))

#visualize it
#labels<-c("Char P","Char Pi-Ca","Aqueous MBD","Burn Severity","Ecosystem Type")
#nodeLabels = labels,
p_pa<-semPlot::semPaths(fit,'std',  edge.label.cex = 1.5,
         label.prop=0.9, rotation = 1, nCharNodes=0,
         equalizeManifests = FALSE, optimizeLatRes = TRUE, 
         edge.width = 0.6, shapeMan = "rectangle", shapeLat = "ellipse", 
         shapeInt = "triangle", sizeInt = 2, sizeLat = 4, 
         curve=2, residuals = FALSE, layout="tree2",
         edge.label.position=0.7, fade = TRUE, colFactor=0.25, 
         node.width = 4)
p_pa2 <- mark_sig(p_pa, fit)
plot(p_pa2)
cowplot::save_plot("../figures/SEM3.pdf", p_pa2, ncol = 1, nrow = 1, base_aspect_ratio= 2:1, dpi=72)

#filtered <0.7 um
model <- '
  # Structural Model
    Solid_P_g_kg ~ Burn_Severity
    XANES_Pi_Ca ~ Burn_Severity
    Leachate_mg_P_per_g_P_in_solid_filt0.7_Mean ~ XANES_Pi_Ca + Solid_P_g_kg
    
  # Residual Variances
    Solid_P_g_kg~~Solid_P_g_kg  
    XANES_Pi_Ca ~~ XANES_Pi_Ca
    Leachate_mg_P_per_g_P_in_solid_filt0.7_Mean ~~ Leachate_mg_P_per_g_P_in_solid_filt0.7_Mean
'

# Fit the SEM model
fit <- sem(model, data = DFF_data_rda_combine)
#fit<-cfa(model, data = data_rda_combine)

# Summarize the results
summary(fit, fit.measures=TRUE, standardized=TRUE, rsquare=TRUE)
fitMeasures(fit, c("chisq", "cfi", "tli", "rmsea", "aic"))

#visualize it
#labels<-c("Char P","Char Pi-Ca","Aqueous MBD","Burn Severity","Ecosystem Type")
#nodeLabels = labels,
p_pa<-semPlot::semPaths(fit,'std',  edge.label.cex = 1.5,
         label.prop=0.9, rotation = 1, nCharNodes=0,
         equalizeManifests = FALSE, optimizeLatRes = TRUE, 
         edge.width = 0.6, shapeMan = "rectangle", shapeLat = "ellipse", 
         shapeInt = "triangle", sizeInt = 2, sizeLat = 4, 
         curve=2, residuals = FALSE, layout="tree2",
         edge.label.position=0.7, fade = TRUE, colFactor=0.25, 
         node.width = 4)
p_pa2 <- mark_sig(p_pa, fit)
plot(p_pa2)
cowplot::save_plot("../figures/SEM3.pdf", p_pa2, ncol = 1, nrow = 1, base_aspect_ratio= 2:1, dpi=72)

#particulates
model <- '
  # Structural Model
    Solid_P_g_kg ~ Burn_Severity
    XANES_Pi_Ca ~ Burn_Severity
    Leachate_mg_P_per_g_P_in_solid_part_Mean ~ XANES_Pi_Ca + Solid_P_g_kg
    
  # Residual Variances
    Solid_P_g_kg~~Solid_P_g_kg  
    XANES_Pi_Ca ~~ XANES_Pi_Ca
    Leachate_mg_P_per_g_P_in_solid_part_Mean ~~ Leachate_mg_P_per_g_P_in_solid_part_Mean
'

# Fit the SEM model
fit <- sem(model, data = DFF_data_rda_combine)
#fit<-cfa(model, data = data_rda_combine)

# Summarize the results
summary(fit, fit.measures=TRUE, standardized=TRUE, rsquare=TRUE)
fitMeasures(fit, c("chisq", "cfi", "tli", "rmsea", "aic"))

#visualize it
#labels<-c("Char P","Char Pi-Ca","Aqueous MBD","Burn Severity","Ecosystem Type")
#nodeLabels = labels,
p_pa<-semPlot::semPaths(fit,'std',  edge.label.cex = 1.5,
         label.prop=0.9, rotation = 1, nCharNodes=0,
         equalizeManifests = FALSE, optimizeLatRes = TRUE, 
         edge.width = 0.6, shapeMan = "rectangle", shapeLat = "ellipse", 
         shapeInt = "triangle", sizeInt = 2, sizeLat = 4, 
         curve=2, residuals = FALSE, layout="tree2",
         edge.label.position=0.7, fade = TRUE, colFactor=0.25, 
         node.width = 4)
p_pa2 <- mark_sig(p_pa, fit)
plot(p_pa2)
cowplot::save_plot("../figures/SEM3.pdf", p_pa2, ncol = 1, nrow = 1, base_aspect_ratio= 2:1, dpi=72)

#molybdate
model <- '
  # Structural Model
    Solid_P_g_kg ~ Burn_Severity
    XANES_Pi_Ca ~ Burn_Severity
    Leachate_mg_MBD_per_g_P_in_solid_filt0.7_Mean ~ XANES_Pi_Ca + Solid_P_g_kg
    
  # Residual Variances
    Solid_P_g_kg~~Solid_P_g_kg  
    XANES_Pi_Ca ~~ XANES_Pi_Ca
    Leachate_mg_MBD_per_g_P_in_solid_filt0.7_Mean ~~ Leachate_mg_MBD_per_g_P_in_solid_filt0.7_Mean
'

# Fit the SEM model
fit <- sem(model, data = DFF_data_rda_combine)
#fit<-cfa(model, data = data_rda_combine)

# Summarize the results
summary(fit, fit.measures=TRUE, standardized=TRUE, rsquare=TRUE)
fitMeasures(fit, c("chisq", "cfi", "tli", "rmsea", "aic"))

#visualize it
#labels<-c("Char P","Char Pi-Ca","Aqueous MBD","Burn Severity","Ecosystem Type")
#nodeLabels = labels,
p_pa<-semPlot::semPaths(fit,'std',  edge.label.cex = 1.5,
         label.prop=0.9, rotation = 1, nCharNodes=0,
         equalizeManifests = FALSE, optimizeLatRes = TRUE, 
         edge.width = 0.6, shapeMan = "rectangle", shapeLat = "ellipse", 
         shapeInt = "triangle", sizeInt = 2, sizeLat = 4, 
         curve=2, residuals = FALSE, layout="tree2",
         edge.label.position=0.7, fade = TRUE, colFactor=0.25, 
         node.width = 4)
p_pa2 <- mark_sig(p_pa, fit)
plot(p_pa2)
cowplot::save_plot("../figures/SEM3.pdf", p_pa2, ncol = 1, nrow = 1, base_aspect_ratio= 2:1, dpi=72)

#SBS
#unfiltered
model <- '
  # Structural Model
    Solid_P_g_kg ~ Burn_Severity
    XANES_Pi_Ca ~ Burn_Severity
    Leachate_mg_P_per_g_P_in_solid_unfilt_Mean ~ XANES_Pi_Ca + Solid_P_g_kg
    
  # Residual Variances
    Solid_P_g_kg~~Solid_P_g_kg  
    XANES_Pi_Ca ~~ XANES_Pi_Ca
    Leachate_mg_P_per_g_P_in_solid_unfilt_Mean ~~ Leachate_mg_P_per_g_P_in_solid_unfilt_Mean
'

# Fit the SEM model
fit <- sem(model, data = SBS_data_rda_combine)
#fit<-cfa(model, data = data_rda_combine)

# Summarize the results
summary(fit, fit.measures=TRUE, standardized=TRUE, rsquare=TRUE)
fitMeasures(fit, c("chisq", "cfi", "tli", "rmsea", "aic"))

#visualize it
#labels<-c("Char P","Char Pi-Ca","Aqueous MBD","Burn Severity","Ecosystem Type")
#nodeLabels = labels,
p_pa<-semPlot::semPaths(fit,'std',  edge.label.cex = 1.5,
         label.prop=0.9, rotation = 1, nCharNodes=0,
         equalizeManifests = FALSE, optimizeLatRes = TRUE, 
         edge.width = 0.6, shapeMan = "rectangle", shapeLat = "ellipse", 
         shapeInt = "triangle", sizeInt = 2, sizeLat = 4, 
         curve=2, residuals = FALSE, layout="tree2",
         edge.label.position=0.7, fade = TRUE, colFactor=0.25, 
         node.width = 4)
p_pa2 <- mark_sig(p_pa, fit)
plot(p_pa2)
cowplot::save_plot("../figures/SEM3.pdf", p_pa2, ncol = 1, nrow = 1, base_aspect_ratio= 2:1, dpi=72)

#filtered <0.7 um
model <- '
  # Structural Model
    Solid_P_g_kg ~ Burn_Severity
    XANES_Pi_Ca ~ Burn_Severity
    Leachate_mg_P_per_g_P_in_solid_filt0.7_Mean ~ XANES_Pi_Ca + Solid_P_g_kg
    
  # Residual Variances
    Solid_P_g_kg~~Solid_P_g_kg  
    XANES_Pi_Ca ~~ XANES_Pi_Ca
    Leachate_mg_P_per_g_P_in_solid_filt0.7_Mean ~~ Leachate_mg_P_per_g_P_in_solid_filt0.7_Mean
'

# Fit the SEM model
fit <- sem(model, data = SBS_data_rda_combine)
#fit<-cfa(model, data = data_rda_combine)

# Summarize the results
summary(fit, fit.measures=TRUE, standardized=TRUE, rsquare=TRUE)
fitMeasures(fit, c("chisq", "cfi", "tli", "rmsea", "aic"))

#visualize it
#labels<-c("Char P","Char Pi-Ca","Aqueous MBD","Burn Severity","Ecosystem Type")
#nodeLabels = labels,
p_pa<-semPlot::semPaths(fit,'std',  edge.label.cex = 1.5,
         label.prop=0.9, rotation = 1, nCharNodes=0,
         equalizeManifests = FALSE, optimizeLatRes = TRUE, 
         edge.width = 0.6, shapeMan = "rectangle", shapeLat = "ellipse", 
         shapeInt = "triangle", sizeInt = 2, sizeLat = 4, 
         curve=2, residuals = FALSE, layout="tree2",
         edge.label.position=0.7, fade = TRUE, colFactor=0.25, 
         node.width = 4)
p_pa2 <- mark_sig(p_pa, fit)
plot(p_pa2)
cowplot::save_plot("../figures/SEM3.pdf", p_pa2, ncol = 1, nrow = 1, base_aspect_ratio= 2:1, dpi=72)

#particulates
model <- '
  # Structural Model
    Solid_P_g_kg ~ Burn_Severity
    XANES_Pi_Ca ~ Burn_Severity
    Leachate_mg_P_per_g_P_in_solid_part_Mean ~ XANES_Pi_Ca + Solid_P_g_kg
    
  # Residual Variances
    Solid_P_g_kg~~Solid_P_g_kg  
    XANES_Pi_Ca ~~ XANES_Pi_Ca
    Leachate_mg_P_per_g_P_in_solid_part_Mean ~~ Leachate_mg_P_per_g_P_in_solid_part_Mean
'

# Fit the SEM model
fit <- sem(model, data = SBS_data_rda_combine)
#fit<-cfa(model, data = data_rda_combine)

# Summarize the results
summary(fit, fit.measures=TRUE, standardized=TRUE, rsquare=TRUE)
fitMeasures(fit, c("chisq", "cfi", "tli", "rmsea", "aic"))

#visualize it
#labels<-c("Char P","Char Pi-Ca","Aqueous MBD","Burn Severity","Ecosystem Type")
#nodeLabels = labels,
p_pa<-semPlot::semPaths(fit,'std',  edge.label.cex = 1.5,
         label.prop=0.9, rotation = 1, nCharNodes=0,
         equalizeManifests = FALSE, optimizeLatRes = TRUE, 
         edge.width = 0.6, shapeMan = "rectangle", shapeLat = "ellipse", 
         shapeInt = "triangle", sizeInt = 2, sizeLat = 4, 
         curve=2, residuals = FALSE, layout="tree2",
         edge.label.position=0.7, fade = TRUE, colFactor=0.25, 
         node.width = 4)
p_pa2 <- mark_sig(p_pa, fit)
plot(p_pa2)
cowplot::save_plot("../figures/SEM3.pdf", p_pa2, ncol = 1, nrow = 1, base_aspect_ratio= 2:1, dpi=72)

#molybdate
model <- '
  # Structural Model
    Solid_P_g_kg ~ Burn_Severity
    XANES_Pi_Ca ~ Burn_Severity
    Leachate_mg_MBD_per_g_P_in_solid_filt0.7_Mean ~ XANES_Pi_Ca + Solid_P_g_kg
    
  # Residual Variances
    Solid_P_g_kg~~Solid_P_g_kg  
    XANES_Pi_Ca ~~ XANES_Pi_Ca
    Leachate_mg_MBD_per_g_P_in_solid_filt0.7_Mean ~~ Leachate_mg_MBD_per_g_P_in_solid_filt0.7_Mean
'

# Fit the SEM model
fit <- sem(model, data = SBS_data_rda_combine)
#fit<-cfa(model, data = data_rda_combine)

# Summarize the results
summary(fit, fit.measures=TRUE, standardized=TRUE, rsquare=TRUE)
fitMeasures(fit, c("chisq", "cfi", "tli", "rmsea", "aic"))

#visualize it
#labels<-c("Char P","Char Pi-Ca","Aqueous MBD","Burn Severity","Ecosystem Type")
#nodeLabels = labels,
p_pa<-semPlot::semPaths(fit,'std',  edge.label.cex = 1.5,
         label.prop=0.9, rotation = 1, nCharNodes=0,
         equalizeManifests = FALSE, optimizeLatRes = TRUE, 
         edge.width = 0.6, shapeMan = "rectangle", shapeLat = "ellipse", 
         shapeInt = "triangle", sizeInt = 2, sizeLat = 4, 
         curve=2, residuals = FALSE, layout="tree2",
         edge.label.position=0.7, fade = TRUE, colFactor=0.25, 
         node.width = 4)
p_pa2 <- mark_sig(p_pa, fit)
plot(p_pa2)
cowplot::save_plot("../figures/SEM3.pdf", p_pa2, ncol = 1, nrow = 1, base_aspect_ratio= 2:1, dpi=72)


#OTHER OPTIONS FOR MODEL SETUPS
#Model 1: chemistry = XANES Pi
model <- '
  # Structural Model
    Solid_P_g_kg ~ Burn_Severity
    XANES_Pi ~ Burn_Severity
    Leachate_mg_P_per_g_P_in_solid_unfilt_Mean ~ XANES_Pi + Solid_P_g_kg
    
  # Residual Variances
    Solid_P_g_kg~~Solid_P_g_kg
    XANES_Pi ~~ XANES_Pi
    Leachate_P_mg_kgchar_unfilt_Mean ~~ Leachate_P_mg_kgchar_unfilt_Mean
'

#Model 2: chemistry = XANES Po
model <- '
  # Structural Model
    Solid_P_g_kg ~ Burn_Severity
    XANES_Po ~ Burn_Severity
    Leachate_P_mg_kgchar_unfilt_Mean ~ XANES_Po + Solid_P_g_kg
    
  # Residual Variances
    Solid_P_g_kg~~Solid_P_g_kg
    XANES_Po ~~ XANES_Po
    Leachate_P_mg_kgchar_unfilt_Mean ~~ Leachate_P_mg_kgchar_unfilt_Mean
'

#Model 3A: chemistry = XANES Pi_Ca
model <- '
  # Structural Model
    Solid_P_g_kg ~ Burn_Severity
    XANES_Pi_Ca ~ Burn_Severity
    Leachate_P_mg_kgchar_unfilt_Mean ~ XANES_Pi_Ca + Solid_P_g_kg
    
  # Residual Variances
    Solid_P_g_kg~~Solid_P_g_kg  
    XANES_Pi_Ca ~~ XANES_Pi_Ca
    Leachate_P_mg_kgchar_unfilt_Mean ~~ Leachate_P_mg_kgchar_unfilt_Mean
'

#Model 3: chemistry = XANES Pi_Mg + Pi_Ca
model <- '
  # Measurement Model; set up the latent variable(s)
    Pi =~ XANES_Pi_Ca + XANES_Pi_Mg
  
  # Structural Model
    Solid_P_g_kg ~ Burn_Severity
    Pi ~ Burn_Severity
    Leachate_P_mg_kgchar_unfilt_Mean ~ Pi + Solid_P_g_kg
    
  # Residual Variances
    Solid_P_g_kg~~Solid_P_g_kg
    XANES_Pi_Ca ~~ XANES_Pi_Ca
    XANES_Pi_Mg ~~ XANES_Pi_Mg
    Leachate_P_mg_kgchar_unfilt_Mean ~~ Leachate_P_mg_kgchar_unfilt_Mean
'

#Model 4: chemistry = XANES Mg + Ca
model <- '
  # Measurement Model; set up the latent variable(s)
    Pi =~ XANES_Ca + XANES_Mg
  
  # Structural Model
    Solid_P_g_kg ~ Burn_Severity
    Pi ~ Burn_Severity
    Leachate_P_mg_kgchar_unfilt_Mean ~ Pi + Solid_P_g_kg
    
  # Residual Variances
    Solid_P_g_kg~~Solid_P_g_kg
    XANES_Ca ~~ XANES_Ca
    XANES_Mg ~~ XANES_Mg
    Leachate_P_mg_kgchar_unfilt_Mean ~~ Leachate_P_mg_kgchar_unfilt_Mean
'

#Model 5: chemistry = NMR Pi
model <- '
  # Structural Model
    Solid_P_g_kg ~ Burn_Severity
    NMR_Pi ~ Burn_Severity
    Leachate_P_mg_kgchar_unfilt_Mean ~ NMR_Pi + Solid_P_g_kg
    
  # Residual Variances
    Solid_P_g_kg~~Solid_P_g_kg
    NMR_Pi ~~ NMR_Pi
    Leachate_P_mg_kgchar_unfilt_Mean ~~ Leachate_P_mg_kgchar_unfilt_Mean
'

#Model 6: chemistry = NMR Po
model <- '
  # Structural Model
    Solid_P_g_kg ~ Burn_Severity
    NMR_Po ~ Burn_Severity
    Leachate_P_mg_kgchar_unfilt_Mean ~ NMR_Po + Solid_P_g_kg
    
  # Residual Variances
    Solid_P_g_kg~~Solid_P_g_kg
    NMR_Po ~~ NMR_Po
    Leachate_P_mg_kgchar_unfilt_Mean ~~ Leachate_P_mg_kgchar_unfilt_Mean
'

#Model 7: chemistry = NMR monoesters
model <- '
  # Structural Model
    Solid_P_g_kg ~ Burn_Severity
    Mono ~ Burn_Severity
    Leachate_P_mg_kgchar_unfilt_Mean ~ Mono + Solid_P_g_kg
    
  # Residual Variances
    Solid_P_g_kg~~Solid_P_g_kg
    Mono ~~ Mono
    Leachate_P_mg_kgchar_unfilt_Mean ~~ Leachate_P_mg_kgchar_unfilt_Mean
'

#Model 8: chemistry = NMR diesters
model <- '
  # Structural Model
    Solid_P_g_kg ~ Burn_Severity
    Di ~ Burn_Severity
    Leachate_P_mg_kgchar_unfilt_Mean ~ Di + Solid_P_g_kg
    
  # Residual Variances
    Solid_P_g_kg~~Solid_P_g_kg
    Di ~~ Di
    Leachate_P_mg_kgchar_unfilt_Mean ~~ Leachate_P_mg_kgchar_unfilt_Mean
'

#Model 9: chemistry = NMR Mono + NMR Di
model <- '
  # Measurement Model; set up the latent variable(s)
    P =~ Mono + Di
  
  # Structural Model
    Solid_P_g_kg ~ Burn_Severity
    P ~ Burn_Severity
    Leachate_P_mg_kgchar_unfilt_Mean ~ P + Solid_P_g_kg
    
  # Residual Variances
    Solid_P_g_kg~~Solid_P_g_kg
    Mono ~~ Mono
    Di ~~ Di
    Leachate_P_mg_kgchar_unfilt_Mean ~~ Leachate_P_mg_kgchar_unfilt_Mean
'

#alternative plot options

semPlot::semPaths(fit, what = "path", whatLabels = "std", style = "lisrel", edge.label.cex = 1, rotation = 2, curve = 2, layoutSplit = FALSE, normalize = FALSE, height = 9, width = 6.5, residScale = 10, edge.label.color = "black")

semPlot::semPaths(fit, style="lisrel", 
        whatLabels = "std", edge.label.cex = 1,  
        label.prop=0.9, edge.label.color = "black", rotation = 4, 
        equalizeManifests = FALSE, optimizeLatRes = TRUE, node.width = 1.5, 
        edge.width = 0.5, shapeMan = "rectangle", shapeLat = "ellipse", 
        shapeInt = "triangle", sizeMan = 4, sizeInt = 2, sizeLat = 4, 
        curve=2, unCol = "#070b8c")

semPaths(object = fit, what = "std", sizeMan = 10,sizeLat = 10,sizeInt = 10, edge.label.cex = 1.5)
```

```{r BS and Ecosystem models}
#Model: chemistry = XANES Pi_Ca only

#unfiltered
model <- '
  # Structural Model
    Solid_P_g_kg ~ Burn_Severity
    XANES_Pi_Ca ~ Burn_Severity
    Solid_P_g_kg ~ Land_Coverage_Category
    XANES_Pi_Ca ~ Land_Coverage_Category
    Leachate_mg_P_per_g_P_in_solid_unfilt_Mean ~ XANES_Pi_Ca + Solid_P_g_kg
    
  # Residual Variances
    Solid_P_g_kg~~Solid_P_g_kg  
    XANES_Pi_Ca ~~ XANES_Pi_Ca
    Leachate_mg_P_per_g_P_in_solid_unfilt_Mean ~~ Leachate_mg_P_per_g_P_in_solid_unfilt_Mean
    
  #covariance
    Burn_Severity~~Land_Coverage_Category
'

# Fit the SEM model
fit <- sem(model, data = data_rda_combine)
#fit<-cfa(model, data = data_rda_combine)

# Summarize the results
summary(fit, fit.measures=TRUE, standardized=TRUE, rsquare=TRUE)
fitMeasures(fit, c("chisq", "cfi", "tli", "rmsea", "aic"))

#visualize it
#labels<-c("Char P","Char Pi-Ca","Aqueous MBD","Burn Severity","Ecosystem Type")
#nodeLabels = labels,
p_pa<-semPlot::semPaths(fit,'std',  edge.label.cex = 1.5,
         label.prop=0.9, rotation = 1, nCharNodes=0,
         equalizeManifests = FALSE, optimizeLatRes = TRUE, 
         edge.width = 0.6, shapeMan = "rectangle", shapeLat = "ellipse", 
         shapeInt = "triangle", sizeInt = 2, sizeLat = 4, 
         curve=2, residuals = FALSE, layout="tree2",
         edge.label.position=0.7, fade = TRUE, colFactor=0.25, 
         node.width = 4)
p_pa2 <- mark_sig(p_pa, fit)
plot(p_pa2)

#filtered <0.7 nominal pore size
model <- '
  # Structural Model
    Solid_P_g_kg ~ Burn_Severity
    XANES_Pi_Ca ~ Burn_Severity
    Solid_P_g_kg ~ Land_Coverage_Category
    XANES_Pi_Ca ~ Land_Coverage_Category
    Leachate_mg_P_per_g_P_in_solid_filt0.7_Mean ~ XANES_Pi_Ca + Solid_P_g_kg
    
  # Residual Variances
    Solid_P_g_kg~~Solid_P_g_kg  
    XANES_Pi_Ca ~~ XANES_Pi_Ca
    Leachate_mg_P_per_g_P_in_solid_filt0.7_Mean ~~ Leachate_mg_P_per_g_P_in_solid_filt0.7_Mean
'

# Fit the SEM model
fit <- sem(model, data = data_rda_combine)
#fit<-cfa(model, data = data_rda_combine)

# Summarize the results
summary(fit, fit.measures=TRUE, standardized=TRUE, rsquare=TRUE)
fitMeasures(fit, c("chisq", "cfi", "tli", "rmsea", "aic"))

#visualize it
#labels<-c("Char P","Char Pi-Ca","Aqueous MBD","Burn Severity","Ecosystem Type")
#nodeLabels = labels,
p_pa<-semPlot::semPaths(fit,'std',  edge.label.cex = 1.5,
         label.prop=0.9, rotation = 1, nCharNodes=0,
         equalizeManifests = FALSE, optimizeLatRes = TRUE, 
         edge.width = 0.6, shapeMan = "rectangle", shapeLat = "ellipse", 
         shapeInt = "triangle", sizeInt = 2, sizeLat = 4, 
         curve=2, residuals = FALSE, layout="tree2",
         edge.label.position=0.7, fade = TRUE, colFactor=0.25, 
         node.width = 4)
p_pa2 <- mark_sig(p_pa, fit)
plot(p_pa2)

#particulate (>0.7um nominal pore size)
model <- '
  # Structural Model
    Solid_P_g_kg ~ Burn_Severity
    XANES_Pi_Ca ~ Burn_Severity
    Solid_P_g_kg ~ Land_Coverage_Category
    XANES_Pi_Ca ~ Land_Coverage_Category
    Leachate_mg_P_per_g_P_in_solid_part_Mean ~ XANES_Pi_Ca + Solid_P_g_kg
    
  # Residual Variances
    Solid_P_g_kg~~Solid_P_g_kg  
    XANES_Pi_Ca ~~ XANES_Pi_Ca
    Leachate_mg_P_per_g_P_in_solid_part_Mean ~~ Leachate_mg_P_per_g_P_in_solid_part_Mean
'

# Fit the SEM model
fit <- sem(model, data = data_rda_combine)
#fit<-cfa(model, data = data_rda_combine)

# Summarize the results
summary(fit, fit.measures=TRUE, standardized=TRUE, rsquare=TRUE)
fitMeasures(fit, c("chisq", "cfi", "tli", "rmsea", "aic"))

#visualize it
#labels<-c("Char P","Char Pi-Ca","Aqueous MBD","Burn Severity","Ecosystem Type")
#nodeLabels = labels,
p_pa<-semPlot::semPaths(fit,'std',  edge.label.cex = 1.5,
         label.prop=0.9, rotation = 1, nCharNodes=0,
         equalizeManifests = FALSE, optimizeLatRes = TRUE, 
         edge.width = 0.6, shapeMan = "rectangle", shapeLat = "ellipse", 
         shapeInt = "triangle", sizeInt = 2, sizeLat = 4, 
         curve=2, residuals = FALSE, layout="tree2",
         edge.label.position=0.7, fade = TRUE, colFactor=0.25, 
         node.width = 4)
p_pa2 <- mark_sig(p_pa, fit)
plot(p_pa2)

#molybdate (<0.7um nominal pore size)
model <- '
  # Structural Model
    Solid_P_g_kg ~ Burn_Severity
    XANES_Pi_Ca ~ Burn_Severity
    Solid_P_g_kg ~ Land_Coverage_Category
    XANES_Pi_Ca ~ Land_Coverage_Category
    Leachate_mg_MBD_per_g_P_in_solid_filt0.7_Mean ~ XANES_Pi_Ca + Solid_P_g_kg
    
  # Residual Variances
    Solid_P_g_kg~~Solid_P_g_kg  
    XANES_Pi_Ca ~~ XANES_Pi_Ca
    Leachate_mg_MBD_per_g_P_in_solid_filt0.7_Mean ~~ Leachate_mg_MBD_per_g_P_in_solid_filt0.7_Mean
'

# Fit the SEM model
fit <- sem(model, data = data_rda_combine)
#fit<-cfa(model, data = data_rda_combine)

# Summarize the results
summary(fit, fit.measures=TRUE, standardized=TRUE, rsquare=TRUE)
fitMeasures(fit, c("chisq", "cfi", "tli", "rmsea", "aic"))

#visualize it
#labels<-c("Char P","Char Pi-Ca","Aqueous MBD","Burn Severity","Ecosystem Type")
#nodeLabels = labels,
p_pa<-semPlot::semPaths(fit,'std',  edge.label.cex = 1.5,
         label.prop=0.9, rotation = 1, nCharNodes=0,
         equalizeManifests = FALSE, optimizeLatRes = TRUE, 
         edge.width = 0.6, shapeMan = "rectangle", shapeLat = "ellipse", 
         shapeInt = "triangle", sizeInt = 2, sizeLat = 4, 
         curve=2, residuals = FALSE, layout="tree2",
         edge.label.position=0.7, fade = TRUE, colFactor=0.25, 
         node.width = 4)
p_pa2 <- mark_sig(p_pa, fit)
plot(p_pa2)



#other SEM setup options
#Model 1: chemistry = XANES Pi
model <- '
  # Structural Model
    Solid_P_g_kg ~ Burn_Severity
    XANES_Pi ~ Burn_Severity
    Solid_P_g_kg ~ Land_Coverage_Category
    XANES_Pi ~ Land_Coverage_Category
    Leachate_P_mg_kgchar_unfilt_Mean ~ XANES_Pi + Solid_P_g_kg
    
  # Residual Variances
    Solid_P_g_kg~~Solid_P_g_kg
    XANES_Pi ~~ XANES_Pi
    Leachate_P_mg_kgchar_unfilt_Mean ~~ Leachate_P_mg_kgchar_unfilt_Mean
'

#Model 2: chemistry = XANES Po
model <- '
  # Structural Model
    Solid_P_g_kg ~ Burn_Severity
    XANES_Po ~ Burn_Severity
    Solid_P_g_kg ~ Land_Coverage_Category
    XANES_Po ~ Land_Coverage_Category
    Leachate_P_mg_kgchar_unfilt_Mean ~ XANES_Po + Solid_P_g_kg
    
  # Residual Variances
    Solid_P_g_kg~~Solid_P_g_kg
    XANES_Po ~~ XANES_Po
    Leachate_P_mg_kgchar_unfilt_Mean ~~ Leachate_P_mg_kgchar_unfilt_Mean
'

#Model 3: chemistry = XANES Pi_Mg + Pi_Ca
model <- '
  # Measurement Model; set up the latent variable(s)
    Pi =~ XANES_Pi_Ca + XANES_Pi_Mg
  
  # Structural Model
    Solid_P_g_kg ~ Burn_Severity
    Pi ~ Burn_Severity
    Solid_P_g_kg ~ Land_Coverage_Category
    Pi ~ Land_Coverage_Category
    Leachate_P_mg_kgchar_unfilt_Mean ~ Pi + Solid_P_g_kg
    
  # Residual Variances
    Solid_P_g_kg~~Solid_P_g_kg
    XANES_Pi_Ca ~~ XANES_Pi_Ca
    XANES_Pi_Mg ~~ XANES_Pi_Mg
    Leachate_P_mg_kgchar_unfilt_Mean ~~ Leachate_P_mg_kgchar_unfilt_Mean
'

#Model 4: chemistry = XANES Mg + Ca
model <- '
  # Measurement Model; set up the latent variable(s)
    Pi =~ XANES_Ca + XANES_Mg
  
  # Structural Model
    Solid_P_g_kg ~ Burn_Severity
    Pi ~ Burn_Severity
    Solid_P_g_kg ~ Land_Coverage_Category
    Pi ~ Land_Coverage_Category
    Leachate_P_mg_kgchar_unfilt_Mean ~ Pi + Solid_P_g_kg
    
  # Residual Variances
    Solid_P_g_kg~~Solid_P_g_kg
    XANES_Ca ~~ XANES_Ca
    XANES_Mg ~~ XANES_Mg
    Leachate_P_mg_kgchar_unfilt_Mean ~~ Leachate_P_mg_kgchar_unfilt_Mean
'

#Model 5: chemistry = NMR Pi
model <- '
  # Structural Model
    Solid_P_g_kg ~ Burn_Severity
    NMR_Pi ~ Burn_Severity
    Solid_P_g_kg ~ Land_Coverage_Category
    NMR_Pi ~ Land_Coverage_Category
    Leachate_P_mg_kgchar_unfilt_Mean ~ NMR_Pi + Solid_P_g_kg
    
  # Residual Variances
    Solid_P_g_kg~~Solid_P_g_kg
    NMR_Pi ~~ NMR_Pi
    Leachate_P_mg_kgchar_unfilt_Mean ~~ Leachate_P_mg_kgchar_unfilt_Mean
'

#Model 6: chemistry = NMR Po
model <- '
  # Structural Model
    Solid_P_g_kg ~ Burn_Severity
    NMR_Po ~ Burn_Severity
    Solid_P_g_kg ~ Land_Coverage_Category
    NMR_Po ~ Land_Coverage_Category
    Leachate_P_mg_kgchar_unfilt_Mean ~ NMR_Po + Solid_P_g_kg
    
  # Residual Variances
    Solid_P_g_kg~~Solid_P_g_kg
    NMR_Po ~~ NMR_Po
    Leachate_P_mg_kgchar_unfilt_Mean ~~ Leachate_P_mg_kgchar_unfilt_Mean
'

#Model 7: chemistry = NMR monoesters
model <- '
  # Structural Model
    Solid_P_g_kg ~ Burn_Severity
    Mono ~ Burn_Severity
    Solid_P_g_kg ~ Land_Coverage_Category
    Mono ~ Land_Coverage_Category
    Leachate_P_mg_kgchar_unfilt_Mean ~ Mono + Solid_P_g_kg
    
  # Residual Variances
    Solid_P_g_kg~~Solid_P_g_kg
    Mono ~~ Mono
    Leachate_P_mg_kgchar_unfilt_Mean ~~ Leachate_P_mg_kgchar_unfilt_Mean
'

#Model 8: chemistry = NMR diesters
model <- '
  # Structural Model
    Solid_P_g_kg ~ Burn_Severity
    Di ~ Burn_Severity
    Solid_P_g_kg ~ Land_Coverage_Category
    Di ~ Land_Coverage_Category
    Leachate_P_mg_kgchar_unfilt_Mean ~ Di + Solid_P_g_kg
    
  # Residual Variances
    Solid_P_g_kg~~Solid_P_g_kg
    Di ~~ Di
    Leachate_P_mg_kgchar_unfilt_Mean ~~ Leachate_P_mg_kgchar_unfilt_Mean
'

#Model 9: chemistry = NMR Mono + NMR Di
model <- '
  # Measurement Model; set up the latent variable(s)
    P =~ Mono + Di
  
  # Structural Model
    Solid_P_g_kg ~ Burn_Severity
    P ~ Burn_Severity
    Solid_P_g_kg ~ Land_Coverage_Category
    P ~ Land_Coverage_Category
    Leachate_P_mg_kgchar_unfilt_Mean ~ P + Solid_P_g_kg
    
  # Residual Variances
    Solid_P_g_kg~~Solid_P_g_kg
    Mono ~~ Mono
    Di ~~ Di
    Leachate_P_mg_kgchar_unfilt_Mean ~~ Leachate_P_mg_kgchar_unfilt_Mean
'




#landcover predict burn severity
#filtered <0.7 nominal pore size
model <- '
  # Structural Model
    Solid_P_g_kg ~ Burn_Severity
    XANES_Pi_Ca ~ Burn_Severity
    Solid_P_g_kg ~ Land_Coverage_Category
    XANES_Pi_Ca ~ Land_Coverage_Category
    Burn_Severity ~ Land_Coverage_Category
    Leachate_mg_P_per_g_P_in_solid_filt0.7_Mean ~ XANES_Pi_Ca + Solid_P_g_kg
    
  # Residual Variances
    Solid_P_g_kg~~Solid_P_g_kg  
    XANES_Pi_Ca ~~ XANES_Pi_Ca
    Leachate_mg_P_per_g_P_in_solid_filt0.7_Mean ~~ Leachate_mg_P_per_g_P_in_solid_filt0.7_Mean
'

# Fit the SEM model
fit <- sem(model, data = data_rda_combine)
#fit<-cfa(model, data = data_rda_combine)

# Summarize the results
summary(fit, fit.measures=TRUE, standardized=TRUE, rsquare=TRUE)
fitMeasures(fit, c("chisq", "cfi", "tli", "rmsea", "aic"))

#visualize it
#labels<-c("Char P","Char Pi-Ca","Aqueous MBD","Burn Severity","Ecosystem Type")
#nodeLabels = labels,
p_pa<-semPlot::semPaths(fit,'std',  edge.label.cex = 1.5,
         label.prop=0.9, rotation = 1, nCharNodes=0,
         equalizeManifests = FALSE, optimizeLatRes = TRUE, 
         edge.width = 0.6, shapeMan = "rectangle", shapeLat = "ellipse", 
         shapeInt = "triangle", sizeInt = 2, sizeLat = 4, 
         curve=2, residuals = FALSE, layout="tree2",
         edge.label.position=0.7, fade = TRUE, colFactor=0.25, 
         node.width = 4)
p_pa2 <- mark_sig(p_pa, fit)
plot(p_pa2)


#particulates >0.7 nominal pore size
model <- '
  # Structural Model
    Solid_P_g_kg ~ Burn_Severity
    XANES_Pi_Ca ~ Burn_Severity
    Solid_P_g_kg ~ Land_Coverage_Category
    XANES_Pi_Ca ~ Land_Coverage_Category
    Burn_Severity ~ Land_Coverage_Category
    Leachate_mg_P_per_g_P_in_solid_part_Mean ~ XANES_Pi_Ca + Solid_P_g_kg
    
  # Residual Variances
    Solid_P_g_kg~~Solid_P_g_kg  
    XANES_Pi_Ca ~~ XANES_Pi_Ca
    Leachate_mg_P_per_g_P_in_solid_part_Mean ~~ Leachate_mg_P_per_g_P_in_solid_part_Mean
'

# Fit the SEM model
fit <- sem(model, data = data_rda_combine)
#fit<-cfa(model, data = data_rda_combine)

# Summarize the results
summary(fit, fit.measures=TRUE, standardized=TRUE, rsquare=TRUE)
fitMeasures(fit, c("chisq", "cfi", "tli", "rmsea", "aic"))

#visualize it
#labels<-c("Char P","Char Pi-Ca","Aqueous MBD","Burn Severity","Ecosystem Type")
#nodeLabels = labels,
p_pa<-semPlot::semPaths(fit,'std',  edge.label.cex = 1.5,
         label.prop=0.9, rotation = 1, nCharNodes=0,
         equalizeManifests = FALSE, optimizeLatRes = TRUE, 
         edge.width = 0.6, shapeMan = "rectangle", shapeLat = "ellipse", 
         shapeInt = "triangle", sizeInt = 2, sizeLat = 4, 
         curve=2, residuals = FALSE, layout="tree2",
         edge.label.position=0.7, fade = TRUE, colFactor=0.25, 
         node.width = 4)
p_pa2 <- mark_sig(p_pa, fit)
plot(p_pa2)
```

##Cluster
```{r cluster analysis}
#solid NMR and XANES species
#https://uc-r.github.io/kmeans_clustering


Burn_Duration, Char_Max_Temp, XANES_Pi, XANES_Fe, XANES_Na, XANES_Ca, XANES_Al, XANES_Mg, XANES_K, XANES_Po_Fe, XANES_Po_Na, XANES_Po_Ca, XANES_Po_Al, XANES_Po_Mg, XANES_Po_K, Solid_P_g_kg, Solid_Ca_g_kg, Solid_Fe_g_kg, Solid_Al_g_kg, Solid_K_g_kg, Solid_Mg_g_kg, Solid_Na_g_kg, Solid_S_g_kg, Solid_C_g_kg, Solid_N_g_kg

 Ortho, Mono, Di, Pyro, 

solid <- data_solids %>%
  select(Parent_ID, Land_Coverage_Category, Burn_Severity, XANES_Pi_Fe, XANES_Pi_Na, XANES_Pi_Ca, XANES_Pi_Al, XANES_Pi_Mg, XANES_Pi_K, XANES_Po) %>%
  unite(Treatment, Parent_ID, Land_Coverage_Category, Burn_Severity) %>%
  column_to_rownames("Treatment") %>%
  scale(center = TRUE, scale = TRUE) 


#K means
#figure out the best number of clusters:
factoextra::fviz_nbclust(solid, kmeans, method = "wss")
factoextra::fviz_nbclust(solid, kmeans, method = "silhouette")
gap_stat <- cluster::clusGap(solid, FUN = kmeans, nstart = 25,
                    K.max = 10, B = 100)
factoextra::fviz_gap_stat(gap_stat)

#Try 6
k6 <- kmeans(solid, centers = 3, nstart = 25)

k3 <- kmeans(dist_stats, centers = 3, nstart = 25)

#cluster numbers will change each time you run this, so just verify these are the right clusters before applying colors 
factoextra::fviz_cluster(k6, data = solid, ggtheme = theme_classic(), ellipse.type = "confidence", show.clust.cent = FALSE)

```

```{r dendro}
dendro = factoextra::get_dist(solid, method ="spearman")
factoextra::fviz_dist(dendro, gradient = list(low = "#00AFBB", mid = "white", high = "#FC4E07"))


cluster_matrix = hclust(dendro)

plot(cluster_matrix)
ggdendro::ggdendrogram(cluster_matrix, rotate= TRUE)

```









#haven't updated below here yet (NMR and XANES code) fix


#spectra stacked
#spectra <- read.csv("~/Library/CloudStorage/OneDrive-SharedLibraries-PNNL/RC-3, River Corridor SFA - Presentations/ESA_2023/Morgan/spectra.csv")


#filt<-spectra[ -c(6:9)]
#filt$P_BSLE_0007_filt07_sample<-filt$P_BSLE_0007_filt07_sample+7
#filt$P_BSLE_0002_filt07_sample<-filt$P_BSLE_0002_filt07_sample+14
#filt$P_BSLE_0050_filt07_sample<-filt$P_BSLE_0050_filt07_sample+21
#filt<-melt(filt, id=c("energy"))

#ggplot(filt, aes(x=energy, y=value))+geom_line(aes(color = variable), show.legend = FALSE)+theme_classic()+ylab("Noramlized Absorption (arb. units)")+ xlab("Energy (eV)")+theme(text = element_text(size = 15))+xlim(2140,2200)+scale_color_manual(values=c('Black','Black', 'Black', 'Black'))




#plot spectra of samples
#BSLE_solid_sample_spectra_normalizedforfinalLCF_12.1.22 <- read.csv("~/PNNL/RC-3, River Corridor SFA - Burn Severity Experiments/Burn Severity Experiment/Data/P_all data streams/P XAS/Processed_final/BSLE_Solids_Final_Fits/BSLE_solid_sample_spectra_normalizedforfinalLCF_12.1.22.csv")


#DFL<-BSLE_solid_sample_spectra_normalizedforfinalLCF_12.1.22[ c(25, 20, 19, 13, 1)]
#DFL<-melt(DFL, id=c("energy"))

#ggplot(DFL, aes(x=energy, y=value))+geom_line()+theme_classic()+ylab("Noramlized Absorption (arb. units)")+ xlab("Energy (eV)")+facet_grid(variable~.)+theme(text = element_text(size = 15))+xlim(2140,2200)



#try to stack them differently
#DFL<-BSLE_solid_sample_spectra_normalizedforfinalLCF_12.1.22[ c(25, 20, 19, 13, 1)]
#DFL$P_BSLE_0073_solidchar_036_fl_4s_avg<-DFL$P_BSLE_0073_solidchar_036_fl_4s_avg+9
#DFL$P_BSLE_0052_solidchar_035_fl_6sc_avg<-DFL$P_BSLE_0052_solidchar_035_fl_6sc_avg+6
#DFL$P_BSLE_0051_solidchar_034_fl_6s_avg<-DFL$P_BSLE_0051_solidchar_034_fl_6s_avg+3
#DFL<-melt(DFL, id=c("energy"))

#DFL.sample.xas.spectra.gradient<-ggplot(DFL, aes(x=energy, y=value))+geom_line(aes(color = variable), show.legend = FALSE)+theme_classic()+ylab("Noramlized Absorption (arb. units)")+ xlab("Energy (eV)")+theme(text = element_text(size = 15))+xlim(2140,2200)+scale_color_manual(values=c('Black','Black', 'Black', 'Black'))






